### 2021-12-15 docs/figs.Rmd
first commit

---
title: Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)"
author: Masatoshi Katabuchi
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
      fig_caption: yes
      theme: spacelab #readable #sandstone #spacelab #flatly
      highlight: pygments #tango #kate
      toc: TRUE
      toc_depth: 2
      number_sections: TRUE
      toc_float:
        collapsed: TRUE
        smooth_scroll: TRUE
        toc: true
---

```{r, echo = F}
rm(list = ls())
```

```{r global_options, include=FALSE}
library(knitr)
basename <- "ms-leaf-disc"
opts_chunk$set(fig.path = paste0("components/figure/", basename, "-"),
               cache.path = paste0("components/cache/", basename, "/"))
knitr::opts_chunk$set(echo=TRUE,
                      cache=TRUE,
                      warning=FALSE,
                      message=FALSE)
```

# Library

```{r, cache=FALSE}
library(tidyverse)
library(tictoc)
library(patchwork)
library(smatr)
library(ggpubr)
library(ggsma)
library(kableExtra)
source("../scripts/util.R")
```

```{r, cache=FALSE}
theme_set(theme_bw())
theme_update(text = element_text(family = "Arial"))
```

# Datasets

```{r}
d <- read_csv("../data/full_data.csv")
d_cv <- read_csv("../data/full_data_cv.csv")

d <- d |>
  filter(!is.na(LMAdisc)) |>
  filter(!is.na(LMAleaf)) |>
  filter(!is.na(LTleaf)) |>
  rename(LT = LTleaf) |>
  rename(LA = LAleaf) |>
  filter(Location %in% c("Ailao_understory", "Mengla_Bubeng", "Yuanjiang_Savanna", "Yakushima")) |>
  #filter(Location != "Yakushima") |>
  mutate(LMAratio = LMAleaf / LMAdisc) |>
  mutate(LDratio = LDleaf / LDdisc)

LA1 <- quantile(d$LA, 0.25, na.rm = TRUE)
LA2 <- quantile(d$LA, 0.5, na.rm = TRUE)
LA3 <- quantile(d$LA, 0.75, na.rm = TRUE)
LT1 <- quantile(d$LT, 0.25, na.rm = TRUE)
LT2 <- quantile(d$LT, 0.5, na.rm = TRUE)
LT3 <- quantile(d$LT, 0.75, na.rm = TRUE)

LA_mid <- median(d$LA)
LT_mid <- median(d$LT, na.rm = TRUE)

d <- d |>
  mutate(LT_gr = case_when(
    LT < LT1 ~ "Very~thin",
    LT < LT2 ~ "Thin",
    LT < LT3 ~ "Thick",
    TRUE ~ "Very~thick")) |>
  mutate(LT_gr = factor(LT_gr, levels = c("Very~thin", "Thin", "Thick",
                                          "Very~thick"))) |>
  mutate(LA_gr = case_when(
    LA < LA1 ~ "Very~small",
    LA < LA2 ~ "Small",
    LA < LA3 ~ "Large",
    TRUE ~ "Very~large")) |>
  mutate(LA_gr = factor(LA_gr, levels = c("Very~small", "Small", "Large",
                                          "Very~large"))) |>
  mutate(LALT_gr = case_when(
   LA < LA_mid & LT < LT_mid ~ "Thin~Small",
   LA < LA_mid & LT >= LT_mid ~ "Thick~Small",
   LA >= LA_mid & LT < LT_mid ~ "Thin~Large",
   LA >= LA_mid & LT >= LT_mid ~ "Thick~Large",
   TRUE ~ "aa"
                          )) |>
  mutate(LA_gr2 = ifelse(LA < LA_mid, "Small-leaved~species",
                         "Large-leaved~species")) |>
  mutate(LT_gr2 = ifelse(LT < LT_mid, "Thin-leaved~species",
                         "Thick-leaved~species"))

d_cv <- d_cv |>
  dplyr::select(Species, Location,
                LMAleaf_cv = LMAleaf, LMAdisc_cv = LMAdisc,
                LDleaf_cv = LDleaf, LDdisc_cv = LDdisc) |>
  #full_join(d) |>
  filter(!is.na(LMAleaf_cv)) |>
  filter(!is.na(LMAdisc_cv))

d_cv2 <- d_cv |>
  full_join(d) |>
  filter(!is.na(LMAleaf_cv)) |>
  filter(!is.na(LMAdisc_cv))

d %>%
  head %>%
  kable() %>%
  kable_styling()
```

# Leaf disc vs whole-leaf LMA (species-level)

## Pooled

```{r LMA-gr2}
p_LALT_grid <- d |>
  ggplot(aes(x = LMAdisc, y = LMAleaf)) +
  geom_point(alpha = 0.8) +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = TRUE) +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  #facet_wrap(~LALT_gr, scale = "fixed", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LMA~(g~m^{-2}))) +
  ylab(expression(Whole-leaf~LMA~(g~m^{-2}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

ggsave("../figs/LMA_sp_gr.png", p_LALT_grid, width = 6, height = 6)
```

![](../figs/LMA_sp_gr.png)

## Separated

```{r LMA-gr-both}
my_col <- RColorBrewer::brewer.pal(4, "RdBu")

p_LALT_grid_both <- d |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(x = LMAdisc, y = LMAleaf, col = punch_size)) +
  geom_point(alpha = 0.6) +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = FALSE) +
  scale_color_manual(values = my_col[c(2, 4)],
                     name = "Diameter of the leaf punch") +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  #facet_wrap(~LALT_gr, scale = "fixed", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LMA~(g~m^{-2}))) +
  ylab(expression(Whole-leaf~LMA~(g~m^{-2}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial"),
    show.legend = FALSE
  ) +
 theme(legend.position = c(0.3, 0.1),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.2, "cm"),
        legend.text = element_text(size = 9),
        legend.title = element_text(size = 9)
 )

ggsave("../figs/LMA_sp_gr_both.png", p_LALT_grid_both, width = 6, height = 6)
```

![](../figs/LMA_sp_gr_both.png)

# SMA table (species-level)

```{r sma}

sma_LMA <- sma(log10(LMAleaf) ~ log10(LMAdisc),
    data = d,
    elev.test = 0,
    slope.test = 1)

sma_LD <- sma(log10(LDleaf) ~ log10(LDdisc),
    data = d,
    elev.test = 0,
    slope.test = 1)

sma_LMA_LALT_gr <- sma(log10(LMAleaf) ~ log10(LMAdisc) * LALT_gr,
    data = d,
    elev.test = 0,
    slope.test = 1)

sma_LD_LALT_gr <- sma(log10(LDleaf) ~ log10(LDdisc) * LALT_gr,
    data = d,
    elev.test = 0,
    slope.test = 1)

my_fun <- function(fit) {
  tb1 <- fit$groupsummary |>
    mutate(Slope = paste0(round(Slope, 2), " [", round(Slope_lowCI, 2), ", ",
                          round(Slope_highCI, 2), "]"))|>
    mutate(Intecept = paste0(round(Int, 2), " [", round(Int_lowCI, 2), ", ",
                          round(Int_highCI, 2), "]"))|>
    mutate(sig_slope = case_when(
                             Slope_highCI < 1 ~ "sig",
                             Slope_lowCI > 1 ~ "sig",
                             TRUE ~ "ns"
                             )) |>
    mutate(sig_int = ifelse(Int_lowCI * Int_highCI > 0, "sig", "ns")) |>
    mutate(r2 = round(r2, 2)) |>
    dplyr::select(Slope, Intecept, r2, sig_slope, sig_int, group)
  tb2 <- tb1 |>
    mutate(Slope = ifelse(sig_slope == "sig", paste0("**", Slope, "**"), Slope)) |>
    mutate(Intecept = ifelse(sig_int == "sig", paste0("**", Intecept, "**"),
                             Intecept)) |>
    dplyr::select(Slope, Intecept, `*R^2^*` = r2)
  list(tb1, tb2, group = tb1$group)
}

tb0_LMA <- my_fun(sma_LMA)
tb0_LD <- my_fun(sma_LD)
tb2_LMA <- my_fun(sma_LMA_LALT_gr)
tb2_LD <- my_fun(sma_LD_LALT_gr)

#tb_dat <- rbind(cbind(tb0_LMA[[2]], tb0_LD[[2]]),
#  cbind(tb2_LMA[[2]], tb2_LD[[2]]))

tb_dat <- rbind(tb0_LMA[[2]], tb2_LMA[[2]])
tb_dat <- cbind(c("All", tb2_LMA$group), tb_dat) |>
  as.data.frame()

tb_dat %>%
  write_csv("../data/tab1.csv")

colnames(tb_dat)[1] <- "Data"
rownames(tb_dat) <- NULL

tb_dat |>
  kable() |>
 #pack_rows("all", 1, 1) |>
 #pack_rows("Site", 2, 6) |>
 #add_header_above(c(" ", "LMA" = 3, "LD" = 3)) |>
  kable_styling()

```

# Leaf disc vs whole-leaf LMA (individual-level)

```{r LMA-ind}
tree <- read_csv("../data/tree_data.csv")

tree <- tree |>
  filter(!is.na(LMAdisc)) |>
  filter(!is.na(LMAleaf)) |>
  filter(!is.na(LTleaf)) |>
  rename(LT = LTleaf) |>
  rename(LA = LAleaf) |>
  mutate(Dry_mass_disc2 = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4 / 2,
   TRUE ~ LMAdisc * 0.889 * 10^-4 / 3
                )) |>
  mutate(Dry_mass_disc = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4,
   TRUE ~ LMAdisc * 0.889 * 10^-4
                ))

LA1_tree <- quantile(tree$LA, 0.25, na.rm = TRUE)
LA2_tree <- quantile(tree$LA, 0.5, na.rm = TRUE)
LA3_tree <- quantile(tree$LA, 0.75, na.rm = TRUE)
LT1_tree <- quantile(tree$LT, 0.25, na.rm = TRUE)
LT2_tree <- quantile(tree$LT, 0.5, na.rm = TRUE)
LT3_tree <- quantile(tree$LT, 0.75, na.rm = TRUE)

LA_mid_tree <- median(tree$LA, na.rm = TRUE)
LT_mid_tree <- median(tree$LT, na.rm = TRUE)

tree <- tree |>
  mutate(LT_gr = case_when(
    LT < LT1_tree ~ "Very~thin",
    LT < LT2_tree ~ "Thin",
    LT < LT3_tree ~ "Thick",
    TRUE ~ "Very~thick")) |>
  mutate(LT_gr = factor(LT_gr, levels = c("Very~thin", "Thin", "Thick",
                                          "Very~thick"))) |>
  mutate(LA_gr = case_when(
    LA < LA1_tree ~ "Very~small",
    LA < LA2_tree ~ "Small",
    LA < LA3_tree ~ "Large",
    TRUE ~ "Very~large")) |>
  mutate(LA_gr = factor(LA_gr, levels = c("Very~small", "Small", "Large",
                                          "Very~large"))) |>
  mutate(LALT_gr = case_when(
   LA < LA_mid_tree & LT < LT_mid_tree ~ "Thin~Small",
   LA < LA_mid_tree & LT >= LT_mid_tree ~ "Thick~Small",
   LA >= LA_mid_tree & LT < LT_mid_tree ~ "Thin~Large",
   LA >= LA_mid_tree & LT >= LT_mid_tree ~ "Thick~Large",
   TRUE ~ "aa"
                          )) |>
  mutate(LA_gr2 = ifelse(LA < LA_mid_tree, "Small-leaved~individuals",
                         "Large-leaved~individuals")) |>
  mutate(LT_gr2 = ifelse(LT < LT_mid_tree, "Thin-leaved~individuals",
                         "Thick-leaved~individuals"))

```

```{r LMA-gr2-ITV}
p_LALT_tree <- tree |>
  ggplot(aes(x = LMAdisc, y = LMAleaf, col = Dry_mass_disc)) +
  geom_point(alpha = 0.8) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total dry mass of \nleaf discs (g)") +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = TRUE) +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LMA~(g~m^{-2}))) +
  ylab(expression(Whole-leaf~LMA~(g~m^{-2}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  ) +
  theme(legend.position = c(0.39, 0.15),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

ggsave("../figs/LMA_ind_gr.png", p_LALT_tree, width = 6, height = 6)
```

![](../figs/LMA_ind_gr.png)

# Divergence (species-level)

```{r LMAratio}
my_col <- RColorBrewer::brewer.pal(4, "RdBu")

LMAratio <- tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(Dry_mass_disc, LMAleaf / LMAdisc,
             col = punch_size
             )) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 1) +
  scale_color_manual(values = my_col[c(2, 4)],
                     name = "Diameter of the leaf punch") +
  xlab("Total dry mass of leaf disc (g)") +
  ylab("Whole-leaf LMA / leaf disc LMA") +
  theme(
        legend.position = c(0.7, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

LMAratio_LT <- tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(LT, LMAleaf / LMAdisc,
            col = Dry_mass_disc
             )) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 1) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total leaf disc \ndry mass (g)") +
  #scale_color_viridis_d() +
  scale_x_log10() +
  xlab("Leaf thickness (mm)") +
  ylab("Whole-leaf LMA / leaf disc LMA") +
  theme(
        legend.position = c(0.7, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

LMAratio_LA <- tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(LA, LMAleaf / LMAdisc,
            col = Dry_mass_disc
             )) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 1) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total leaf disc \ndry mass (g)") +
  #scale_color_viridis_d() +
  scale_x_log10() +
  xlab(expression(Leaf~area~(m^2))) +
  ylab("Whole-leaf LMA / leaf disc LMA") +
  theme(
        legend.position = "none",
        #legend.position = c(0.2, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

p_ratio <- LMAratio + LMAratio_LT + LMAratio_LA +
  plot_annotation(tag_levels = "a")

ggsave("../figs/LMAratio2.png", p_ratio, width = 9, height = 3)
```

![](../figs/LMAratio2.png)

Check for heteroscedasticity.

```{r}
#LMAratio
lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ log(Dry_mass_disc), tree))
lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ (Dry_mass_disc), tree))
lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ log(LT), tree))
lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ log(LA), tree))
```

# LMA and LD (species-level)

```{r LMA-LD}
d_leaf <- d |>
  dplyr::select(c(Species:Contributor, LMA = LMAleaf, LDMC = LDMCleaf, LD = LDleaf)) |>
  pivot_longer(LMA:LD, names_to = "trait", values_to = "Whole-leaf") |>
  filter(Location != "Yakushima" | trait != "LD") |>
  filter(Location != "Yakushima" | trait != "LMA")

d_disc <- d |>
  dplyr::select(Species, Location, LMA = LMAdisc, LDMC = LDMCdisc, LD = LDdisc) |>
  pivot_longer(LMA:LD, names_to = "trait", values_to = "Leaf Disc") |>
  filter(Location != "Yakushima" | trait != "LD") |>
  filter(Location != "Yakushima" | trait != "LMA")

d2 <- full_join(d_leaf, d_disc) |>
  mutate(trait = factor(trait, c("LMA", "LDMC", "LD"))) |>
  mutate(trait_lab = factor(trait,
                            labels = c("LMA~(g~m^{-2})",
                                       "LDMC~(g~g^{-1})",
                                       "LD~(g~cm^{-3})"
                            )))

p_all <- d2 |>
  filter(trait != "LDMC") |>
  ggplot(aes(x = `Leaf Disc`, y = `Whole-leaf`)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_log10() +
  scale_y_log10() +
#  geom_smooth(method = "lm", se = FALSE) +
  geom_sma(se = TRUE) +
  facet_wrap(~trait_lab, scale = "free", labeller = label_parsed) +
  stat_cor(
    #aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
 #   label.x = 2
  )

ggsave("../figs/fig1.png", p_all, width = 6, height = 3)
```

![](../figs/fig1.png)

# CV

```{r cv}
p_cv1 <- d_cv |>
  ggplot(aes(x = LMAdisc_cv, y = LMAleaf_cv)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
  scale_y_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
  geom_sma(se = TRUE) +
  ylab("CV of whole-leaf LMA") +
  xlab("CV of leaf disc LMA") +
  coord_fixed() +
  stat_cor(
           label.x.npc = 0.3,
           label.y.npc = 0,
           vjust = 1.5,
           aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
               )

p_cv2 <- d_cv |>
  filter(Location != "Yakushima") |>
  ggplot(aes(x = LMAdisc_cv, y = LMAleaf_cv)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_continuous(trans = "sqrt") +
  scale_y_continuous(trans = "sqrt") +
  geom_sma(se = TRUE) +
  ggtitle("Diameter: 0.6 cm") +
  ylab("CV of whole-leaf LMA") +
  xlab("CV of leaf disc LMA") +
  #coord_fixed(xlim = c(0.01, 5.4), ylim = c(0.01, 5.4)) +
  #coord_fixed() +
  stat_cor(
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
  )

p_cv3 <- d_cv |>
  filter(Location == "Yakushima") |>
  ggplot(aes(x = LMAdisc_cv, y = LMAleaf_cv)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_continuous(trans = "sqrt") +
  scale_y_continuous(trans = "sqrt") +
  geom_sma(se = TRUE) +
  ggtitle("Diameter: 1.0 cm") +
  ylab("CV of whole-leaf LMA") +
  xlab("CV of leaf disc LMA") +
  #coord_fixed(xlim = c(0.01, 5.4), ylim = c(0.01, 5.4)) +
  #coord_fixed() +
  stat_cor(
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
  )

p_cv <- (p_cv2 + p_cv3) +
  plot_annotation(tag_levels = "a")

ggsave("../figs/fig_cv2.png", p_cv, width = 6, height = 3)

ggsave("../figs/fig_cv.png", p_cv1, width = 3, height = 3)

```

## Pooled

![](../figs/fig_cv.png)

## Separated

![](../figs/fig_cv2.png)

# Leaf support cost (species-level)

```{r petiole}
d3 <- read_csv("../data-raw/leaf_traits_for_Katabuchi.csv")

yaku <- d3 |>
  filter(Growthform != "H") |>
  mutate(Location = "Yakushima") |>
  mutate(Biomes = "ST2") |>
  mutate(Garden = "NO") |>
  mutate(MAT = NA) |>
  mutate(MAP = NA) |>
  mutate(Contributor = "Onoda Yusuke") |>
  rename(
                LA = `LA mean (leaf let)`,
                LT = `Lamina thickness`,
                LMAdisc = `LD LMA`,
                LMAleaf = `Whole leaf LMA`,
                LDMCleaf = `LDMC`,
                LDdisc = `TD`
  ) |>
  mutate(LDleaf = LMAleaf / LT * 10^-3) %>%
  mutate(LDMCdisc = NA) |>
  mutate(LTdisc = NA) |>
  mutate(Growthform = ifelse(Growthform == "W", "Trees", Growthform)) |>
  mutate(petiole_ratio = `petiole DW`/`Scanned leaf DW`)

yaku_sp <- yaku |>
  group_by(Species) |>
  summarize_at(
               .vars = vars(
             LMAdisc,
             LMAleaf,
             LDMCdisc,
             LDMCleaf,
             LDdisc,
             LDleaf,
             LT,
             LTdisc,
             LA,
             petiole_ratio
               ),
    .funs =  \(x)mean(x, na.rm = TRUE)) |>
  filter(petiole_ratio > 0) |>
  filter(!is.na(LMAdisc))

pet1 <- ggplot(yaku_sp, aes(x = petiole_ratio, y = LMAleaf/LMAdisc)) +
  geom_point() +
  scale_x_log10() +
  #xlab(expression(Petiole/leaf~dry~mass~ratio(g~g^-1))) +
  xlab("Petiole / leaf dry mass ratio") +
  ylab("Whole-leaf / leaf disc LMA ratio") +
  geom_smooth(method = "lm") +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

pet2 <- ggplot(yaku_sp, aes(x = petiole_ratio, y = LA)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Petiole / leaf dry mass ratio") +
  ylab(expression(Leaf~area~(g~cm^2))) +
  geom_smooth(method = "lm") +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

pet3 <- pet2 + pet1 +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(face = "bold"))

ggsave("../figs/petiole.png", pet3, width = 8, height = 4)

```

![](../figs/petiole.png)

# Computing Environment

```{r}
devtools::session_info()
```

### 2021-12-15 ms/LMA_method.Rmd
first commit

---
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linenumbers
output:
  html_document:
    toc: FALSE
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

```{r caching, include=FALSE}
library(knitr)
library(tidyverse)
library(methods)
source("../scripts/rmd_func.R")
basename <- "LMA_method"
opts_chunk$set(fig.path = paste("figs/", sep=""))
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE,
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

# https://github.com/haozhu233/kableExtra/issues/477
options(kableExtra.auto_format = FALSE)
library(kableExtra)

val <- yaml::yaml.load_file("../values.yml")
```

Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

$$ $$

Phisamai Maenpuen^1,2,3^,
Masatoshi Katabuchi^1,\*^,
Yusuke Onoda^4^,
Cong Zhou^1,2^,
Jiao-Lin Zhang^1,3\*^,
Ya-Jun Chen^1,3,5^

$$ $$

^1^ CAS Key Laboratory of Tropical Forest Ecology, Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences, Menglun, Yunnan 666303, China

^2^ University of Chinese Academy of Sciences, Beijing 100049, China

^3^ Center of Plant Ecology, Core Botanical Gardens, Chinese Academy of Sciences, Yunnan 666303, China

^4^ Graduate School of Agriculture, Kyoto University, Kyoto 606-8502, Japan

^5^ Savanna Ecosystem Research Station, Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences, Yuanjiang, Yunnan 6663300, China

$$ $$

**Corresponding Authors**:

Masatoshi Katabuchi

E-mail: mattocci27@gmail.com

Jiao-Lin Zhang

Tel: +86 691 871 3046;
Fax: +86 691 871 5070;
E-mail: zjl@xtbg.org.cn

$$ $$

Manuscript received _______; revision accepted _______.

**Running title**: Leaf disc and whole-leaf LMA

\newpage

# ABSTRACT

**PREMISE:**
Leaf mass per area (LMA), which is the key trait in leaf economic spectrum and plant growth analysis, is measured from leaf discs or whole leaves.
These differences in the measurement methods may lead to large differences in the estimates of LMA values.

**METHODS:**
We determined LMA using leaf discs and whole-leaf (including petiole) for `r val$all_sp` woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match, whether the differences in the estimates are associated with leaf size and thickness, and whether intraspecifc variation for each species match.

**RESULTS:**
Disc-based estimates of species and individual mean LMA matched well whole-leaf estimates.
Thin and large leaves had weaker correlations between leaf disc and whole-leaf estimates.
Variability of LMA estimates within species (i.e., amount of intraspecific variation) only weakly matched between whole-leaf and disc-based estimates (*R^2^* = `r val$cv_r2`).
We also found that sample with small total dry mass of leaf discs tended to show greater differences between leaf disc and whole-leaf LMA.

**CONCLUSIONS:**
Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (9.4% differences in our samples), but their accuracy depends on leaf size, leaf thickness, and sizes of leaf punch.
Therefore, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
Quantifying trait variation using leaf disc should be considered with caution.

**KEY WORDS:**
intraspecific variation,
leaf density,
leaf economic spectrum,
leaf heterogeneity,
leaf punch,
leaf size,
leaf thickness,
petiole,
specific leaf area,
within-leaf variation

# INTRODUCTION

Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area thus reflecting a cost for light interception, which is the key trait of the leaf economic spectrum (LES) [@Wright2004a; @Poorter2009; @Onoda2017].
Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover [@Wright2004a].
In contrast, resource-conservative species (slow-growing species) often have higher LMA values with the opposite patterns [@Garnier1994; @Wright2004a; @Reich2014; @Diaz2016].
The LMA is also frequently used in plant growth analysis [@Evans1972; @Poorter2014; @Falster2018] because relative growth rates (RGR) can be decomposed into the product of net assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR $\times$  LMR $\times$ LMA^-1^).
Another appealing feature of LMA is that it is relatively easy to measure large numbers of species [i.e., 'soft' trait, @Diaz2004].
Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago [@Hanson1917].

LMA values can be determined by either
1) a whole leaf including or excluding petioles, and
2) a leaf disc excluding all major veins or petioles [@Perez-Harguindeguy2013; @Kattge2020].
Although some studies do not make clear what protocol was followed, these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
If leaf disc LMA largely and consistently underestimates whole-leaf LMA, some calibrations may be required to combine or compare those different estimates [@Kraft2008; @Onoda2011].
If divergencies between the estimates based on the different methods are large and inconsistent (i.e., low *R^2^* values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
To date, however, only a database from a single region, Panama Plant Traits Database [@Wright2010], is available in the TRY [@Kattge2020] that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.

Given that leaf disc samples have more sources of intraspecific trait variation (ITV) than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified as a coefficient of variance (CV).
Sources of ITV for whole-leaf samples is variation among individuals within the same species and variation among leaves within the same individuals [@Messier2010; @Messier2017].
An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
Thus, extents of ITV for each species based on whole-leaf and leaf discs samples may not match.
Despite the importance of ITV in community ecology [@Kichenin2013; @Siefert2015], the effect of different measurement methods on the extent of ITV has been largely ignored.

In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf thicknesses, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
We collected a total of `r val$all_sp` woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
We predicted that the overall relationship between whole-leaf LMA and disc LMA would be weaker than previous reported LMA data (*R^2^* = 0.92 for whole-leaves in @Kraft2008, *R^2^* = 0.92 for leaf laminas in @Onoda2011) because we collected data with various leaf sizes from a wide range of climates.
We also predicted that species with larger and/or thinner leaves would show weaker correlations.
Finally, we predicted that amounts of intraspecifc variations for each species do not match well between whole-leaf and leaf disc based estimates.

# MATERIALS AND METHODS

*Data sources*

We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
In total, we used `r val$all_sp` woody species and `r val$all_tree` individuals.
The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.

*Measurements of leaf disc and whole-leaf LMA*

At the TRF site, we collected leaf samples from trees within reach of a canopy crane (88 m tall with a 60 m long boom).
In the HDS, and STF sites, we used a 12-m long pruner to collect samples for most of the target species.
In case of tall individuals that out of the reach of pruner, we used a rope climbing to reach the canopy, then sampled branches with the long pruner.
In Yakushima, we used 15-m poles for our leaf sampling.
At least six sun-exposed healthy leaves were sampled from each of 3 to 6 individuals for each species.
Trait values were averaged at the species- and individual-level for the analyses.
For compound-leaved species, we referred a leaflet (the minimum photosynthetic unit) as a single leaf in our study.

To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins.
Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset.
Fresh leaf area (LA; cm^-2^) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package *LeafArea* [@Katabuchi2015].
Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf using a micrometer (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
Thickness of each leaf disc was also measured for the Yunnan dataset but not for the Yakushima dataset, which enables us to estimate whole-leaf and leaf disc leaf tissue density (LD; g cm^-3^) separately in the Yunnan dataset.
Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a precision at 0.0001 g.
In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (`r val$pet_sp` out of `r val$yaku_sp` species) to quantify leaf support costs.
Dry mass for leaf discs were recorded 2-3 discs together for each leaf.
Based on those measurements of whole-leaf and leaf disc samples, LMA (g m^-2^) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
We do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S2).

*Statistical analyses*

Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the samples and different leaf area and thickness groups.
Species and individual groups were divided into four categories based on the medians of leaf area and leaf thickness across all species and all individuals, respectively:
thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species (individuals).
Median values are as following:
small-leaved species (LA < `r val$LA_mid` cm^2^),
thin-leaved species (LT < `r val$LT_mid` mm),
small-leaved individuals (LA < `r val$LA_mid2` cm^2^),
and thin-leaved individuals (LT < `r val$LT_mid2` mm).

The amount of intraspecific variation of LMA was calculated using coefficient of variation of log-normally distributed data; $CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$, where $s_{\mathrm{ln}}$ is the sample standard deviation in the log-transformed data [@Julious2000].
We also considered CV on the arithmetic scale; $CV = s/\bar{x}$, where $s$ is the sample standard deviation and $\bar{x}$ is the sample mean.
However, these two different CV calculations only negligibly altered the bivariate relationship and did not change our conclusion, and thus we will report CV of log-normally distributed data in the main text.

SMA analyses were run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
Confidence intervals of SMA estimates were based on 1000 bootstraps.
All statistical analyses were conducted in R version 4.1.2 [@RCoreTeam2021].

# RESULTS

Disc-based estimates of species mean LMA matched well whole-leaf estimates (Table 1; *R^2^* = `r val$r2_LMA` for all species).
Species with thicker and smaller leaves had stronger correlations between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
There was a negative correlation between species mean leaf area and leaf thickness (*r* = `r val$LA_LT_r`, *P* `r val$LA_LT_p`, *n* = `r val$LA_LT_n`).
When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4% greater than disc-based estimates in the arithmetic scale.
Large-leaved species also had significant positive intercepts, suggesting that whole-leaf estimates of LMA were 22.1% greater than disc-based estimates in the arithmetic scale (Table 1).
Intercepts did not differ for small-leaved species (Table 1).

Disc-based estimates of individual mean LMA also showed positive correlations with whole-leaf estimates but their *R^2^* values were smaller than those for the species means (Fig. 2).
Similar to the species-level pattern, individuals with thicker and smaller leaves had stronger correlations (Fig. 2).
The relationships of the whole-leaf LMA : disc leaf LMA ratio with total dry mass for the leaf disc (we weighted 2-3 discs together), with leaf thickness, and with leaf area were heteroscedastic (unequal variance, *P* < 0.001; Appendix S3).
Samples with small total dry mass, thin leaves, and larger leaves tended to show greater variance (Fig. 2; Appendix S3).
The total dry mass of leaf disc was positively correlated with both leaf thickness and leaf punch size (Appendix S4).
Amounts of intraspecific variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig. 3; *R^2^* = `r val$cv_r2`).

# DISCUSSION

Disc-based traits explained interspecific variations in whole-leaf LMA (*R^2^* = `r val$r2_LMA`, *n* = `r val$N3`) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported  (*R^2^* = 0.92, *n* = 409,  for whole-leaves in @Kraft2008, *R^2^* = 0.92, *n* = 364 for leaf laminas in @Onoda2011).
Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4% differences) or large-leaved species were used (22.1% differences).
Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration.
However, the strength of correlations highly depended on leaf area, thickness (Fig. 1) and sizes of leaf punches (Appendix S3 and S5).

Larger leaves generally invest disproportionally more mass into dense midribs and major veins for support [@Niinemets2006; @Niinemets2007; @Sack2012], and thinner leaves have distinct veins and have kite-type appearances [@Grubb1986].
As we predicted, thicker and/or smaller leaves tended to show greater *R^2^* values between whole-leaf and leaf disc estimates (Figs 1. and 2).
Large-leaved species had greater whole-leaf LMA than leaf disc LMA (Table 1), which is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles.
This is also supported by the subset of our dataset in which we measured leaf lamina and petiole dry mass separately.
We confirmed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass, and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Appendix S6).

Meanwhile, our results are seemingly inconsistent with a previous study that used thin and soft leaves and found high *R^2^* values (*R^2^* = 0.92; @Kraft2008).
@Kraft2008 used sapling leaves under closed canopy that are thinner than adult leaves [@Kitajima2010; @Oktavia2020].
Shade leaves tend to have thinner leaves than sun leaves because of fewer layers of palisade mesophyll cells [@Onoda2008; @Terashima2001].
The relatively low *R^2^* values for thin-leaved species and individuals in our study compared to the previous study may suggest not only the effect of distinct veins on variance in LMA [@John2017] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Fig. 2; Appendices S3), and thus thin-leaved species, which have smaller dry mass (Appendix S4), tended to showed the low *R^2^* values especially when we used a smaller leaf punch (diameter: 0.6 cm; Appendix S5).

Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig. 3; *R^2^* = `r val$cv_r2`).
This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species *Alocasia macrorrhiza*, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions [@Li2013a].
Because calculating the mean values generally diminishes the effect of within-sample variation, the relationship between disc-based estimates of individual mean LMA and its whole-leaf estimates will be stronger than the relationship between leaf disc CV and whole-leaf CV.
Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
This is consistent with the *R^2^* values in our results (Figs. 1-3).
The mismatch of ITV between whole-leaf and disc-based estimate could be ignored in community-level ITV studies [i.e., @Siefert2015], which quantify the total variance of ITV within communities.
However, it is likely to change patterns for species-level ITV studies [i.e., @Albert2010a], which quantify extents of ITV for each species, since species with high ITV based on leaf-disc estimates do not always have to show high ITV for whole-leaf estimates.
This problem will be more obvious when one uses smaller leaf punches (Appendix S7).

The present study was designed to examine the extent to which whole leaf and leaf disc LMA matched.
Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA.
However, larger and thinner leaves tended to show the large discrepancies between the leaf disc and whole-leaf estimates, and thus when one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis), appropriate calibrations are necessary.
Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches are also the important sources of variance between whole-leaf and leaf disc LMA.
This is probably because small dry mass inflates measurement errors and small leaf disc size inflates trait variation within leaves.
Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be large.
Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity [@Parry2002], because the photosynthetic activity occurs most in lamina rather than in veins for C~3~ plants [@Hibberd2002; @Gao2018].
Leaf disc LMA is also the preferred method for quantifying leaf lamina density, which avoid effects of veins.
However, if the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.

# ACKNOWLEDGMENTS

The authors thank Lian-Bin Tao and Peng-Yun Yan for field work.
This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).
PM was supported by financial support from CAS-TWAS President’s Fellowship for International Doctoral Students.
MK was supported by CAS President’s International Fellowship Initiative (2020FYB0003).

# AUTHOR CONTRIBUTIONS

PM, MK, and YJC conceived the study;
PM, YO, and YJC collected data;
MK and CZ performed the analysis;
MK and YJC led the writing of the paper; and
all authors contributed to revisions.

# DATA AVAILABILITY STATEMENT

Data and codes for this manuscript are archived and available on Zenodo (XXX).

# SUPPORTING INFORMATION

Additional supporting information may be found online in the Supporting Information section at the end of the article.

**APPENDIX S1.**
Site information.

**APPENDIX S2.**
Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).

**APPENDIX S3.**
Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and (c) leaf area.

**APPENDIX S4.**
Summary of multiple regression for log-transformed total dry mass of leaf discs.

**APPENDIX S5.**
Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.

**APPENDIX S6.**
Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.

**APPENDIX S7.**
Relationships between coefficient of variation (CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and (b) 1.0 cm diameter leaf punch.

# LITERATURE CITED

<div id="refs"></div>

\newpage

```{r tb1, echo=FALSE}
tab1 <- read.csv("../data/tab1.csv")
colnames(tab1) <- c("Data", "Slope", "Intercept", "*R^2^*")

tab1 <- tab1 |>
  mutate(Data = case_when(
                        Data == "Thick~Large" ~ "Thick-large",
                        Data == "Thick~Small" ~ "Thick-small",
                        Data == "Thin~Large" ~ "Thin-large",
                        Data == "Thin~Small" ~ "Thin-small",
                        TRUE ~ Data
                        ))
if ("html" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
  tab1 |>
    kable(format = "html") |>
    kable_classic()
} else if ("docx" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
  tab1 |>
    kable(format = "pipe")
} else if ("latex" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
  tab1 |>
    kable(format = "pipe")
}

```

**Table. 1.**
Relationships between species mean leaf leaf mass per area (LMA) values determined by using whole leaves and leaf discs across all species and within species groups.
Data are divided into four categories based on the quartiles:
thin and small-leaved,
thin and large-leaved,
thick and small-leaved,
and thick and large-leaved species.
SMA slope (95% CI), intercepts (95% CI), and *R^2^* values are reported.
Statistically significant differences (*P* < 0.05) in slopes and intercepts are highlighted in bold.

\newpage

**Fig. 1.**
Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
Species groups are divided into four categories on the basis of the medians of the leaf size and leaf thickness across all the species.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (*P* < 0.001).

![](../figs/LMA_sp_gr.png)

\newpage

**Fig. 2.**
Relationships between individual leaf mass per area (LMA) determined by using whole leaves and leaf discs.
Individual groups are divided into four categories based on the basis of the medians of the leaf size and leaf thickness across all the individuals.
All the correlations are significant (*P* < 0.001).
Details as in Fig. 1.

![](../figs/LMA_ind_gr.png)

\newpage

**Fig. 3.**
Relationships between coefficient of variation (CV) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
The correlation is significant (*P* < 0.001).
Details as in Fig. 1.
Note that the axes are square root scales.

![](../figs/fig_cv.png)

### 2021-12-15 scripts/LA.R

@@ -1,0 +1,405 @@
+library(tidyverse)
+library(tictoc)
+#library(xlsx)
+
+rm(list = ls())
+data_name <- list.files("data")
+data_name <- data_name[str_detect(data_name, "PV")]
+data_name <- data_name[str_detect(data_name, "csv$")]
+data_name <- data_name[!str_detect(data_name, "Yuanjiang")]
+data_name2 <- paste0("data/",data_name)
+
+#d <- #read.csv("data/PV_Bubeng.csv")
+
+#for (k in 1:3) {
+for (k in 1:length(data_name2)) {
+  d <- read.csv(data_name2[k])
+
+  d2 <- d
+  d2[is.na(d2)] <- "hoge"
+
+  tmp <- NULL
+  LA <- NULL
+  for (j in 1:ncol(d2))
+    for (i in 1:nrow(d2)) {
+      if(str_detect(d2[i, j ], "SWC") == TRUE) {
+        tmp <- c(tmp, j)
+        LA <- c(LA, d2[i - 2, j  + 1])
+      }
+  }
+  LA <- as.numeric(LA)
+  #LA <- LA[!is.na(LA)]
+
+# because some data starts from the 2nd row
+  sp_name <- names(d)
+  #sp_name <- c(names(d), d[1,] |> as.character())
+  sp_name2 <- sp_name[!str_detect(sp_name, "水势|重量|塞重|干重|湿重|面积|结束|[a-z]|[0-9]$")]
+  #sp_name2 <- sp_name[!str_detect(sp_name, "X|长|宽|质量|叶重|水势|重量|塞重|干重|湿重|面积|结束|[a-z]|[0-9]$")]
+  sp_name3 <- str_split_fixed(sp_name2, "[0-9]\\.\\.|[0-9]\\.|[0-9]", 3)
+
+  sp_name4 <- NULL
+  for (i in 1:nrow(sp_name3)) {
+    for (j in 1:ncol(sp_name3))
+      if (sp_name3[i,j] != "X" & sp_name3[i,j] != "")
+      sp_name4 <- c(sp_name4, sp_name3[i, j])
+  }
+
+  sp_name5 <- str_split_fixed(sp_name4[sp_name4 != "NA"], " ", 2)
+  sp_name6 <- NULL
+  for (i in 1:nrow(sp_name5)) {
+    for (j in 1:ncol(sp_name5))
[…]

### 2021-12-15 scripts/data_cleaning.R

@@ -1,0 +1,5 @@
+# TRY
+
+# XTBG
+
+# other sites

### 2021-12-15 scripts/docker-env.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+echo LOCAL_UID=$(id -u $USER) > .env
+echo LOCAL_GID=$(id -g $USER) >> .env

### 2021-12-15 scripts/entrypoint.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+USER_ID=${LOCAL_UID:-9001}
+GROUP_ID=${LOCAL_GID:-9001}
+
+echo "Starting with UID : $USER_ID, GID: $GROUP_ID"
+useradd -u $USER_ID -o -m app
+groupmod -g $GROUP_ID app
+export HOME=/home/app
+
+exec /usr/sbin/gosu app "$@"

### 2021-12-15 scripts/rmd_func.R

@@ -1,0 +1,52 @@
+page_break <- function(section = NULL){
+  if(knitr:::pandoc_to() == "latex") {
+    paste("\\newpage \n #", section)
+  } else {paste("#####", section)}
+}
+
+# number tables
+# from http://stackoverflow.com/a/18672268/1036500
+# library(knitr)
+
+#to = local({
+#  i <- 0
+#  function(x) {
+#    i <<- i + 1
+#    paste("<table><caption>",
+#    '**Table ****', i, '**: ', x,
+#    "</caption><colgroup><col width='100'></col></colgroup><thead><tr class='header'></tr></thead><tbody></tbody></table><p>", sep = '')
+#  }
+#})
+#knit_hooks$set(tab.cap = function(before, options, envir) {
+#  if(before) # caption above tables
+#    to(options$tab.cap)
+#})
+#default_output_hook = knit_hooks$get("output")
+#knit_hooks$set(output = function(x, options) {
+#  if (is.null(options$tab.cap) == F)
+#    x
+#  else
+#    default_output_hook(x, options)
+#})
+#
+# This is a knitr hook to enable figure and table captions
+# number figures
+# from http://stackoverflow.com/a/18672268/1036500
+#tn <- local({
+#  i <- 0
+#  function(x) {
+#    i <<- i + 1
+#    paste("<figure><figcaption>", '**Figure ****', i, '**: ', x, "</figcaption><colgroup><col width='100'></col></colgroup><thead><tr class='header'></tr></thead><tbody></tbody></figure><p>", sep = '')
+#  }
+#})
+#knit_hooks$set(fig.cap = function(before, options, envir) {
+#  if(!before)
+#    tn(options$fig.cap)
+#})
+#default_output_hook = knit_hooks$get("output")
+#knit_hooks$set(output = function(x, options) {
+#  if (is.null(options$fig.cap) == F)
+#    x
+#  else
+#    default_output_hook(x, options)
+#})

### 2021-12-15 scripts/util.R

@@ -1,0 +1,10 @@
+# To save ggplot figures
+my_ggsave <- function(plot, filename, height = 11.4, width = 11.4, dpi = 200, units = "cm", ...){
+    ggsave(filename = filename,
+           plot = plot,
+           height = height,
+           width = width,
+           units = units,
+           dpi = dpi,
+           ...)
+}

### 2021-12-15 docs/CV.Rmd
first commit

---
title: CV
author: Masatoshi Katabuchi
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
      fig_caption: yes
      theme: spacelab #readable #sandstone #spacelab #flatly
      highlight: pygments #tango #kate
      toc: TRUE
      toc_depth: 2
      number_sections: TRUE
      toc_float:
        collapsed: TRUE
        smooth_scroll: TRUE
        toc: true
---

```{r}
library(tidyverse)
```

# MVN version

## Model

First, we foucs on the species means.
Trait X (whole leaf LMA) for *i*th species is:
$$
X_i \sim N(\mu, \sigma_x^2).
$$

Trait Y (leaf disc LMA) for *i*th species is:

$$
Y_i = X_i + \epsilon_i
$$

where 
$$
\epsilon_i \sim N(0, \sigma_{\epsilon}^2) 
$$

**Q1: Do species mean of whole-leaf LMA and leaf disc LMA match well?**

This can be rephrased as testing the covariance between species mean of whole-leaf LMA and leaf disc LMA.
(i.e., 
$\mathrm{Cov}(X_i, Y_i)$
).
This will be simple and it depends on $\sigma_y$.

Then, let's look at the intraspecifc variation (ITV).
Trait x and y for *j*th leaf of *i*th species are assumed to follow a
multivariate normal distribution (MVN) because there should be positve covariances
between the trait values with species (i.e., individual that has large x should
have large y too).

$$
\begin{bmatrix}
x_{ij} \\
y_{ij} 
\end{bmatrix}
\sim MVN(
\begin{bmatrix}
\mu_{i} \\
\mu_{i} 
\end{bmatrix}
,
\begin{bmatrix}
\sigma_{xi}^2 & \rho\sigma_{xi}\sigma_{yi} \\
\rho\sigma_{xi}\sigma_{yi} & \sigma_{yi}^2 \\
\end{bmatrix}
)
$$

where $\mathrm{log}\sigma_{xi}$ and $\mathrm{log}\sigma_{yi}$ follow a MVN because there should be positive covariances
between the extents of intraspecifc variation (i.e., species that have large ITV
should have large ITV for both x and y traits).

$$
\begin{bmatrix}
\mathrm{log}\sigma_{x i} \\
\mathrm{log}\sigma_{y i}
\end{bmatrix}
\sim MVN(
\begin{bmatrix}
\tau_{x} \\
\tau_{y} 
\end{bmatrix}
,
\begin{bmatrix}
\hat{\sigma_{x}}^2 & \rho'\hat{\sigma_{x}}\hat{\sigma_{y}} \\
\rho'\hat{\sigma_{x}}\hat{\sigma_{y}} & \hat{\sigma_{y}}^2 \\
\end{bmatrix}
).
$$

Alternatively, ITV can be written as:

$$
x_{ij} \sim N(\mu_i, \sigma_{xi}^2)
$$

$$
y_{ij} = x_{ij} + \epsilon_{ij} 
$$

$$
\epsilon_{ij} \sim N(0,  \sigma_{\epsilon i}^2).
$$

CV of trait x for *i*th species is:

$$
CV_{xi} = \frac{\sigma_{xi}}{\mu_i}
$$

or

$$
CV = \sqrt{exp(\sigma_{xi}^2) - 1}.
$$

**Q2: Does the extent of intraspecifc variation match between the whole-leaf and
leaf disc estimates?**

This can be rephrased as testing the covariance between CV of LMA for each species estimated by whole-leaf and leaf disc.
(i.e., 
$\mathrm{Cov}(CV_{x}, CV_{y})$
).

## Example

```{r}
cv <- \(x) sd(x)/mean(x)
cv_ln <- \(x) sqrt(exp(var(x)) - 1)
```

```{r, eval=TRUE}
set.seed(123)
# n: sp
n <- 100
# m: trees for each species
m <- 10

mu <- 5
sig_x <- 1
sig_e <- 0.5
tau_x <- -1
sig_tx_hat <- 0.3
tau_y <- -1
sig_ty_hat <- 0.5

x <- rnorm(n, mu, sig_x)
y <- x + rnorm(n, 0, sig_e^2)
```

```{r}
rho0 <- 0.3
S0 <- c(sig_tx_hat^2, rho0 * sig_tx_hat * sig_ty_hat,
    rho0 * sig_tx_hat * sig_ty_hat, sig_ty_hat^2) |>
    matrix(ncol = 2)

sig_t <- mvtnorm::rmvnorm(n, mean = c(tau_x, tau_y), sigma = S0) |>
  exp()
```

```{r,eval=TRUE}
rho <- 0.5
tmp <- NULL
for (i in 1:length(mu_i)) {
  S <- c(sig_t[i,1]^2, rho * sig_t[i,1] * sig_t[i,2],
    rho * sig_t[i,1] * sig_t[i,2], sig_t[i,2]^2) |>
    matrix(ncol = 2)
  tmp <- rbind(tmp, mvtnorm::rmvnorm(m, mean = rep(mu_i[i], 2), sigma = S))
}
colnames(tmp) <- c("x", "y")

trait <- tmp |>
  as_tibble() |>
  mutate(sp = rep(1:n, each = m)) |>
  mutate(tree = rep(1:m, n))

cv_dat <- trait |>
  group_by(sp) |>
  summarise_at(
               .vars = vars(x, y),
               .funs = cv)

cv_dat2 <- trait |>
  group_by(sp) |>
  summarise_at(
               .vars = vars(x, y),
               .funs = cv_ln)
```

Species mean.

```{r}
plot(x, y)
cor.test(x, y)
```

Each tree.

```{r}
plot(y ~ x, trait)
cor.test(trait$y, trait$x)
```

CV.

```{r}
plot(y ~ x, cv_dat, log = "xy")
cor.test(log(cv_dat$y), log(cv_dat$x))
```

## Log-normal CV

$$
CV = \sqrt{exp(\mathrm{V}|x|) - 1}
$$

CV.

```{r}
plot(y ~ x, cv_dat2, log = "xy")
cor.test(log(cv_dat2$y), log(cv_dat2$x))
```

# Non-MVN version

## Example

```{r, eval=TRUE}
set.seed(123)
# n: sp
n <- 100
# m: trees for each species
m <- 10

mu <- 5
sig_x <- 1
sig_tx_hat <- 0.3
tau_x <- -1
mu_i <- rnorm(n, mu, sig_x)
sig_tx <- rnorm(n, tau_x, sig_tx_hat) |> exp()
x <- mapply(rnorm, m, mu_i, sig_tx)

tau_e <- -0.2
sig_te_hat <- 0.1
sig_te <- rnorm(n, tau_e, sig_te_hat) |> exp()
e <- mapply(rnorm, m, 0, sig_te^2)

y <- x + e

x <- as.numeric(x)
y <- as.numeric(y)

trait <- tibble(x, y) |>
  mutate(sp = rep(1:n, each = m)) |>
  mutate(tree = rep(1:m, n))

cv_dat <- trait |>
  group_by(sp) |>
  summarise_at(
               .vars = vars(x, y),
               .funs = cv)

mean_dat <- trait |>
  group_by(sp) |>
  summarise_at(
               .vars = vars(x, y),
               .funs = mean)

cv_dat2 <- trait |>
  group_by(sp) |>
  summarise_at(
               .vars = vars(x, y),
               .funs = cv_ln)

```

Species mean.

```{r}
plot(y ~ x, mean_dat)
cor.test(mean_dat$y, mean_dat$x)
```

Each tree.

```{r}
plot(y ~ x, trait)
cor.test(trait$y, trait$x)
```

CV.

```{r}
plot(y ~ x, cv_dat, log = "xy")
cor.test(log(cv_dat$y), log(cv_dat$x))
```

```{r, eval=FALSE, echo=FALSE}
x <- seq(0.1, 1.5, length = 80)
plot(x, sqrt(exp(x^2) - 1), type = "l")
lines(x, x, lty = 2)
lines(x, x^2, lty = 3)
lines(x, exp(x), lty = 4)
```

### 2021-12-15 docs/figs_long.Rmd
first commit

---
title: LMA figures
author: Masatoshi Katabuchi
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
      fig_caption: yes
      theme: spacelab #readable #sandstone #spacelab #flatly
      highlight: pygments #tango #kate
      toc: TRUE
      toc_depth: 2
      number_sections: TRUE
      toc_float:
        collapsed: TRUE
        smooth_scroll: TRUE
        toc: true
---

```{r, echo = F}
rm(list = ls())
```

```{r global_options, include=FALSE}
library(knitr)
basename <- "ms-trait-method"
opts_chunk$set(fig.path = paste0("components/figure/", basename, "-"),
               cache.path = paste0("components/cache/", basename, "/"))
knitr::opts_chunk$set(echo=TRUE,
                      cache=TRUE,
                      warning=FALSE,
                      message=FALSE)
```

# Library

```{r, cache=FALSE}
library(tidyverse)
library(tictoc)
library(patchwork)
library(smatr)
library(ggrepel)
library(ggpubr)
library(ggsma)
library(kableExtra)
library(lavaan)
source("../scripts/util.R")
```

```{r, cache=FALSE}
theme_set(theme_bw())
theme_update(text = element_text(family = "Arial"))
```

# Datasets

- with_pet: whole leaf with everything
- without_pet: whole leaf excluding midlib and petile
- disc: leaf disc

```{r}
d <- read_csv("../data/full_data.csv")
d_cv <- read_csv("../data/full_data_cv.csv")

d |>
  filter(LDleaf < 0.1)

d <- d |>
  filter(!is.na(LMAdisc)) |>
  filter(!is.na(LMAleaf)) |>
  filter(!is.na(LTleaf)) |>
  rename(LT = LTleaf) |>
  rename(LA = LAleaf) |>
  filter(Location %in% c("Ailao_understory", "Mengla_Bubeng", "Yuanjiang_Savanna", "Yakushima")) |>
  #filter(Location != "Yakushima") |>
  #mutate(LMAleaf = LMAlamina) |>
  mutate(LMAratio = LMAleaf / LMAdisc) |>
  mutate(LDratio = LDleaf / LDdisc)

table(d$Location, d$Contributor)
table(d$Location, d$Biomes)

LA1 <- quantile(d$LA, 0.25, na.rm = TRUE)
LA2 <- quantile(d$LA, 0.5, na.rm = TRUE)
LA3 <- quantile(d$LA, 0.75, na.rm = TRUE)
LT1 <- quantile(d$LT, 0.25, na.rm = TRUE)
LT2 <- quantile(d$LT, 0.5, na.rm = TRUE)
LT3 <- quantile(d$LT, 0.75, na.rm = TRUE)

LA_mid <- median(d$LA)
LT_mid <- median(d$LT, na.rm = TRUE)

d <- d |>
  mutate(LT_gr = case_when(
    LT < LT1 ~ "Very~thin",
    LT < LT2 ~ "Thin",
    LT < LT3 ~ "Thick",
    TRUE ~ "Very~thick")) |>
  mutate(LT_gr = factor(LT_gr, levels = c("Very~thin", "Thin", "Thick",
                                          "Very~thick"))) |>
  mutate(LA_gr = case_when(
    LA < LA1 ~ "Very~small",
    LA < LA2 ~ "Small",
    LA < LA3 ~ "Large",
    TRUE ~ "Very~large")) |>
  mutate(LA_gr = factor(LA_gr, levels = c("Very~small", "Small", "Large",
                                          "Very~large"))) |>
  mutate(LALT_gr = case_when(
   LA < LA_mid & LT < LT_mid ~ "Thin~Small",
   LA < LA_mid & LT >= LT_mid ~ "Thick~Small",
   LA >= LA_mid & LT < LT_mid ~ "Thin~Large",
   LA >= LA_mid & LT >= LT_mid ~ "Thick~Large",
   TRUE ~ "aa"
                          )) |>
  mutate(LA_gr2 = ifelse(LA < LA_mid, "Small-leaved~species",
                         "Large-leaved~species")) |>
  mutate(LT_gr2 = ifelse(LT < LT_mid, "Thin-leaved~species",
                         "Thick-leaved~species"))

d_cv <- d_cv |>
  dplyr::select(Species, Location,
                LMAleaf_cv = LMAleaf, LMAdisc_cv = LMAdisc,
                LDleaf_cv = LDleaf, LDdisc_cv = LDdisc) |>
  #full_join(d) |>
  filter(!is.na(LMAleaf_cv)) |>
  filter(!is.na(LMAdisc_cv))

d_cv2 <- d_cv |>
  full_join(d) |>
  filter(!is.na(LMAleaf_cv)) |>
  filter(!is.na(LMAdisc_cv))

d %>%
  head %>%
  kable() %>%
  kable_styling()
```

```{r}

d |>
  ggplot(aes(LA, fill = Location)) +
  geom_histogram() +
  geom_vline(xintercept = LA_mid)

```

```{r, p_all}

tic()
p_all <- d |>
ggplot(aes(LMAdisc, LMAleaf)) +
  facet_grid(LALT_gr ~ Location) +
  geom_abline(intercept = 0, slope = 1, lty = 2)  +
  geom_point() +
  geom_sma(se = TRUE) +
  scale_x_log10() +
  scale_y_log10() +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )
toc()

ggsave("../figs/p_all.png", p_all, width = 8, height = 8)

```

![](../figs/p_all.png)

```{r}

d |>
ggplot(aes(LMAdisc, LMAleaf, col = EveDec)) +
  facet_grid(LALT_gr ~ Location) +
  geom_abline(intercept = 0, slope = 1)  +
  geom_point() +
  geom_sma(se = FALSE) +
  scale_x_log10() +
  scale_y_log10() +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

d |>
ggplot(aes(LMAdisc, LMAleaf, col = EveDec)) +
  facet_wrap( ~ EveDec) +
  geom_abline(intercept = 0, slope = 1)  +
  geom_point() +
  geom_sma(se = FALSE) +
  scale_x_log10() +
  scale_y_log10() +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

d |>
  ggplot(aes(LMAleaf, LMAleaf / LMAdisc, col = Location)) +
  geom_point() +
  scale_x_log10()

d |>
  filter(Location == "Mengla_Bubeng") |>
  filter(LALT_gr == "Thin~Small") |>
  DT::datatable()

```

# errors

```{r}

d_cv2 |>
  ggplot(aes(x = LMAdisc, y = LMAdisc_cv, col = Location)) +
    geom_point() +
  scale_x_log10()

```

```{r, eval=FALSE}

set.seed(123)

n <- 100
sig_m <- 0.2
sig_a <- 0.2
sig_d <- 0.2
mu <- rlnorm(n, log(80), 0.6)
#logLMAleaf <- rnorm(n, log(mu), sig_d)
logLMAleaf <- rnorm(n, log(mu), sqrt(sig_m^2 + sig_a^2))
logLMAdisc <- rnorm(n, log(mu), sig_d)
cor(logLMAleaf, logLMAdisc)^2

plot(logLMAdisc, logLMAleaf)

M <- rlnorm(n, log(10), 0.8)
A <- rlnorm(n, 3 * log(M), 0.3)
plot(M, A, log = "xy")
LMA <- M / A
sd(log(LMA))
sig <- sqrt(sig_m^2 + sig_a^2)

mean_ <- NULL
sd_ <- NULL
for (i in 1:1000) {
  bb <- rnorm(n) - rnorm(n)
  mean_[i] <- mean(bb)
  sd_[i] <- sd(bb)
}

hist(mean_)
hist(sd_)
hist((sd_)^2)

cv <- \(x) sqrt(exp(sd(log(x[!is.na(x)]))^2) - 1)

cv(d$LMAleaf)
cv(d$LMAdisc)

d |>
  filter(Location == "Yakushima") |>
  pull(LMAleaf) |>
  sd()
d |>
  filter(Location == "Yakushima") |>
  pull(LMAdisc) |>
  sd()

d |>
  filter(Location != "Yakushima") |>
  pull(LMAleaf) |>
  sd()
d |>
  filter(Location != "Yakushima") |>
  pull(LMAdisc) |>
  sd()

d |>
  pull(LMAleaf) |>
  sd()
d |>
  pull(LMAdisc) |>
  sd()

cv(tmp$LMAleaf)
cv(tmp$LMAdisc)

cv(tmp2$LMAleaf)
cv(tmp2$LMAdisc)

```

```{r}

tmp <- read_csv("../data-raw/LMA_Raw.csv") |>
 mutate(LMAratio = LMAleaf / LMAdisc) |>
 mutate(LTdisc = (Thickness1_disc + Thickness2_disc + Thickness3_disc) / 3) |>
 mutate(LTlefa = (Thickness1_leaf + Thickness2_leaf + Thickness3_leaf) / 3) |>
 mutate(LDratio = LDleaf / LDdisc) |>
 mutate(LTratio = LTleaf / LTdisc)

log(tmp$LDratio) |> mean(na.rm = TRUE)
log(tmp$LMAratio) |> mean(na.rm = TRUE)
log(tmp$LTratio) |> mean(na.rm = TRUE)

log(tmp$LDratio) |> var(na.rm = TRUE)
log(tmp$LMAratio) |> var(na.rm = TRUE)
log(tmp$LTratio) |> var(na.rm = TRUE)

ggplot(tmp, aes(LTratio, LMAratio)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10()

cor.test(log(tmp$LTratio), log(tmp$LMAratio))

ggplot(tmp, aes(LTleaf, Thickness1_disc))  +
  geom_point() +
  scale_x_log10() +
  scale_y_log10()

hist(tmp$LMAleaf/tmp$LMAdisc)

log(tmp$LMAratio) |> sd(na.rm = TRUE)
log(tmp$LTleaf / tmp$Thickness1_disc) |> sd(na.rm = TRUE)
log(tmp$LDleaf / tmp$LDdisc) |> sd(na.rm = TRUE)

sig_fun <- \(sig1, sig2) {
  sig <- 1 / (1/sig1^2 + 1/sig2^2)
  sqrt(sig)
}

sqrt(0.253^2 + 0.152^2)

sig_fun(0.253, 0.152)

sig_fun(0.4, 0.6)

cor.test(log(tmp$LTleaf), log(tmp$Thickness1_disc))

tmp |>
  ggplot(aes(Dry_mass_disc, LMAleaf / LMAdisc)) +
  geom_point() +
  scale_x_log10()

tmp |>
  ggplot(aes(LMAdisc, LMAleaf / LMAdisc)) +
  geom_point() +
  scale_x_log10()

tmp |>
  ggplot(aes(Dry_mass_leaf, LMAleaf / LMAdisc)) +
  geom_point() +
  scale_x_log10()

tmp |>
  ggplot(aes(Leaf_area_leaf, LMAleaf / LMAdisc)) +
  geom_point() +
  scale_x_log10()

```

```{r}

tmp2 <- read_csv("../data-raw/leaf_traits_for_Katabuchi.csv")

tmp2 <- tmp2 |>
  rename(LMAleaf = "Whole leaf LMA") |>
  rename(LMAdisc = "LD LMA") |>
  mutate(Dry_mass_disc = LMAdisc * 1.57 * 10^-4)

tmp2 |>
  ggplot(aes(Dry_mass_disc * 2, LMAleaf / LMAdisc)) +
  geom_point() +
  scale_x_log10()

tmp2 |>
  ggplot(aes(`Scanned leaf DW`, LMAleaf / LMAdisc)) +
  geom_point() +
  scale_x_log10()

tmp2 |>
  ggplot(aes(`LA mean (leaf let)`, LMAleaf / LMAdisc)) +
  geom_point() +
  scale_x_log10()

```

```{r LMA-gr2}

p_LALT_grid <- d |>
  ggplot(aes(x = LMAdisc, y = LMAleaf)) +
  geom_point(alpha = 0.8) +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = TRUE) +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  #facet_wrap(~LALT_gr, scale = "fixed", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LMA~(g~m^{-2}))) +
  ylab(expression(Whole-leaf~LMA~(g~m^{-2}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

ggsave("../figs/LMA_sp_gr.png", p_LALT_grid, width = 6, height = 6)

```

![](../figs/LMA_sp_gr.png)

```{r LMA-gr-both}

my_col <- RColorBrewer::brewer.pal(4, "RdBu")

p_LALT_grid_both <- d |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(x = LMAdisc, y = LMAleaf, col = punch_size)) +
  geom_point(alpha = 0.6) +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = FALSE) +
  scale_color_manual(values = my_col[c(2, 4)],
                     name = "Diameter of the leaf punch") +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  #facet_wrap(~LALT_gr, scale = "fixed", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LMA~(g~m^{-2}))) +
  ylab(expression(Whole-leaf~LMA~(g~m^{-2}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial"),
    show.legend = FALSE
  ) +
 theme(legend.position = c(0.3, 0.1),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.2, "cm"),
        legend.text = element_text(size = 9),
        legend.title = element_text(size = 9)
 )
p_LALT_grid_both

ggsave("../figs/LMA_sp_gr_both.png", p_LALT_grid_both, width = 6, height = 6)

```

![](../figs/LMA_sp_gr_both.png)

```{r LD-gr2}
p2_LALT_grid <- d |>
  filter(Location != "Yakushima") |>
  ggplot(aes(x = LDdisc, y = LDleaf)) +
  geom_point(alpha = 0.9) +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = TRUE) +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LD~(g~cm^{-3}))) +
  ylab(expression(Whole-leaf~LD~(g~cm^{-3}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

ggsave("../figs/LD_sp_gr.png", p2_LALT_grid, width = 6, height = 6)
```

![](../figs/LD_sp_gr.png)

```{r}
d |>
  ggplot(aes(x = LALT_gr, y = LMAleaf)) +
  geom_boxplot()
```

# SMA table

```{r}

sma_LMA <- sma(log10(LMAleaf) ~ log10(LMAdisc),
    data = d,
    elev.test = 0,
    slope.test = 1)

sma_LD <- sma(log10(LDleaf) ~ log10(LDdisc),
    data = d,
    elev.test = 0,
    slope.test = 1)

sma_LMA_LALT_gr <- sma(log10(LMAleaf) ~ log10(LMAdisc) * LALT_gr,
    data = d,
    elev.test = 0,
    slope.test = 1)

sma_LD_LALT_gr <- sma(log10(LDleaf) ~ log10(LDdisc) * LALT_gr,
    data = d,
    elev.test = 0,
    slope.test = 1)

my_fun <- function(fit) {
  tb1 <- fit$groupsummary |>
    mutate(Slope = paste0(round(Slope, 2), " [", round(Slope_lowCI, 2), ", ",
                          round(Slope_highCI, 2), "]"))|>
    mutate(Intecept = paste0(round(Int, 2), " [", round(Int_lowCI, 2), ", ",
                          round(Int_highCI, 2), "]"))|>
    mutate(sig_slope = case_when(
                             Slope_highCI < 1 ~ "sig",
                             Slope_lowCI > 1 ~ "sig",
                             TRUE ~ "ns"
                             )) |>
    mutate(sig_int = ifelse(Int_lowCI * Int_highCI > 0, "sig", "ns")) |>
    mutate(r2 = round(r2, 2)) |>
    dplyr::select(Slope, Intecept, r2, sig_slope, sig_int, group)
  tb2 <- tb1 |>
    mutate(Slope = ifelse(sig_slope == "sig", paste0("**", Slope, "**"), Slope)) |>
    mutate(Intecept = ifelse(sig_int == "sig", paste0("**", Intecept, "**"),
                             Intecept)) |>
    dplyr::select(Slope, Intecept, `*R^2^*` = r2)
  list(tb1, tb2, group = tb1$group)
}

tb0_LMA <- my_fun(sma_LMA)
tb0_LD <- my_fun(sma_LD)
tb2_LMA <- my_fun(sma_LMA_LALT_gr)
tb2_LD <- my_fun(sma_LD_LALT_gr)

#tb_dat <- rbind(cbind(tb0_LMA[[2]], tb0_LD[[2]]),
#  cbind(tb2_LMA[[2]], tb2_LD[[2]]))

tb_dat <- rbind(tb0_LMA[[2]], tb2_LMA[[2]])
tb_dat <- cbind(c("All", tb2_LMA$group), tb_dat) |>
  as.data.frame()

tb_dat %>%
  write_csv("../data/tab1.csv")

colnames(tb_dat)[1] <- "Data"
rownames(tb_dat) <- NULL

tb_dat |>
  kable() |>
 #pack_rows("all", 1, 1) |>
 #pack_rows("Site", 2, 6) |>
 #add_header_above(c(" ", "LMA" = 3, "LD" = 3)) |>
  kable_styling()

```

# ITV

- Yakushima: 1 cm diameter 2 discs
- Yunnan: 0.5 cm diamter, 3 discs

```{r}
tree <- read_csv("../data/tree_data.csv")

tree <- tree |>
  filter(!is.na(LMAdisc)) |>
  filter(!is.na(LMAleaf)) |>
  filter(!is.na(LTleaf)) |>
  rename(LT = LTleaf) |>
  rename(LA = LAleaf) |>
  mutate(Dry_mass_disc2 = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4 / 2,
   TRUE ~ LMAdisc * 0.889 * 10^-4 / 3
                )) |>
  mutate(Dry_mass_disc = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4,
   TRUE ~ LMAdisc * 0.889 * 10^-4
                ))

table(tree$Location, tree$Contributor)
table(tree$Location, tree$Biomes)

LA1_tree <- quantile(tree$LA, 0.25, na.rm = TRUE)
LA2_tree <- quantile(tree$LA, 0.5, na.rm = TRUE)
LA3_tree <- quantile(tree$LA, 0.75, na.rm = TRUE)
LT1_tree <- quantile(tree$LT, 0.25, na.rm = TRUE)
LT2_tree <- quantile(tree$LT, 0.5, na.rm = TRUE)
LT3_tree <- quantile(tree$LT, 0.75, na.rm = TRUE)

LA_mid_tree <- median(tree$LA, na.rm = TRUE)
LT_mid_tree <- median(tree$LT, na.rm = TRUE)

tree <- tree |>
  mutate(LT_gr = case_when(
    LT < LT1_tree ~ "Very~thin",
    LT < LT2_tree ~ "Thin",
    LT < LT3_tree ~ "Thick",
    TRUE ~ "Very~thick")) |>
  mutate(LT_gr = factor(LT_gr, levels = c("Very~thin", "Thin", "Thick",
                                          "Very~thick"))) |>
  mutate(LA_gr = case_when(
    LA < LA1_tree ~ "Very~small",
    LA < LA2_tree ~ "Small",
    LA < LA3_tree ~ "Large",
    TRUE ~ "Very~large")) |>
  mutate(LA_gr = factor(LA_gr, levels = c("Very~small", "Small", "Large",
                                          "Very~large"))) |>
  mutate(LALT_gr = case_when(
   LA < LA_mid_tree & LT < LT_mid_tree ~ "Thin~Small",
   LA < LA_mid_tree & LT >= LT_mid_tree ~ "Thick~Small",
   LA >= LA_mid_tree & LT < LT_mid_tree ~ "Thin~Large",
   LA >= LA_mid_tree & LT >= LT_mid_tree ~ "Thick~Large",
   TRUE ~ "aa"
                          )) |>
  mutate(LA_gr2 = ifelse(LA < LA_mid_tree, "Small-leaved~individuals",
                         "Large-leaved~individuals")) |>
  mutate(LT_gr2 = ifelse(LT < LT_mid_tree, "Thin-leaved~individuals",
                         "Thick-leaved~individuals"))

```

```{r}

tree |>
  group_by(LALT_gr) |>
  summarise(
          sd_LMAleaf = log10(LMAleaf) |> sd(),
          sd_LA = log10(LA) |> sd(),
          sd_LMAdisc = log10(LMAdisc) |> sd(),
          cv_LMAleaf = sd(log10(LMAleaf)) / mean(log10(LMAleaf)),
          cv_LMAdisc = sd(log10(LMAdisc)) / mean(log10(LMAdisc)),
          mean_LMAleaf = log10(LMAleaf) |> mean(),
          mean_LMAdisc = log10(LMAdisc) |> mean())

tree$LMAdisc |> log10() |> sd()
tree$LMAleaf |> log10() |> sd()

tree |>
  ggplot(aes(LMAdisc, LMAleaf, col = Dry_mass_disc)) +
    facet_grid(LALT_gr ~ Location) +
    geom_abline(intercept = 0, slope = 1)  +
    geom_point() +
    scale_color_viridis_c(trans = "log10") +
    geom_sma(se = FALSE) +
    scale_x_log10() +
    scale_y_log10() +
    stat_cor(
      aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
    )

```

```{r, LMAratio}

my_col <- RColorBrewer::brewer.pal(4, "RdBu")

LMAratio <- tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(Dry_mass_disc, LMAleaf / LMAdisc,
           # col = Dry_mass_disc
             col = punch_size
             )) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 1) +
  #scale_color_viridis_c(trans = "log10",
#                        name = "Total leaf disc \ndry mass (g)") +
  #scale_color_viridis_d() +
  scale_color_manual(values = my_col[c(2, 4)],
                     name = "Diameter of the leaf punch") +
#  scale_x_log10() +
  xlab("Total dry mass of leaf disc (g)") +
  ylab("Whole-leaf LMA / leaf disc LMA") +
  theme(
        legend.position = c(0.7, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))
#LMAratio

lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ log(Dry_mass_disc), tree))
lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ (Dry_mass_disc), tree))
lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ log(LT), tree))
lmtest::bptest(lm(log(LMAleaf / LMAdisc) ~ log(LA), tree))

LMAratio_LT <- tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(LT, LMAleaf / LMAdisc,
            col = Dry_mass_disc
             )) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 1) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total leaf disc \ndry mass (g)") +
  #scale_color_viridis_d() +
  scale_x_log10() +
  xlab("Leaf thickness (mm)") +
  ylab("Whole-leaf LMA / leaf disc LMA") +
  theme(
        legend.position = c(0.7, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))
#LMAratio_LT

LMAratio_LA <- tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(LA, LMAleaf / LMAdisc,
            col = Dry_mass_disc
             )) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 1) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total leaf disc \ndry mass (g)") +
  #scale_color_viridis_d() +
  scale_x_log10() +
  xlab(expression(Leaf~area~(m^2))) +
  ylab("Whole-leaf LMA / leaf disc LMA") +
  theme(
        legend.position = "none",
        #legend.position = c(0.2, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))
#LMAratio_LT

p_ratio <- LMAratio + LMAratio_LT + LMAratio_LA +
  plot_annotation(tag_levels = "a")

LDratio <- tree |>
  filter(Location != "Yakushima") |>
  ggplot(aes(Dry_mass_disc, LDleaf / LDdisc, col =
             Dry_mass_disc)) +
  geom_point(alpha = 0.8, show.legend = FALSE) +
  geom_hline(yintercept = 1) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total leaf disc \ndry mass (g)") +
  # scale_color_viridis_d() +
  # scale_x_log10() +
  xlab("Total dry mass of leaf disc (g)") +
  ylab("Whole-leaf LD / leaf disc LD") +
  theme(
        legend.position = "none",
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.4, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

#p_ratio <- LMAratio + LDratio  +
#  plot_annotation(tag_levels = "a")

ggsave("../figs/LMAratio.png", LMAratio, width = 3, height = 3)
ggsave("../figs/LMAratio2.png", p_ratio, width = 9, height = 3)

tmp <- tree |>
  filter(Location != "Yakushima") |>
  mutate(LDratio = LDleaf / LDdisc) |>
  mutate(LMAratio = LMAleaf / LMAdisc)

cor(tmp$LDratio, tmp$LMAratio)
cor(log(tmp$LDratio), log(tmp$LMAratio))

```

![](../figs/LMAratio.png)

![](../figs/LMAratio2.png)

```{r, LMAratio4}

LMAratio4 <- tree |>
  filter(Location != "Yakushima") |>
  ggplot(aes(LMAleaf / LMAdisc, LDleaf / LDdisc, col =
             Dry_mass_disc)) +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_point(alpha = 0.8) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total leaf disc \ndry mass (g)") +
  #scale_color_viridis_d() +
#  scale_x_log10() +
  ylab("Whole-leaf LD / leaf disc LD") +
  xlab("Whole-leaf LMA / leaf disc LMA") +
  theme(
        legend.position = c(0.8, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

ggsave("../figs/LMAratio4.png", LMAratio4, width = 3, height = 3)

```

![](../figs/LMAratio4.png)

```{r, LMAratio3}

LMAratio3 <- tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  ggplot(aes(LA, LMAleaf / LMAdisc,
           # col = Dry_mass_disc
             col = punch_size
             )) +
  geom_point(alpha = 0.6) +
  geom_hline(yintercept = 1) +
  #scale_color_viridis_c(trans = "log10",
#                        name = "Total leaf disc \ndry mass (g)") +
  #scale_color_viridis_d() +
  scale_x_log10() +
  scale_color_manual(values = my_col[c(2, 4)],
                     name = "Diameter of the leaf punch") +
  ylab("Whole-leaf LMA / leaf disc LMA") +
  xlab("Leaf area") +
  theme(
        legend.position = c(0.8, 0.75),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

tree |>
  mutate(punch_size = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) %>%
    lm(LMAleaf/LMAdisc ~ log(LT) + log(LA) + log(Dry_mass_disc) + punch_size, .) |>
  summary()

ggsave("../figs/LMAratio3.png", LMAratio3, width = 3, height = 3)

```

![](../figs/LMAratio2.png)

```{r}
tree |>
  ggplot(aes(x = LALT_gr, y = LMAleaf)) +
  geom_boxplot()
```

```{r LMA-gr2-ITV}

p_LALT_tree <- tree |>
  ggplot(aes(x = LMAdisc, y = LMAleaf, col = Dry_mass_disc)) +
  geom_point(alpha = 0.8) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total dry mass of \nleaf discs (g)") +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = TRUE) +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LMA~(g~m^{-2}))) +
  ylab(expression(Whole-leaf~LMA~(g~m^{-2}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  ) +
  theme(legend.position = c(0.39, 0.15),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

ggsave("../figs/LMA_ind_gr.png", p_LALT_tree, width = 6, height = 6)

fit <- lm(log10(LMAleaf / LMAdisc) ~ log10(Dry_mass_disc), tree)
lmtest::bptest(fit)

```

![](../figs/LMA_ind_gr.png)

```{r LD-gr2-ITV}
p2_LALT_tree <- tree |>
  filter(Location != "Yakushima") |>
  ggplot(aes(x = LDdisc, y = LDleaf, col = Dry_mass_disc)) +
  geom_point(alpha = 0.8) +
  scale_color_viridis_c(trans = "log10",
                        name = "Total dry mass of \nleaf discs (g)") +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = TRUE) +
  facet_grid(LA_gr2~LT_gr2, scale = "free", labeller = label_parsed) +
  xlab(expression(Leaf~disc~LD~(g~cm^{-3}))) +
  ylab(expression(Whole-leaf~LD~(g~cm^{-3}))) +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  ) +
  theme(legend.position = c(0.9, 0.15),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.4, "cm"),
        legend.text = element_text(size=7),
        legend.title = element_text(size=7))

ggsave("../figs/LD_ind_gr.png", p2_LALT_tree, width = 6, height = 6)
```

![](../figs/LD_ind_gr.png)

```{r}

tree |>
  group_by(Location) |>
  summarise(min = min(Dry_mass_disc))

tree |>
  ggplot(aes(Dry_mass_disc, LMAleaf / LMAdisc, col = Location)) +
  geom_point() +
  geom_vline(xintercept = 0.005) +
  scale_x_log10()

tree |>
  ggplot(aes(LMAdisc, LMAleaf / LMAdisc, col = Location)) +
  geom_point() +
#  geom_vline(xintercept = 0.005) +
  scale_x_log10()

tree |>
  filter(Dry_mass_disc < 0.007) |>
  ggplot(aes(LMAdisc, LMAleaf)) +
  #ggplot(aes(LMAdisc, LMAleaf, col = Location)) +
  geom_point() +
  scale_x_log10() +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  geom_sma(se = FALSE) +
#  facet_wrap(~ Location) |>
  stat_cor(
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
  )

table(tree$EveDec, tree$LALT_gr)

r2 <- NULL
r22 <- NULL
n1 <- NULL
n2 <- NULL
for (i in 5:200) {
  tree_sub <- tree |>
    filter(Dry_mass_disc < i / 4000)
  tree_sub2 <- tree |>
    filter(Dry_mass_disc > i / 4000)
  if (nrow(tree_sub) >= 10) {
    r2[i] <- cor(log(tree_sub$LMAdisc), log(tree_sub$LMAleaf)) ^2
    r22[i] <- cor(log(tree_sub2$LMAdisc), log(tree_sub2$LMAleaf)) ^2
    n1[i] <- nrow(tree_sub)
    n2[i] <- nrow(tree_sub2)
  }
}
r2_dat <- tibble(r2, r22, n1, n2, dry_mass = (1:200) / 2000)

r2_dat |>
  filter(r2 > 0.6)

r2_dat <- tibble(`Data with dry mass smaller than the x-axis` = r2,
                 `Data with dry mass greater than the x-axis` = r22, n1, n2, dry_mass = (1:200) / 2000)

fig_dry <- r2_dat |>
  pivot_longer(1:2) |>
  filter(dry_mass < 0.05) |>
  filter(!is.na(value)) |>
  ggplot(aes(x = dry_mass, y = value, col = value))  +
  geom_point(alpha = 0.8) +
  geom_line() +
  scale_color_viridis_c(name = expression(italic(R^2))) +
  facet_wrap(~name)  +
  scale_x_log10(breaks = c(0.005, 0.01, 0.02, 0.03, 0.05)) +
#  coord_cartesian(xlim=c(0.002, 0.05)) +
  xlab("Dry mass of leaf disc(s) (g)") +
#  ylab(expression(italic(R^2)~between~whole-leaf~and~leaf~disc~LMA)) +
  ylab(expression(atop(italic(R^2)~between~whole-leaf~and,
                 leaf~disc~LMA))) +
  theme(legend.position = c(0.9, 0.25),
        legend.key.size = unit(0.5, "cm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.text.align = 0,
        legend.key.height = unit(0.4, "cm"),
        legend.text = element_text(size=6),
        legend.title = element_text(size=6))
ggsave("../figs/fig_dry_mass.png", fig_dry, width = 6, height = 3)

tree |>
  arrange(-Dry_mass_disc) |>
  ggplot(aes(LMAdisc, LMAleaf, col = Dry_mass_disc)) +
  geom_point(alpha = 0.8) +
  scale_color_viridis_c(trans = "log10") +
  scale_x_log10() +
  scale_y_log10()

tree |>
  ggplot(aes(Dry_mass_disc, fill = Location, col = Location)) +
  geom_histogram(position = "identity", alpha = 0.6) +
  scale_x_log10() +
  geom_vline(xintercept = 0.005) +
  geom_vline(xintercept = 0.0001)

tree |>
  ggplot(aes(Dry_mass_disc, fill = Location, col = Location)) +
  geom_histogram(position = "identity", alpha = 0.6) +
  facet_wrap( ~LALT_gr) +
  scale_x_log10() +
  geom_vline(xintercept = 0.005)

```

# LMA and LD

## Species mean

```{r}

d_leaf <- d |>
  dplyr::select(c(Species:Contributor, LMA = LMAleaf, LDMC = LDMCleaf, LD = LDleaf)) |>
  pivot_longer(LMA:LD, names_to = "trait", values_to = "Whole-leaf") |>
  filter(Location != "Yakushima" | trait != "LD") |>
  filter(Location != "Yakushima" | trait != "LMA")

d_disc <- d |>
  dplyr::select(Species, Location, LMA = LMAdisc, LDMC = LDMCdisc, LD = LDdisc) |>
  pivot_longer(LMA:LD, names_to = "trait", values_to = "Leaf Disc") |>
  filter(Location != "Yakushima" | trait != "LD") |>
  filter(Location != "Yakushima" | trait != "LMA")

d2 <- full_join(d_leaf, d_disc) |>
  mutate(trait = factor(trait, c("LMA", "LDMC", "LD"))) |>
  mutate(trait_lab = factor(trait,
                            labels = c("LMA~(g~m^{-2})",
                                       "LDMC~(g~g^{-1})",
                                       "LD~(g~cm^{-3})"
                            )))

d2 |>
  filter(trait == "LMA") |>
  filter(!is.na(`Whole-leaf`)) |>
  filter(!is.na(`Leaf Disc`)) |>
  dim()

d2 |>
  filter(trait == "LD") |>
  filter(!is.na(`Whole-leaf`)) |>
  filter(!is.na(`Leaf Disc`)) |>
  dim()

p_all <- d2 |>
  filter(trait != "LDMC") |>
  ggplot(aes(x = `Leaf Disc`, y = `Whole-leaf`)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_log10() +
  scale_y_log10() +
#  geom_smooth(method = "lm", se = FALSE) +
  geom_sma(se = TRUE) +
  facet_wrap(~trait_lab, scale = "free", labeller = label_parsed) +
  stat_cor(
    #aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~"))
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
 #   label.x = 2
  )

ggsave("../figs/fig1.png", p_all, width = 6, height = 3)

```

![](../figs/fig1.png)

## CV

```{r}

p_cv1 <- d_cv |>
  ggplot(aes(x = LMAdisc_cv, y = LMAleaf_cv)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
  scale_y_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
  geom_sma(se = TRUE) +
  ylab("CV of whole-leaf LMA") +
  xlab("CV of leaf disc LMA") +
  coord_fixed() +
  stat_cor(
           label.x.npc = 0.3,
           label.y.npc = 0,
           vjust = 1.5,
           aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
               )
#p_cv1

cor(sqrt(d_cv$LMAleaf_cv), sqrt(d_cv$LMAdisc_cv))^2

p_cv2 <- d_cv |>
  filter(Location != "Yakushima") |>
  ggplot(aes(x = LMAdisc_cv, y = LMAleaf_cv)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_continuous(trans = "sqrt") +
  scale_y_continuous(trans = "sqrt") +
  geom_sma(se = TRUE) +
  ggtitle("Diameter: 0.6 cm") +
  ylab("CV of whole-leaf LMA") +
  xlab("CV of leaf disc LMA") +
  #coord_fixed(xlim = c(0.01, 5.4), ylim = c(0.01, 5.4)) +
  #coord_fixed() +
  stat_cor(
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
  )

p_cv3 <- d_cv |>
  filter(!is.na(LDdisc_cv)) |>
  filter(!is.na(LDleaf_cv)) |>
  filter(Location != "Yakushima") |>
  ggplot(aes(x = LDdisc_cv, y = LDleaf_cv)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_log10() +
  scale_y_log10() +
  geom_sma(se = TRUE) +
  ggtitle("Diameter: 0.6 cm") +
  ylab("CV of whole-leaf LD") +
  xlab("CV of leaf disc LD") +
  #coord_fixed(xlim = c(0.01, 5.4), ylim = c(0.01, 5.4)) +
  #coord_fixed() +
  stat_cor(
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
  )

hoge <- d_cv |>
  filter(Location != "Yakushima")
cor(sqrt(hoge$LMAleaf_cv), sqrt(hoge$LMAdisc_cv))^2

hoge <- d_cv |>
  filter(Location == "Yakushima")

cor(sqrt(hoge$LMAleaf_cv), sqrt(hoge$LMAdisc_cv))^2

cor(sqrt(d_cv$LMAleaf_cv), sqrt(d_cv$LMAdisc_cv))^2

#cor.test(log(hoge$LDleaf_cv), log(hoge$LDdisc_cv))

p_cv4 <- d_cv |>
  filter(Location == "Yakushima") |>
  ggplot(aes(x = LMAdisc_cv, y = LMAleaf_cv)) +
  geom_abline(intercept = 0, slope = 1, lty = 2) +
  geom_point(alpha = 0.6) +
  scale_x_continuous(trans = "sqrt") +
  scale_y_continuous(trans = "sqrt") +
  geom_sma(se = TRUE) +
  ggtitle("Diameter: 1.0 cm") +
  ylab("CV of whole-leaf LMA") +
  xlab("CV of leaf disc LMA") +
  #coord_fixed(xlim = c(0.01, 5.4), ylim = c(0.01, 5.4)) +
  #coord_fixed() +
  stat_cor(
    aes(label = paste(..rr.label..,  ..n.label.., sep = "~`,`~"), family = "Arial")
  )

p_cv <- (p_cv2 + p_cv4) +
  plot_annotation(tag_levels = "a")

ggsave("../figs/fig_cv2.png", p_cv, width = 6, height = 3)

ggsave("../figs/fig_cv.png", p_cv1, width = 3, height = 3)

ggsave("../figs/fig_cv_yaku.png", p_cv4, width = 3, height = 3)

```

![](../figs/fig_cv.png)

![](../figs/fig_cv2.png)

We need to check sample size

```{r}
tmp <- table(d$Biomes, d$LA_gr) |> as.data.frame()
ggplot(tmp, aes(x = Var1, y = Freq, fill = Var2)) +
  geom_col(position = "fill")

ggplot(tmp, aes(x = Var2, y = Freq, fill = Var1)) +
  geom_col(position = "fill")

tmp2 <- table(d$Biomes, d$LT_gr) |> as.data.frame()
ggplot(tmp2, aes(x = Var1, y = Freq, fill = Var2)) +
  geom_col(position = "fill")

ggplot(tmp2, aes(x = Var2, y = Freq, fill = Var1)) +
  geom_col(position = "fill")

tmp3 <- table(d$Biomes, d$LALT_gr) |> as.data.frame()
ggplot(tmp3, aes(x = Var1, y = Freq, fill = Var2)) +
  geom_col(position = "fill")

ggplot(tmp3, aes(x = Var2, y = Freq, fill = Var1)) +
  geom_col(position = "fill")

```

```{r}

d |>
  #filter(LALT_gr == "Thin~Small") |>
  filter(LALT_gr == "Thin~Small") |>
  ggplot(aes(x = LA, y = LMAratio, col = Location)) +
    geom_point() +
    geom_abline(intercept = 1, slope = 0) +
#    geom_sma(se = TRUE) +
    facet_wrap(~Location) +
    scale_x_log10()

d |>
  #filter(LALT_gr == "Thin~Small") |>
  ggplot(aes(LMAratio, fill = Location)) +
    geom_histogram(position = "identity", alpha = 0.6)

d |>
  #filter(LALT_gr == "Thin~Small") |>
  ggplot(aes(y = LMAratio, x = Location, fill = Location)) +
    geom_violin(alpha = 0.6)

d |>
  ggplot(aes(x = LA, y = LMAratio, col = Location)) +
    geom_point() +
    geom_abline(intercept = 1, slope = 0) +
    facet_wrap(~LALT_gr, scale = "free_x") +
    scale_x_log10()

d |>
  ggplot(aes(x = LT, y = LMAratio, col = Location)) +
    geom_point() +
    geom_abline(intercept = 1, slope = 0) +
    facet_wrap(~LALT_gr, scale = "free_x") +
    scale_x_log10()

d |>
  ggplot(aes(x = LMAdisc, y = LMAleaf, col = Location)) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1, lty = 2) +
    facet_wrap(~LALT_gr, scale = "free") +
#    geom_sma(se = FALSE) +
    scale_x_log10() +
    scale_y_log10() +
   # stat_cor(
   #          aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"))
   # )

d |>
  ggplot(aes(x = LMAdisc, y = LMAleaf, col = LALT_gr)) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1, lty = 2) +
    facet_wrap(~Location, scale = "free") +
    scale_x_log10() +
    scale_y_log10()

```

```{r}
d |>
  filter(LALT_gr == "Thin~Small") |>
  #filter(LALT_gr == "Thick~Large") |>
  DT::datatable()

hoge <- tree |>
  arrange(-LMAleaf/LMAdisc) %>%
    head

```

# Path

```{r}

tree2 <- tree |>
  mutate(PCH = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm")) |>
  mutate(d = LMAleaf/LMAdisc) |>
  mutate(LMA = abs(d - 1) |> log()) |>
  mutate(LT = log(LT)) |>
  mutate(LA = log(LA)) |>
  mutate(DM = log(Dry_mass_disc)) |>
  mutate(LMAw = log(LMAleaf)) |>
  mutate(LMAd = log(LMAdisc))

model1 <- 'LMA ~ LT + LA + DM
           DM ~ LT + LA + PCH'
          #LT ~ LA
fit1 <- sem(model1, data = tree2)
fitMeasures(fit1)

#lm(LMA ~ scale(exp(DM)) * scale(LT), tree2) |>
#  summary()
#

#plot(exp(LMA) ~ LT, tree2)
#plot(exp(LMA) ~ DM, tree2)

lm(LMA ~ LT * DM, tree2) |>
  summary()
lm(LMA ~ LT, tree2) |>
  summary()
lm(LMA ~ DM, tree2) |>
  summary()
#modificationindices(fit1)

#parameterEstimates(fit1, standardized = TRUE) |>
#  as_tibble() |>
#  filter(op == "~")j

standardizedSolution(fit1) |>
  DT::datatable()

p <- semPlot::semPaths(fit1,
                  layout = "tree",
                  shapeLat = "ellipse",
                  whatLabels  = "stand",
                  residuals = FALSE,
                  nDigits = 3, shapeMan = "square", sizeMan = 8,
                  sizeLat = 8, sizeLat2 = 8, style = "lisrel",
                  residScale = 12, curve = 2.5, optimizeLatRes = T,
                  edge.color = "black",
                  rotation = 2, edge.label.cex = 1)

pvalue_cutoff <- 0.05
obj <- semPlot:::semPlotModel(fit1)

original_Pars <- obj@Pars

check_Pars <- obj@Pars %>%
  dplyr::filter(!(edge %in% c("int","<->") | lhs == rhs))
# this is the list of paramater to sift thru
keep_Pars <- obj@Pars %>%
  dplyr::filter(edge %in% c("int","<->") | lhs == rhs)
# this is the list of paramater to keep asis
test_against <- lavaan::standardizedSolution(fit1) %>%
  dplyr::filter(pvalue < pvalue_cutoff, rhs != lhs)

test_against_rev <- test_against %>%
  rename(rhs2 = lhs,
         lhs = rhs) %>%
    rename(rhs = rhs2)
# I'll have to reverse it myself, and test against both orders

checked_Pars <-
    check_Pars %>% semi_join(test_against, by = c("lhs", "rhs")) %>%
    bind_rows(
        check_Pars %>% semi_join(test_against_rev, by = c("lhs", "rhs"))
    )

obj@Pars <- keep_Pars %>% bind_rows(checked_Pars)

#let's verify by looking at the list of the edges we removed from the object
anti_join(original_Pars, obj@Pars)

tmp <- RColorBrewer::brewer.pal(4, "RdBu")[c(4, 1)]
p2 <- semPlot::semPaths(obj,
                  "par",
                  whatLabels  = "stand",
                  exoCov = FALSE,
                  residuals = FALSE,
                  style = "lisrel",
                  sizeMan = 10,
                  sizeInt = 15,
                  sizeLat = 5,
                  posCol = tmp,
                  edge.label.cex = 2,
                  fade = FALSE)

png("../figs/path.png", width = 4, height = 4, units = "in", res = 200)
plot(p2)
dev.off()

```

```{r, eval=FALSE, echo=TRUE}

tree <- read_csv("./data/tree_data.csv")

tree2 <- tree |>
  filter(!is.na(LMAdisc)) |>
  filter(!is.na(LMAleaf)) |>
  filter(!is.na(LTleaf)) |>
  rename(LT = LTleaf) |>
  rename(LA = LAleaf) |>
  mutate(Dry_mass_disc2 = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4 / 2,
   TRUE ~ LMAdisc * 0.889 * 10^-4 / 3
                )) |>
  mutate(Dry_mass_disc = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4,
   TRUE ~ LMAdisc * 0.889 * 10^-4
                )) |>
  mutate(PCH = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm"))

fit <- lm(log(Dry_mass_disc) ~ scale(log(LT)) + scale(log(LA)) + PCH, tree2)

s <- summary(fit)
tb <- s$coefficients |> round(3) |> signif(3)
colnames(tb) <- c("Estimate", "SE", "t-value", "*P* value")
tb[,4] <- ifelse(tb[,4] < 0.001, "< 0.001", tb[,4])
rownames(tb)[2] <- "log(Leaf thickness)"
rownames(tb)[3] <- "log(Leaf area)"
rownames(tb)[4] <- "Large leaf punch"

tb |>
  kable() |>
  kable_styling()
```

# Petiole

## Yakushima

```{r, eval=TRUE}
d3 <- read_csv("../data-raw/leaf_traits_for_Katabuchi.csv")

yaku <- d3 |>
  filter(Growthform != "H") |>
  mutate(Location = "Yakushima") |>
  mutate(Biomes = "ST2") |>
  mutate(Garden = "NO") |>
  mutate(MAT = NA) |>
  mutate(MAP = NA) |>
  mutate(Contributor = "Onoda Yusuke") |>
  rename(
                LA = `LA mean (leaf let)`,
                LT = `Lamina thickness`,
                LMAdisc = `LD LMA`,
                LMAleaf = `Whole leaf LMA`,
                LDMCleaf = `LDMC`,
                LDdisc = `TD`
  ) |>
  mutate(LDleaf = LMAleaf / LT * 10^-3) %>%
  mutate(LDMCdisc = NA) |>
  mutate(LTdisc = NA) |>
  mutate(Growthform = ifelse(Growthform == "W", "Trees", Growthform)) |>
  mutate(petiole_ratio = `petiole DW`/`Scanned leaf DW`)# |>
#  filter(!is.na(petiole_ratio))

d3 |>
  filter(Species == "Symplocos_myrtacea") |>
  DT::datatable()

yaku_sp <- yaku |>
  group_by(Species) |>
  summarize_at(
               .vars = vars(
             LMAdisc,
             LMAleaf,
             LDMCdisc,
             LDMCleaf,
             LDdisc,
             LDleaf,
             LT,
             LTdisc,
             LA,
             petiole_ratio
               ),
    .funs =  \(x)mean(x, na.rm = TRUE)) |>
  filter(petiole_ratio > 0) |>
  filter(!is.na(LMAdisc))

pet1 <- ggplot(yaku_sp, aes(x = petiole_ratio, y = LMAleaf/LMAdisc)) +
  geom_point() +
  scale_x_log10() +
  #xlab(expression(Petiole/leaf~dry~mass~ratio(g~g^-1))) +
  xlab("Petiole / leaf dry mass ratio") +
  ylab("Whole-leaf / leaf disc LMA ratio") +
  geom_smooth(method = "lm") +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

pet2 <- ggplot(yaku_sp, aes(x = petiole_ratio, y = LA)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  xlab("Petiole / leaf dry mass ratio") +
  ylab(expression(Leaf~area~(g~cm^2))) +
  geom_smooth(method = "lm") +
  stat_cor(
    aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
  )

pet3 <- pet2 + pet1 +
  plot_annotation(tag_levels = "a") &
  theme(plot.tag = element_text(face = "bold"))

ggsave("../figs/petiole.png", pet3, width = 8, height = 4)

x <- rnorm(100)
y <- rnorm(100)

cv_x <- sd(x) / mean(x)
cv_y <- sd(y) / mean(y)
cov(x, y)
cov(cv_x, cv_y)

hist(yaku_sp$petiole_ratio)
hist(yaku_sp$LMAleaf/yaku_sp$LMAdisc)

```

![](../figs/petiole.png)

## CV test

```{r, eval=FALSE}

cv_ln <- \(sigma) sqrt(exp(sigma^2) - 1)
sigma <- 0.8
e <- seq(0.1, 2, length = 80)
plot(sigma*e, cv_ln(sigma*e), type = "l", col = "blue")
points(sigma*e, sigma*e, type = "l")
#points(sigma*e, sigma*e*e, type = "l", col = "red")

# rlnorm(10, 0, 0.001)

cv <- \(x) sd(x)/mean(x)
cv_e <- \(x, e) sqrt(var(x) + var(e))/mean(x)

cv2 <- \(mu1,sig1, sig2) {sqrt(sig1^2*sig2^2 + mu1*sig2^2 + sig1^2)}

mu <- 2
sig1 <- seq(0.1, 2, length = 80)
sig2 <- 0.9
plot(sig1, sig1, type = "l")
points(sig1, cv2(mu, sig1, sig2), type = "l", col = "blue")

tmp <- rnorm(100, mu, sig)
mean(tmp)
sd(tmp)
cv(tmp)

mu <- 10
sig <- 2
hoge <- NULL
e <- rlnorm(100, 0, 0.5)
hist(e)
for (i in 1:100){
 hoge[i] <- cv(rnorm(100, mu, sig)) / cv(rnorm(100, mu, sig) * e)
}

hist(hoge)
rnorm(100, -3, 0.4) |> exp() |> hist()

sqrt(3 + 2)
sqrt(3)

x <- rnorm(1000)
y <- rnorm(1000, 0, 10)
cov(x, x+y)
cov(x, y) + var(x)
var(x)

1 - pbinom(7, 20, 0.25)
1 - pnorm(1.29)

# sp
n <- 100
# tree
m <- 10
mu <- 10
sig <- 2
sig2 <- 0.5
sig3 <- 1

#set.seed(123)
mu_i <- rnorm(n, mu, sig)
mu2_i <- mu_i + rnorm(n, 0, sig2)

cv1 <- mapply(rnorm, m, mu_i, sig3) |>
  apply(2, cv)
cv2 <- mapply(rnorm, m, mu2_i, sig3) |>
  apply(2, cv)
plot(cv1, cv2)
cor.test(cv1, cv2)

```

# Computing Environment

```{r}
devtools::session_info()
```

### 2021-12-15 ms/LMA_method.tex
first commit

%%
% Copyright (c) 2017 - 2020, Pascal Wagler;
% Copyright (c) 2014 - 2020, John MacFarlane
%
% All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions
% are met:
%
% - Redistributions of source code must retain the above copyright
% notice, this list of conditions and the following disclaimer.
%
% - Redistributions in binary form must reproduce the above copyright
% notice, this list of conditions and the following disclaimer in the
% documentation and/or other materials provided with the distribution.
%
% - Neither the name of John MacFarlane nor the names of other
% contributors may be used to endorse or promote products derived
% from this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
% "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
% LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
% FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE
% COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
% INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING,
% BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
% LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
% LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN
% ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
% POSSIBILITY OF SUCH DAMAGE.
%%

%%
% This is the Eisvogel pandoc LaTeX template.
%
% For usage information and examples visit the official GitHub page:
% https://github.com/Wandmalfarbe/pandoc-latex-template
%%

\DeclareUnicodeCharacter{2212}{-}

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*,table}{xcolor}
%
\documentclass[
  12pt,
  a4paper,
,tablecaptionabove
]{scrartcl}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\definecolor{default-linkcolor}{HTML}{A50000}
\definecolor{default-filecolor}{HTML}{A50000}
\definecolor{default-citecolor}{HTML}{4077C0}
\definecolor{default-urlcolor}{HTML}{4077C0}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  breaklinks=true,
  pdfcreator={LaTeX via pandoc with the Eisvogel template}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
% add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
\usepackage{footnotebackref}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

% Make use of float-package and set default placement for figures to H.
% The option H means 'PUT IT HERE' (as  opposed to the standard h option which means 'You may put it here if you like').
\usepackage{float}
\floatplacement{figure}{H}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{lineno}
\linenumbers

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\date{}

%%
%% added
%%

%
% language specification
%
% If no language is specified, use English as the default main document language.
%

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
    % Workaround for bug in Polyglossia that breaks `\familydefault` when `\setmainlanguage` is used.
  % See https://github.com/Wandmalfarbe/pandoc-latex-template/issues/8
  % See https://github.com/reutenauer/polyglossia/issues/186
  % See https://github.com/reutenauer/polyglossia/issues/127
  \renewcommand*\familydefault{\sfdefault}
    % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

%
% for the background color of the title page
%

%
% break urls
%
\PassOptionsToPackage{hyphens}{url}

%
% When using babel or polyglossia with biblatex, loading csquotes is recommended
% to ensure that quoted texts are typeset according to the rules of your main language.
%
\usepackage{csquotes}

%
% captions
%
%\definecolor{caption-color}{HTML}{777777}
\definecolor{caption-color}{HTML}{37474F}
%\usepackage[font={stretch=1.2}, textfont={color=caption-color}, position=top, skip=4mm, labelfont=bf, singlelinecheck=false, justification=raggedright]{caption}
\usepackage[font={stretch=1}, textfont={color=caption-color}, position=top, skip=2mm, labelfont=bf, singlelinecheck=false, justification=raggedright]{caption}
\setcapindent{0em}

%
% blockquote
%
\definecolor{blockquote-border}{RGB}{221,221,221}
\definecolor{blockquote-text}{RGB}{119,119,119}
\usepackage{mdframed}
\newmdenv[rightline=false,bottomline=false,topline=false,linewidth=3pt,linecolor=blockquote-border,skipabove=\parskip]{customblockquote}
\renewenvironment{quote}{\begin{customblockquote}\list{}{\rightmargin=0em\leftmargin=0em}%
\item\relax\color{blockquote-text}\ignorespaces}{\unskip\unskip\endlist\end{customblockquote}}

%
% Source Sans Pro as the de­fault font fam­ily
% Source Code Pro for monospace text
%
% 'default' option sets the default
% font family to Source Sans Pro, not \sfdefault.
%
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
    \usepackage[default]{sourcesanspro}
  \usepackage{sourcecodepro}
  %\usepackage{}
  \else % if not pdftex
    \usepackage[default]{sourcesanspro}
  \usepackage{sourcecodepro}
  %\usepackage{}

  % XeLaTeX specific adjustments for straight quotes: https://tex.stackexchange.com/a/354887
  % This issue is already fixed (see https://github.com/silkeh/latex-sourcecodepro/pull/5) but the
  % fix is still unreleased.
  % TODO: Remove this workaround when the new version of sourcecodepro is released on CTAN.
  \ifxetex
    \makeatletter
    \defaultfontfeatures[\ttfamily]
      { Numbers   = \sourcecodepro@figurestyle,
        Scale     = \SourceCodePro@scale,
        Extension = .otf }
    \setmonofont
      [ UprightFont    = *-\sourcecodepro@regstyle,
        ItalicFont     = *-\sourcecodepro@regstyle It,
        BoldFont       = *-\sourcecodepro@boldstyle,
        BoldItalicFont = *-\sourcecodepro@boldstyle It ]
      {SourceCodePro}
    \makeatother
  \fi
  \fi

%
% heading color
%
\definecolor{heading-color}{RGB}{40,40,40}
\addtokomafont{section}{\color{heading-color}}
% When using the classes report, scrreprt, book,
% scrbook or memoir, uncomment the following line.
%\addtokomafont{chapter}{\color{heading-color}}

%
% variables for title and author
%
\usepackage{titling}
\title{}
\author{}

%
% tables
%

\definecolor{table-row-color}{HTML}{F5F5F5}
\definecolor{table-rule-color}{HTML}{999999}

%\arrayrulecolor{black!40}
\arrayrulecolor{table-rule-color}     % color of \toprule, \midrule, \bottomrule
\setlength\heavyrulewidth{0.3ex}      % thickness of \toprule, \bottomrule
\renewcommand{\arraystretch}{1.3}     % spacing (padding)

%
% remove paragraph indention
%
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

%
%
% Listings
%
%

%
% header and footer
%
\usepackage{fancyhdr}

\fancypagestyle{eisvogel-header-footer}{
  \fancyhead{}
  \fancyfoot{}
  \lhead[]{}
  \chead[]{}
  \rhead[]{}
  %\lfoot[\thepage]{}
  \cfoot[]{}
  \cfoot[]{\thepage}
  \renewcommand{\headrulewidth}{0.0pt}
 % \renewcommand{\footrulewidth}{0.0pt}
 % \renewcommand{\headrulewidth}{0.4pt}
 % \renewcommand{\footrulewidth}{0.4pt}
}
\pagestyle{eisvogel-header-footer}

%%
%% end added
%%

\begin{document}

%%
%% begin titlepage
%%

%%
%% end titlepage
%%

Sources and consequences of mismatch between leaf disc and whole-leaf
leaf mass per area (LMA)

\[ \]

Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
Katabuchi\textsuperscript{1,*}, Yusuke Onoda\textsuperscript{4}, Cong
Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
Chen\textsuperscript{1,3,5}

\[ \]

\textsuperscript{1} CAS Key Laboratory of Tropical Forest Ecology,
Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences,
Menglun, Yunnan 666303, China

\textsuperscript{2} University of Chinese Academy of Sciences, Beijing
100049, China

\textsuperscript{3} Center of Plant Ecology, Core Botanical Gardens,
Chinese Academy of Sciences, Yunnan 666303, China

\textsuperscript{4} Graduate School of Agriculture, Kyoto University,
Kyoto 606-8502, Japan

\textsuperscript{5} Savanna Ecosystem Research Station, Xishuangbanna
Tropical Botanical Garden, Chinese Academy of Sciences, Yuanjiang,
Yunnan 6663300, China

\[ \]

\textbf{Corresponding Authors}:

Masatoshi Katabuchi

E-mail:
\href{mailto:mattocci27@gmail.com}{\nolinkurl{mattocci27@gmail.com}}

Jiao-Lin Zhang

Tel: +86 691 871 3046; Fax: +86 691 871 5070; E-mail:
\href{mailto:zjl@xtbg.org.cn}{\nolinkurl{zjl@xtbg.org.cn}}

\[ \]

Manuscript received \_\_\_\_\_\_\_; revision accepted \_\_\_\_\_\_\_.

\textbf{Running title}: Leaf disc and whole-leaf LMA

\newpage

\hypertarget{abstract}{%
\section{ABSTRACT}\label{abstract}}

\textbf{PREMISE:} Leaf mass per area (LMA), which is the key trait in
leaf economic spectrum and plant growth analysis, is measured from leaf
discs or whole leaves. These differences in the measurement methods may
lead to large differences in the estimates of LMA values.

\textbf{METHODS:} We determined LMA using leaf discs and whole-leaf
(including petiole) for 334 woody species from a wide range of biomes
(tropics, subtropics, savanna, and temperate) to examine what extent
whole-leaf and leaf disc LMA match, whether the differences in the
estimates are associated with leaf size and thickness, and whether
intraspecifc variation for each species match.

\textbf{RESULTS:} Disc-based estimates of species and individual mean
LMA matched well whole-leaf estimates. Thin and large leaves had weaker
correlations between leaf disc and whole-leaf estimates. Variability of
LMA estimates within species (i.e., amount of intraspecific variation)
only weakly matched between whole-leaf and disc-based estimates
(\emph{R\textsuperscript{2}} = 0.31). We also found that sample with
small total dry mass of leaf discs tended to show greater differences
between leaf disc and whole-leaf LMA.

\textbf{CONCLUSIONS:} Mean values of leaf disc LMA are generally good
proxies for mean values of whole-leaf LMA with appropriate calibration
(9.4\% differences in our samples), but their accuracy depends on leaf
size, leaf thickness, and sizes of leaf punch. Therefore, using an
appropriate size of leaf punch is important for obtaining stable
estimates of leaf disc LMA that matches well with whole-leaf LMA.
Quantifying trait variation using leaf disc should be considered with
caution.

\textbf{KEY WORDS:} intraspecific variation, leaf density, leaf economic
spectrum, leaf heterogeneity, leaf punch, leaf size, leaf thickness,
petiole, specific leaf area, within-leaf variation

\hypertarget{introduction}{%
\section{INTRODUCTION}\label{introduction}}

Leaf mass per area (LMA), determined by lamina thickness and leaf tissue
density (LD), describes how much biomass is invested into given
photosynthetic leaf area thus reflecting a cost for light interception,
which is the key trait of the leaf economic spectrum (LES)
(\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
\protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009};
\protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}). Generally,
resource-acquisitive species (fast-growing species) tend to have low LMA
values, showing high photosynthesis, high nutrients, and often have fast
leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al.,
2004}). In contrast, resource-conservative species (slow-growing
species) often have higher LMA values with the opposite patterns
(\protect\hyperlink{ref-Garnier1994}{Garnier and Laurent, 1994};
\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
\protect\hyperlink{ref-Reich2014}{Reich, 2014};
\protect\hyperlink{ref-Diaz2016}{Díaz et al., 2016}). The LMA is also
frequently used in plant growth analysis
(\protect\hyperlink{ref-Evans1972}{Evans, 1972};
\protect\hyperlink{ref-Poorter2014}{Poorter et al., 2014};
\protect\hyperlink{ref-Falster2018}{Falster et al., 2018}) because
relative growth rates (RGR) can be decomposed into the product of net
assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR
\(\times\) LMR \(\times\) LMA\textsuperscript{-1}). Another appealing
feature of LMA is that it is relatively easy to measure large numbers of
species (i.e., `soft' trait, \protect\hyperlink{ref-Diaz2004}{Díaz et
al., 2004}). Therefore, LMA has been of interests to ecologists and
widely used since the first report more than a century ago
(\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).

LMA values can be determined by either 1) a whole leaf including or
excluding petioles, and 2) a leaf disc excluding all major veins or
petioles
(\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et
al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}).
Although some studies do not make clear what protocol was followed,
these differences in the measurement methods may lead to large
discrepancies in the estimates of LMA values because the major vein
allocation (major vein, which includes first to second or third-order
veins, volume per area) has been reported to be one of the main
determinants for the variation in LMA
(\protect\hyperlink{ref-John2017}{John et al., 2017}). Since larger
leaves tend to invest more of their mass into dense midribs and petiole
for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al.,
2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves
have clearly visible and large-diameter veins with less uniform leaf
structure (i.e., kite-type leaves;
(\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the
estimates of whole-leaf LMA and leaf disc LMA might be greater for
larger and thinner leaves. If leaf disc LMA largely and consistently
underestimates whole-leaf LMA, some calibrations may be required to
combine or compare those different estimates
(\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008};
\protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}). If divergencies
between the estimates based on the different methods are large and
inconsistent (i.e., low \emph{R\textsuperscript{2}} values), this is
difficult to calibrate and should inflate errors in the subsequent
analyses. To date, however, only a database from a single region, Panama
Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al.,
2010}), is available in the TRY
(\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both
estimates of LMA from small leaf discs and whole leaves including
petioles, limiting of our understanding of under what conditions
estimates of LMA from leaf discs are reliable estimates of whole-leaf
LMA.

Given that leaf disc samples have more sources of intraspecific trait
variation (ITV) than whole-leaf samples, the effects of discrepancies
between whole-leaf LMA and leaf disc LMA might be large when ITV is
quantified as a coefficient of variance (CV). Sources of ITV for
whole-leaf samples is variation among individuals within the same
species and variation among leaves within the same individuals
(\protect\hyperlink{ref-Messier2010}{Messier et al., 2010},
\protect\hyperlink{ref-Messier2017}{2017}). An additional source of
trait variation for leaf disc samples is variation among leaf discs
within the same leaves. Thus, extents of ITV for each species based on
whole-leaf and leaf discs samples may not match. Despite the importance
of ITV in community ecology
(\protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013};
\protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), the effect
of different measurement methods on the extent of ITV has been largely
ignored.

In this study, we aimed to investigate what extent whole-leaf (including
petiole) and leaf disc LMA match, whether the relationships between
whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf
thicknesses, and whether amounts of intraspecifc variations for each
match between whole-leaf and leaf disc based estimates. We collected a
total of 334 woody species from four biomes (tropics, subtropics,
savanna, and warm-temperate) to cover the wide range of geography. We
predicted that the overall relationship between whole-leaf LMA and disc
LMA would be weaker than previous reported LMA data
(\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in Kraft et al.
(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
0.92 for leaf laminas in Onoda et al.
(\protect\hyperlink{ref-Onoda2011}{2011})) because we collected data
with various leaf sizes from a wide range of climates. We also predicted
that species with larger and/or thinner leaves would show weaker
correlations. Finally, we predicted that amounts of intraspecifc
variations for each species do not match well between whole-leaf and
leaf disc based estimates.

\hypertarget{materials-and-methods}{%
\section{MATERIALS AND METHODS}\label{materials-and-methods}}

\emph{Data sources}

We used newly compiled individual-level plant datasets form a wide
ranges of biomes in China and Japan (Table S1) to examine the
relationship between whole-leaf and leaf disc-based estimates of leaf
traits. First, the Yunnan dataset is from three forest plots in Yunnan
province, Southwest China, which includes a tropical rain forest (TRF),
a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet
forest (STF), with a total of 141 species and 846 individuals. Second,
the Yakushima data is from a warm-temperate forest in Yakushima island,
Japan, with a total of 193 species and 519 individuals. In total, we
used 334 woody species and 1365 individuals. The methodologies for trait
sampling and measurement are slightly different between the Yunnan and
the Yakushima dataset, which we describe bellow.

\emph{Measurements of leaf disc and whole-leaf LMA}

At the TRF site, we collected leaf samples from trees within reach of a
canopy crane (88 m tall with a 60 m long boom). In the HDS, and STF
sites, we used a 12-m long pruner to collect samples for most of the
target species. In case of tall individuals that out of the reach of
pruner, we used a rope climbing to reach the canopy, then sampled
branches with the long pruner. In Yakushima, we used 15-m poles for our
leaf sampling. At least six sun-exposed healthy leaves were sampled from
each of 3 to 6 individuals for each species. Trait values were averaged
at the species- and individual-level for the analyses. For
compound-leaved species, we referred a leaflet (the minimum
photosynthetic unit) as a single leaf in our study.

To determine what extent LMA values were affected by the different
methods, LMA were determined (i) LMA based on a whole leaf including
petioles and (ii) LMA based on leaf disc avoiding thick veins. Three
0.6-cm diameter discs were taken from the base, middle and tip of each
leaf using a hole punch in the Yunnan dataset. Two 1.0-cm diameter discs
were taken from each leaf were in the Yakushima dataset. Fresh leaf area
(LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including
petioles and midribs) was measured using a scanner and ImageJ software
by the R package \emph{LeafArea}
(\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}). Fresh leaf
thickness (LT; mm) was measured using a micrometer in three points at
the base, middle and tip of the leaf using a micrometer (Mitutoyo
293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at
0.001 mm. Thickness of each leaf disc was also measured for the Yunnan
dataset but not for the Yakushima dataset, which enables us to estimate
whole-leaf and leaf disc leaf tissue density (LD; g
cm\textsuperscript{-3}) separately in the Yunnan dataset. Leaf dry mass
(whole leaves including petioles and midribs, and leaf discs) was
recorded after drying 80°C for over 48 h to constant weight using an
electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a
precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
and petiole dry mass were also determined separately (81 out of 193
species) to quantify leaf support costs. Dry mass for leaf discs were
recorded 2-3 discs together for each leaf. Based on those measurements
of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was
calculated as the ratio of leaf dry mass to fresh leaf area, and LD was
calculated as the ratio of LMA to LT. We do not present results of LD in
the main text, because differences between whole-leaf LD and leaf disc
LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
and measurement errors of leaf thickness (Appendix S2).

\emph{Statistical analyses}

Bivariate trait relationships between disc-based and whole-leaf
log-transformed LMA were summarized with variance explained
(\emph{R\textsuperscript{2}}) based on Pearson correlations and with
standardized major axis (SMA) regressions
(\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the
samples and different leaf area and thickness groups. Species and
individual groups were divided into four categories based on the medians
of leaf area and leaf thickness across all species and all individuals,
respectively: thin and small-leaved, thin and large-leaved, thick and
small-leaved, thick and large-leaved species (individuals). Median
values are as following: small-leaved species (LA \textless{} 29.5
cm\textsuperscript{2}), thin-leaved species (LT \textless{} 0.28 mm),
small-leaved individuals (LA \textless{} 34.7 cm\textsuperscript{2}),
and thin-leaved individuals (LT \textless{} 0.26 mm).

The amount of intraspecific variation of LMA was calculated using
coefficient of variation of log-normally distributed data;
\(CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}\), where \(s_{\mathrm{ln}}\) is
the sample standard deviation in the log-transformed data
(\protect\hyperlink{ref-Julious2000}{Julious and Debarnot, 2000}). We
also considered CV on the arithmetic scale; \(CV = s/\bar{x}\), where
\(s\) is the sample standard deviation and \(\bar{x}\) is the sample
mean. However, these two different CV calculations only negligibly
altered the bivariate relationship and did not change our conclusion,
and thus we will report CV of log-normally distributed data in the main
text.

SMA analyses were run using the R package \emph{smatr}
(\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this
included tests for slope heterogeneity and elevation differences between
disc-based and whole-leaf estimates of LMA values. Confidence intervals
of SMA estimates were based on 1000 bootstraps. All statistical analyses
were conducted in R version 4.1.2
(\protect\hyperlink{ref-RCoreTeam2021}{R Core Team, 2021}).

\hypertarget{results}{%
\section{RESULTS}\label{results}}

Disc-based estimates of species mean LMA matched well whole-leaf
estimates (Table 1; \emph{R\textsuperscript{2}} = 0.87 for all species).
Species with thicker and smaller leaves had stronger correlations
between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
There was a negative correlation between species mean leaf area and leaf
thickness (\emph{r} = -0.29, \emph{P} \textless{} 0.05, \emph{n} = 334).
When we pooled all the species, there were significant differences in
intercepts for species mean LMA (Table 1), suggesting that the
whole-leaf estimates of LMA were 9.4\% greater than disc-based estimates
in the arithmetic scale. Large-leaved species also had significant
positive intercepts, suggesting that whole-leaf estimates of LMA were
22.1\% greater than disc-based estimates in the arithmetic scale (Table
1). Intercepts did not differ for small-leaved species (Table 1).

Disc-based estimates of individual mean LMA also showed positive
correlations with whole-leaf estimates but their
\emph{R\textsuperscript{2}} values were smaller than those for the
species means (Fig. 2). Similar to the species-level pattern,
individuals with thicker and smaller leaves had stronger correlations
(Fig. 2). The relationships of the whole-leaf LMA : disc leaf LMA ratio
with total dry mass for the leaf disc (we weighted 2-3 discs together),
with leaf thickness, and with leaf area were heteroscedastic (unequal
variance, \emph{P} \textless{} 0.001; Appendix S3). Samples with small
total dry mass, thin leaves, and larger leaves tended to show greater
variance (Fig. 2; Appendix S3). The total dry mass of leaf disc was
positively correlated with both leaf thickness and leaf punch size
(Appendix S4). Amounts of intraspecific variation (CV; coefficient of
variation) only weakly matched between whole-leaf and disc-based
estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.31).

\hypertarget{discussion}{%
\section{DISCUSSION}\label{discussion}}

Disc-based traits explained interspecific variations in whole-leaf LMA
(\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the
strength of their relationship was approximately same or slightly weaker
than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} =
409, for whole-leaves in Kraft et al.
(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
(\protect\hyperlink{ref-Onoda2011}{2011})). Standardized major axis
(SMA) regression analysis showed significantly greater intercepts when
all the species were pooled (9.4\% differences) or large-leaved species
were used (22.1\% differences). Together, these findings suggest that
disc-based estimates can be generally used as good proxies for their
whole-leaf estimates with appropriate calibration. However, the strength
of correlations highly depended on leaf area, thickness (Fig. 1) and
sizes of leaf punches (Appendix S3 and S5).

Larger leaves generally invest disproportionally more mass into dense
midribs and major veins for support
(\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006},
\protect\hyperlink{ref-Niinemets2007}{2007};
\protect\hyperlink{ref-Sack2012}{Sack et al., 2012}), and thinner leaves
have distinct veins and have kite-type appearances
(\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}). As we predicted,
thicker and/or smaller leaves tended to show greater
\emph{R\textsuperscript{2}} values between whole-leaf and leaf disc
estimates (Figs 1. and 2). Large-leaved species had greater whole-leaf
LMA than leaf disc LMA (Table 1), which is consistent with the pattern
of large leaves disproportionately investing in more leaf veins and/or
petioles. This is also supported by the subset of our dataset in which
we measured leaf lamina and petiole dry mass separately. We confirmed
that leaf disc and whole-leaf LMA estimate diverged for species with
greater investment in petiole dry mass, and large-leaved species tended
to have greater investment for petiole dry mass than small-leaved
species (Appendix S6).

Meanwhile, our results are seemingly inconsistent with a previous study
that used thin and soft leaves and found high
\emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92;
Kraft et al. (\protect\hyperlink{ref-Kraft2008}{2008})). Kraft et al.
(\protect\hyperlink{ref-Kraft2008}{2008}) used sapling leaves under
closed canopy that are thinner than adult leaves
(\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010};
\protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}). Shade
leaves tend to have thinner leaves than sun leaves because of fewer
layers of palisade mesophyll cells
(\protect\hyperlink{ref-Terashima2001}{Terashima et al., 2001};
\protect\hyperlink{ref-Onoda2008}{Onoda et al., 2008}). The relatively
low \emph{R\textsuperscript{2}} values for thin-leaved species and
individuals in our study compared to the previous study may suggest not
only the effect of distinct veins on variance in LMA
(\protect\hyperlink{ref-John2017}{John et al., 2017}) but also technical
difficulty in measuring tiny weight of discs in lower LMA leaves. We
found that estimates of whole-leaf and leaf disc LMA diverged when total
dry mass of leaf discs was small (Fig. 2; Appendices S3), and thus
thin-leaved species, which have smaller dry mass (Appendix S4), tended
to showed the low \emph{R\textsuperscript{2}} values especially when we
used a smaller leaf punch (diameter: 0.6 cm; Appendix S5).

Even though we used the same species, the same individuals and the same
trait (LMA) to estimate the extents of intraspecific trait variation
(ITV), the explained variance of the relationship between whole-leaf and
disc-based estimate was surprisingly small (Fig. 3;
\emph{R\textsuperscript{2}} = 0.31). This is probably because leaf disc
samples have more sources of ITV than whole-leaf samples (i.e.,
variation among leaf discs within the same leaves). Although there are
not many studies that quantified trait variation within a single leaf, a
previous study that used a giant leaved species \emph{Alocasia
macrorrhiza}, suggests that LMA varied within leaves due to reduced
water supply and demand from midrib to outer regions
(\protect\hyperlink{ref-Li2013a}{Li et al., 2013}). Because calculating
the mean values generally diminishes the effect of within-sample
variation, the relationship between disc-based estimates of individual
mean LMA and its whole-leaf estimates will be stronger than the
relationship between leaf disc CV and whole-leaf CV. Thus, leaf disc and
whole-leaf estimates of species means will show the strongest
relationship. This is consistent with the \emph{R\textsuperscript{2}}
values in our results (Figs. 1-3). The mismatch of ITV between
whole-leaf and disc-based estimate could be ignored in community-level
ITV studies (i.e., \protect\hyperlink{ref-Siefert2015}{Siefert et al.,
2015}), which quantify the total variance of ITV within communities.
However, it is likely to change patterns for species-level ITV studies
(i.e., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}), which
quantify extents of ITV for each species, since species with high ITV
based on leaf-disc estimates do not always have to show high ITV for
whole-leaf estimates. This problem will be more obvious when one uses
smaller leaf punches (Appendix S7).

The present study was designed to examine the extent to which whole leaf
and leaf disc LMA matched. Our study shows that mean values of leaf disc
LMA is generally a good proxy for mean values of whole-leaf LMA.
However, larger and thinner leaves tended to show the large
discrepancies between the leaf disc and whole-leaf estimates, and thus
when one needs to mix leaf disc LMA and whole-leaf LMA in a single
analysis (e.g., meta-analysis), appropriate calibrations are necessary.
Although our study was not designed to evaluate the effects of diameter
sizes of leaf punches, the sizes of leaf punches are also the important
sources of variance between whole-leaf and leaf disc LMA. This is
probably because small dry mass inflates measurement errors and small
leaf disc size inflates trait variation within leaves. Additionally,
although the mean values of leaf disc and whole-leaf LMA matched well,
quantifying trait variation using leaf discs should be considered with
caution, because variation among leaf discs within the same leaves
(including measurement errors) seems to be large. Leaf discs, which can
target leaf lamina avoiding leaf veins, are useful and essential for
biochemical determinations such as measurements of Rubisco activity
(\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because the
photosynthetic activity occurs most in lamina rather than in veins for
C\textsubscript{3} plants (\protect\hyperlink{ref-Hibberd2002}{Hibberd
and Quick, 2002}; \protect\hyperlink{ref-Gao2018}{Gao et al., 2018}).
Leaf disc LMA is also the preferred method for quantifying leaf lamina
density, which avoid effects of veins. However, if the objective is to
use leaf disc LMA as an alternative for whole-leaf LMA, using an
appropriate size of leaf punch is important for obtaining stable
estimates of leaf disc LMA that matches well with whole-leaf LMA.

\hypertarget{acknowledgments}{%
\section{ACKNOWLEDGMENTS}\label{acknowledgments}}

The authors thank Lian-Bin Tao and Peng-Yun Yan for field work. This
work was funded by the National Natural Science Foundation of China
(41861144016, 32071735, 31570406, 32171507), the CAS `Light of West
China' Program, Yunnan Provincial Science and Technology Department
(2018HB068). PM was supported by financial support from CAS-TWAS
President's Fellowship for International Doctoral Students. MK was
supported by CAS President's International Fellowship Initiative
(2020FYB0003).

\hypertarget{author-contributions}{%
\section{AUTHOR CONTRIBUTIONS}\label{author-contributions}}

PM, MK, and YJC conceived the study; PM, YO, and YJC collected data; MK
and CZ performed the analysis; MK and YJC led the writing of the paper;
and all authors contributed to revisions.

\hypertarget{data-availability-statement}{%
\section{DATA AVAILABILITY
STATEMENT}\label{data-availability-statement}}

Data and codes for this manuscript are archived and available on Zenodo
(XXX).

\hypertarget{supporting-information}{%
\section{SUPPORTING INFORMATION}\label{supporting-information}}

Additional supporting information may be found online in the Supporting
Information section at the end of the article.

\textbf{APPENDIX S1.} Site information.

\textbf{APPENDIX S2.} Generalization for a relationship between ratios
of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf
tissue density (LD), and leaf thickness (LT).

\textbf{APPENDIX S3.} Relationships between whole-leaf LMA : disc leaf
LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and
(c) leaf area.

\textbf{APPENDIX S4.} Summary of multiple regression for log-transformed
total dry mass of leaf discs.

\textbf{APPENDIX S5.} Relationships between species mean leaf mass per
area (LMA) determined by using whole leaves and leaf discs.

\textbf{APPENDIX S6.} Relationships between petiole to leaf dry mass
ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.

\textbf{APPENDIX S7.} Relationships between coefficient of variation
(CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm
diameter leaf punch, and (b) 1.0 cm diameter leaf punch.

\hypertarget{literature-cited}{%
\section{LITERATURE CITED}\label{literature-cited}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Albert2010a}{}}%
Albert, C. H., W. Thuiller, N. G. Yoccoz, A. Soudant, F. Boucher, P.
Saccone, and S. Lavorel. 2010.
\href{https://doi.org/10.1111/j.1365-2745.2010.01651.x}{Intraspecific
functional variability: {Extent}, structure and sources of variation}.
\emph{Journal of Ecology} 98: 604--613.

\leavevmode\vadjust pre{\hypertarget{ref-Diaz2004}{}}%
Díaz, S., J. G. Hodgson, K. Thompson, M. Cabido, J. H. C. Cornelissen,
A. Jalili, G. Montserrat-Martí, et al. 2004.
\href{https://doi.org/10.1658/1100-9233(2004)015\%5B0295:TPTTDE\%5D2.0.CO;2}{The
plant traits that drive ecosystems: {Evidence} from three continents}.
\emph{Journal of Vegetation Science} 15: 295.

\leavevmode\vadjust pre{\hypertarget{ref-Diaz2016}{}}%
Díaz, S., J. Kattge, J. H. C. Cornelissen, I. J. Wright, S. Lavorel, S.
Dray, B. Reu, et al. 2016.
\href{https://doi.org/10.1038/nature16489}{The global spectrum of plant
form and function}. \emph{Nature} 529: 167--171.

\leavevmode\vadjust pre{\hypertarget{ref-Evans1972}{}}%
Evans, G. C. 1972. The quantitative analysis of plant growth. {Univ of
California Press}.

\leavevmode\vadjust pre{\hypertarget{ref-Falster2018}{}}%
Falster, D. S., R. A. Duursma, and R. G. FitzJohn. 2018.
\href{https://doi.org/10.1073/pnas.1714044115}{How functional traits
influence plant growth and shade tolerance across the life cycle}.
\emph{Proceedings of the National Academy of Sciences} 115:
E6789--E6798.

\leavevmode\vadjust pre{\hypertarget{ref-Gao2018}{}}%
Gao, Z., W. Shen, and G. Chen. 2018.
\href{https://doi.org/10.1093/jxb/ery155}{Uncovering {C4-like}
photosynthesis in {C3} vascular cells}. \emph{Journal of Experimental
Botany} 69: 3531--3540.

\leavevmode\vadjust pre{\hypertarget{ref-Garnier1994}{}}%
Garnier, E., and G. Laurent. 1994.
\href{https://doi.org/10.1111/j.1469-8137.1994.tb04036.x}{Leaf anatomy,
specific mass and water content in congeneric annual and perennial grass
species}. \emph{New Phytologist} 128: 725--736.

\leavevmode\vadjust pre{\hypertarget{ref-Grubb1986}{}}%
Grubb, P. 1986. Sclerophylls, pachyphylls, and pycnophylls: {The} nature
and significance of hard leaf surface. \emph{Insects and the Plant
Surface}: 137--150.

\leavevmode\vadjust pre{\hypertarget{ref-Hanson1917}{}}%
Hanson, H. C. 1917. Leaf-structure as related to environment.
\emph{American Journal of Botany}: 533--560.

\leavevmode\vadjust pre{\hypertarget{ref-Hibberd2002}{}}%
Hibberd, J. M., and W. P. Quick. 2002.
\href{https://doi.org/10.1038/415451a}{Characteristics of {C4}
photosynthesis in stems and petioles of {C3} flowering plants}.
\emph{Nature} 415: 451--454.

\leavevmode\vadjust pre{\hypertarget{ref-John2017}{}}%
John, G. P., C. Scoffoni, T. N. Buckley, R. Villar, H. Poorter, and L.
Sack. 2017. \href{https://doi.org/10.1111/ele.12739}{The anatomical and
compositional basis of leaf mass per area}. \emph{Ecology Letters} 20:
412--425.

\leavevmode\vadjust pre{\hypertarget{ref-Julious2000}{}}%
Julious, S. A., and C. A. Debarnot. 2000. Why are pharmacokinetic data
summarized by arithmetic means? \emph{Journal of Biopharmaceutical
Statistics} 10: 55--71.

\leavevmode\vadjust pre{\hypertarget{ref-Katabuchi2015}{}}%
Katabuchi, M. 2015.
\href{https://doi.org/10.1007/s11284-015-1307-x}{{LeafArea}: An {R}
package for rapid digital image analysis of leaf area}. \emph{Ecological
Research} 30: 1073--1077.

\leavevmode\vadjust pre{\hypertarget{ref-Kattge2020}{}}%
Kattge, J., G. Bönisch, S. Díaz, S. Lavorel, I. C. Prentice, P. Leadley,
S. Tautenhahn, et al. 2020.
\href{https://doi.org/10.1111/gcb.14904}{{TRY} plant trait database
\textendash{} enhanced coverage and open access}. \emph{Global Change
Biology} 26: 119--188.

\leavevmode\vadjust pre{\hypertarget{ref-Kichenin2013}{}}%
Kichenin, E., D. A. Wardle, D. A. Peltzer, C. W. Morse, and G. T.
Freschet. 2013.
\href{https://doi.org/10.1111/1365-2435.12116}{Contrasting effects of
plant inter- and intraspecific variation on community-level trait
measures along an environmental gradient}. \emph{Functional Ecology} 27:
1254--1261.

\leavevmode\vadjust pre{\hypertarget{ref-Kitajima2010}{}}%
Kitajima, K., and L. Poorter. 2010.
\href{https://doi.org/10.1111/j.1469-8137.2010.03212.x}{Tissue-level
leaf toughness, but not lamina thickness, predicts sapling leaf lifespan
and shade tolerance of tropical tree species}. \emph{New Phytologist}
186: 708--721.

\leavevmode\vadjust pre{\hypertarget{ref-Kraft2008}{}}%
Kraft, N. J. B., R. Valencia, and D. D. Ackerly. 2008.
\href{https://doi.org/10.1126/science.1160662}{Functional {Traits} and
{Niche-Based Tree Community Assembly} in an {Amazonian Forest}}.
\emph{Science} 322: 580--582.

\leavevmode\vadjust pre{\hypertarget{ref-Li2013a}{}}%
Li, S., Y.-J. Zhang, L. Sack, C. Scoffoni, A. Ishida, Y.-J. Chen, and
K.-F. Cao. 2013. \href{https://doi.org/10.1371/journal.pone.0066016}{The
heterogeneity and spatial patterning of structure and physiology across
the leaf surface in giant leaves of alocasia macrorrhiza}. \emph{PLOS
ONE} 8: 1--10.

\leavevmode\vadjust pre{\hypertarget{ref-Messier2017}{}}%
Messier, J., B. J. McGill, B. J. Enquist, and M. J. Lechowicz. 2017.
\href{https://doi.org/10.1111/ecog.02006}{Trait variation and
integration across scales: Is the leaf economic spectrum present at
local scales?} \emph{Ecography} 40: 685--697.

\leavevmode\vadjust pre{\hypertarget{ref-Messier2010}{}}%
Messier, J., B. J. McGill, and M. J. Lechowicz. 2010.
\href{https://doi.org/10.1111/j.1461-0248.2010.01476.x}{How do traits
vary across ecological scales? {A} case for trait-based ecology}.
\emph{Ecology Letters} 13: 838--848.

\leavevmode\vadjust pre{\hypertarget{ref-Niinemets2007}{}}%
Niinemets, Ü., A. Portsmuth, D. Tena, M. Tobias, S. Matesanz, and F.
Valladares. 2007. \href{https://doi.org/10.1093/aob/mcm107}{Do we
underestimate the importance of leaf size in plant economics?
{Disproportional} scaling of support costs within the spectrum of leaf
physiognomy}. \emph{Annals of Botany} 100: 283--303.

\leavevmode\vadjust pre{\hypertarget{ref-Niinemets2006}{}}%
Niinemets, Ü., A. Portsmuth, and M. Tobias. 2006.
\href{https://doi.org/10.1111/j.1469-8137.2006.01741.x}{Leaf size
modifies support biomass distribution among stems, petioles and mid-ribs
in temperate plants}. \emph{New Phytologist} 171: 91--104.

\leavevmode\vadjust pre{\hypertarget{ref-Oktavia2020}{}}%
Oktavia, D., and G. Jin. 2020.
\href{https://doi.org/10.1016/j.baae.2020.09.010}{Variations in leaf
morphological and chemical traits in response to life stages, plant
functional types, and habitat types in an old-growth temperate forest}.
\emph{Basic and Applied Ecology} 49: 22--33.

\leavevmode\vadjust pre{\hypertarget{ref-Onoda2008}{}}%
Onoda, Y., F. Schieving, and N. P. R. Anten. 2008.
\href{https://doi.org/10.1093/aob/mcn013}{Effects of light and nutrient
availability on leaf mechanical properties of {Plantago} major: {A}
conceptual approach}. \emph{Annals of Botany} 101: 727--736.

\leavevmode\vadjust pre{\hypertarget{ref-Onoda2011}{}}%
Onoda, Y., M. Westoby, P. B. Adler, A. M. F. Choong, F. J. Clissold, J.
H. C. Cornelissen, S. Díaz, et al. 2011.
\href{https://doi.org/10.1111/j.1461-0248.2010.01582.x}{Global patterns
of leaf mechanical properties}. \emph{Ecology Letters} 14: 301--312.

\leavevmode\vadjust pre{\hypertarget{ref-Onoda2017}{}}%
Onoda, Y., I. J. Wright, J. R. Evans, K. Hikosaka, K. Kitajima, Ü.
Niinemets, H. Poorter, et al. 2017.
\href{https://doi.org/10.1111/nph.14496}{Physiological and structural
tradeoffs underlying the leaf economics spectrum}. \emph{New
Phytologist} 214: 1447--1463.

\leavevmode\vadjust pre{\hypertarget{ref-Parry2002}{}}%
Parry, M. A., P. J. Andralojc, S. Khan, P. J. Lea, and A. J. Keys. 2002.
Rubisco activity: Effects of drought stress. \emph{Annals of Botany} 89:
833--839.

\leavevmode\vadjust pre{\hypertarget{ref-Perez-Harguindeguy2013}{}}%
Pérez-Harguindeguy, N., S. Díaz, E. Garnier, S. Lavorel, H. Poorter, P.
Jaureguiberry, M. S. Bret-Harte, et al. 2013.
\href{https://doi.org/10.1071/BT12225}{New handbook for standardised
measurement of plant functional traits worldwide}. \emph{Australian
Journal of Botany} 61: 167--234.

\leavevmode\vadjust pre{\hypertarget{ref-Poorter2014}{}}%
Poorter, H., H. Lambers, and J. R. Evans. 2014.
\href{https://doi.org/10.1111/nph.12547}{Trait correlation networks: {A}
whole-plant perspective on the recently criticized leaf economic
spectrum}. \emph{New Phytologist} 201: 378--382.

\leavevmode\vadjust pre{\hypertarget{ref-Poorter2009}{}}%
Poorter, H., Ü. Niinemets, L. Poorter, I. J. Wright, and R. Villar.
2009. \href{https://doi.org/10.1111/j.1469-8137.2009.02830.x}{Causes and
consequences of variation in leaf mass per area ({LMA}): {A}
meta-analysis}. \emph{New Phytologist} 182: 565--588.

\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2021}{}}%
R Core Team. 2021. R: {A} language and environment for statistical
computing. {R Foundation for Statistical Computing}, {Vienna, Austria}.

\leavevmode\vadjust pre{\hypertarget{ref-Reich2014}{}}%
Reich, P. B. 2014. \href{https://doi.org/10.1111/1365-2745.12211}{The
world-wide 'fast-slow' plant economics spectrum: {A} traits manifesto}.
\emph{Journal of Ecology} 102: 275--301.

\leavevmode\vadjust pre{\hypertarget{ref-Sack2012}{}}%
Sack, L., C. Scoffoni, A. D. McKown, K. Frole, M. Rawls, J. C. Havran,
H. Tran, and T. Tran. 2012. Developmentally based scaling of leaf
venation architecture explains global ecological patterns. \emph{Nature
Communications} 3: 1--10.

\leavevmode\vadjust pre{\hypertarget{ref-Siefert2015}{}}%
Siefert, A., C. Violle, L. Chalmandrier, C. H. Albert, A. Taudiere, A.
Fajardo, L. W. Aarssen, et al. 2015.
\href{https://doi.org/10.1111/ele.12508}{A global meta-analysis of the
relative extent of intraspecific trait variation in plant communities}.
\emph{Ecology Letters} 18: 1406--1419.

\leavevmode\vadjust pre{\hypertarget{ref-Terashima2001}{}}%
Terashima, I., S.-I. Miyazawa, and Y. T. Hanba. 2001.
\href{https://doi.org/10.1007/PL00013972}{Why are {Sun Leaves Thicker}
than {Shade Leaves}? \textemdash{} {Consideration} based on {Analyses}
of {CO2 Diffusion} in the {Leaf}}. \emph{Journal of Plant Research} 114:
93--105.

\leavevmode\vadjust pre{\hypertarget{ref-Warton2012a}{}}%
Warton, D. I., R. A. Duursma, D. S. Falster, and S. Taskinen. 2012.
\href{https://doi.org/10.1111/j.2041-210X.2011.00153.x}{Smatr
3\textendash{} an {R} package for estimation and inference about
allometric lines}. \emph{Methods in Ecology and Evolution} 3: 257--259.

\leavevmode\vadjust pre{\hypertarget{ref-Warton2006}{}}%
Warton, D. I., I. J. Wright, D. S. Falster, and M. Westoby. 2006.
\href{https://doi.org/10.1017/S1464793106007007}{Bivariate line-fitting
methods for allometry}. \emph{Biological Reviews of the Cambridge
Philosophical Society} 81: 259--291.

\leavevmode\vadjust pre{\hypertarget{ref-Wright2004a}{}}%
Wright, I. J., P. B. Reich, M. Westoby, D. D. Ackerly, Z. Baruch, F.
Bongers, J. Cavender-Bares, et al. 2004.
\href{https://doi.org/10.1038/nature02403}{The worldwide leaf economics
spectrum}. \emph{Nature} 428: 821--827.

\leavevmode\vadjust pre{\hypertarget{ref-Wright2010}{}}%
Wright, S. J., K. Kitajima, N. J. B. Kraft, P. B. Reich, I. J. Wright,
D. E. Bunker, R. Condit, et al. 2010.
\href{https://doi.org/10.1890/09-2335.1}{Functional traits and the
growth-mortality trade-off in tropical trees}. \emph{Ecology} 91:
3664--3674.

\end{CSLReferences}

\newpage

\begin{longtable}[]{@{}lllr@{}}
\toprule
Data & Slope & Intercept & \emph{R\textsuperscript{2}} \\
\midrule
\endhead
All & 0.97 {[}0.94, 1.01{]} & \textbf{0.09 {[}0.02, 0.16{]}} & 0.87 \\
Thick-large & 0.93 {[}0.85, 1.03{]} & \textbf{0.19 {[}0.01, 0.37{]}} &
0.86 \\
Thick-small & 1.02 {[}0.97, 1.07{]} & 0 {[}-0.11, 0.11{]} & 0.93 \\
Thin-large & 0.91 {[}0.82, 1.02{]} & \textbf{0.2 {[}0.02, 0.37{]}} &
0.71 \\
Thin-small & 0.93 {[}0.83, 1.03{]} & 0.16 {[}-0.02, 0.35{]} & 0.84 \\
\bottomrule
\end{longtable}

\textbf{Table. 1.} Relationships between species mean leaf leaf mass per
area (LMA) values determined by using whole leaves and leaf discs across
all species and within species groups. Data are divided into four
categories based on the quartiles: thin and small-leaved, thin and
large-leaved, thick and small-leaved, and thick and large-leaved
species. SMA slope (95\% CI), intercepts (95\% CI), and
\emph{R\textsuperscript{2}} values are reported. Statistically
significant differences (\emph{P} \textless{} 0.05) in slopes and
intercepts are highlighted in bold.

\newpage

\textbf{Fig. 1.} Relationships between species mean leaf mass per area
(LMA) determined by using whole leaves and leaf discs. Species groups
are divided into four categories on the basis of the medians of the leaf
size and leaf thickness across all the species. Dashed lines indicate
1:1 lines. Blue solid lines indicate standardized major axis
regressions. The 95\% confidence intervals are presented as the shaded
area. All the correlations are significant (\emph{P} \textless{} 0.001).

\includegraphics{../figs/LMA_sp_gr.png}

\newpage

\textbf{Fig. 2.} Relationships between individual leaf mass per area
(LMA) determined by using whole leaves and leaf discs. Individual groups
are divided into four categories based on the basis of the medians of
the leaf size and leaf thickness across all the individuals. All the
correlations are significant (\emph{P} \textless{} 0.001). Details as in
Fig. 1.

\includegraphics{../figs/LMA_ind_gr.png}

\newpage

\textbf{Fig. 3.} Relationships between coefficient of variation (CV) in
leaf trait values determined by using whole leaves and leaf discs: (a)
leaf mass per area (LMA). The correlation is significant (\emph{P}
\textless{} 0.001). Details as in Fig. 1. Note that the axes are square
root scales.

\includegraphics{../figs/fig_cv.png}

\end{document}

### 2021-12-15 ms/LMA_method_old.tex
first commit

--- 2021-12-15 ms/LMA_method.tex
@@
 Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
-Chen\textsuperscript{1,3,5}
+Chen\textsuperscript{1,3}
 
@@
 Kyoto 606-8502, Japan
-
-\textsuperscript{5} Savanna Ecosystem Research Station, Xishuangbanna
-Tropical Botanical Garden, Chinese Academy of Sciences, Yuanjiang,
-Yunnan 6663300, China
 
@@
 \textbf{METHODS:} We determined LMA using leaf discs and whole-leaf
-(including petiole) for 334 woody species from a wide range of biomes
-(tropics, subtropics, savanna, and temperate) to examine what extent
-whole-leaf and leaf disc LMA match, whether the differences in the
-estimates are associated with leaf size and thickness, and whether
-intraspecifc variation for each species match.
+(including petiole) for 334 woody species from across biomes (tropics,
+subtropics, savanna, and temperate) to examine what extent whole-leaf
+and leaf disc LMA match, whether the differences in the estimates are
+associated with leaf size and thickness, and whether intraspecifc
+variation for each species match.
 
@@
 (9.4\% differences in our samples), but their accuracy depends on leaf
-size, leaf thickness, and sizes of leaf punch. Therefore, using an
-appropriate size of leaf punch is important for obtaining stable
+size, leaf thickness, and sizes of leaf punch. Therefore, using
+appropriate sizes of leaf punch is important for obtaining stable
 estimates of leaf disc LMA that matches well with whole-leaf LMA.
@@
 
-\textbf{KEY WORDS:} intraspecific variation, leaf density, leaf economic
-spectrum, leaf heterogeneity, leaf punch, leaf size, leaf thickness,
-petiole, specific leaf area, within-leaf variation
+\textbf{Key words:}
+
+intraspecific variation, leaf density, leaf economic spectrum, leaf
+heterogeneity, leaf punch, leaf size, leaf thickness, petiole, specific
+leaf area, within-leaf variation
 
@@
 
-LMA values can be determined by either 1) a whole leaf including or
+LMA values are measured from either 1) a whole leaf including or
 excluding petioles, and 2) a leaf disc excluding all major veins or
@@
 (\protect\hyperlink{ref-John2017}{John et al., 2017}). Since larger
-leaves tend to invest more of their mass into dense midribs and petiole
+leaves should invest more of their mass into dense midribs and petiole
 for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al.,
@@
 have clearly visible and large-diameter veins with less uniform leaf
-structure (i.e., kite-type leaves;
-(\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the
+structure {[}i.e., kite-type leaves; Grubb
+(\protect\hyperlink{ref-Grubb1986}{1986}){]}, discrepancies in the
 estimates of whole-leaf LMA and leaf disc LMA might be greater for
-larger and thinner leaves. If leaf disc LMA largely and consistently
-underestimates whole-leaf LMA, some calibrations may be required to
-combine or compare those different estimates
-(\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008};
-\protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}). If divergencies
-between the estimates based on the different methods are large and
-inconsistent (i.e., low \emph{R\textsuperscript{2}} values), this is
-difficult to calibrate and should inflate errors in the subsequent
-analyses. To date, however, only a database from a single region, Panama
-Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al.,
-2010}), is available in the TRY
-(\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both
-estimates of LMA from small leaf discs and whole leaves including
-petioles, limiting of our understanding of under what conditions
-estimates of LMA from leaf discs are reliable estimates of whole-leaf
-LMA.
+larger and thinner leaves. If leaf disc LMA largely underestimates
+whole-leaf LMA, some calibrations may be required to combine or compare
+those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et
+al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}). If
+divergencies between the estimates based on the different methods are
+large (i.e., low \emph{R\textsuperscript{2}} values), this is difficult
+to calibrate and should inflate errors in the subsequent analyses. To
+date, however, only a database from a single region, Panama Plant Traits
+Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is
+available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al.,
+2020}) that have both estimates of LMA from small leaf discs and whole
+leaves including petioles, limiting of our understanding of under what
+conditions estimates of LMA from leaf discs are reliable estimates of
+whole-leaf LMA.
 
@@
 
-In this study, we aimed to investigate what extent whole-leaf (including
-petiole) and leaf disc LMA match, whether the relationships between
-whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf
+In this study, we aimed to investigate to which extent whole-leaf
+(including petiole) and leaf disc LMA match, whether the relationships
+between whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf
 thicknesses, and whether amounts of intraspecifc variations for each
 match between whole-leaf and leaf disc based estimates. We collected a
-total of 334 woody species from four biomes (tropics, subtropics,
+total of 334 woody species from across biomes (tropics, subtropics,
 savanna, and warm-temperate) to cover the wide range of geography. We
@@
 (\protect\hyperlink{ref-Onoda2011}{2011})) because we collected data
-with various leaf sizes from a wide range of climates. We also predicted
-that species with larger and/or thinner leaves would show weaker
-correlations. Finally, we predicted that amounts of intraspecifc
+with various leaf sizes from the wide range of climates. We also
+predicted that species with larger and/or thinner leaves would show
+weaker correlations. Finally, we predicted that amounts of intraspecifc
 variations for each species do not match well between whole-leaf and
@@
 
-We used newly compiled individual-level plant datasets form a wide
-ranges of biomes in China and Japan (Table S1) to examine the
-relationship between whole-leaf and leaf disc-based estimates of leaf
-traits. First, the Yunnan dataset is from three forest plots in Yunnan
-province, Southwest China, which includes a tropical rain forest (TRF),
-a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet
-forest (STF), with a total of 141 species and 846 individuals. Second,
-the Yakushima data is from a warm-temperate forest in Yakushima island,
-Japan, with a total of 193 species and 519 individuals. In total, we
-used 334 woody species and 1365 individuals. The methodologies for trait
-sampling and measurement are slightly different between the Yunnan and
-the Yakushima dataset, which we describe bellow.
-
-\emph{Measurements of leaf disc and whole-leaf LMA}
+We used newly compiled individual-level plant datasets from broad
+regions to examine the relationship between leaf traits estimates based
+on whole-leaf and leaf disc across wide ranges of geography in China and
+Japan (Table S1). First, the Yunnan dataset is from forest plots in
+Yunnan province, Southwest China, which includes a tropical rain forest
+(TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen
+wet forest (STF), with a total of 141 species and 846 individuals.
+Second, the Yakushima data is from a warm-temperate forest in Yakushima
+island, Japan, with a total of 193 species and 519 individuals. In
+total, we used 334 woody species and 1365 individuals. The trait
+sampling methodology are slightly different between the Yunnan and the
+Yakushima dataset, which we describe bellow.
+
+\emph{Measurements of disc-based and whole-leaf LMA}
 
@@
 canopy crane (88 m tall with a 60 m long boom). In the HDS, and STF
-sites, we used a 12-m long pruner to collect samples for most of the
+sites, we used 12-m long pruner to collect samples for most of the
 target species. In case of tall individuals that out of the reach of
@@
 branches with the long pruner. In Yakushima, we used 15-m poles for our
-leaf sampling. At least six sun-exposed healthy leaves were sampled from
-each of 3 to 6 individuals for each species. Trait values were averaged
-at the species- and individual-level for the analyses. For
-compound-leaved species, we referred a leaflet (the minimum
-photosynthetic unit) as a single leaf in our study.
+leaf sampling. At least twelve sun-exposed healthy leaves were sampled
+from 3 to 6 individuals for each species. Trait values were averaged at
+the species- and individual-level for the analyses. For compound-leaved
+species, we referred a leaflet (the minimum photosynthetic unit) as a
+single leaf in our study.
 
@@
 petioles and (ii) LMA based on leaf disc avoiding thick veins. Three
-0.6-cm diameter discs were taken from the base, middle and tip of each
-leaf using a hole punch in the Yunnan dataset. Two 1.0-cm diameter discs
-were taken from each leaf were in the Yakushima dataset. Fresh leaf area
-(LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including
-petioles and midribs) was measured using a scanner and ImageJ software
-by the R package \emph{LeafArea}
+small discs were taken from the base, middle and tip of each leaf using
+a 0.6-cm diameter hole punch in the Yunnan dataset. Two large discs from
+each leaf were taken using a 1.0-cm diameter hole punch in the Yakushima
+dataset. Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials
+(whole leaves including petioles and midribs) was measured using scanner
+and ImageJ software by the R package \emph{LeafArea}
 (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}). Fresh leaf
@@
 of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was
-calculated as the ratio of leaf dry mass to fresh leaf area, and LD was
-calculated as the ratio of LMA to LT. We do not present results of LD in
-the main text, because differences between whole-leaf LD and leaf disc
-LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
-and measurement errors of leaf thickness (Appendix S2).
+calculated as the ratio of leaf dry mass to fresh leaf area, and leaf
+tissue density (LD; g cm\textsuperscript{-3}) was calculated as the
+ratio of LMA to LT. We do not present results of LD in the main text,
+because differences between whole-leaf LD and leaf disc LD only depends
+on the ratio between whole-leaf LMA and leaf disc LMA and measurement
+errors of leaf thickness (Appendix S2).
 
@@
 small-leaved, thick and large-leaved species (individuals). Median
-values are as following: small-leaved species (LA \textless{} 29.5
+values are as following: small-leaved species (LA \textless{} 29.3
 cm\textsuperscript{2}), thin-leaved species (LT \textless{} 0.28 mm),
@@
 There was a negative correlation between species mean leaf area and leaf
-thickness (\emph{r} = -0.29, \emph{P} \textless{} 0.05, \emph{n} = 334).
+thickness (\emph{r} = -0.3, \emph{P} \textless{} 0.05, \emph{n} = 335).
 When we pooled all the species, there were significant differences in
@@
 22.1\% greater than disc-based estimates in the arithmetic scale (Table
-1). Intercepts did not differ for small-leaved species (Table 1).
+1). While intercepts did not differ for small-leaved species (Table 1).
 
@@
 correlations with whole-leaf estimates but their
-\emph{R\textsuperscript{2}} values were smaller than those for the
+\emph{R\textsuperscript{2}} values are smaller than those for the
 species means (Fig. 2). Similar to the species-level pattern,
 individuals with thicker and smaller leaves had stronger correlations
-(Fig. 2). The relationships of the whole-leaf LMA : disc leaf LMA ratio
-with total dry mass for the leaf disc (we weighted 2-3 discs together),
-with leaf thickness, and with leaf area were heteroscedastic (unequal
-variance, \emph{P} \textless{} 0.001; Appendix S3). Samples with small
-total dry mass, thin leaves, and larger leaves tended to show greater
-variance (Fig. 2; Appendix S3). The total dry mass of leaf disc was
-positively correlated with both leaf thickness and leaf punch size
-(Appendix S4). Amounts of intraspecific variation (CV; coefficient of
-variation) only weakly matched between whole-leaf and disc-based
-estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.31).
+(Fig. 2). The relationships between whole-leaf LMA : disc leaf LMA and
+total dry mass for the leaf disc (we weighted 2-3 discs together), leaf
+thickness, and leaf area were heteroscedastic (unequal variance,
+\emph{P} \textless{} 0.001). Samples with small total dry mass, thin
+leaves, and larger leaves tended to show greater variance (Fig. 2;
+Appendix S3). The total dry mass of leaf disc was positively correlated
+with both leaf thickness and leaf punch size (Appendix S4). Amounts of
+intraspecific variation (CV; coefficient of variation) only weakly
+matched between whole-leaf and disc-based estimate (Fig. 3;
+\emph{R\textsuperscript{2}} = 0.31).
 
@@
 Disc-based traits explained interspecific variations in whole-leaf LMA
-(\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the
+(\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 335) quite well, and the
 strength of their relationship was approximately same or slightly weaker
@@
 \protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}). Shade
-leaves tend to have thinner leaves than sun leaves because of fewer
-layers of palisade mesophyll cells
+leaves tend to have thinner leaves than sun leaves because of the small
+size and number of palisade mesophyll cells
 (\protect\hyperlink{ref-Terashima2001}{Terashima et al., 2001};
@@
 only the effect of distinct veins on variance in LMA
-(\protect\hyperlink{ref-John2017}{John et al., 2017}) but also technical
-difficulty in measuring tiny weight of discs in lower LMA leaves. We
-found that estimates of whole-leaf and leaf disc LMA diverged when total
-dry mass of leaf discs was small (Fig. 2; Appendices S3), and thus
-thin-leaved species, which have smaller dry mass (Appendix S4), tended
-to showed the low \emph{R\textsuperscript{2}} values especially when we
-used a smaller leaf punch (diameter: 0.6 cm; Appendix S5).
+(\protect\hyperlink{ref-John2017}{John et al., 2017}) but also
+measurement errors for those samples. We found that estimates of
+whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs
+were small (Fig. 2; Appendices S3), and thus thin-leaved species, which
+have smaller dry mass (Appendix S4), tended to showed the low
+\emph{R\textsuperscript{2}} values especially when we used a smaller
+leaf punch (diameter: 0.6 cm; Appendix S5).
 
@@
 values in our results (Figs. 1-3). The mismatch of ITV between
-whole-leaf and disc-based estimate could be ignored in community-level
+whole-leaf and disc-based estimate could be ignored for community-level
 ITV studies (i.e., \protect\hyperlink{ref-Siefert2015}{Siefert et al.,
@@
 quantify extents of ITV for each species, since species with high ITV
-based on leaf-disc estimates do not always have to show high ITV for
+based on leaf-disc estimates do not always have to have high ITV for
 whole-leaf estimates. This problem will be more obvious when one uses
@@
 although the mean values of leaf disc and whole-leaf LMA matched well,
-quantifying trait variation using leaf discs should be considered with
+quantifying trait variation using leaf disc should be considered with
 caution, because variation among leaf discs within the same leaves
@@
 biochemical determinations such as measurements of Rubisco activity
-(\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because the
-photosynthetic activity occurs most in lamina rather than in veins for
+(\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because
+photosynthetic is less active in veins than in mesophyll cells for
 C\textsubscript{3} plants (\protect\hyperlink{ref-Hibberd2002}{Hibberd
@@
 Leaf disc LMA is also the preferred method for quantifying leaf lamina
-density, which avoid effects of veins. However, if the objective is to
-use leaf disc LMA as an alternative for whole-leaf LMA, using an
-appropriate size of leaf punch is important for obtaining stable
-estimates of leaf disc LMA that matches well with whole-leaf LMA.
+density avoiding veins. However, if the objective is to use leaf disc
+LMA as an alternative for whole-leaf LMA, using an appropriate size of
+leaf punch is important for obtaining stable estimates of leaf disc LMA
+that matches well with whole-leaf LMA.
 
@@
 work was funded by the National Natural Science Foundation of China
-(41861144016, 32071735, 31570406, 32171507), the CAS `Light of West
-China' Program, Yunnan Provincial Science and Technology Department
-(2018HB068). PM was supported by financial support from CAS-TWAS
-President's Fellowship for International Doctoral Students. MK was
-supported by CAS President's International Fellowship Initiative
-(2020FYB0003).
+(41861144016, 32071735, 31570406), the `Light of West China' Program of
+CAS, Yunnan Provincial Science and Technology Department (2018HB068). PM
+was supported by financial support from CAS-TWAS President's Fellowship
+for International Doctoral Students. MK was supported by CAS President's
+International Fellowship Initiative (2020FYB0003).
 
@@
 
-\hypertarget{data-availability-statement}{%
-\section{DATA AVAILABILITY
-STATEMENT}\label{data-availability-statement}}
+\hypertarget{data-availability}{%
+\section{DATA AVAILABILITY}\label{data-availability}}
 
@@
 
-\textbf{APPENDIX S1.} Site information.
-
-\textbf{APPENDIX S2.} Generalization for a relationship between ratios
-of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf
-tissue density (LD), and leaf thickness (LT).
-
-\textbf{APPENDIX S3.} Relationships between whole-leaf LMA : disc leaf
-LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and
-(c) leaf area.
-
-\textbf{APPENDIX S4.} Summary of multiple regression for log-transformed
-total dry mass of leaf discs.
-
-\textbf{APPENDIX S5.} Relationships between species mean leaf mass per
-area (LMA) determined by using whole leaves and leaf discs.
-
-\textbf{APPENDIX S6.} Relationships between petiole to leaf dry mass
-ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
-
-\textbf{APPENDIX S7.} Relationships between coefficient of variation
-(CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm
-diameter leaf punch, and (b) 1.0 cm diameter leaf punch.
+\textbf{APPENDIX S1-7.} Site information, generalization for a
+relationship between ratios of disc-based and whole-leaf estimates of
+leaf mass per area (LMA), leaf tissue density (LD), and complete figures
+for mismatch between leaf disc and whole-leaf LMA.
 
@@
 Grubb, P. 1986. Sclerophylls, pachyphylls, and pycnophylls: {The} nature
-and significance of hard leaf surface. \emph{Insects and the Plant
-Surface}: 137--150.
+and significance of hard leaf surface. \emph{Insects and the plant
+surface}: 137--150.
 
@@
 Julious, S. A., and C. A. Debarnot. 2000. Why are pharmacokinetic data
-summarized by arithmetic means? \emph{Journal of Biopharmaceutical
-Statistics} 10: 55--71.
+summarized by arithmetic means? \emph{Journal of biopharmaceutical
+statistics} 10: 55--71.
 
@@
 Parry, M. A., P. J. Andralojc, S. Khan, P. J. Lea, and A. J. Keys. 2002.
-Rubisco activity: Effects of drought stress. \emph{Annals of Botany} 89:
+Rubisco activity: Effects of drought stress. \emph{Annals of botany} 89:
 833--839.
@@
 \endhead
-All & 0.97 {[}0.94, 1.01{]} & \textbf{0.09 {[}0.02, 0.16{]}} & 0.87 \\
+All & 0.98 {[}0.94, 1.01{]} & \textbf{0.09 {[}0.02, 0.16{]}} & 0.87 \\
 Thick-large & 0.93 {[}0.85, 1.03{]} & \textbf{0.19 {[}0.01, 0.37{]}} &
@@
 
-\textbf{Table. 1.} Relationships between species mean leaf leaf mass per
-area (LMA) values determined by using whole leaves and leaf discs across
-all species and within species groups. Data are divided into four
-categories based on the quartiles: thin and small-leaved, thin and
-large-leaved, thick and small-leaved, and thick and large-leaved
-species. SMA slope (95\% CI), intercepts (95\% CI), and
-\emph{R\textsuperscript{2}} values are reported. Statistically
-significant differences (\emph{P} \textless{} 0.05) in slopes and
-intercepts are highlighted in bold.
+\textbf{Table. 1.} Relationships between species mean leaf trait values
+determined by using whole leaves and leaf discs across all species and
+within species groups. Data are divided into four categories based on
+the quartiles: thin and small-leaved, thin and large-leaved, thick and
+small-leaved, and thick and large-leaved species. SMA slope (95\% CI),
+intercepts (95\% CI), and \emph{R\textsuperscript{2}} values are
+reported. Statistically significant differences (\emph{P} \textless{}
+0.05) in slopes and intercepts are highlighted in bold.
 

### 2021-12-15 ms/SI.Rmd
first commit

---
title: "Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)"
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linenumbers
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

```{r caching, include=FALSE, eval=TRUE}
library(knitr)
library(tidyverse)
library(methods)
source("../scripts/rmd_func.R")
basename <- "LMA_method"
opts_chunk$set(fig.path = paste("figs/", sep=""))
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE,
               comment = NA, verbose = TRUE, echo=FALSE)
# PDF-based figures
opts_chunk$set(dev='pdf')

# https://github.com/haozhu233/kableExtra/issues/477
options(kableExtra.auto_format = FALSE)
library(kableExtra)

val <- yaml::yaml.load_file("../values.yml")
```

# Appendix S1:

Site information.
MAT: mean annual temperature,
MAP: mean annual precipitation,
SPEI: Standardized Precipitation Evapotranspiration Index.

| Site name  | Vegetation                             | Elevation (m) | Locations          | MAT (℃) | MAP (mm) | Dry period (month) | Canopy height (m) | Species number  |
|------------|----------------------------------------|---------------|--------------------|---------|----------|--------------------|-------------------|-----------------|
| Bubeng     | Tropical forest (TRF)                  | 780           | 21°37'N, 101°35' E | 21      | 1532     | 6                  | 35-45             | `r val$TRF`     |
| Ailao-shan | Subtropical evergreen wet forest (STF) | 2500          | 24°32'N,101°01'E   | 11.7    | 1931     | -                  | 25                | `r val$STF`     |
| Yuanjiang  | Hot-dry savanna  (HDS)                 | 480           | 23°28'N, 102°10'E  | 24.7    | 732.8    | 6                  | 4-6               | `r val$HDS`     |
| Yakushima  | Warm-temperate forest        | 14 - 1748     | 30°38'N, 130°62'E  | 19.4    | 4477     | -                  |       -            | `r val$yaku_sp` |

The site information and climate data referred to @Fei2018 and @Song2017.
The 6-month-SPEI data were extracted from the Global SPEI database (http://spei.csic.es/map/maps.html#months=1#month=7#year=2019).

\newpage

# Appendix S2:

Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
For the *i* tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:

$$
\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} \frac{LTw_i}{LTd_i}
$$

where *d* indicates disc-based estimates, *w* indicates whole-leaf based estimates.

Because thickness is measured on leaf lamina whether one uses a leaf disc or a whole-leaf, the expected ratio between thickness for a leaf disc and a whole-leaf should be 1.
The above relationship, therefore, can be rewritten using lognormally distributed multiplicative error ($\epsilon_i$) on the arithmetic scale:

$$
\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim N(0, \sigma^2).
$$

LMA requires two times measurements (mass and area) and LD requires three time measurements (mass, area and thickness), and thus variance in the ratio of whole-leaf LD and leaf disc LD should be greater than that of LMA.

As we expected LD, showed the slightly smaller *R^2^* value than LMA (Figure below) in the Yunnan dataset.
We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LTw~i~/LTd~i~ =1), the scatter plots will be identical for LMA and LD.
Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.

![](../figs/fig1.png){ width="600" style="display: block; margin: 0 auto" }

Figure: Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (*P* < 0.001).

\newpage

# Appendix S3:

Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and (c) leaf area.
(b) and (c) follow the same legend.
All the relationships were heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together in (a)).
Samples with small total dry mass, thin leaves, and larger leaves tended to show greater variance.

![](../figs/LMAratio2.png){style="display: block; margin: 0 auto" }

\newpage

# Appendix S4:

Summary of multiple regression for log-transformed total dry mass of leaf discs.
The leaf punch size is described as an effect of '1.0 cm diameter' compared with '0.6 cm diameter'.

```{r, eval=TRUE, echo=FALSE}
tree <- read_csv("../data/tree_data.csv")

tree2 <- tree |>
  filter(!is.na(LMAdisc)) |>
  filter(!is.na(LMAleaf)) |>
  filter(!is.na(LTleaf)) |>
  rename(LT = LTleaf) |>
  rename(LA = LAleaf) |>
  mutate(Dry_mass_disc2 = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4 / 2,
   TRUE ~ LMAdisc * 0.889 * 10^-4 / 3
                )) |>
  mutate(Dry_mass_disc = case_when(
   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4,
   TRUE ~ LMAdisc * 0.889 * 10^-4
                )) |>
  mutate(PCH = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm"))

fit <- lm(log(Dry_mass_disc) ~ scale(log(LT)) + scale(log(LA)) + PCH, tree2)

s <- summary(fit)
tb <- s$coefficients |> round(3) |> signif(3)
colnames(tb) <- c("Estimate", "SE", "t-value", "*P* value")
tb[,4] <- ifelse(tb[,4] < 0.001, "< 0.001", tb[,4])
rownames(tb)[2] <- "log(Leaf thickness)"
rownames(tb)[3] <- "log(Leaf area)"
rownames(tb)[4] <- "Large leaf punch"

tb |>
  kable() |>
  kable_styling()
```

\newpage

# Appendix S5:

Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
Species groups are divided into four categories on the basis of the medians of the leaf size and leaf thickness across all the species.
Estimates obtained by different leaf punches are plotted separately in different colors.
All the correlations are significant (*P* < 0.001).

![](../figs/LMA_sp_gr_both.png){ width="600" style="display: block; margin: 0 auto" }

# Appendix S6:

Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
Blue solid lines indicate ordinary least squares (OLS) regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (*P* < 0.001).

![](../figs/petiole.png){ width="600" style="display: block; margin: 0 auto" }

\newpage

# Appendix S7:

Relationships between coefficient of variation (CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and (b) 1.0 cm diameter leaf punch.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (*P* < 0.01).
Note that the axes are square root scales.

![](../figs/fig_cv2.png){ width="600" style="display: block; margin: 0 auto" }

\newpage
# LITERATURE CITED

### 2021-12-15 ms/SI.tex
first commit

--- 2021-12-15 ms/LMA_method_old.tex
@@
 \hypersetup{
+  pdftitle={Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)},
   hidelinks,
@@
 
+\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
+mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
 \date{}
@@
 \usepackage{titling}
-\title{}
+\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
+mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
 \author{}
@@
   \fancyfoot{}
-  \lhead[]{}
+  \lhead[]{Maenpuen et al.~Appendix S1-7: Sources and consequences of
+mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
   \chead[]{}
-  \rhead[]{}
+  \rhead[Maenpuen et al.~Appendix S1-7: Sources and consequences of
+mismatch between leaf disc and whole-leaf leaf mass per area (LMA)]{}
   %\lfoot[\thepage]{}
@@
 
-Sources and consequences of mismatch between leaf disc and whole-leaf
-leaf mass per area (LMA)
+\hypertarget{appendix-s1}{%
+\section{Appendix S1:}\label{appendix-s1}}
 
-\[ \]
+Site information. MAT: mean annual temperature, MAP: mean annual
+precipitation, SPEI: Standardized Precipitation Evapotranspiration
+Index.
 
-Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
-Katabuchi\textsuperscript{1,*}, Yusuke Onoda\textsuperscript{4}, Cong
-Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
-Chen\textsuperscript{1,3}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0741}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.2469}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0926}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0556}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0617}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1173}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1049}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Site name
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Vegetation
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Elevation (m)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Locations
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+MAT (℃)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+MAP (mm)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Dry period (month)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Canopy height (m)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Species number
+\end{minipage} \\
+\midrule
+\endhead
+Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35' E & 21 & 1532 &
+6 & 35-45 & 60 \\
+Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 &
+24°32'N,101°01'E & 11.7 & 1931 & - & 25 & 47 \\
+Yuanjiang & Hot-dry savanna (HDS) & 480 & 23°28'N, 102°10'E & 24.7 &
+732.8 & 6 & 4-6 & 34 \\
+Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 19.4
+& 4477 & - & - & 193 \\
+\bottomrule
+\end{longtable}
 
-\[ \]
-
-\textsuperscript{1} CAS Key Laboratory of Tropical Forest Ecology,
-Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences,
-Menglun, Yunnan 666303, China
-
-\textsuperscript{2} University of Chinese Academy of Sciences, Beijing
-100049, China
-
-\textsuperscript{3} Center of Plant Ecology, Core Botanical Gardens,
-Chinese Academy of Sciences, Yunnan 666303, China
-
-\textsuperscript{4} Graduate School of Agriculture, Kyoto University,
-Kyoto 606-8502, Japan
-
-\[ \]
-
-\textbf{Corresponding Authors}:
-
-Masatoshi Katabuchi
-
-E-mail:
-\href{mailto:mattocci27@gmail.com}{\nolinkurl{mattocci27@gmail.com}}
-
-Jiao-Lin Zhang
-
-Tel: +86 691 871 3046; Fax: +86 691 871 5070; E-mail:
-\href{mailto:zjl@xtbg.org.cn}{\nolinkurl{zjl@xtbg.org.cn}}
-
-\[ \]
-
-Manuscript received \_\_\_\_\_\_\_; revision accepted \_\_\_\_\_\_\_.
-
-\textbf{Running title}: Leaf disc and whole-leaf LMA
+The site information and climate data referred to Fei et al.
+(\protect\hyperlink{ref-Fei2018}{2018}) and Song et al.
+(\protect\hyperlink{ref-Song2017}{2017}). The 6-month-SPEI data were
+extracted from the Global SPEI database
+(\url{http://spei.csic.es/map/maps.html\#months=1\#month=7\#year=2019}).
 
@@
 
-\hypertarget{abstract}{%
-\section{ABSTRACT}\label{abstract}}
+\hypertarget{appendix-s2}{%
+\section{Appendix S2:}\label{appendix-s2}}
 
-\textbf{PREMISE:} Leaf mass per area (LMA), which is the key trait in
-leaf economic spectrum and plant growth analysis, is measured from leaf
-discs or whole leaves. These differences in the measurement methods may
-lead to large differences in the estimates of LMA values.
+Generalization for a relationship between ratios of disc-based and
+whole-leaf estimates of leaf mass per area (LMA), leaf tissue density
+(LD), and leaf thickness (LT). For the \emph{i} tree individual or
+species, the relationship between ratios of disc-based and whole-leaf
+estimates of LMA, LD, and LT is:
 
-\textbf{METHODS:} We determined LMA using leaf discs and whole-leaf
-(including petiole) for 334 woody species from across biomes (tropics,
-subtropics, savanna, and temperate) to examine what extent whole-leaf
-and leaf disc LMA match, whether the differences in the estimates are
-associated with leaf size and thickness, and whether intraspecifc
-variation for each species match.
+\[
+\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} \frac{LTw_i}{LTd_i}
+\]
 
-\textbf{RESULTS:} Disc-based estimates of species and individual mean
-LMA matched well whole-leaf estimates. Thin and large leaves had weaker
-correlations between leaf disc and whole-leaf estimates. Variability of
-LMA estimates within species (i.e., amount of intraspecific variation)
-only weakly matched between whole-leaf and disc-based estimates
-(\emph{R\textsuperscript{2}} = 0.31). We also found that sample with
-small total dry mass of leaf discs tended to show greater differences
-between leaf disc and whole-leaf LMA.
+where \emph{d} indicates disc-based estimates, \emph{w} indicates
+whole-leaf based estimates.
 
-\textbf{CONCLUSIONS:} Mean values of leaf disc LMA are generally good
-proxies for mean values of whole-leaf LMA with appropriate calibration
-(9.4\% differences in our samples), but their accuracy depends on leaf
-size, leaf thickness, and sizes of leaf punch. Therefore, using
-appropriate sizes of leaf punch is important for obtaining stable
-estimates of leaf disc LMA that matches well with whole-leaf LMA.
-Quantifying trait variation using leaf disc should be considered with
-caution.
+Because thickness is measured on leaf lamina whether one uses a leaf
+disc or a whole-leaf, the expected ratio between thickness for a leaf
+disc and a whole-leaf should be 1. The above relationship, therefore,
+can be rewritten using lognormally distributed multiplicative error
+(\(\epsilon_i\)) on the arithmetic scale:
 
-\textbf{Key words:}
+\[
+\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim N(0, \sigma^2).
+\]
 
-intraspecific variation, leaf density, leaf economic spectrum, leaf
-heterogeneity, leaf punch, leaf size, leaf thickness, petiole, specific
-leaf area, within-leaf variation
+LMA requires two times measurements (mass and area) and LD requires
+three time measurements (mass, area and thickness), and thus variance in
+the ratio of whole-leaf LD and leaf disc LD should be greater than that
+of LMA.
 
-\hypertarget{introduction}{%
-\section{INTRODUCTION}\label{introduction}}
+As we expected LD, showed the slightly smaller
+\emph{R\textsuperscript{2}} value than LMA (Figure below) in the Yunnan
+dataset. We have independent measurement for thickness for leaf discs
+and whole-leaves in the Yunnan dataset. If we use the same leaf
+thickness values for leaf discs and whole-leaves (i.e.,
+LTw\textsubscript{i}/LTd\textsubscript{i} =1), the scatter plots will be
+identical for LMA and LD. Consequently, we do not perform further
+analyses for LD, because differences between whole-leaf LD and leaf disc
+LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
+and measurement errors of leaf thickness.
 
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue
-density (LD), describes how much biomass is invested into given
-photosynthetic leaf area thus reflecting a cost for light interception,
-which is the key trait of the leaf economic spectrum (LES)
-(\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
-\protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009};
-\protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}). Generally,
-resource-acquisitive species (fast-growing species) tend to have low LMA
-values, showing high photosynthesis, high nutrients, and often have fast
-leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al.,
-2004}). In contrast, resource-conservative species (slow-growing
-species) often have higher LMA values with the opposite patterns
-(\protect\hyperlink{ref-Garnier1994}{Garnier and Laurent, 1994};
-\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
-\protect\hyperlink{ref-Reich2014}{Reich, 2014};
-\protect\hyperlink{ref-Diaz2016}{Díaz et al., 2016}). The LMA is also
-frequently used in plant growth analysis
-(\protect\hyperlink{ref-Evans1972}{Evans, 1972};
-\protect\hyperlink{ref-Poorter2014}{Poorter et al., 2014};
-\protect\hyperlink{ref-Falster2018}{Falster et al., 2018}) because
-relative growth rates (RGR) can be decomposed into the product of net
-assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR
-\(\times\) LMR \(\times\) LMA\textsuperscript{-1}). Another appealing
-feature of LMA is that it is relatively easy to measure large numbers of
-species (i.e., `soft' trait, \protect\hyperlink{ref-Diaz2004}{Díaz et
-al., 2004}). Therefore, LMA has been of interests to ecologists and
-widely used since the first report more than a century ago
-(\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
+\includegraphics[width=6.25in,height=\textheight]{../figs/fig1.png}
 
-LMA values are measured from either 1) a whole leaf including or
-excluding petioles, and 2) a leaf disc excluding all major veins or
-petioles
-(\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et
-al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}).
-Although some studies do not make clear what protocol was followed,
-these differences in the measurement methods may lead to large
-discrepancies in the estimates of LMA values because the major vein
-allocation (major vein, which includes first to second or third-order
-veins, volume per area) has been reported to be one of the main
-determinants for the variation in LMA
-(\protect\hyperlink{ref-John2017}{John et al., 2017}). Since larger
-leaves should invest more of their mass into dense midribs and petiole
-for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al.,
-2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves
-have clearly visible and large-diameter veins with less uniform leaf
-structure {[}i.e., kite-type leaves; Grubb
-(\protect\hyperlink{ref-Grubb1986}{1986}){]}, discrepancies in the
-estimates of whole-leaf LMA and leaf disc LMA might be greater for
-larger and thinner leaves. If leaf disc LMA largely underestimates
-whole-leaf LMA, some calibrations may be required to combine or compare
-those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et
-al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}). If
-divergencies between the estimates based on the different methods are
-large (i.e., low \emph{R\textsuperscript{2}} values), this is difficult
-to calibrate and should inflate errors in the subsequent analyses. To
-date, however, only a database from a single region, Panama Plant Traits
-Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is
-available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al.,
-2020}) that have both estimates of LMA from small leaf discs and whole
-leaves including petioles, limiting of our understanding of under what
-conditions estimates of LMA from leaf discs are reliable estimates of
-whole-leaf LMA.
+Figure: Relationships between species mean leaf mass per area (LMA) and
+leaf tissue density (LD) determined by using whole leaves and leaf discs
+for the Yunnan dataset that has both leaf thickness for leaf discs and
+whole leaves. Dashed lines indicate 1:1 lines. Blue solid lines indicate
+standardized major axis regressions. The 95\% confidence intervals are
+presented as the shaded area. All the correlations are significant
+(\emph{P} \textless{} 0.001).
 
-Given that leaf disc samples have more sources of intraspecific trait
-variation (ITV) than whole-leaf samples, the effects of discrepancies
-between whole-leaf LMA and leaf disc LMA might be large when ITV is
-quantified as a coefficient of variance (CV). Sources of ITV for
-whole-leaf samples is variation among individuals within the same
-species and variation among leaves within the same individuals
-(\protect\hyperlink{ref-Messier2010}{Messier et al., 2010},
-\protect\hyperlink{ref-Messier2017}{2017}). An additional source of
-trait variation for leaf disc samples is variation among leaf discs
-within the same leaves. Thus, extents of ITV for each species based on
-whole-leaf and leaf discs samples may not match. Despite the importance
-of ITV in community ecology
-(\protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013};
-\protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), the effect
-of different measurement methods on the extent of ITV has been largely
-ignored.
+\newpage
 
-In this study, we aimed to investigate to which extent whole-leaf
-(including petiole) and leaf disc LMA match, whether the relationships
-between whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf
-thicknesses, and whether amounts of intraspecifc variations for each
-match between whole-leaf and leaf disc based estimates. We collected a
-total of 334 woody species from across biomes (tropics, subtropics,
-savanna, and warm-temperate) to cover the wide range of geography. We
-predicted that the overall relationship between whole-leaf LMA and disc
-LMA would be weaker than previous reported LMA data
-(\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
-0.92 for leaf laminas in Onoda et al.
-(\protect\hyperlink{ref-Onoda2011}{2011})) because we collected data
-with various leaf sizes from the wide range of climates. We also
-predicted that species with larger and/or thinner leaves would show
-weaker correlations. Finally, we predicted that amounts of intraspecifc
-variations for each species do not match well between whole-leaf and
-leaf disc based estimates.
+\hypertarget{appendix-s3}{%
+\section{Appendix S3:}\label{appendix-s3}}
 
-\hypertarget{materials-and-methods}{%
-\section{MATERIALS AND METHODS}\label{materials-and-methods}}
+Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry
+mass for the leaf disc, (b) leaf thickness, and (c) leaf area. (b) and
+(c) follow the same legend. All the relationships were heteroscedastic
+(unequal variance, \emph{p} \textless{} 0.001; all the samples were
+analyzed together in (a)). Samples with small total dry mass, thin
+leaves, and larger leaves tended to show greater variance.
 
-\emph{Data sources}
+\includegraphics{../figs/LMAratio2.png}
 
-We used newly compiled individual-level plant datasets from broad
-regions to examine the relationship between leaf traits estimates based
-on whole-leaf and leaf disc across wide ranges of geography in China and
-Japan (Table S1). First, the Yunnan dataset is from forest plots in
-Yunnan province, Southwest China, which includes a tropical rain forest
-(TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen
-wet forest (STF), with a total of 141 species and 846 individuals.
-Second, the Yakushima data is from a warm-temperate forest in Yakushima
-island, Japan, with a total of 193 species and 519 individuals. In
-total, we used 334 woody species and 1365 individuals. The trait
-sampling methodology are slightly different between the Yunnan and the
-Yakushima dataset, which we describe bellow.
+\newpage
 
-\emph{Measurements of disc-based and whole-leaf LMA}
+\hypertarget{appendix-s4}{%
+\section{Appendix S4:}\label{appendix-s4}}
 
-At the TRF site, we collected leaf samples from trees within reach of a
-canopy crane (88 m tall with a 60 m long boom). In the HDS, and STF
-sites, we used 12-m long pruner to collect samples for most of the
-target species. In case of tall individuals that out of the reach of
-pruner, we used a rope climbing to reach the canopy, then sampled
-branches with the long pruner. In Yakushima, we used 15-m poles for our
-leaf sampling. At least twelve sun-exposed healthy leaves were sampled
-from 3 to 6 individuals for each species. Trait values were averaged at
-the species- and individual-level for the analyses. For compound-leaved
-species, we referred a leaflet (the minimum photosynthetic unit) as a
-single leaf in our study.
+Summary of multiple regression for log-transformed total dry mass of
+leaf discs. The leaf punch size is described as an effect of `1.0 cm
+diameter' compared with `0.6 cm diameter'.
 
-To determine what extent LMA values were affected by the different
-methods, LMA were determined (i) LMA based on a whole leaf including
-petioles and (ii) LMA based on leaf disc avoiding thick veins. Three
-small discs were taken from the base, middle and tip of each leaf using
-a 0.6-cm diameter hole punch in the Yunnan dataset. Two large discs from
-each leaf were taken using a 1.0-cm diameter hole punch in the Yakushima
-dataset. Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials
-(whole leaves including petioles and midribs) was measured using scanner
-and ImageJ software by the R package \emph{LeafArea}
-(\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}). Fresh leaf
-thickness (LT; mm) was measured using a micrometer in three points at
-the base, middle and tip of the leaf using a micrometer (Mitutoyo
-293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at
-0.001 mm. Thickness of each leaf disc was also measured for the Yunnan
-dataset but not for the Yakushima dataset, which enables us to estimate
-whole-leaf and leaf disc leaf tissue density (LD; g
-cm\textsuperscript{-3}) separately in the Yunnan dataset. Leaf dry mass
-(whole leaves including petioles and midribs, and leaf discs) was
-recorded after drying 80°C for over 48 h to constant weight using an
-electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a
-precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
-and petiole dry mass were also determined separately (81 out of 193
-species) to quantify leaf support costs. Dry mass for leaf discs were
-recorded 2-3 discs together for each leaf. Based on those measurements
-of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was
-calculated as the ratio of leaf dry mass to fresh leaf area, and leaf
-tissue density (LD; g cm\textsuperscript{-3}) was calculated as the
-ratio of LMA to LT. We do not present results of LD in the main text,
-because differences between whole-leaf LD and leaf disc LD only depends
-on the ratio between whole-leaf LMA and leaf disc LMA and measurement
-errors of leaf thickness (Appendix S2).
+\begin{longtable}[]{@{}lllll@{}}
+\toprule
+& Estimate & SE & t-value & \emph{P} value \\
+\midrule
+\endhead
+(Intercept) & -4.86 & 0.012 & -410 & \textless{} 0.001 \\
+log(Leaf thickness) & 0.223 & 0.009 & 23.7 & \textless{} 0.001 \\
+log(Leaf area) & -0.092 & 0.01 & -9.27 & \textless{} 0.001 \\
+Large leaf punch & 0.391 & 0.021 & 18.7 & \textless{} 0.001 \\
+\bottomrule
+\end{longtable}
 
-\emph{Statistical analyses}
+\newpage
 
-Bivariate trait relationships between disc-based and whole-leaf
-log-transformed LMA were summarized with variance explained
-(\emph{R\textsuperscript{2}}) based on Pearson correlations and with
-standardized major axis (SMA) regressions
-(\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the
-samples and different leaf area and thickness groups. Species and
-individual groups were divided into four categories based on the medians
-of leaf area and leaf thickness across all species and all individuals,
-respectively: thin and small-leaved, thin and large-leaved, thick and
-small-leaved, thick and large-leaved species (individuals). Median
-values are as following: small-leaved species (LA \textless{} 29.3
-cm\textsuperscript{2}), thin-leaved species (LT \textless{} 0.28 mm),
-small-leaved individuals (LA \textless{} 34.7 cm\textsuperscript{2}),
-and thin-leaved individuals (LT \textless{} 0.26 mm).
+\hypertarget{appendix-s5}{%
+\section{Appendix S5:}\label{appendix-s5}}
 
-The amount of intraspecific variation of LMA was calculated using
-coefficient of variation of log-normally distributed data;
-\(CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}\), where \(s_{\mathrm{ln}}\) is
-the sample standard deviation in the log-transformed data
-(\protect\hyperlink{ref-Julious2000}{Julious and Debarnot, 2000}). We
-also considered CV on the arithmetic scale; \(CV = s/\bar{x}\), where
-\(s\) is the sample standard deviation and \(\bar{x}\) is the sample
-mean. However, these two different CV calculations only negligibly
-altered the bivariate relationship and did not change our conclusion,
-and thus we will report CV of log-normally distributed data in the main
-text.
+Relationships between species mean leaf mass per area (LMA) determined
+by using whole leaves and leaf discs. Species groups are divided into
+four categories on the basis of the medians of the leaf size and leaf
+thickness across all the species. Estimates obtained by different leaf
+punches are plotted separately in different colors. All the correlations
+are significant (\emph{P} \textless{} 0.001).
 
-SMA analyses were run using the R package \emph{smatr}
-(\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this
-included tests for slope heterogeneity and elevation differences between
-disc-based and whole-leaf estimates of LMA values. Confidence intervals
-of SMA estimates were based on 1000 bootstraps. All statistical analyses
-were conducted in R version 4.1.2
-(\protect\hyperlink{ref-RCoreTeam2021}{R Core Team, 2021}).
+\includegraphics[width=6.25in,height=\textheight]{../figs/LMA_sp_gr_both.png}
 
-\hypertarget{results}{%
-\section{RESULTS}\label{results}}
+\hypertarget{appendix-s6}{%
+\section{Appendix S6:}\label{appendix-s6}}
 
-Disc-based estimates of species mean LMA matched well whole-leaf
-estimates (Table 1; \emph{R\textsuperscript{2}} = 0.87 for all species).
-Species with thicker and smaller leaves had stronger correlations
-between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
-There was a negative correlation between species mean leaf area and leaf
-thickness (\emph{r} = -0.3, \emph{P} \textless{} 0.05, \emph{n} = 335).
-When we pooled all the species, there were significant differences in
-intercepts for species mean LMA (Table 1), suggesting that the
-whole-leaf estimates of LMA were 9.4\% greater than disc-based estimates
-in the arithmetic scale. Large-leaved species also had significant
-positive intercepts, suggesting that whole-leaf estimates of LMA were
-22.1\% greater than disc-based estimates in the arithmetic scale (Table
-1). While intercepts did not differ for small-leaved species (Table 1).
+Relationships between petiole to leaf dry mass ratio and (a) leaf area
+and (b) whole-leaf to leaf disc LMA ratio. Blue solid lines indicate
+ordinary least squares (OLS) regressions. The 95\% confidence intervals
+are presented as the shaded area. All the correlations are significant
+(\emph{P} \textless{} 0.001).
 
-Disc-based estimates of individual mean LMA also showed positive
-correlations with whole-leaf estimates but their
-\emph{R\textsuperscript{2}} values are smaller than those for the
-species means (Fig. 2). Similar to the species-level pattern,
-individuals with thicker and smaller leaves had stronger correlations
-(Fig. 2). The relationships between whole-leaf LMA : disc leaf LMA and
-total dry mass for the leaf disc (we weighted 2-3 discs together), leaf
-thickness, and leaf area were heteroscedastic (unequal variance,
-\emph{P} \textless{} 0.001). Samples with small total dry mass, thin
-leaves, and larger leaves tended to show greater variance (Fig. 2;
-Appendix S3). The total dry mass of leaf disc was positively correlated
-with both leaf thickness and leaf punch size (Appendix S4). Amounts of
-intraspecific variation (CV; coefficient of variation) only weakly
-matched between whole-leaf and disc-based estimate (Fig. 3;
-\emph{R\textsuperscript{2}} = 0.31).
+\includegraphics[width=6.25in,height=\textheight]{../figs/petiole.png}
 
-\hypertarget{discussion}{%
-\section{DISCUSSION}\label{discussion}}
+\newpage
 
-Disc-based traits explained interspecific variations in whole-leaf LMA
-(\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 335) quite well, and the
-strength of their relationship was approximately same or slightly weaker
-than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} =
-409, for whole-leaves in Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
-0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
-(\protect\hyperlink{ref-Onoda2011}{2011})). Standardized major axis
-(SMA) regression analysis showed significantly greater intercepts when
-all the species were pooled (9.4\% differences) or large-leaved species
-were used (22.1\% differences). Together, these findings suggest that
-disc-based estimates can be generally used as good proxies for their
-whole-leaf estimates with appropriate calibration. However, the strength
-of correlations highly depended on leaf area, thickness (Fig. 1) and
-sizes of leaf punches (Appendix S3 and S5).
+\hypertarget{appendix-s7}{%
+\section{Appendix S7:}\label{appendix-s7}}
 
-Larger leaves generally invest disproportionally more mass into dense
-midribs and major veins for support
-(\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006},
-\protect\hyperlink{ref-Niinemets2007}{2007};
-\protect\hyperlink{ref-Sack2012}{Sack et al., 2012}), and thinner leaves
-have distinct veins and have kite-type appearances
-(\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}). As we predicted,
-thicker and/or smaller leaves tended to show greater
-\emph{R\textsuperscript{2}} values between whole-leaf and leaf disc
-estimates (Figs 1. and 2). Large-leaved species had greater whole-leaf
-LMA than leaf disc LMA (Table 1), which is consistent with the pattern
-of large leaves disproportionately investing in more leaf veins and/or
-petioles. This is also supported by the subset of our dataset in which
-we measured leaf lamina and petiole dry mass separately. We confirmed
-that leaf disc and whole-leaf LMA estimate diverged for species with
-greater investment in petiole dry mass, and large-leaved species tended
-to have greater investment for petiole dry mass than small-leaved
-species (Appendix S6).
+Relationships between coefficient of variation (CV) in LMA determined by
+using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and
+(b) 1.0 cm diameter leaf punch. Dashed lines indicate 1:1 lines. Blue
+solid lines indicate standardized major axis regressions. The 95\%
+confidence intervals are presented as the shaded area. All the
+correlations are significant (\emph{P} \textless{} 0.01). Note that the
+axes are square root scales.
 
-Meanwhile, our results are seemingly inconsistent with a previous study
-that used thin and soft leaves and found high
-\emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92;
-Kraft et al. (\protect\hyperlink{ref-Kraft2008}{2008})). Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}) used sapling leaves under
-closed canopy that are thinner than adult leaves
-(\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010};
-\protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}). Shade
-leaves tend to have thinner leaves than sun leaves because of the small
-size and number of palisade mesophyll cells
-(\protect\hyperlink{ref-Terashima2001}{Terashima et al., 2001};
-\protect\hyperlink{ref-Onoda2008}{Onoda et al., 2008}). The relatively
-low \emph{R\textsuperscript{2}} values for thin-leaved species and
-individuals in our study compared to the previous study may suggest not
-only the effect of distinct veins on variance in LMA
-(\protect\hyperlink{ref-John2017}{John et al., 2017}) but also
-measurement errors for those samples. We found that estimates of
-whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs
-were small (Fig. 2; Appendices S3), and thus thin-leaved species, which
-have smaller dry mass (Appendix S4), tended to showed the low
-\emph{R\textsuperscript{2}} values especially when we used a smaller
-leaf punch (diameter: 0.6 cm; Appendix S5).
+\includegraphics[width=6.25in,height=\textheight]{../figs/fig_cv2.png}
 
-Even though we used the same species, the same individuals and the same
-trait (LMA) to estimate the extents of intraspecific trait variation
-(ITV), the explained variance of the relationship between whole-leaf and
-disc-based estimate was surprisingly small (Fig. 3;
-\emph{R\textsuperscript{2}} = 0.31). This is probably because leaf disc
-samples have more sources of ITV than whole-leaf samples (i.e.,
-variation among leaf discs within the same leaves). Although there are
-not many studies that quantified trait variation within a single leaf, a
-previous study that used a giant leaved species \emph{Alocasia
-macrorrhiza}, suggests that LMA varied within leaves due to reduced
-water supply and demand from midrib to outer regions
-(\protect\hyperlink{ref-Li2013a}{Li et al., 2013}). Because calculating
-the mean values generally diminishes the effect of within-sample
-variation, the relationship between disc-based estimates of individual
-mean LMA and its whole-leaf estimates will be stronger than the
-relationship between leaf disc CV and whole-leaf CV. Thus, leaf disc and
-whole-leaf estimates of species means will show the strongest
-relationship. This is consistent with the \emph{R\textsuperscript{2}}
-values in our results (Figs. 1-3). The mismatch of ITV between
-whole-leaf and disc-based estimate could be ignored for community-level
-ITV studies (i.e., \protect\hyperlink{ref-Siefert2015}{Siefert et al.,
-2015}), which quantify the total variance of ITV within communities.
-However, it is likely to change patterns for species-level ITV studies
-(i.e., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}), which
-quantify extents of ITV for each species, since species with high ITV
-based on leaf-disc estimates do not always have to have high ITV for
-whole-leaf estimates. This problem will be more obvious when one uses
-smaller leaf punches (Appendix S7).
-
-The present study was designed to examine the extent to which whole leaf
-and leaf disc LMA matched. Our study shows that mean values of leaf disc
-LMA is generally a good proxy for mean values of whole-leaf LMA.
-However, larger and thinner leaves tended to show the large
-discrepancies between the leaf disc and whole-leaf estimates, and thus
-when one needs to mix leaf disc LMA and whole-leaf LMA in a single
-analysis (e.g., meta-analysis), appropriate calibrations are necessary.
-Although our study was not designed to evaluate the effects of diameter
-sizes of leaf punches, the sizes of leaf punches are also the important
-sources of variance between whole-leaf and leaf disc LMA. This is
-probably because small dry mass inflates measurement errors and small
-leaf disc size inflates trait variation within leaves. Additionally,
-although the mean values of leaf disc and whole-leaf LMA matched well,
-quantifying trait variation using leaf disc should be considered with
-caution, because variation among leaf discs within the same leaves
-(including measurement errors) seems to be large. Leaf discs, which can
-target leaf lamina avoiding leaf veins, are useful and essential for
-biochemical determinations such as measurements of Rubisco activity
-(\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because
-photosynthetic is less active in veins than in mesophyll cells for
-C\textsubscript{3} plants (\protect\hyperlink{ref-Hibberd2002}{Hibberd
-and Quick, 2002}; \protect\hyperlink{ref-Gao2018}{Gao et al., 2018}).
-Leaf disc LMA is also the preferred method for quantifying leaf lamina
-density avoiding veins. However, if the objective is to use leaf disc
-LMA as an alternative for whole-leaf LMA, using an appropriate size of
-leaf punch is important for obtaining stable estimates of leaf disc LMA
-that matches well with whole-leaf LMA.
-
-\hypertarget{acknowledgments}{%
-\section{ACKNOWLEDGMENTS}\label{acknowledgments}}
-
-The authors thank Lian-Bin Tao and Peng-Yun Yan for field work. This
-work was funded by the National Natural Science Foundation of China
-(41861144016, 32071735, 31570406), the `Light of West China' Program of
-CAS, Yunnan Provincial Science and Technology Department (2018HB068). PM
-was supported by financial support from CAS-TWAS President's Fellowship
-for International Doctoral Students. MK was supported by CAS President's
-International Fellowship Initiative (2020FYB0003).
-
-\hypertarget{author-contributions}{%
-\section{AUTHOR CONTRIBUTIONS}\label{author-contributions}}
-
-PM, MK, and YJC conceived the study; PM, YO, and YJC collected data; MK
-and CZ performed the analysis; MK and YJC led the writing of the paper;
-and all authors contributed to revisions.
-
-\hypertarget{data-availability}{%
-\section{DATA AVAILABILITY}\label{data-availability}}
-
-Data and codes for this manuscript are archived and available on Zenodo
-(XXX).
-
-\hypertarget{supporting-information}{%
-\section{SUPPORTING INFORMATION}\label{supporting-information}}
-
-Additional supporting information may be found online in the Supporting
-Information section at the end of the article.
-
-\textbf{APPENDIX S1-7.} Site information, generalization for a
-relationship between ratios of disc-based and whole-leaf estimates of
-leaf mass per area (LMA), leaf tissue density (LD), and complete figures
-for mismatch between leaf disc and whole-leaf LMA.
+\newpage
 
 \hypertarget{literature-cited}{%
-\section{LITERATURE CITED}\label{literature-cited}}
+\section*{LITERATURE CITED}\label{literature-cited}}
+\addcontentsline{toc}{section}{LITERATURE CITED}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Albert2010a}{}}%
-Albert, C. H., W. Thuiller, N. G. Yoccoz, A. Soudant, F. Boucher, P.
-Saccone, and S. Lavorel. 2010.
-\href{https://doi.org/10.1111/j.1365-2745.2010.01651.x}{Intraspecific
-functional variability: {Extent}, structure and sources of variation}.
-\emph{Journal of Ecology} 98: 604--613.
+\leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
+Fei, X., Q. Song, Y. Zhang, Y. Liu, L. Sha, G. Yu, L. Zhang, et al.
+2018. \href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon
+exchanges and their responses to temperature and precipitation in forest
+ecosystems in {Yunnan}, {Southwest China}}. \emph{Science of The Total
+Environment} 616--617: 824--840.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Diaz2004}{}}%
-Díaz, S., J. G. Hodgson, K. Thompson, M. Cabido, J. H. C. Cornelissen,
-A. Jalili, G. Montserrat-Martí, et al. 2004.
-\href{https://doi.org/10.1658/1100-9233(2004)015\%5B0295:TPTTDE\%5D2.0.CO;2}{The
-plant traits that drive ecosystems: {Evidence} from three continents}.
-\emph{Journal of Vegetation Science} 15: 295.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Diaz2016}{}}%
-Díaz, S., J. Kattge, J. H. C. Cornelissen, I. J. Wright, S. Lavorel, S.
-Dray, B. Reu, et al. 2016.
-\href{https://doi.org/10.1038/nature16489}{The global spectrum of plant
-form and function}. \emph{Nature} 529: 167--171.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Evans1972}{}}%
-Evans, G. C. 1972. The quantitative analysis of plant growth. {Univ of
-California Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Falster2018}{}}%
-Falster, D. S., R. A. Duursma, and R. G. FitzJohn. 2018.
-\href{https://doi.org/10.1073/pnas.1714044115}{How functional traits
-influence plant growth and shade tolerance across the life cycle}.
-\emph{Proceedings of the National Academy of Sciences} 115:
-E6789--E6798.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gao2018}{}}%
-Gao, Z., W. Shen, and G. Chen. 2018.
-\href{https://doi.org/10.1093/jxb/ery155}{Uncovering {C4-like}
-photosynthesis in {C3} vascular cells}. \emph{Journal of Experimental
-Botany} 69: 3531--3540.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Garnier1994}{}}%
-Garnier, E., and G. Laurent. 1994.
-\href{https://doi.org/10.1111/j.1469-8137.1994.tb04036.x}{Leaf anatomy,
-specific mass and water content in congeneric annual and perennial grass
-species}. \emph{New Phytologist} 128: 725--736.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Grubb1986}{}}%
-Grubb, P. 1986. Sclerophylls, pachyphylls, and pycnophylls: {The} nature
-and significance of hard leaf surface. \emph{Insects and the plant
-surface}: 137--150.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hanson1917}{}}%
-Hanson, H. C. 1917. Leaf-structure as related to environment.
-\emph{American Journal of Botany}: 533--560.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hibberd2002}{}}%
-Hibberd, J. M., and W. P. Quick. 2002.
-\href{https://doi.org/10.1038/415451a}{Characteristics of {C4}
-photosynthesis in stems and petioles of {C3} flowering plants}.
-\emph{Nature} 415: 451--454.
-
-\leavevmode\vadjust pre{\hypertarget{ref-John2017}{}}%
-John, G. P., C. Scoffoni, T. N. Buckley, R. Villar, H. Poorter, and L.
-Sack. 2017. \href{https://doi.org/10.1111/ele.12739}{The anatomical and
-compositional basis of leaf mass per area}. \emph{Ecology Letters} 20:
-412--425.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Julious2000}{}}%
-Julious, S. A., and C. A. Debarnot. 2000. Why are pharmacokinetic data
-summarized by arithmetic means? \emph{Journal of biopharmaceutical
-statistics} 10: 55--71.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Katabuchi2015}{}}%
-Katabuchi, M. 2015.
-\href{https://doi.org/10.1007/s11284-015-1307-x}{{LeafArea}: An {R}
-package for rapid digital image analysis of leaf area}. \emph{Ecological
-Research} 30: 1073--1077.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kattge2020}{}}%
-Kattge, J., G. Bönisch, S. Díaz, S. Lavorel, I. C. Prentice, P. Leadley,
-S. Tautenhahn, et al. 2020.
-\href{https://doi.org/10.1111/gcb.14904}{{TRY} plant trait database
-\textendash{} enhanced coverage and open access}. \emph{Global Change
-Biology} 26: 119--188.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kichenin2013}{}}%
-Kichenin, E., D. A. Wardle, D. A. Peltzer, C. W. Morse, and G. T.
-Freschet. 2013.
-\href{https://doi.org/10.1111/1365-2435.12116}{Contrasting effects of
-plant inter- and intraspecific variation on community-level trait
-measures along an environmental gradient}. \emph{Functional Ecology} 27:
-1254--1261.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kitajima2010}{}}%
-Kitajima, K., and L. Poorter. 2010.
-\href{https://doi.org/10.1111/j.1469-8137.2010.03212.x}{Tissue-level
-leaf toughness, but not lamina thickness, predicts sapling leaf lifespan
-and shade tolerance of tropical tree species}. \emph{New Phytologist}
-186: 708--721.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kraft2008}{}}%
-Kraft, N. J. B., R. Valencia, and D. D. Ackerly. 2008.
-\href{https://doi.org/10.1126/science.1160662}{Functional {Traits} and
-{Niche-Based Tree Community Assembly} in an {Amazonian Forest}}.
-\emph{Science} 322: 580--582.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Li2013a}{}}%
-Li, S., Y.-J. Zhang, L. Sack, C. Scoffoni, A. Ishida, Y.-J. Chen, and
-K.-F. Cao. 2013. \href{https://doi.org/10.1371/journal.pone.0066016}{The
-heterogeneity and spatial patterning of structure and physiology across
-the leaf surface in giant leaves of alocasia macrorrhiza}. \emph{PLOS
-ONE} 8: 1--10.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Messier2017}{}}%
-Messier, J., B. J. McGill, B. J. Enquist, and M. J. Lechowicz. 2017.
-\href{https://doi.org/10.1111/ecog.02006}{Trait variation and
-integration across scales: Is the leaf economic spectrum present at
-local scales?} \emph{Ecography} 40: 685--697.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Messier2010}{}}%
-Messier, J., B. J. McGill, and M. J. Lechowicz. 2010.
-\href{https://doi.org/10.1111/j.1461-0248.2010.01476.x}{How do traits
-vary across ecological scales? {A} case for trait-based ecology}.
-\emph{Ecology Letters} 13: 838--848.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Niinemets2007}{}}%
-Niinemets, Ü., A. Portsmuth, D. Tena, M. Tobias, S. Matesanz, and F.
-Valladares. 2007. \href{https://doi.org/10.1093/aob/mcm107}{Do we
-underestimate the importance of leaf size in plant economics?
-{Disproportional} scaling of support costs within the spectrum of leaf
-physiognomy}. \emph{Annals of Botany} 100: 283--303.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Niinemets2006}{}}%
-Niinemets, Ü., A. Portsmuth, and M. Tobias. 2006.
-\href{https://doi.org/10.1111/j.1469-8137.2006.01741.x}{Leaf size
-modifies support biomass distribution among stems, petioles and mid-ribs
-in temperate plants}. \emph{New Phytologist} 171: 91--104.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Oktavia2020}{}}%
-Oktavia, D., and G. Jin. 2020.
-\href{https://doi.org/10.1016/j.baae.2020.09.010}{Variations in leaf
-morphological and chemical traits in response to life stages, plant
-functional types, and habitat types in an old-growth temperate forest}.
-\emph{Basic and Applied Ecology} 49: 22--33.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Onoda2008}{}}%
-Onoda, Y., F. Schieving, and N. P. R. Anten. 2008.
-\href{https://doi.org/10.1093/aob/mcn013}{Effects of light and nutrient
-availability on leaf mechanical properties of {Plantago} major: {A}
-conceptual approach}. \emph{Annals of Botany} 101: 727--736.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Onoda2011}{}}%
-Onoda, Y., M. Westoby, P. B. Adler, A. M. F. Choong, F. J. Clissold, J.
-H. C. Cornelissen, S. Díaz, et al. 2011.
-\href{https://doi.org/10.1111/j.1461-0248.2010.01582.x}{Global patterns
-of leaf mechanical properties}. \emph{Ecology Letters} 14: 301--312.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Onoda2017}{}}%
-Onoda, Y., I. J. Wright, J. R. Evans, K. Hikosaka, K. Kitajima, Ü.
-Niinemets, H. Poorter, et al. 2017.
-\href{https://doi.org/10.1111/nph.14496}{Physiological and structural
-tradeoffs underlying the leaf economics spectrum}. \emph{New
-Phytologist} 214: 1447--1463.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Parry2002}{}}%
-Parry, M. A., P. J. Andralojc, S. Khan, P. J. Lea, and A. J. Keys. 2002.
-Rubisco activity: Effects of drought stress. \emph{Annals of botany} 89:
-833--839.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Perez-Harguindeguy2013}{}}%
-Pérez-Harguindeguy, N., S. Díaz, E. Garnier, S. Lavorel, H. Poorter, P.
-Jaureguiberry, M. S. Bret-Harte, et al. 2013.
-\href{https://doi.org/10.1071/BT12225}{New handbook for standardised
-measurement of plant functional traits worldwide}. \emph{Australian
-Journal of Botany} 61: 167--234.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poorter2014}{}}%
-Poorter, H., H. Lambers, and J. R. Evans. 2014.
-\href{https://doi.org/10.1111/nph.12547}{Trait correlation networks: {A}
-whole-plant perspective on the recently criticized leaf economic
-spectrum}. \emph{New Phytologist} 201: 378--382.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poorter2009}{}}%
-Poorter, H., Ü. Niinemets, L. Poorter, I. J. Wright, and R. Villar.
-2009. \href{https://doi.org/10.1111/j.1469-8137.2009.02830.x}{Causes and
-consequences of variation in leaf mass per area ({LMA}): {A}
-meta-analysis}. \emph{New Phytologist} 182: 565--588.
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2021}{}}%
-R Core Team. 2021. R: {A} language and environment for statistical
-computing. {R Foundation for Statistical Computing}, {Vienna, Austria}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Reich2014}{}}%
-Reich, P. B. 2014. \href{https://doi.org/10.1111/1365-2745.12211}{The
-world-wide 'fast-slow' plant economics spectrum: {A} traits manifesto}.
-\emph{Journal of Ecology} 102: 275--301.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sack2012}{}}%
-Sack, L., C. Scoffoni, A. D. McKown, K. Frole, M. Rawls, J. C. Havran,
-H. Tran, and T. Tran. 2012. Developmentally based scaling of leaf
-venation architecture explains global ecological patterns. \emph{Nature
-Communications} 3: 1--10.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Siefert2015}{}}%
-Siefert, A., C. Violle, L. Chalmandrier, C. H. Albert, A. Taudiere, A.
-Fajardo, L. W. Aarssen, et al. 2015.
-\href{https://doi.org/10.1111/ele.12508}{A global meta-analysis of the
-relative extent of intraspecific trait variation in plant communities}.
-\emph{Ecology Letters} 18: 1406--1419.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Terashima2001}{}}%
-Terashima, I., S.-I. Miyazawa, and Y. T. Hanba. 2001.
-\href{https://doi.org/10.1007/PL00013972}{Why are {Sun Leaves Thicker}
-than {Shade Leaves}? \textemdash{} {Consideration} based on {Analyses}
-of {CO2 Diffusion} in the {Leaf}}. \emph{Journal of Plant Research} 114:
-93--105.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Warton2012a}{}}%
-Warton, D. I., R. A. Duursma, D. S. Falster, and S. Taskinen. 2012.
-\href{https://doi.org/10.1111/j.2041-210X.2011.00153.x}{Smatr
-3\textendash{} an {R} package for estimation and inference about
-allometric lines}. \emph{Methods in Ecology and Evolution} 3: 257--259.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Warton2006}{}}%
-Warton, D. I., I. J. Wright, D. S. Falster, and M. Westoby. 2006.
-\href{https://doi.org/10.1017/S1464793106007007}{Bivariate line-fitting
-methods for allometry}. \emph{Biological Reviews of the Cambridge
-Philosophical Society} 81: 259--291.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wright2004a}{}}%
-Wright, I. J., P. B. Reich, M. Westoby, D. D. Ackerly, Z. Baruch, F.
-Bongers, J. Cavender-Bares, et al. 2004.
-\href{https://doi.org/10.1038/nature02403}{The worldwide leaf economics
-spectrum}. \emph{Nature} 428: 821--827.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wright2010}{}}%
-Wright, S. J., K. Kitajima, N. J. B. Kraft, P. B. Reich, I. J. Wright,
-D. E. Bunker, R. Condit, et al. 2010.
-\href{https://doi.org/10.1890/09-2335.1}{Functional traits and the
-growth-mortality trade-off in tropical trees}. \emph{Ecology} 91:
-3664--3674.
+\leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
+Song, Q.-H., Y.-P. Zhang, L.-Q. Sha, X.-B. Deng, Y. Deng, C.-S. Wu,
+Z.-Y. Lu, et al. 2017.
+\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature
+variability in a tropical rainforest, subtropical evergreen forest, and
+savanna forest in {Southwest China}}. \emph{iForest - Biogeosciences and
+Forestry} 10: 611.
 
@@
 
-\newpage
-
-\begin{longtable}[]{@{}lllr@{}}
-\toprule
-Data & Slope & Intercept & \emph{R\textsuperscript{2}} \\
-\midrule
-\endhead
-All & 0.98 {[}0.94, 1.01{]} & \textbf{0.09 {[}0.02, 0.16{]}} & 0.87 \\
-Thick-large & 0.93 {[}0.85, 1.03{]} & \textbf{0.19 {[}0.01, 0.37{]}} &
-0.86 \\
-Thick-small & 1.02 {[}0.97, 1.07{]} & 0 {[}-0.11, 0.11{]} & 0.93 \\
-Thin-large & 0.91 {[}0.82, 1.02{]} & \textbf{0.2 {[}0.02, 0.37{]}} &
-0.71 \\
-Thin-small & 0.93 {[}0.83, 1.03{]} & 0.16 {[}-0.02, 0.35{]} & 0.84 \\
-\bottomrule
-\end{longtable}
-
-\textbf{Table. 1.} Relationships between species mean leaf trait values
-determined by using whole leaves and leaf discs across all species and
-within species groups. Data are divided into four categories based on
-the quartiles: thin and small-leaved, thin and large-leaved, thick and
-small-leaved, and thick and large-leaved species. SMA slope (95\% CI),
-intercepts (95\% CI), and \emph{R\textsuperscript{2}} values are
-reported. Statistically significant differences (\emph{P} \textless{}
-0.05) in slopes and intercepts are highlighted in bold.
-
-\newpage
-
-\textbf{Fig. 1.} Relationships between species mean leaf mass per area
-(LMA) determined by using whole leaves and leaf discs. Species groups
-are divided into four categories on the basis of the medians of the leaf
-size and leaf thickness across all the species. Dashed lines indicate
-1:1 lines. Blue solid lines indicate standardized major axis
-regressions. The 95\% confidence intervals are presented as the shaded
-area. All the correlations are significant (\emph{P} \textless{} 0.001).
-
-\includegraphics{../figs/LMA_sp_gr.png}
-
-\newpage
-
-\textbf{Fig. 2.} Relationships between individual leaf mass per area
-(LMA) determined by using whole leaves and leaf discs. Individual groups
-are divided into four categories based on the basis of the medians of
-the leaf size and leaf thickness across all the individuals. All the
-correlations are significant (\emph{P} \textless{} 0.001). Details as in
-Fig. 1.
-
-\includegraphics{../figs/LMA_ind_gr.png}
-
-\newpage
-
-\textbf{Fig. 3.} Relationships between coefficient of variation (CV) in
-leaf trait values determined by using whole leaves and leaf discs: (a)
-leaf mass per area (LMA). The correlation is significant (\emph{P}
-\textless{} 0.001). Details as in Fig. 1. Note that the axes are square
-root scales.
-
-\includegraphics{../figs/fig_cv.png}
-
 \end{document}

### 2021-12-15 scripts/database.R

@@ -1,0 +1,13 @@
+library(tidyverse)
+library(RSQLite)
+
+if (file.exists("./data/try.sqlite3")) system("rm ./data/try.sqlite3")
+db <- dbConnect(SQLite(), "./data/try.sqlite3", synchronous="off")
+
+d <- read_delim("./data/TRY_DATA.txt", "\t")
+
+db %>% dbWriteTable("try", d)
+
+data_list <- dbListTables(db)
+
+print(paste("Created:", data_list))

### 2021-12-21 ms/LMA_method.Rmd
updated author info

@@
 
-Phisamai Maenpuen^1,2,3^,
+Phisamai Maenpuen^1,2,3\*^,
 Masatoshi Katabuchi^1,\*^,
@@
 Cong Zhou^1,2^,
-Jiao-Lin Zhang^1,3\*^,
+Jiao-Lin Zhang^1,3^,
 Ya-Jun Chen^1,3,5^
@@
 E-mail: zjl@xtbg.org.cn
+
+\* These authors contributed equally to this work.
 

### 2021-12-21 ms/LMA_method.tex
updated author info

@@
 
-Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
+Phisamai Maenpuen\textsuperscript{1,2,3*}, Masatoshi
 Katabuchi\textsuperscript{1,*}, Yusuke Onoda\textsuperscript{4}, Cong
-Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
+Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3}, Ya-Jun
 Chen\textsuperscript{1,3,5}
@@
 \href{mailto:zjl@xtbg.org.cn}{\nolinkurl{zjl@xtbg.org.cn}}
+
+* These authors contributed equally to this work.
 

### 2022-04-01 ms/response_letter.Rmd
added letter template

---
geometry: margin=1in
link-citations: yes
#csl: templates/xxxx.csl
#bibliography: xxxx.bib
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
 # - \linenumbers
output:
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: no
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

> AE comments: Thanks for the submission. I agree with the reviewers that the paper has merit and will be of interest to many researchers because LMA is a widely used trait. Both reviewers have some feedback for you to consider. Reviewer 1's suggestions would require extensive revisions to address. Reviewer 2 has suggested a modification to the title. I think the existing title is fine if you prefer to keep that but would ask you to carefully consider all other comments carefully.

> Reviewer #1: Summary of Manuscript:
> This manuscript compares two methods of measuring LMA (leaf mass per area), an ecologically important functional trait in plants. It is a carefully executed and useful piece of work, in that LMA is a very widely measured plant trait and many readers will be interested in identifying the best methods to use when measuring LMA in their system, as well as how to compare their own measurements to other published estimates. However, I believe the paper needs modification; I include recommendations, including three major concerns, below:

test

> 1. Framing: I think the paper misses an opportunity to provide a bit more context for why the study is important. The authors could provide more concrete examples of why standardizing LMA techniques across studies matters: e.g. what is the ecological significance of an LMA measurement difference between the two methods?  This could also be set up in the introduction by providing more context for LMA as a functional trait. For example, by citing the TRY database, the authors could provide readers with the importance and ubiquity of LMA relative to other plant traits (e.g. of all the studies of plant traits in TRY, how many report LMA?)

> 2. A crucial thing for readers to know is how to "convert" one method's estimate of LMA to another: the authors could report an equation (or a few, accounting for some additional covariates such as leaf area and leaf thickness, which this paper identifies as important modifiers of the relationship) that scholars could use in the future if trying to compare LMA estimates collected using different methods. In other words, taking the eq from Appendix 2 and modifying it given the results of this study.

> 3. I am confused and unconvinced by the inclusion and discussion of intraspecific trait variation on several levels. First, the authors do not clearly explain ITV, its importance, or its relevance to LMA. Secondly, the methods used to quantify ITV are not recommended (see Yang et al 2020. Large underestimation of intraspecific trait variation and its improvements. Frontiers in Plant Science); ideally the authors should use Bao's CV estimator. Finally, there is little interpretation of the results of their analysis. I think this metric needs to either be excluded entirely or significantly expanded upon.

> Line comments:

> L49 I think the introduction would benefit from an initial sentence to give more context for the definition of LMA (perhaps by restructuring this paragraph to introduce traits and the LES first, and then defining LMA in that context).

> L69-73 This sentence is crucial for your hypotheses but is buried in the middle of this paragraph. I suggest breaking this paragraph (beginning on line 63) up into 2: the first describing different methods of measurement and how commonly each are used, and any previous attempts to compare them. The second paragraph can get into which leaf types are likely to give similar or different estimates based on the two metrics and why.

> L82-84 I find this introduction of ITV to be confusing. ITV has a robust literature which is not cited here (for a recent review, see Westerband, Funk, and Barton, 2021. Intraspecific trait variation in plants: a renewed focus on its role in ecological processes. Annals of botany). The authors should briefly introduce this concept and it's ecological relevance before applying it to their question of which method generates greater estimates of ITV and why.

> L99-100 It may bear repeating here why you expect the estimates to match up better for smaller and/or thicker leaves

> L101-102 again, might be worth stating why (even if it is discussed above)

> L107- 113 The description of the sites/data is a little confusing: it seems that there are two datasets: one which includes 3 different sites, and another that includes a fourth site, for which a subset of the samples had additional measurement taken. I recommend clarifying this section to explain the different levels of organization, as well as including some of the methodological data in Table S1 (e.g. number of total samples, whether leaf thickness was measured, leaf punch size).

> L148-151 why were the species divided at all? Why not analyze the data as a single group, using leaf area and leaf thickness as (continuous) covariates? Dividing the species into groups this way turns a continuous variable into a categorical one, which is poor statistical practice.

> L154-160 see major comment 3

> L169-172 This is the major result of the paper. I suggest making it the first line of the results section (however I would modify it to fit the individual, rather than species-mean, level data: see below).

> L175-176 Based on this, I am confused about the statistical approach. Did the authors separately run regressions for species-level means and individual level means? If so, it is almost a statistical inevitability that the individual level analysis would have a lower r2 than the species level analysis: therefore I would not report this as a result, per se. In addition, the species level means is more or less meaningless in the context of this paper: much more importantly is the comparison of individual based measurements. I would therefore remove the species level results form the manuscript, and instead only report on the individual level data.

> L182 I believe leaf punch size was something that varied between datasets, and was never measured on the same leaves. I'm therefore confused as to how the authors are interpreting the effect of "leaf punch size" in their models: could this not simply be a reflection of the different species represented in the different datasets?

> L183-184 Which metric had higher ITV? That is a more relevant result than simply the R2 value.

> L193 you mention "appropriate calibration": it would be extremely useful if the authors were to report an equation (or several) for converting LMA measured by one metric to the other, ideally that incorporate leaf area and thickness (see major comment).

> L201-204 This is a result, and an important one (again, I'm thinking of readers who are looking for advice on how to measure LMA): it should be reported in the results section.

> L247 is this reported in the results somewhere? I thought the multiple discs/leaf were measured together?

> Appendix S2 seems to be missing the x axis titles

> Reviewer #2: In this work, the authors compared two methods to measure LMA of plants: leaf disc sampling and whole-leaf sampling using 334 woody species from East Asia. The main finding are that (i) mean values of leaf disc LMA is a good proxy for mean values of whole-leaf LMA; (ii) larger and thinner leaves tended to show the large discrepancies between the leaf disc and whole-leaf estimates. Therefore, the present work implies that when one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis), appropriate calibrations are necessary. This manuscript was well written. At least, I can read the whole manuscript fast. The study is valuable for choosing a better approach when calculating LMA. I suggest minor to moderate revisions for this manuscript.

> General Comments:

> In the Introduction section, the authors had better add some introduction to the leaf disc sampling method, since this method was focused to make a comparison with the whole-leaf sampling method for calculating LMA.

> The authors had better explain why they used the LMA values with leaf petioles mass.

> Line-specific Comments:

> Line 1: Suggest adding "- evidence from 334 woody species" in the title.

> Lines 26 and 51: Change "the key trait" to "an important functional trait".

> Line 57: I think that the following reference helps to support this statement, because LMA values were found to vary across leaf age, and LMA also exhibits a plasticity to climate when leaves enter the maturation stage (Jiao et al., 2022).
> Jiao, Y., Niklas, K.J., Wang, L., Yu, K., Li, Y., Shi, P. 2022. Influence of leaf age on the scaling relationships of lamina biomass vs. area. Frontiers in Plant Science In press.

> Line 70: Please consider citing the following references:

> Li, Y., Shi, P., Niinemets, Ü., Song, Y., Yu, K., Schrader, J., Niklas, K.J. 2022. Diminishing returns among lamina fresh and dry mass, surface area, and petiole fresh mass among nine Lauraceae species. American Journal of Botany In press. doi: 10.1002/ajb2.1812

> Li, Y., Zheng, Y., Ratkowsky, D.A., Wei, H., Shi, P. 2022. Application of an ovate leaf shape model to evaluate leaf bilateral asymmetry and calculate lamina centroid location. Frontiers in Plant Science, 12: 822907. doi: 10.3389/fpls.2021.822907

> Lines 97 and 98: Drop the numerical values of R squared. There is no need to exhibit the results here.

> Lines 105 and 106: Why did you only collect the data in China and Japan. Here, I think, you had better add one to three sentences to explain the feasibility of showing general results for other floras.

> Lines 124 and 125: Why did you maintain leaf petiole in calculating LMA? It is strange for me, because it might inflate LMA given that its definition is dry mass per unit leaf area. What is the meaning for "avoiding thick veins"? Do you mean in the experiment you punch the positions without having the secondary order veins?

> Lines 129-131: Can you class the leaf shapes of 334 woody species you have used? It will affect your sampling positions you are describing here.

> Lines 151-153: I think, a frequency of LA is needed as a supplementary figure to show the feasibility of such divisions.

> Line 157: Are you that the unit of CV is not a percentage? In general, an unitless variable, we usually use its percentage.

> Line 163: It is incorrect to use 1000 bootstrap replates to calculate a confidence interval! In general, >= 30 replates are enough for calculating a standard deviation, and >= 2000 replates to calculate a confidence interval.

> Lines 168 and 169: It is a strange result for me. Leaf area has been demonstrated to be negatively correlated to mean leaf thickness at the species level (see Figure 4 in Lin et al., 2018). It seems that you obtained a negative correlation based on the pooled data of biomes. If possible, I suggest adding several sentences to discuss the reasons for the pooled data in the Discussion section.

> Lin, S., Shao, L., Hui, C., Song, Y., Reddy, G.V.P., Gielis, J., Li, F., Ding, Y., Wei, Q., Shi, P. 2018. Why does not the leaf weight-area allometry of bamboos follow the 3/2-power law? Frontiers in Plant Science 9: 583, https://doi.org/10.1016/10.3389/fpls.2018.00583

> Line 171: "… were 9.4% greater than disc-based estimates …" Can you provide a standard deviation or a confidence interval for 9.4%? In general, we can use the bootstrap method to get it.

### 2022-04-04 _targets.R
clean name

@@ -1,0 +1,70 @@
+library(targets)
+library(tarchetypes)
+library(furrr)
+
+source("R/data_clean.R")
+
+options(clustermq.scheduler = "multiprocess")
+plan(multisession, workers = parallel::detectCores())
+tar_option_set(packages = c(
+  "tidyverse",
+  "patchwork",
+  "ggsma",
+  "smatr",
+  "janitor"
+))
+
+list(
+  # data cleaning ----------------------------------
+  tar_target(
+    lma_raw,
+    "data-raw/lma_raw.csv",
+    format = "file"
+  ),
+  tar_target( 
+    lma_la,
+    "data-raw/lma_la.csv",
+    format = "file"
+  ),
+  tar_target(
+    lma_yaku,
+    "data-raw/leaf_traits_for_katabuchi.csv",
+    format = "file"
+  ),
+  tar_target(
+    lma_raw_re,
+    clean_lma_raw(lma_raw)
+  ),
+  tar_target(
+    lma_la_re,
+    clean_lma_la(lma_la)
+  ),
+  tar_target(
+    lma_yaku_re,
+    clean_lma_yaku(lma_yaku)
+  ),
+  tar_target(
+    full_data_csv,
+    data_clean(lma_raw_re, lma_la_re, lma_yaku_re)
+  ),
+  tar_target(
+    full_data_cv_csv,
+    data_clean_cv(lma_raw_re, lma_yaku_re)
+  ),
+  tar_target(
+    tree_data_csv,
+    data_clean_tree(lma_raw_re, lma_yaku_re)
+  ),
+  tar_target(
+    sp_mean,
+    sp_dat_mean(full_data_csv)
+  ),
+  tar_target(
+    sp_cv,
+    sp_dat_cv(full_data_cv_csv)
+  ),
+  tar_target(
+    tree_dat,
+    tree_dat_clean(tree_data_csv)
+  )
+)

### 2022-04-04 run.R

@@ -1,0 +1,6 @@
+targets::tar_make_clustermq(
+  workers = parallel::detectCores(),
+  reporter = "silent"
+)
+
+# targets::tar_make()

### 2022-04-05 _targets.R
sma table

@@ -72,8 +72,22 @@ list(
     tree_dat,
     tree_dat_clean(tree_data_csv)
   ),
+
+  # analyses and figs ---------------------------------------------
   tar_target(
-    la_lt_grid_plot,
-    la_lt_grid(sp_mean)
+    lalt_pool_grid_plot,
+    lalt_pool_grid(sp_mean)
+  ),
+  tar_target(
+    lalt_sep_grid_plot,
+    lalt_sep_grid(sp_mean)
+  ),
+  tar_target(
+    sma_tab,
+    generate_sma_tab(sp_mean)
+  ),
+  tar_render(
+    report,
+    "report.Rmd"
   )
 )

### 2022-04-05 report.Rmd
sma table

---
Title: "your title"
author: "Masatoshi Katabuchi"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: TRUE
    toc_float:
     collapsed: TRUE
     smooth_scroll: TRUE
     toc: true
---

```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  fig.show = "hold"
)
```

```{r}
library(tidyverse)
library(targets)
library(kableExtra)
```

# Leaf disc vs whole-leaf LMA (species-level)

```{r}
tar_read(lalt_pool_grid_plot)
```

```{r}
theme_set(theme_bw())
theme_update(text = element_text(family = "Arial"))
```

## Pooled

```{r}
tar_read(lalt_pool_grid_plot)
```

## Seprated

```{r}
tar_read(lalt_sep_grid_plot)
```

## SMA table (species-level)

```{r}
tar_load(sma_tab)
sma_tab |>
  kable() |>
  kable_styling()
```

### 2022-04-06 R/data_clean.R
clean

@@ -25,8 +25,8 @@ clean_lma_yaku <- function(lma_yaku) {
       ld_disc = td) |>
     mutate(ld_leaf = lma_leaf / lt * 10^-3) %>%
     mutate(ldmc_disc = NA) |>
-    mutate(lt_disc = NA)
-
+    mutate(lt_disc = NA) |>
+    mutate(petiole_ratio = petiole_dw / scanned_leaf_dw)
   yaku
 }
 
@@ -385,4 +385,25 @@ tree_dat_clean <- function(tree_data_csv) {
                            "Thick-leaved~individuals"))
 
   tree
+}
+
+create_yaku_sp <- function(lma_yaku_re) {
+  lma_yaku_re |>
+    group_by(species) |>
+    summarize_at(
+                 .vars = vars(
+               lma_disc,
+               lma_leaf,
+               ldmc_disc,
+               ldmc_leaf,
+               ld_disc,
+               ld_leaf,
+               lt,
+               lt_disc,
+               la,
+               petiole_ratio
+                 ),
+      .funs =  \(x)mean(x, na.rm = TRUE)) |>
+    filter(petiole_ratio > 0) |>
+    filter(!is.na(lma_disc))
 }

### 2022-04-06 R/ind_analysis.R

@@ -1,0 +1,116 @@
+lalt_tree_grid <- function(tree) {
+  tree |>
+    ggplot(aes(x = lma_disc, y = lma_leaf, col = dry_mass_disc)) +
+    geom_point(alpha = 0.8) +
+    scale_color_viridis_c(
+      trans = "log10",
+      name = "Total dry mass of \nleaf discs (g)"
+    ) +
+    scale_x_log10() +
+    scale_y_log10() +
+    geom_abline(slope = 1, intercept = 0, lty = 2) +
+    geom_sma(se = TRUE) +
+    facet_grid(la_gr2 ~ lt_gr2, scale = "free", labeller = label_parsed) +
+    xlab(expression(Leaf ~ disc ~ LMA ~ (g ~ m^{
+      -2
+    }))) +
+    ylab(expression(Whole - leaf ~ LMA ~ (g ~ m^{
+      -2
+    }))) +
+    stat_cor(
+      aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
+    ) +
+    theme(
+      legend.position = c(0.39, 0.15),
+      legend.key.size = unit(0.5, "cm"),
+      legend.spacing.y = unit(0.1, "cm"),
+      legend.text.align = 0,
+      legend.key.height = unit(0.3, "cm"),
+      legend.text = element_text(size = 7),
+      legend.title = element_text(size = 7)
+    )
+}
+
+
+ratio_combine <- function(tree) {
+  my_col <- RColorBrewer::brewer.pal(4, "RdBu")
+
+  ratio_mass <- tree |>
+    mutate(punch_size = ifelse(location == "Yakushima", "1.0 cm", "0.6 cm")) |>
+    ggplot(aes(dry_mass_disc, lma_leaf / lma_disc,
+      col = punch_size
+    )) +
+    geom_point(alpha = 0.6) +
+    geom_hline(yintercept = 1) +
+    scale_color_manual(
+      values = my_col[c(2, 4)],
+      name = "Diameter of the leaf punch"
+    ) +
+    xlab("Total dry mass of leaf disc (g)") +
+    ylab("Whole-leaf LMA / leaf disc LMA") +
+    theme(
+      legend.position = c(0.7, 0.75),
+      legend.key.size = unit(0.5, "cm"),
+      legend.spacing.y = unit(0.1, "cm"),
+      legend.text.align = 0,
+      legend.key.height = unit(0.3, "cm"),
[…]

### 2022-04-06 R/sp_analysis.R

@@ -1,6 +1,6 @@
 
 #' @title Leaf disc vs whole-leaf LMA (pooled species-level)
-lalt_pool_grid <- function(data) {
+lalt_pool_grid_point <- function(data) {
   data |>
     ggplot(aes(x = lma_disc, y = lma_leaf)) +
     geom_point(alpha = 0.8) +
@@ -16,13 +16,14 @@ lalt_pool_grid <- function(data) {
       -2
     }))) +
     stat_cor(
-      aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
+      aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"),
+          family = "Helvetica")
     )
 }
 
 
 #' @title Leaf disc vs whole-leaf LMA (separted species-level)
-lalt_sep_grid <- function(data) {
+lalt_sep_grid_point <- function(data) {
   my_col <- RColorBrewer::brewer.pal(4, "RdBu")
   data |>
     mutate(punch_size = ifelse(location == "Yakushima", "1.0 cm", "0.6 cm")) |>
@@ -133,4 +134,146 @@ generate_sma_tab <- function(sp_mean) {
   colnames(tb)[1] <- "Data"
 
   tb
+}
+
+#' @title LMA and LD (species-level)
+lma_ld_wrap_point <- function(sp_mean) {
+  d_leaf <- sp_mean |>
+    dplyr::select(c(species:data_contributor,
+      lma = lma_leaf, ldmc = ldmc_leaf, ld = ld_leaf
+    )) |>
+    pivot_longer(lma:ld, names_to = "trait", values_to = "whole_leaf") |>
+    filter(location != "Yakushima" | trait != "ld") |>
+    filter(location != "Yakushima" | trait != "lma")
+  d_disc <- sp_mean |>
+    dplyr::select(species, location, lma = lma_disc, ldmc = ldmc_disc, ld = ld_disc) |>
+    pivot_longer(lma:ld, names_to = "trait", values_to = "leaf_disc") |>
+    filter(location != "Yakushima" | trait != "ld") |>
+    filter(location != "Yakushima" | trait != "lma")
+  d2 <- full_join(d_leaf, d_disc) |>
+    mutate(trait = factor(trait, c("lma", "ldmc", "ld"))) |>
[…]

### 2022-04-06 report.Rmd
clean

@@
 ---
-Title: "your title"
+title: Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)"
 author: "Masatoshi Katabuchi"
@@
 
-```{r}
-tar_read(lalt_pool_grid_plot)
-```
-
-```{r}
-theme_set(theme_bw())
-theme_update(text = element_text(family = "Arial"))
-```
-
 ## Pooled
 
-```{r}
-tar_read(lalt_pool_grid_plot)
-```
+![](figs/lalt_pool_grid.png)
 
@@
 
-```{r}
-tar_read(lalt_sep_grid_plot)
-```
+![](figs/lalt_sep_grid.png)
 
-## SMA table (species-level)
+# SMA table (species-level)
 
@@
 ```
+
+# Leaf disc vs whole-leaf LMA (individual-level)
+
+![](figs/lalt_tree_grid.png)
+
+# Divergence (species-level)
+
+![](figs/ratio.png)
+
+# LMA and LD (species-level)
+
+![](figs/lma_ld.png)
+
+# CV
+
+![](figs/cv_pool.png)
+
+![](figs/cv_sep.png)
+
+# Leaf support cost (species-level)
+
+![](figs/petiole.png)
+
+# Computing Environment
+
+```{r}
+devtools::session_info()
+```
+
+```{r}
+tar_visnetwork()
+```

### 2022-04-06 R/fig_write.R

@@ -1,0 +1,39 @@
+
+
+get_name <- function(x) deparse(substitute(x))
+
+create_plot_dat <- function(plot_list) {
+  plots <- sapply(plot_list, get_name) |> names()
+
+  file_png <- str_replace_all(plots, "_plot", ".png")
+  file_tiff <- str_replace_all(plots, "_plot", ".tiff")
+  file_pdf <- str_replace_all(plots, "_plot", ".pdf")
+
+  file_png <- paste0("figs/", file_png)
+  file_tiff <- paste0("figs/", file_tiff)
+  file_pdf <- paste0("figs/", file_pdf)
+
+  plot_dat <- tibble(plots, file_png, file_tiff, file_pdf)
+  plot_dat
+}
+
+
+save_tiff <- function(file_tiff, plots, width, height) {
+  message("plot")
+  get(plots) |> print()
+
+  message("file")
+  file_tiff |> print()
+
+  # ggsave(file_tiff,
+  #   plots,
+  #   dpi = 300,
+  #   width = width,
+  #   height = height
+  # )
+}
+
+
+#
+#
+# mcmapply(save_tiff, hoge, hoge2)

### 2022-04-06 _targets.R

@@ -25,7 +25,7 @@ tar_option_set(packages = c(
 ))
 
 theme_set(theme_bw())
-#theme_update(text = element_text(family = "Arial"))
+theme_update(text = element_text(family = "Arial"))
 
 #
 list(
@@ -93,10 +93,48 @@ list(
     lalt_pool_grid_point(sp_mean)
   ),
 
+  tar_target(
+    lalt_pool_grid_png,
+    ggsave(
+      "figs/lalt_pool_grid.png",
+      lalt_pool_grid_plot,
+      dpi = 300,
+      width = 6,
+      height = 6
+    )
+  ),
+  tar_target(
+    lalt_pool_grid_pdf,
+    ggsave(
+      "figs/lalt_pool_grid.pdf",
+      lalt_pool_grid_plot,
+      width = 6,
+      height = 6
+    )
+  ),
 
   tar_target(
     lalt_sep_grid_plot,
     lalt_sep_grid_point(sp_mean)
+  ),
+  tar_target(
+    lalt_sep_grid_png,
+    ggsave(
+      "figs/lalt_sep_grid.png",
+      lalt_sep_grid_plot,
+      dpi = 300,
+      width = 6,
+      height = 6
+    )
+  ),
+  tar_target(
+    lalt_sep_grid_pdf,
+    ggsave(
+      "figs/lalt_sep_grid.pdf",
+      lalt_sep_grid_plot,
+      width = 6,
+      height = 6
+    )
   ),
 
   tar_target(
@@ -185,25 +223,7 @@ list(
   #     list(6, 6, 6, 6, 3, 3, 3, 5)
   # )),
 
-  tar_target(
-    test,
-    mapply(function(filename, plot, width, height)ggsave(filename = filename, plot = plot, width = width, height = height),
-      list(
-        "figs/lalt_pool_grid.tiff",
-        "figs/lalt_sep_grid.tiff"),
-      list(
-        lalt_pool_grid_plot,
-        lalt_sep_grid_plot),
-      list(6, 7),
-      list(6, 6)
-  )),
-   # tar_target(
-   #   fig_tiff,
-   #   mapply(save_tiff,
-   #            plot_dat$file_tiff,
-   #            plot_dat$plots,
-   #            plot_dat$width, plot_dat$height)
-   # ),
+
   tar_render(
     report,
     "report.Rmd"

### 2022-04-06 report.Rmd
clean for docker

@@
 
+```{r, include=FALSE}
+tar_load(lalt_pool_grid_png)
+```
+
 ![](figs/lalt_pool_grid.png)
@@
 ## Seprated
+
+```{r, include=FALSE}
+tar_load(lalt_sep_grid_png)
+```
 
@@
 
+```{r, include=FALSE}
+tar_load(lalt_tree_grid_png)
+```
+
 ![](figs/lalt_tree_grid.png)
@@
 # Divergence (species-level)
+
+```{r, include=FALSE}
+tar_load(ratio_png)
+```
 
@@
 
+```{r, include=FALSE}
+tar_load(lma_ld_png)
+```
+
 ![](figs/lma_ld.png)
@@
 
+```{r, include=FALSE}
+tar_load(cv_pool_png)
+```
+
 ![](figs/cv_pool.png)
+
+```{r, include=FALSE}
+tar_load(cv_sep_png)
+```
 
@@
 # Leaf support cost (species-level)
+
+```{r, include=FALSE}
+tar_load(petiole_png)
+```
 

### 2022-04-06 R/ind_analysis.R

@@ -20,7 +20,9 @@ lalt_tree_grid <- function(tree) {
     stat_cor(
       aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
     ) +
+    theme_bw() +
     theme(
+      text = element_text(family = "Arial"),
       legend.position = c(0.39, 0.15),
       legend.key.size = unit(0.5, "cm"),
       legend.spacing.y = unit(0.1, "cm"),
@@ -48,6 +50,7 @@ ratio_combine <- function(tree) {
     ) +
     xlab("Total dry mass of leaf disc (g)") +
     ylab("Whole-leaf LMA / leaf disc LMA") +
+    theme_bw() +
     theme(
       legend.position = c(0.7, 0.75),
       legend.key.size = unit(0.5, "cm"),
@@ -73,6 +76,7 @@ ratio_combine <- function(tree) {
     scale_x_log10() +
     xlab("Leaf thickness (mm)") +
     ylab("Whole-leaf LMA / leaf disc LMA") +
+    theme_bw() +
     theme(
       legend.position = c(0.7, 0.75),
       legend.key.size = unit(0.5, "cm"),
@@ -98,6 +102,7 @@ ratio_combine <- function(tree) {
     scale_x_log10() +
     xlab(expression(Leaf ~ area ~ (m^2))) +
     ylab("Whole-leaf LMA / leaf disc LMA") +
+    theme_bw() +
     theme(
       legend.position = "none",
       # legend.position = c(0.2, 0.75),
@@ -110,7 +115,10 @@ ratio_combine <- function(tree) {
     )
 
   p_ratio <- ratio_mass + ratio_lt + ratio_la +
-    plot_annotation(tag_levels = "a")
+    plot_annotation(tag_levels = "a") &
+    #theme_bw() &
+    theme(
+      text = element_text(family = "Arial"))
 
   p_ratio
 }

### 2022-04-06 R/sp_analysis.R

@@ -18,7 +18,9 @@ lalt_pool_grid_point <- function(data) {
     stat_cor(
       aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"),
           family = "Helvetica")
-    )
+    ) +
+    theme_bw() +
+    theme(text = element_text(family = "Arial"))
 }
 
 
@@ -48,7 +50,9 @@ lalt_sep_grid_point <- function(data) {
       aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial"),
       show.legend = FALSE
     ) +
+    theme_bw() +
     theme(
+      text = element_text(family = "Arial"),
       legend.position = c(0.3, 0.1),
       legend.key.size = unit(0.5, "cm"),
       legend.spacing.y = unit(0.1, "cm"),
@@ -173,7 +177,10 @@ lma_ld_wrap_point <- function(sp_mean) {
         label = paste(..rr.label.., ..n.label.., sep = "~`,`~"),
         family = "Arial"
       )
-    )
+    ) +
+    theme_bw() +
+    theme(
+      text = element_text(family = "Arial"))
   p_all
 }
 
@@ -195,7 +202,10 @@ cv_pool_point <- function(sp_cv) {
       label.y.npc = 0,
       vjust = 1.5,
       aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
-    )
+    ) +
+    theme_bw() +
+    theme(
+      text = element_text(family = "Arial"))
 }
 
 cv_sep_point <- function(sp_cv) {
@@ -240,7 +250,10 @@ cv_sep_point <- function(sp_cv) {
     )
 
   (p_cv1 + p_cv2) +
-    plot_annotation(tag_levels = "a")
+    plot_annotation(tag_levels = "a") &
+    theme_bw() &
+    theme(
+      text = element_text(family = "Arial"))
 }
 
 
@@ -275,5 +288,6 @@ petiole_point <- function(yaku_sp) {
 
   pet2 + pet1 +
     plot_annotation(tag_levels = "a") &
+    theme_bw() &
     theme(plot.tag = element_text(face = "bold"))
 }

### 2022-04-06 _targets.R

@@ -1,8 +1,6 @@
 library(targets)
 library(tarchetypes)
-library(furrr)
 library(tidyverse)
-library(parallel)
 
 source("R/util.R")
 source("R/data_clean.R")
@@ -11,8 +9,7 @@ source("R/ind_analysis.R")
 source("R/fig_write.R")
 
 options(clustermq.scheduler = "multiprocess")
-options(mc.cores = detectCores()) # 4
-plan(multisession, workers = parallel::detectCores())
+
 tar_option_set(packages = c(
   "tidyverse",
   "patchwork",
@@ -20,14 +17,9 @@ tar_option_set(packages = c(
   "ggpubr",
   "smatr",
   "janitor",
-  "extrafont",
-  "parallel"
+  "extrafont"
 ))
 
-theme_set(theme_bw())
-theme_update(text = element_text(family = "Arial"))
-
-#
 list(
   # data cleaning ----------------------------------
   tar_target(
@@ -101,7 +93,8 @@ list(
       dpi = 300,
       width = 6,
       height = 6
-    )
+    ),
+    format = "file"
   ),
   tar_target(
     lalt_pool_grid_pdf,
@@ -110,7 +103,8 @@ list(
       lalt_pool_grid_plot,
       width = 6,
       height = 6
-    )
+    ),
+    format = "file"
   ),
 
   tar_target(
@@ -125,7 +119,8 @@ list(
       dpi = 300,
       width = 6,
       height = 6
-    )
+    ),
+    format = "file"
   ),
   tar_target(
     lalt_sep_grid_pdf,
@@ -134,7 +129,8 @@ list(
       lalt_sep_grid_plot,
       width = 6,
       height = 6
-    )
+    ),
+    format = "file"
   ),
 
   tar_target(
@@ -146,20 +142,104 @@ list(
     lalt_tree_grid_plot,
     lalt_tree_grid(tree)
   ),
+  tar_target(
+    lalt_tree_grid_png,
+    ggsave(
+      "figs/lalt_tree_grid.png",
+      lalt_tree_grid_plot,
+      dpi = 300,
+      width = 6,
+      height = 6
+    ),
+    format = "file"
+  ),
+  tar_target(
+    lalt_tree_grid_pdf,
+    ggsave(
+      "figs/lalt_tree_grid.pdf",
+      lalt_tree_grid_plot,
+      width = 6,
[…]

### 2022-04-07 ms/LMA_method.Rmd
udpate make

--- 2021-12-15 ms/LMA_method.Rmd
@@
     #template: null
-    pandoc_args:
+    pandoc_arg:
       - "--filter"
@@
 Phisamai Maenpuen^1,2,3^,
-Masatoshi Katabuchi^1,\*^,
+Masatoshi Katabuchi^1\*^,
 Yusuke Onoda^4^,
@@
 
-![](../figs/LMA_sp_gr.png)
+![](../figs/lalt_pool_grid.png)
 
@@
 
-![](../figs/LMA_ind_gr.png)
+![](../figs/lalt_tree_grid.png)
 
@@
 
-![](../figs/fig_cv.png)
+![](../figs/cv_pool.png)

### 2022-04-07 run.R

@@ -3,4 +3,4 @@ targets::tar_make_clustermq(
   reporter = "silent"
 )
 
-# targets::tar_make()
+#targets::tar_make()

### 2022-04-07 ms/LMA_method.tex
udpate make

--- 2021-12-15 ms/LMA_method.tex
@@
 Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
-Katabuchi\textsuperscript{1,*}, Yusuke Onoda\textsuperscript{4}, Cong
+Katabuchi\textsuperscript{1*}, Yusuke Onoda\textsuperscript{4}, Cong
 Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
@@
 a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet
-forest (STF), with a total of 141 species and 846 individuals. Second,
-the Yakushima data is from a warm-temperate forest in Yakushima island,
-Japan, with a total of 193 species and 519 individuals. In total, we
-used 334 woody species and 1365 individuals. The methodologies for trait
-sampling and measurement are slightly different between the Yunnan and
-the Yakushima dataset, which we describe bellow.
+forest (STF), with a total of species and individuals. Second, the
+Yakushima data is from a warm-temperate forest in Yakushima island,
+Japan, with a total of 193 species and individuals. In total, we used
+334 woody species and individuals. The methodologies for trait sampling
+and measurement are slightly different between the Yunnan and the
+Yakushima dataset, which we describe bellow.
 
@@
 precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
-and petiole dry mass were also determined separately (81 out of 193
+and petiole dry mass were also determined separately (87 out of 193
 species) to quantify leaf support costs. Dry mass for leaf discs were
@@
 small-leaved, thick and large-leaved species (individuals). Median
-values are as following: small-leaved species (LA \textless{} 29.5
-cm\textsuperscript{2}), thin-leaved species (LT \textless{} 0.28 mm),
-small-leaved individuals (LA \textless{} 34.7 cm\textsuperscript{2}),
-and thin-leaved individuals (LT \textless{} 0.26 mm).
+values are as following: small-leaved species (LA \textless{}
+cm\textsuperscript{2}), thin-leaved species (LT \textless{} mm),
+small-leaved individuals (LA \textless{} cm\textsuperscript{2}), and
+thin-leaved individuals (LT \textless{} mm).
 
@@
 Disc-based estimates of species mean LMA matched well whole-leaf
-estimates (Table 1; \emph{R\textsuperscript{2}} = 0.87 for all species).
+estimates (Table 1; \emph{R\textsuperscript{2}} = for all species).
 Species with thicker and smaller leaves had stronger correlations
@@
 There was a negative correlation between species mean leaf area and leaf
-thickness (\emph{r} = -0.29, \emph{P} \textless{} 0.05, \emph{n} = 334).
-When we pooled all the species, there were significant differences in
-intercepts for species mean LMA (Table 1), suggesting that the
-whole-leaf estimates of LMA were 9.4\% greater than disc-based estimates
-in the arithmetic scale. Large-leaved species also had significant
-positive intercepts, suggesting that whole-leaf estimates of LMA were
-22.1\% greater than disc-based estimates in the arithmetic scale (Table
-1). Intercepts did not differ for small-leaved species (Table 1).
+thickness (\emph{r} = , \emph{P} , \emph{n} = ). When we pooled all the
+species, there were significant differences in intercepts for species
+mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were
+9.4\% greater than disc-based estimates in the arithmetic scale.
+Large-leaved species also had significant positive intercepts,
+suggesting that whole-leaf estimates of LMA were 22.1\% greater than
+disc-based estimates in the arithmetic scale (Table 1). Intercepts did
+not differ for small-leaved species (Table 1).
 
@@
 Disc-based traits explained interspecific variations in whole-leaf LMA
-(\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the
+(\emph{R\textsuperscript{2}} = , \emph{n} = ) quite well, and the
 strength of their relationship was approximately same or slightly weaker
@@
 
-\includegraphics{../figs/LMA_sp_gr.png}
+\includegraphics{../figs/lalt_pool_grid.png}
 
@@
 
-\includegraphics{../figs/LMA_ind_gr.png}
+\includegraphics{../figs/lalt_tree_grid.png}
 
@@
 
-\includegraphics{../figs/fig_cv.png}
+\includegraphics{../figs/cv_pool.png}
 

### 2022-04-07 ms/SI.Rmd
clean

@@
 library(methods)
-source("../scripts/rmd_func.R")
+library(targets)
 basename <- "LMA_method"
-opts_chunk$set(fig.path = paste("figs/", sep=""))
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE,
-               comment = NA, verbose = TRUE, echo=FALSE)
+opts_chunk$set(fig.path = paste("figs/", sep = ""))
+opts_chunk$set(tidy = FALSE,
+               warning = FALSE,
+               message = FALSE,
+               comment = NA,
+               verbose = TRUE,
+               cache = FALSE,
+               echo = FALSE)
 # PDF-based figures
@@
 
-val <- yaml::yaml.load_file("../values.yml")
+val <- yaml::yaml.load_file("values.yml")
 ```
@@
 
-![](../figs/fig1.png){ width="600" style="display: block; margin: 0 auto" }
+![](../figs/lma_ld.png){ width="600" style="display: block; margin: 0 auto" }
 
@@
 
-![](../figs/LMAratio2.png){style="display: block; margin: 0 auto" }
+![](../figs/ratio.png){style="display: block; margin: 0 auto" }
 
@@
 ```{r, eval=TRUE, echo=FALSE}
-tree <- read_csv("../data/tree_data.csv")
-
-tree2 <- tree |>
-  filter(!is.na(LMAdisc)) |>
-  filter(!is.na(LMAleaf)) |>
-  filter(!is.na(LTleaf)) |>
-  rename(LT = LTleaf) |>
-  rename(LA = LAleaf) |>
-  mutate(Dry_mass_disc2 = case_when(
-   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4 / 2,
-   TRUE ~ LMAdisc * 0.889 * 10^-4 / 3
-                )) |>
-  mutate(Dry_mass_disc = case_when(
-   Location == "Yakushima" ~ LMAdisc * 1.57 * 10^-4,
-   TRUE ~ LMAdisc * 0.889 * 10^-4
-                )) |>
-  mutate(PCH = ifelse(Location == "Yakushima", "1.0 cm", "0.6 cm"))
-
-fit <- lm(log(Dry_mass_disc) ~ scale(log(LT)) + scale(log(LA)) + PCH, tree2)
-
-s <- summary(fit)
-tb <- s$coefficients |> round(3) |> signif(3)
-colnames(tb) <- c("Estimate", "SE", "t-value", "*P* value")
-tb[,4] <- ifelse(tb[,4] < 0.001, "< 0.001", tb[,4])
-rownames(tb)[2] <- "log(Leaf thickness)"
-rownames(tb)[3] <- "log(Leaf area)"
-rownames(tb)[4] <- "Large leaf punch"
-
-tb |>
-  kable() |>
+tar_load(dm_lm_tab)
+dm_lm_tab |>
+  kable(format = "html") |>
   kable_styling()
@@
 
-![](../figs/LMA_sp_gr_both.png){ width="600" style="display: block; margin: 0 auto" }
+![](../figs/lalt_sep_grid.png){ width="600" style="display: block; margin: 0 auto" }
 
@@
 
-![](../figs/fig_cv2.png){ width="600" style="display: block; margin: 0 auto" }
+![](../figs/cv_sep.png){ width="600" style="display: block; margin: 0 auto" }
 

### 2022-04-07 R/sp_analysis.R
clean

@@ -178,6 +178,8 @@ lma_ld_wrap_point <- function(sp_mean) {
         family = "Arial"
       )
     ) +
+    xlab("Leaf disc") +
+    ylab("Whole-leaf") +
     theme_bw() +
     theme(
       text = element_text(family = "Arial"))

### 2022-04-07 _targets.R

@@ -306,8 +306,17 @@ list(
     format = "file"
   ),
 
+  tar_target(
+    dm_lm_tab,
+    dm_lm(tree)
+  ),
   tar_render(
     report,
     "report.Rmd"
+   ),
+  tar_render(
+    si,
+    "ms/SI.Rmd",
+    output_format = "html_document"
    )
 )

### 2022-04-08 ms/LMA_method.tex
add Bao's CV

@@
 only weakly matched between whole-leaf and disc-based estimates
-(\emph{R\textsuperscript{2}} = 0.31). We also found that sample with
+(\emph{R\textsuperscript{2}} = 0.32). We also found that sample with
 small total dry mass of leaf discs tended to show greater differences
@@
 variation) only weakly matched between whole-leaf and disc-based
-estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.31).
+estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.32).
 
@@
 disc-based estimate was surprisingly small (Fig. 3;
-\emph{R\textsuperscript{2}} = 0.31). This is probably because leaf disc
+\emph{R\textsuperscript{2}} = 0.32). This is probably because leaf disc
 samples have more sources of ITV than whole-leaf samples (i.e.,

### 2022-04-08 R/data_clean.R

@@ -1,6 +1,22 @@
 #' @title CV
 cv <- \(x, na.rm = TRUE) sd(log(x), na.rm = TRUE) / mean(log(x), na.rm = TRUE)
 
+#' @title Bao's CV with log-transformation
+cv4 <- function(x, log = TRUE) {
+  x <- x[!is.na(x)]
+  if (log) x <- log(x)
+  n <- length(x)
+  mu <- mean(x)
+  sig <- sd(x)
+  cv1 <- sig / mu
+  gamma1 <- sum(((x - mu) / sig)^3) / n
+  gamma2 <- sum(((x - mu) / sig)^4) / n
+  cv4 <- cv1 - cv1^3 / n + cv1 / (4 * n)
+        + cv1^2 * gamma1 / (2 * n) + cv1 * gamma2 / (8 * n)
+  cv4
+}
+
+
 clean_lma_yaku <- function(lma_yaku) {
   d3 <- read_csv(lma_yaku) |>
     clean_names(abbreviations = c("LMA", "LD", "LDMC", "LT"))
@@ -165,7 +181,7 @@ data_clean_cv <- function(d, d3) {
         lt_disc,
         leaf_area_leaf
       ),
-      .funs = cv
+      .funs = cv4
     )
 
   sp_list <- d |>
@@ -188,15 +204,15 @@ data_clean_cv <- function(d, d3) {
       # mat,
       # map,
       data_contributor,
-      lma_disc = cv(lma_disc, na.rm = TRUE),
-      lma_leaf = cv(lma_leaf, na.rm = TRUE),
+      lma_disc = cv4(lma_disc),
+      lma_leaf = cv4(lma_leaf),
       # ldmc_disc = ldmc_disc,
-      # ldmc_leaf = cv(ldmc_leaf, na.rm = TRUE),
-      ld_disc = cv(ld_disc, na.rm = TRUE),
-      ld_leaf = cv(ld_leaf, na.rm = TRUE),
-      lt = cv(lt, na.rm = TRUE),
-      lt_disc = cv(lt_disc, na.rm = TRUE),
-      la = cv(la, na.rm = TRUE)
+      # ldmc_leaf = cv4(ldmc_leaf, na.rm = TRUE),
+      ld_disc = cv4(ld_disc),
+      ld_leaf = cv4(ld_leaf),
+      lt = cv4(lt),
+      lt_disc = cv4(lt_disc),
+      la = cv4(la)
     ) |>
     unique()
 

### 2022-04-08 R/ind_analysis.R
nboot 2000

@@ -9,7 +9,7 @@ lalt_tree_grid <- function(tree) {
     scale_x_log10() +
     scale_y_log10() +
     geom_abline(slope = 1, intercept = 0, lty = 2) +
-    geom_sma(se = TRUE) +
+    geom_sma(se = TRUE, nboot = 2000) +
     facet_grid(la_gr2 ~ lt_gr2, scale = "free", labeller = label_parsed) +
     xlab(expression(Leaf ~ disc ~ LMA ~ (g ~ m^{
       -2

### 2022-04-08 R/sp_analysis.R
nboot 2000

@@ -7,7 +7,7 @@ lalt_pool_grid_point <- function(data) {
     scale_x_log10() +
     scale_y_log10() +
     geom_abline(slope = 1, intercept = 0, lty = 2) +
-    geom_sma(se = TRUE) +
+    geom_sma(se = TRUE, nboot = 2000) +
     facet_grid(la_gr2 ~ lt_gr2, scale = "free", labeller = label_parsed) +
     xlab(expression(Leaf ~ disc ~ LMA ~ (g ~ m^{
       -2
@@ -170,7 +170,7 @@ lma_ld_wrap_point <- function(sp_mean) {
     geom_point(alpha = 0.6) +
     scale_x_log10() +
     scale_y_log10() +
-    geom_sma(se = TRUE) +
+    geom_sma(se = TRUE, nboot = 2000) +
     facet_wrap(~trait_lab, scale = "free", labeller = label_parsed) +
     stat_cor(
       aes(
@@ -195,7 +195,7 @@ cv_pool_point <- function(sp_cv) {
     geom_point(alpha = 0.6) +
     scale_x_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
     scale_y_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
-    geom_sma(se = TRUE) +
+    geom_sma(se = TRUE, nboot = 2000) +
     ylab("CV of whole-leaf LMA") +
     xlab("CV of leaf disc LMA") +
     coord_fixed() +
@@ -218,7 +218,7 @@ cv_sep_point <- function(sp_cv) {
     geom_point(alpha = 0.6) +
     scale_x_continuous(trans = "sqrt") +
     scale_y_continuous(trans = "sqrt") +
-    geom_sma(se = TRUE) +
+    geom_sma(se = TRUE, nboot = 2000) +
     ggtitle("Diameter: 0.6 cm") +
     ylab("CV of whole-leaf LMA") +
     xlab("CV of leaf disc LMA") +

### 2022-04-08 _targets.R
sma table for tree

@@ -140,8 +140,13 @@ list(
   ),
 
   tar_target(
-    sma_tab,
+    sma_sp_tab,
     generate_sma_tab(sp_mean)
+  ),
+
+  tar_target(
+    sma_tree_tab,
+    generate_sma_tab(tree)
   ),
 
   tar_target(

### 2022-04-09 _targets.R
stan

@@ -1,6 +1,8 @@
 library(targets)
 library(tarchetypes)
 library(tidyverse)
+library(stantargets)
+library(cmdstanr)
 
 source("R/util.R")
 source("R/data_clean.R")
@@ -8,6 +10,7 @@ source("R/sp_analysis.R")
 source("R/ind_analysis.R")
 source("R/fig_write.R")
 source("R/yml.R")
+source("R/stan.R")
 
 options(clustermq.scheduler = "multiprocess")
 
@@ -17,9 +20,14 @@ tar_option_set(packages = c(
   "ggsma",
   "ggpubr",
   "smatr",
+  "parallel",
   "janitor",
   "extrafont"
 ))
+
+Sys.setenv(CMDSTAN = "/opt/cmdstan/cmdstan-2.29.0")
+set_cmdstan_path("/opt/cmdstan/cmdstan-2.29.0")
+cmdstan_version()
 
 list(
   # data cleaning ----------------------------------
@@ -84,6 +92,97 @@ list(
       sp_mean, full_data_cv_csv, tree, lma_yaku_re)
   ),
   # analyses and figs ---------------------------------------------
+
+  tar_target(
+    stan_sim_dat,
+    create_dummy_data(100)
+  ),
+  tar_target(
+    stan_sp_dat,
+    clean_stan_data(sp_mean)
+  ),
+
+  tar_target(
+    stan_tree_dat,
+    clean_stan_data(tree)
+  ),
+  tar_target(
+    stan_sp_dat_noint,
+    clean_stan_data(sp_mean, interaction = FALSE)
+  ),
+  tar_target(
+    stan_tree_dat_noint,
+    clean_stan_data(tree, interaction = FALSE)
+  ),
+  tar_stan_mcmc(
+    fit_sim,
+    "stan/model.stan",
+    data = stan_sim_dat,
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 1000,
+    iter_sampling = 1000,
+    seed = 123
+   ),
+  tar_stan_mcmc(
+    fit_sp,
+    "stan/model.stan",
+    data = stan_sp_dat,
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 1000,
+    iter_sampling = 1000,
+    seed = 123
+   ),
+  tar_stan_mcmc(
+    fit_tree,
+    "stan/model.stan",
[…]

### 2022-04-09 R/stan.R
stan

@@ -1,0 +1,37 @@
+clean_stan_data <- function(sp_mean, interaction = TRUE) {
+  x <- cbind(
+    intercept = rep(1, nrow(sp_mean)),
+    #lma_disc = sp_mean$lma_disc |> log10() |> scale(),
+    la = sp_mean$la |> log() |> scale(),
+    lt = sp_mean$lt |> log() |> scale()
+  )
+  if (interaction) {
+    x <- cbind(x, x[, 2] * x[, 3])
+    colnames(x) <- c("intercept", "la", "lt", "lalt")
+  } else {
+    colnames(x) <- c("intercept", "la", "lt")
+  }
+  list(
+    N = nrow(sp_mean),
+    K = ncol(x),
+    log_y = log(sp_mean$lma_leaf),
+    log_lma_disc = sp_mean$lma_disc |> log() |> scale() |> as.numeric(),
+    x = x)
+}
+
+create_dummy_data <- function(n) {
+  xx1 <- rnorm(n)
+  xx2 <- rnorm(n)
+  xx3 <- rnorm(n)
+  x <- cbind(rep(1, n), xx2, xx3)
+  sig <- 1.41 + 1 * xx2 - 1 * xx3
+  sig <- rnorm(n, sig, 0.2)
+  yy <- rnorm(n, 0.3 + 0.9 * xx1, exp(sig))
+  #lm(yy ~ xx1) |> summary()
+  list(
+    N = n,
+    K = ncol(x),
+    log_y = yy,
+    log_lma_disc = xx1,
+    x = x)
+}

### 2022-04-12 ms/LMA_method.tex
update docker

@@
 precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
-and petiole dry mass were also determined separately (87 out of 193
+and petiole dry mass were also determined separately (86 out of 193
 species) to quantify leaf support costs. Dry mass for leaf discs were

### 2022-04-21 ms/LMA_method.Rmd
add subsection for Bayes

@@
 
+*new subsection*
+
+To quantify the effect of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA, we built hierarchical Bayes models.
+The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf size and leaf thickness on the log-scale;
+
+$$
+\mathrm{ln}(LMA_{Wi}) \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i)
+$$
+
+$$
+\tilde{\mu_i} = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i})
+$$
+
+where $LMA_{Wi}$, $LMA_{Di}$, $LA_{i}$, $LT_{i}$ are the whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree *i*, respectively.
+$\tilde{\mu_i}$ is the effect of leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree *i*, and $\sigma_i$ is the variance of whole-leaf LMA for tree *i*, and $\beta$ are coefficients.
+
+The variance of whole-leaf LMA ($\sigma_i$) was assumed to follow a normal distribution;
+
+$$
+\mathrm{ln}(\sigma_i) \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega)
+$$
+
+$$
+\tilde{\sigma_i} = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i})
+$$
+
+where $\tilde{\sigma_i}$ is the effect of leaf area and leaf thickness on the variance of whole-leaf LMA,
+$\omega$ is a scaling hyperparameter, and $\gamma$ are coefficients.
+To allow comparisons among parameter estimates, $\mathrm{ln}(LA)$ and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
+
+Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan [@Carpenter2017] using the weakly-informative priors [@Gelman2008].
+See supplement XXXX for more detail.
+The Stan code use to fit models is available from Github at: [https://github.com/mattocci27/leaf-disc](https://github.com/mattocci27/leaf-disc).
+Convergence of the posterior distribution was assessed with the Gelman-Rubin statistic with a convergence threshold of 1.1 for all parameters [@Gelman2013].
+
+*new subsection*
+
 Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the samples and different leaf area and thickness groups.
@@
 
-The amount of intraspecific variation of LMA was calculated using coefficient of variation of log-normally distributed data; $CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$, where $s_{\mathrm{ln}}$ is the sample standard deviation in the log-transformed data [@Julious2000].
-We also considered CV on the arithmetic scale; $CV = s/\bar{x}$, where $s$ is the sample standard deviation and $\bar{x}$ is the sample mean.
-However, these two different CV calculations only negligibly altered the bivariate relationship and did not change our conclusion, and thus we will report CV of log-normally distributed data in the main text.
+*new subsection?*
+
+The amount of intraspecific variation (ITV) was calculated using Bao's CV estimator [@Yang2020];
+
+$$
+CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N}
+$$
+
+where $CV_1 = s/\bar{x}$, $s$ is the sample standard deviation and $\bar{x}$ is the sample mean, *N* is the sample size, and $\gamma_1$ and $\gamma_2$ are the skewness and kurtosis of the trait distribution.
+Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small [@Yang2020].
 
 SMA analyses were run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
-Confidence intervals of SMA estimates were based on 1000 bootstraps.
-All statistical analyses were conducted in R version 4.1.2 [@RCoreTeam2021].
+Confidence intervals of SMA estimates were based on 2000 bootstraps.
+All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022].
 

### 2022-04-21 ms/LMA_method.tex
add subsection for Bayes

@@
 only weakly matched between whole-leaf and disc-based estimates
-(\emph{R\textsuperscript{2}} = 0.32). We also found that sample with
+(\emph{R\textsuperscript{2}} = 0.33). We also found that sample with
 small total dry mass of leaf discs tended to show greater differences
@@
 
+\emph{new subsection}
+
+To quantify the effect of leaf sizes and thicknesses on the relationship
+between whole-leaf and leaf disc LMA, we built hierarchical Bayes
+models. The whole-leaf LMA was assumed to follow a normal distribution
+(N) with the mean of leaf disc LMA and covariates of leaf size and leaf
+thickness on the log-scale;
+
+\[
+\mathrm{ln}(LMA_{Wi}) \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i)
+\]
+
+\[
+\tilde{\mu_i} = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i})
+\]
+
+where \(LMA_{Wi}\), \(LMA_{Di}\), \(LA_{i}\), \(LT_{i}\) are the
+whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree
+\emph{i}, respectively. \(\tilde{\mu_i}\) is the effect of leaf area and
+leaf thickness on the mean estimates for the whole-leaf LMA of tree
+\emph{i}, and \(\sigma_i\) is the variance of whole-leaf LMA for tree
+\emph{i}, and \(\beta\) are coefficients.
+
+The variance of whole-leaf LMA (\(\sigma_i\)) was assumed to follow a
+normal distribution;
+
+\[
+\mathrm{ln}(\sigma_i) \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega)
+\]
+
+\[
+\tilde{\sigma_i} = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i})
+\]
+
+where \(\tilde{\sigma_i}\) is the effect of leaf area and leaf thickness
+on the variance of whole-leaf LMA, \(\omega\) is a scaling
+hyperparameter, and \(\gamma\) are coefficients. To allow comparisons
+among parameter estimates, \(\mathrm{ln}(LA)\) and \(\mathrm{ln}(LT)\)
+were scaled to a mean of 0 and standard deviation of 1.
+
+Posterior distributions of all parameters were estimated using the
+Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan
+(\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}) using
+the weakly-informative priors (\protect\hyperlink{ref-Gelman2008}{Gelman
+et al., 2008}). See supplement XXXX for more detail. The Stan code use
+to fit models is available from Github at:
+\url{https://github.com/mattocci27/leaf-disc}. Convergence of the
+posterior distribution was assessed with the Gelman-Rubin statistic with
+a convergence threshold of 1.1 for all parameters
+(\protect\hyperlink{ref-Gelman2013}{Gelman et al., 2013}).
+
+\emph{new subsection}
+
 Bivariate trait relationships between disc-based and whole-leaf
@@
 
-The amount of intraspecific variation of LMA was calculated using
-coefficient of variation of log-normally distributed data;
-\(CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}\), where \(s_{\mathrm{ln}}\) is
-the sample standard deviation in the log-transformed data
-(\protect\hyperlink{ref-Julious2000}{Julious and Debarnot, 2000}). We
-also considered CV on the arithmetic scale; \(CV = s/\bar{x}\), where
-\(s\) is the sample standard deviation and \(\bar{x}\) is the sample
-mean. However, these two different CV calculations only negligibly
-altered the bivariate relationship and did not change our conclusion,
-and thus we will report CV of log-normally distributed data in the main
-text.
+\emph{new subsection?}
+
+The amount of intraspecific variation (ITV) was calculated using Bao's
+CV estimator (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020});
+
+\[
+CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N}
+\]
+
+where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and
+\(\bar{x}\) is the sample mean, \emph{N} is the sample size, and
+\(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait
+distribution. Bao's CV estimator is a robust method to quantify ITV
+based on coefficient of variation (CV) when sample size is small
+(\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
 
@@
 disc-based and whole-leaf estimates of LMA values. Confidence intervals
-of SMA estimates were based on 1000 bootstraps. All statistical analyses
-were conducted in R version 4.1.2
-(\protect\hyperlink{ref-RCoreTeam2021}{R Core Team, 2021}).
+of SMA estimates were based on 2000 bootstraps. All statistical analyses
+were conducted in R version 4.1.3
+(\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}).
 
@@
 variation) only weakly matched between whole-leaf and disc-based
-estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.32).
+estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.33).
 
@@
 disc-based estimate was surprisingly small (Fig. 3;
-\emph{R\textsuperscript{2}} = 0.32). This is probably because leaf disc
+\emph{R\textsuperscript{2}} = 0.33). This is probably because leaf disc
 samples have more sources of ITV than whole-leaf samples (i.e.,
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+Carpenter, B., A. Gelman, M. D. Hoffman, D. Lee, B. Goodrich, M.
+Betancourt, M. Brubaker, et al. 2017.
+\href{https://doi.org/10.18637/jss.v076.i01}{Stan : {A Probabilistic
+Programming Language}}. \emph{Journal of Statistical Software} 76:
+1--32.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Diaz2004}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Gelman2013}{}}%
+Gelman, A., J. B. Carlin, H. S. Stern, D. B. Dunson, A. Vehtari, and D.
+B. Rubin. 2013. Bayesian {Data Analysis}, {Third Edition}. {Taylor \&
+Francis}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gelman2008}{}}%
+Gelman, A., A. Jakulin, M. G. Pittau, and Y. S. Su. 2008.
+\href{https://doi.org/10.1214/08-AOAS191}{A weakly informative default
+prior distribution for logistic and other regression models}.
+\emph{Annals of Applied Statistics} 2: 1360--1383.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Grubb1986}{}}%
@@
 412--425.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Julious2000}{}}%
-Julious, S. A., and C. A. Debarnot. 2000. Why are pharmacokinetic data
-summarized by arithmetic means? \emph{Journal of Biopharmaceutical
-Statistics} 10: 55--71.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2021}{}}%
-R Core Team. 2021. R: {A} language and environment for statistical
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
+R Core Team. 2022. R: {A} language and environment for statistical
 computing. {R Foundation for Statistical Computing}, {Vienna, Austria}.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Yang2020}{}}%
+Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020.
+Large {Underestimation} of {Intraspecific Trait Variation} and {Its
+Improvements}. \emph{Frontiers in Plant Science} 11.
+
 \end{CSLReferences}
@@
 \begin{longtable}[]{@{}lllr@{}}
-\toprule
+\toprule()
 Data & Slope & Intercept & \emph{R\textsuperscript{2}} \\
-\midrule
+\midrule()
 \endhead
@@
 Thin-small & 0.93 {[}0.83, 1.03{]} & 0.16 {[}-0.02, 0.35{]} & 0.84 \\
-\bottomrule
+\bottomrule()
 \end{longtable}

### 2022-04-26 ms/LMA_method.Rmd
bookdown

@@
       - "pandoc-crossref"
-  word_document:
+  bookdown::word_document2:
     fig_width: 6
@@
 basename <- "LMA_method"
-opts_chunk$set(fig.path = paste("figs/", sep=""))
-opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE,
-               comment = NA, verbose = TRUE, echo=FALSE)
+opts_chunk$set(fig.path = paste("figs/", sep = ""))
+opts_chunk$set(
+  tidy = FALSE, warning = FALSE, message = FALSE,
+  comment = NA, verbose = TRUE, echo = FALSE
+)
 # PDF-based figures
-opts_chunk$set(dev='pdf')
+opts_chunk$set(dev = "pdf")
 
@@
 }
-
 ```

### 2022-04-26 ms/LMA_method.Rmd

@@
     toc: FALSE
-  pdf_document:
+#  pdf_document:
+  bookdown::pdf_document2:
     keep_md: false
@@
     fig_caption: yes
+    number_sections: no
     toc: FALSE
@@
 
-*Statistical analyses*
+*Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA*
 
-*new subsection*
+To quantify the effect of leaf area and thickness on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
+The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf area and leaf thickness on the log-scale;
 
-To quantify the effect of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA, we built hierarchical Bayes models.
-The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf size and leaf thickness on the log-scale;
-
-$$
-\mathrm{ln}(LMA_{Wi}) \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i)
-$$
-
-$$
-\tilde{\mu_i} = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i})
-$$
+\begin{align}
+\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i) (\#eq:LMA)\\
+\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i}) (\#eq:mu)
+\end{align}
 
@@
 
-$$
-\mathrm{ln}(\sigma_i) \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega)
-$$
-
-$$
-\tilde{\sigma_i} = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i})
-$$
+\begin{align}
+\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega) (\#eq:ln-sigma) \\
+\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i}) (\#eq:tilde-sigma)
+\end{align}
 
@@
 
-*new subsection*
+*Bivariate trait relationships for mean and CV*
 
@@
 
-*new subsection?*
-
 The amount of intraspecific variation (ITV) was calculated using Bao's CV estimator [@Yang2020];
 
-$$
-CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N}
-$$
+\begin{align}
+CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} (\#eq:CV)
+\end{align}
 

### 2022-04-26 ms/LMA_method.tex

@@
 
-Sources and consequences of mismatch between leaf disc and whole-leaf
-leaf mass per area (LMA)
+Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)
 
@@
 
-Phisamai Maenpuen\textsuperscript{1,2,3}, Masatoshi
-Katabuchi\textsuperscript{1*}, Yusuke Onoda\textsuperscript{4}, Cong
-Zhou\textsuperscript{1,2}, Jiao-Lin Zhang\textsuperscript{1,3*}, Ya-Jun
-Chen\textsuperscript{1,3,5}
+Phisamai Maenpuen\textsuperscript{1,2,3},
+Masatoshi Katabuchi\textsuperscript{1*},
+Yusuke Onoda\textsuperscript{4},
+Cong Zhou\textsuperscript{1,2},
+Jiao-Lin Zhang\textsuperscript{1,3*},
+Ya-Jun Chen\textsuperscript{1,3,5}
 
@@
 
-\textsuperscript{1} CAS Key Laboratory of Tropical Forest Ecology,
-Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences,
-Menglun, Yunnan 666303, China
-
-\textsuperscript{2} University of Chinese Academy of Sciences, Beijing
-100049, China
-
-\textsuperscript{3} Center of Plant Ecology, Core Botanical Gardens,
-Chinese Academy of Sciences, Yunnan 666303, China
-
-\textsuperscript{4} Graduate School of Agriculture, Kyoto University,
-Kyoto 606-8502, Japan
-
-\textsuperscript{5} Savanna Ecosystem Research Station, Xishuangbanna
-Tropical Botanical Garden, Chinese Academy of Sciences, Yuanjiang,
-Yunnan 6663300, China
+\textsuperscript{1} CAS Key Laboratory of Tropical Forest Ecology, Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences, Menglun, Yunnan 666303, China
+
+\textsuperscript{2} University of Chinese Academy of Sciences, Beijing 100049, China
+
+\textsuperscript{3} Center of Plant Ecology, Core Botanical Gardens, Chinese Academy of Sciences, Yunnan 666303, China
+
+\textsuperscript{4} Graduate School of Agriculture, Kyoto University, Kyoto 606-8502, Japan
+
+\textsuperscript{5} Savanna Ecosystem Research Station, Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences, Yuanjiang, Yunnan 6663300, China
 
@@
 
-E-mail:
-\href{mailto:mattocci27@gmail.com}{\nolinkurl{mattocci27@gmail.com}}
+E-mail: \href{mailto:mattocci27@gmail.com}{\nolinkurl{mattocci27@gmail.com}}
 
@@
 
-Tel: +86 691 871 3046; Fax: +86 691 871 5070; E-mail:
-\href{mailto:zjl@xtbg.org.cn}{\nolinkurl{zjl@xtbg.org.cn}}
+Tel: +86 691 871 3046;
+Fax: +86 691 871 5070;
+E-mail: \href{mailto:zjl@xtbg.org.cn}{\nolinkurl{zjl@xtbg.org.cn}}
 
@@
 
-\textbf{PREMISE:} Leaf mass per area (LMA), which is the key trait in
-leaf economic spectrum and plant growth analysis, is measured from leaf
-discs or whole leaves. These differences in the measurement methods may
-lead to large differences in the estimates of LMA values.
-
-\textbf{METHODS:} We determined LMA using leaf discs and whole-leaf
-(including petiole) for 334 woody species from a wide range of biomes
-(tropics, subtropics, savanna, and temperate) to examine what extent
-whole-leaf and leaf disc LMA match, whether the differences in the
-estimates are associated with leaf size and thickness, and whether
-intraspecifc variation for each species match.
-
-\textbf{RESULTS:} Disc-based estimates of species and individual mean
-LMA matched well whole-leaf estimates. Thin and large leaves had weaker
-correlations between leaf disc and whole-leaf estimates. Variability of
-LMA estimates within species (i.e., amount of intraspecific variation)
-only weakly matched between whole-leaf and disc-based estimates
-(\emph{R\textsuperscript{2}} = 0.33). We also found that sample with
-small total dry mass of leaf discs tended to show greater differences
-between leaf disc and whole-leaf LMA.
-
-\textbf{CONCLUSIONS:} Mean values of leaf disc LMA are generally good
-proxies for mean values of whole-leaf LMA with appropriate calibration
-(9.4\% differences in our samples), but their accuracy depends on leaf
-size, leaf thickness, and sizes of leaf punch. Therefore, using an
-appropriate size of leaf punch is important for obtaining stable
-estimates of leaf disc LMA that matches well with whole-leaf LMA.
-Quantifying trait variation using leaf disc should be considered with
-caution.
-
-\textbf{KEY WORDS:} intraspecific variation, leaf density, leaf economic
-spectrum, leaf heterogeneity, leaf punch, leaf size, leaf thickness,
-petiole, specific leaf area, within-leaf variation
+\textbf{PREMISE:}
+Leaf mass per area (LMA), which is the key trait in leaf economic spectrum and plant growth analysis, is measured from leaf discs or whole leaves.
+These differences in the measurement methods may lead to large differences in the estimates of LMA values.
+
+\textbf{METHODS:}
+We determined LMA using leaf discs and whole-leaf (including petiole) for 334 woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match, whether the differences in the estimates are associated with leaf size and thickness, and whether intraspecifc variation for each species match.
+
+\textbf{RESULTS:}
+Disc-based estimates of species and individual mean LMA matched well whole-leaf estimates.
+Thin and large leaves had weaker correlations between leaf disc and whole-leaf estimates.
+Variability of LMA estimates within species (i.e., amount of intraspecific variation) only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.33).
+We also found that sample with small total dry mass of leaf discs tended to show greater differences between leaf disc and whole-leaf LMA.
+
+\textbf{CONCLUSIONS:}
+Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (9.4\% differences in our samples), but their accuracy depends on leaf size, leaf thickness, and sizes of leaf punch.
+Therefore, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
+Quantifying trait variation using leaf disc should be considered with caution.
+
+\textbf{KEY WORDS:}
+intraspecific variation,
+leaf density,
+leaf economic spectrum,
+leaf heterogeneity,
+leaf punch,
+leaf size,
+leaf thickness,
+petiole,
+specific leaf area,
+within-leaf variation
 
@@
 
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue
-density (LD), describes how much biomass is invested into given
-photosynthetic leaf area thus reflecting a cost for light interception,
-which is the key trait of the leaf economic spectrum (LES)
-(\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
-\protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009};
-\protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}). Generally,
-resource-acquisitive species (fast-growing species) tend to have low LMA
-values, showing high photosynthesis, high nutrients, and often have fast
-leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al.,
-2004}). In contrast, resource-conservative species (slow-growing
-species) often have higher LMA values with the opposite patterns
-(\protect\hyperlink{ref-Garnier1994}{Garnier and Laurent, 1994};
-\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004};
-\protect\hyperlink{ref-Reich2014}{Reich, 2014};
-\protect\hyperlink{ref-Diaz2016}{Díaz et al., 2016}). The LMA is also
-frequently used in plant growth analysis
-(\protect\hyperlink{ref-Evans1972}{Evans, 1972};
-\protect\hyperlink{ref-Poorter2014}{Poorter et al., 2014};
-\protect\hyperlink{ref-Falster2018}{Falster et al., 2018}) because
-relative growth rates (RGR) can be decomposed into the product of net
-assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR
-\(\times\) LMR \(\times\) LMA\textsuperscript{-1}). Another appealing
-feature of LMA is that it is relatively easy to measure large numbers of
-species (i.e., `soft' trait, \protect\hyperlink{ref-Diaz2004}{Díaz et
-al., 2004}). Therefore, LMA has been of interests to ecologists and
-widely used since the first report more than a century ago
-(\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
-
-LMA values can be determined by either 1) a whole leaf including or
-excluding petioles, and 2) a leaf disc excluding all major veins or
-petioles
-(\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et
-al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}).
-Although some studies do not make clear what protocol was followed,
-these differences in the measurement methods may lead to large
-discrepancies in the estimates of LMA values because the major vein
-allocation (major vein, which includes first to second or third-order
-veins, volume per area) has been reported to be one of the main
-determinants for the variation in LMA
-(\protect\hyperlink{ref-John2017}{John et al., 2017}). Since larger
-leaves tend to invest more of their mass into dense midribs and petiole
-for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al.,
-2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves
-have clearly visible and large-diameter veins with less uniform leaf
-structure (i.e., kite-type leaves;
-(\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the
-estimates of whole-leaf LMA and leaf disc LMA might be greater for
-larger and thinner leaves. If leaf disc LMA largely and consistently
-underestimates whole-leaf LMA, some calibrations may be required to
-combine or compare those different estimates
-(\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008};
-\protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}). If divergencies
-between the estimates based on the different methods are large and
-inconsistent (i.e., low \emph{R\textsuperscript{2}} values), this is
-difficult to calibrate and should inflate errors in the subsequent
-analyses. To date, however, only a database from a single region, Panama
-Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al.,
-2010}), is available in the TRY
-(\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both
-estimates of LMA from small leaf discs and whole leaves including
-petioles, limiting of our understanding of under what conditions
-estimates of LMA from leaf discs are reliable estimates of whole-leaf
-LMA.
-
-Given that leaf disc samples have more sources of intraspecific trait
-variation (ITV) than whole-leaf samples, the effects of discrepancies
-between whole-leaf LMA and leaf disc LMA might be large when ITV is
-quantified as a coefficient of variance (CV). Sources of ITV for
-whole-leaf samples is variation among individuals within the same
-species and variation among leaves within the same individuals
-(\protect\hyperlink{ref-Messier2010}{Messier et al., 2010},
-\protect\hyperlink{ref-Messier2017}{2017}). An additional source of
-trait variation for leaf disc samples is variation among leaf discs
-within the same leaves. Thus, extents of ITV for each species based on
-whole-leaf and leaf discs samples may not match. Despite the importance
-of ITV in community ecology
-(\protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013};
-\protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), the effect
-of different measurement methods on the extent of ITV has been largely
-ignored.
-
-In this study, we aimed to investigate what extent whole-leaf (including
-petiole) and leaf disc LMA match, whether the relationships between
-whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf
-thicknesses, and whether amounts of intraspecifc variations for each
-match between whole-leaf and leaf disc based estimates. We collected a
-total of 334 woody species from four biomes (tropics, subtropics,
-savanna, and warm-temperate) to cover the wide range of geography. We
-predicted that the overall relationship between whole-leaf LMA and disc
-LMA would be weaker than previous reported LMA data
-(\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
-0.92 for leaf laminas in Onoda et al.
-(\protect\hyperlink{ref-Onoda2011}{2011})) because we collected data
-with various leaf sizes from a wide range of climates. We also predicted
-that species with larger and/or thinner leaves would show weaker
-correlations. Finally, we predicted that amounts of intraspecifc
-variations for each species do not match well between whole-leaf and
-leaf disc based estimates.
+Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area thus reflecting a cost for light interception, which is the key trait of the leaf economic spectrum (LES) (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
+Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}).
+In contrast, resource-conservative species (slow-growing species) often have higher LMA values with the opposite patterns (\protect\hyperlink{ref-Garnier1994}{Garnier and Laurent, 1994}; \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Reich2014}{Reich, 2014}; \protect\hyperlink{ref-Diaz2016}{Díaz et al., 2016}).
+The LMA is also frequently used in plant growth analysis (\protect\hyperlink{ref-Evans1972}{Evans, 1972}; \protect\hyperlink{ref-Poorter2014}{Poorter et al., 2014}; \protect\hyperlink{ref-Falster2018}{Falster et al., 2018}) because relative growth rates (RGR) can be decomposed into the product of net assimilation rate (NAR), leaf mass ratio (LMR) and LMA (i.e., RGR = NAR \(\times\) LMR \(\times\) LMA\textsuperscript{-1}).
+Another appealing feature of LMA is that it is relatively easy to measure large numbers of species (i.e., `soft' trait, \protect\hyperlink{ref-Diaz2004}{Díaz et al., 2004}).
+Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago (\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
+
+LMA values can be determined by either
+1) a whole leaf including or excluding petioles, and
+2) a leaf disc excluding all major veins or petioles (\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}).
+Although some studies do not make clear what protocol was followed, these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}).
+Since larger leaves tend to invest more of their mass into dense midribs and petiole for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
+If leaf disc LMA largely and consistently underestimates whole-leaf LMA, some calibrations may be required to combine or compare those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
+If divergencies between the estimates based on the different methods are large and inconsistent (i.e., low \emph{R\textsuperscript{2}} values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
+To date, however, only a database from a single region, Panama Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.
+
+Given that leaf disc samples have more sources of intraspecific trait variation (ITV) than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified as a coefficient of variance (CV).
+Sources of ITV for whole-leaf samples is variation among individuals within the same species and variation among leaves within the same individuals (\protect\hyperlink{ref-Messier2010}{Messier et al., 2010}, \protect\hyperlink{ref-Messier2017}{2017}).
+An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
+Thus, extents of ITV for each species based on whole-leaf and leaf discs samples may not match.
+Despite the importance of ITV in community ecology (\protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013}; \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), the effect of different measurement methods on the extent of ITV has been largely ignored.
+
+In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf thicknesses, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
+We collected a total of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
+We predicted that the overall relationship between whole-leaf LMA and disc LMA would be weaker than previous reported LMA data (\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in Kraft et al.
+(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} = 0.92 for leaf laminas in Onoda et al.
+(\protect\hyperlink{ref-Onoda2011}{2011})) because we collected data with various leaf sizes from a wide range of climates.
+We also predicted that species with larger and/or thinner leaves would show weaker correlations.
+Finally, we predicted that amounts of intraspecifc variations for each species do not match well between whole-leaf and leaf disc based estimates.
 
@@
 
-We used newly compiled individual-level plant datasets form a wide
-ranges of biomes in China and Japan (Table S1) to examine the
-relationship between whole-leaf and leaf disc-based estimates of leaf
-traits. First, the Yunnan dataset is from three forest plots in Yunnan
-province, Southwest China, which includes a tropical rain forest (TRF),
-a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet
-forest (STF), with a total of species and individuals. Second, the
-Yakushima data is from a warm-temperate forest in Yakushima island,
-Japan, with a total of 193 species and individuals. In total, we used
-334 woody species and individuals. The methodologies for trait sampling
-and measurement are slightly different between the Yunnan and the
-Yakushima dataset, which we describe bellow.
+We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
+First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
+Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
+In total, we used 334 woody species and individuals.
+The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.
 
@@
 
-At the TRF site, we collected leaf samples from trees within reach of a
-canopy crane (88 m tall with a 60 m long boom). In the HDS, and STF
-sites, we used a 12-m long pruner to collect samples for most of the
-target species. In case of tall individuals that out of the reach of
-pruner, we used a rope climbing to reach the canopy, then sampled
-branches with the long pruner. In Yakushima, we used 15-m poles for our
-leaf sampling. At least six sun-exposed healthy leaves were sampled from
-each of 3 to 6 individuals for each species. Trait values were averaged
-at the species- and individual-level for the analyses. For
-compound-leaved species, we referred a leaflet (the minimum
-photosynthetic unit) as a single leaf in our study.
-
-To determine what extent LMA values were affected by the different
-methods, LMA were determined (i) LMA based on a whole leaf including
-petioles and (ii) LMA based on leaf disc avoiding thick veins. Three
-0.6-cm diameter discs were taken from the base, middle and tip of each
-leaf using a hole punch in the Yunnan dataset. Two 1.0-cm diameter discs
-were taken from each leaf were in the Yakushima dataset. Fresh leaf area
-(LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including
-petioles and midribs) was measured using a scanner and ImageJ software
-by the R package \emph{LeafArea}
-(\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}). Fresh leaf
-thickness (LT; mm) was measured using a micrometer in three points at
-the base, middle and tip of the leaf using a micrometer (Mitutoyo
-293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at
-0.001 mm. Thickness of each leaf disc was also measured for the Yunnan
-dataset but not for the Yakushima dataset, which enables us to estimate
-whole-leaf and leaf disc leaf tissue density (LD; g
-cm\textsuperscript{-3}) separately in the Yunnan dataset. Leaf dry mass
-(whole leaves including petioles and midribs, and leaf discs) was
-recorded after drying 80°C for over 48 h to constant weight using an
-electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a
-precision at 0.0001 g. In the subset of Yakushima dataset, leaf lamina
-and petiole dry mass were also determined separately (86 out of 193
-species) to quantify leaf support costs. Dry mass for leaf discs were
-recorded 2-3 discs together for each leaf. Based on those measurements
-of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was
-calculated as the ratio of leaf dry mass to fresh leaf area, and LD was
-calculated as the ratio of LMA to LT. We do not present results of LD in
-the main text, because differences between whole-leaf LD and leaf disc
-LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
-and measurement errors of leaf thickness (Appendix S2).
-
-\emph{Statistical analyses}
-
-\emph{new subsection}
-
-To quantify the effect of leaf sizes and thicknesses on the relationship
-between whole-leaf and leaf disc LMA, we built hierarchical Bayes
-models. The whole-leaf LMA was assumed to follow a normal distribution
-(N) with the mean of leaf disc LMA and covariates of leaf size and leaf
-thickness on the log-scale;
-
-\[
-\mathrm{ln}(LMA_{Wi}) \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i)
-\]
-
-\[
-\tilde{\mu_i} = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i})
-\]
-
-where \(LMA_{Wi}\), \(LMA_{Di}\), \(LA_{i}\), \(LT_{i}\) are the
-whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree
-\emph{i}, respectively. \(\tilde{\mu_i}\) is the effect of leaf area and
-leaf thickness on the mean estimates for the whole-leaf LMA of tree
-\emph{i}, and \(\sigma_i\) is the variance of whole-leaf LMA for tree
-\emph{i}, and \(\beta\) are coefficients.
-
-The variance of whole-leaf LMA (\(\sigma_i\)) was assumed to follow a
-normal distribution;
-
-\[
-\mathrm{ln}(\sigma_i) \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega)
-\]
-
-\[
-\tilde{\sigma_i} = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i})
-\]
-
-where \(\tilde{\sigma_i}\) is the effect of leaf area and leaf thickness
-on the variance of whole-leaf LMA, \(\omega\) is a scaling
-hyperparameter, and \(\gamma\) are coefficients. To allow comparisons
-among parameter estimates, \(\mathrm{ln}(LA)\) and \(\mathrm{ln}(LT)\)
-were scaled to a mean of 0 and standard deviation of 1.
-
-Posterior distributions of all parameters were estimated using the
-Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan
-(\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}) using
-the weakly-informative priors (\protect\hyperlink{ref-Gelman2008}{Gelman
-et al., 2008}). See supplement XXXX for more detail. The Stan code use
-to fit models is available from Github at:
-\url{https://github.com/mattocci27/leaf-disc}. Convergence of the
-posterior distribution was assessed with the Gelman-Rubin statistic with
-a convergence threshold of 1.1 for all parameters
-(\protect\hyperlink{ref-Gelman2013}{Gelman et al., 2013}).
-
-\emph{new subsection}
-
-Bivariate trait relationships between disc-based and whole-leaf
-log-transformed LMA were summarized with variance explained
-(\emph{R\textsuperscript{2}}) based on Pearson correlations and with
-standardized major axis (SMA) regressions
-(\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the
-samples and different leaf area and thickness groups. Species and
-individual groups were divided into four categories based on the medians
-of leaf area and leaf thickness across all species and all individuals,
-respectively: thin and small-leaved, thin and large-leaved, thick and
-small-leaved, thick and large-leaved species (individuals). Median
-values are as following: small-leaved species (LA \textless{}
-cm\textsuperscript{2}), thin-leaved species (LT \textless{} mm),
-small-leaved individuals (LA \textless{} cm\textsuperscript{2}), and
-thin-leaved individuals (LT \textless{} mm).
-
-\emph{new subsection?}
-
-The amount of intraspecific variation (ITV) was calculated using Bao's
-CV estimator (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020});
-
-\[
-CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N}
-\]
-
-where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and
-\(\bar{x}\) is the sample mean, \emph{N} is the sample size, and
-\(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait
-distribution. Bao's CV estimator is a robust method to quantify ITV
-based on coefficient of variation (CV) when sample size is small
-(\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
-
-SMA analyses were run using the R package \emph{smatr}
-(\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this
-included tests for slope heterogeneity and elevation differences between
-disc-based and whole-leaf estimates of LMA values. Confidence intervals
-of SMA estimates were based on 2000 bootstraps. All statistical analyses
-were conducted in R version 4.1.3
-(\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}).
+At the TRF site, we collected leaf samples from trees within reach of a canopy crane (88 m tall with a 60 m long boom).
+In the HDS, and STF sites, we used a 12-m long pruner to collect samples for most of the target species.
+In case of tall individuals that out of the reach of pruner, we used a rope climbing to reach the canopy, then sampled branches with the long pruner.
+In Yakushima, we used 15-m poles for our leaf sampling.
+At least six sun-exposed healthy leaves were sampled from each of 3 to 6 individuals for each species.
+Trait values were averaged at the species- and individual-level for the analyses.
+For compound-leaved species, we referred a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
+
+To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins.
+Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
+Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset.
+Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
+Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf using a micrometer (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
+Thickness of each leaf disc was also measured for the Yunnan dataset but not for the Yakushima dataset, which enables us to estimate whole-leaf and leaf disc leaf tissue density (LD; g cm\textsuperscript{-3}) separately in the Yunnan dataset.
+Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a precision at 0.0001 g.
+In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (86 out of 193 species) to quantify leaf support costs.
+Dry mass for leaf discs were recorded 2-3 discs together for each leaf.
+Based on those measurements of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
+We do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S2).
+
+\emph{Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA}
+
+To quantify the effect of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA, we built hierarchical Bayes models.
+The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of leaf size and leaf thickness on the log-scale;
+
+\begin{align}
+\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i) \label{eq:LMA}\\
+\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i}) \label{eq:mu}
+\end{align}
+
+where \(LMA_{Wi}\), \(LMA_{Di}\), \(LA_{i}\), \(LT_{i}\) are the whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree \emph{i}, respectively.
+\(\tilde{\mu_i}\) is the effect of leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree \emph{i}, and \(\sigma_i\) is the variance of whole-leaf LMA for tree \emph{i}, and \(\beta\) are coefficients.
+
+The variance of whole-leaf LMA (\(\sigma_i\)) was assumed to follow a normal distribution;
+
+\begin{align}
+\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega) \label{eq:ln-sigma} \\
+\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i}) \label{eq:tilde-sigma}
+\end{align}
+
+where \(\tilde{\sigma_i}\) is the effect of leaf area and leaf thickness on the variance of whole-leaf LMA,
+\(\omega\) is a scaling hyperparameter, and \(\gamma\) are coefficients.
+To allow comparisons among parameter estimates, \(\mathrm{ln}(LA)\) and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
+
+Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}) using the weakly-informative priors (\protect\hyperlink{ref-Gelman2008}{Gelman et al., 2008}).
+See supplement XXXX for more detail.
+The Stan code use to fit models is available from Github at: \url{https://github.com/mattocci27/leaf-disc}.
+Convergence of the posterior distribution was assessed with the Gelman-Rubin statistic with a convergence threshold of 1.1 for all parameters (\protect\hyperlink{ref-Gelman2013}{Gelman et al., 2013}).
+
+\emph{Bivariate trait relationships}
+
+Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with standardized major axis (SMA) regressions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the samples and different leaf area and thickness groups.
+Species and individual groups were divided into four categories based on the medians of leaf area and leaf thickness across all species and all individuals, respectively:
+thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species (individuals).
+Median values are as following:
+small-leaved species (LA \textless{} cm\textsuperscript{2}),
+thin-leaved species (LT \textless{} mm),
+small-leaved individuals (LA \textless{} cm\textsuperscript{2}),
+and thin-leaved individuals (LT \textless{} mm).
+
+\emph{Intraspecifc variation}
+
+The amount of intraspecific variation (ITV) was calculated using Bao's CV estimator (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020});
+
+\begin{align}
+CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} \label{eq:CV}
+\end{align}
+
+where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and \(\bar{x}\) is the sample mean, \emph{N} is the sample size, and \(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait distribution.
+Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
+
+SMA analyses were run using the R package \emph{smatr} (\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
+Confidence intervals of SMA estimates were based on 2000 bootstraps.
+All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}).
 
@@
 
-Disc-based estimates of species mean LMA matched well whole-leaf
-estimates (Table 1; \emph{R\textsuperscript{2}} = for all species).
-Species with thicker and smaller leaves had stronger correlations
-between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
-There was a negative correlation between species mean leaf area and leaf
-thickness (\emph{r} = , \emph{P} , \emph{n} = ). When we pooled all the
-species, there were significant differences in intercepts for species
-mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were
-9.4\% greater than disc-based estimates in the arithmetic scale.
-Large-leaved species also had significant positive intercepts,
-suggesting that whole-leaf estimates of LMA were 22.1\% greater than
-disc-based estimates in the arithmetic scale (Table 1). Intercepts did
-not differ for small-leaved species (Table 1).
-
-Disc-based estimates of individual mean LMA also showed positive
-correlations with whole-leaf estimates but their
-\emph{R\textsuperscript{2}} values were smaller than those for the
-species means (Fig. 2). Similar to the species-level pattern,
-individuals with thicker and smaller leaves had stronger correlations
-(Fig. 2). The relationships of the whole-leaf LMA : disc leaf LMA ratio
-with total dry mass for the leaf disc (we weighted 2-3 discs together),
-with leaf thickness, and with leaf area were heteroscedastic (unequal
-variance, \emph{P} \textless{} 0.001; Appendix S3). Samples with small
-total dry mass, thin leaves, and larger leaves tended to show greater
-variance (Fig. 2; Appendix S3). The total dry mass of leaf disc was
-positively correlated with both leaf thickness and leaf punch size
-(Appendix S4). Amounts of intraspecific variation (CV; coefficient of
-variation) only weakly matched between whole-leaf and disc-based
-estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.33).
+Disc-based estimates of species mean LMA matched well whole-leaf estimates (Table 1; \emph{R\textsuperscript{2}} = for all species).
+Species with thicker and smaller leaves had stronger correlations between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
+There was a negative correlation between species mean leaf area and leaf thickness (\emph{r} = , \emph{P} , \emph{n} = ).
+When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4\% greater than disc-based estimates in the arithmetic scale.
+Large-leaved species also had significant positive intercepts, suggesting that whole-leaf estimates of LMA were 22.1\% greater than disc-based estimates in the arithmetic scale (Table 1).
+Intercepts did not differ for small-leaved species (Table 1).
+
+Disc-based estimates of individual mean LMA also showed positive correlations with whole-leaf estimates but their \emph{R\textsuperscript{2}} values were smaller than those for the species means (Fig.
+2).
+Similar to the species-level pattern, individuals with thicker and smaller leaves had stronger correlations (Fig. 2).
+The relationships of the whole-leaf LMA : disc leaf LMA ratio with total dry mass for the leaf disc (we weighted 2-3 discs together), with leaf thickness, and with leaf area were heteroscedastic (unequal variance, \emph{P} \textless{} 0.001; Appendix S3).
+Samples with small total dry mass, thin leaves, and larger leaves tended to show greater variance (Fig. 2; Appendix S3).
+The total dry mass of leaf disc was positively correlated with both leaf thickness and leaf punch size (Appendix S4).
+Amounts of intraspecific variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.33).
 
@@
 
-Disc-based traits explained interspecific variations in whole-leaf LMA
-(\emph{R\textsuperscript{2}} = , \emph{n} = ) quite well, and the
-strength of their relationship was approximately same or slightly weaker
-than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} =
-409, for whole-leaves in Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} =
-0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
-(\protect\hyperlink{ref-Onoda2011}{2011})). Standardized major axis
-(SMA) regression analysis showed significantly greater intercepts when
-all the species were pooled (9.4\% differences) or large-leaved species
-were used (22.1\% differences). Together, these findings suggest that
-disc-based estimates can be generally used as good proxies for their
-whole-leaf estimates with appropriate calibration. However, the strength
-of correlations highly depended on leaf area, thickness (Fig. 1) and
-sizes of leaf punches (Appendix S3 and S5).
-
-Larger leaves generally invest disproportionally more mass into dense
-midribs and major veins for support
-(\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006},
-\protect\hyperlink{ref-Niinemets2007}{2007};
-\protect\hyperlink{ref-Sack2012}{Sack et al., 2012}), and thinner leaves
-have distinct veins and have kite-type appearances
-(\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}). As we predicted,
-thicker and/or smaller leaves tended to show greater
-\emph{R\textsuperscript{2}} values between whole-leaf and leaf disc
-estimates (Figs 1. and 2). Large-leaved species had greater whole-leaf
-LMA than leaf disc LMA (Table 1), which is consistent with the pattern
-of large leaves disproportionately investing in more leaf veins and/or
-petioles. This is also supported by the subset of our dataset in which
-we measured leaf lamina and petiole dry mass separately. We confirmed
-that leaf disc and whole-leaf LMA estimate diverged for species with
-greater investment in petiole dry mass, and large-leaved species tended
-to have greater investment for petiole dry mass than small-leaved
-species (Appendix S6).
-
-Meanwhile, our results are seemingly inconsistent with a previous study
-that used thin and soft leaves and found high
-\emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92;
-Kraft et al. (\protect\hyperlink{ref-Kraft2008}{2008})). Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}) used sapling leaves under
-closed canopy that are thinner than adult leaves
-(\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010};
-\protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}). Shade
-leaves tend to have thinner leaves than sun leaves because of fewer
-layers of palisade mesophyll cells
-(\protect\hyperlink{ref-Terashima2001}{Terashima et al., 2001};
-\protect\hyperlink{ref-Onoda2008}{Onoda et al., 2008}). The relatively
-low \emph{R\textsuperscript{2}} values for thin-leaved species and
-individuals in our study compared to the previous study may suggest not
-only the effect of distinct veins on variance in LMA
-(\protect\hyperlink{ref-John2017}{John et al., 2017}) but also technical
-difficulty in measuring tiny weight of discs in lower LMA leaves. We
-found that estimates of whole-leaf and leaf disc LMA diverged when total
-dry mass of leaf discs was small (Fig. 2; Appendices S3), and thus
-thin-leaved species, which have smaller dry mass (Appendix S4), tended
-to showed the low \emph{R\textsuperscript{2}} values especially when we
-used a smaller leaf punch (diameter: 0.6 cm; Appendix S5).
-
-Even though we used the same species, the same individuals and the same
-trait (LMA) to estimate the extents of intraspecific trait variation
-(ITV), the explained variance of the relationship between whole-leaf and
-disc-based estimate was surprisingly small (Fig. 3;
-\emph{R\textsuperscript{2}} = 0.33). This is probably because leaf disc
-samples have more sources of ITV than whole-leaf samples (i.e.,
-variation among leaf discs within the same leaves). Although there are
-not many studies that quantified trait variation within a single leaf, a
-previous study that used a giant leaved species \emph{Alocasia
-macrorrhiza}, suggests that LMA varied within leaves due to reduced
-water supply and demand from midrib to outer regions
-(\protect\hyperlink{ref-Li2013a}{Li et al., 2013}). Because calculating
-the mean values generally diminishes the effect of within-sample
-variation, the relationship between disc-based estimates of individual
-mean LMA and its whole-leaf estimates will be stronger than the
-relationship between leaf disc CV and whole-leaf CV. Thus, leaf disc and
-whole-leaf estimates of species means will show the strongest
-relationship. This is consistent with the \emph{R\textsuperscript{2}}
-values in our results (Figs. 1-3). The mismatch of ITV between
-whole-leaf and disc-based estimate could be ignored in community-level
-ITV studies (i.e., \protect\hyperlink{ref-Siefert2015}{Siefert et al.,
-2015}), which quantify the total variance of ITV within communities.
-However, it is likely to change patterns for species-level ITV studies
-(i.e., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}), which
-quantify extents of ITV for each species, since species with high ITV
-based on leaf-disc estimates do not always have to show high ITV for
-whole-leaf estimates. This problem will be more obvious when one uses
-smaller leaf punches (Appendix S7).
-
-The present study was designed to examine the extent to which whole leaf
-and leaf disc LMA matched. Our study shows that mean values of leaf disc
-LMA is generally a good proxy for mean values of whole-leaf LMA.
-However, larger and thinner leaves tended to show the large
-discrepancies between the leaf disc and whole-leaf estimates, and thus
-when one needs to mix leaf disc LMA and whole-leaf LMA in a single
-analysis (e.g., meta-analysis), appropriate calibrations are necessary.
-Although our study was not designed to evaluate the effects of diameter
-sizes of leaf punches, the sizes of leaf punches are also the important
-sources of variance between whole-leaf and leaf disc LMA. This is
-probably because small dry mass inflates measurement errors and small
-leaf disc size inflates trait variation within leaves. Additionally,
-although the mean values of leaf disc and whole-leaf LMA matched well,
-quantifying trait variation using leaf discs should be considered with
-caution, because variation among leaf discs within the same leaves
-(including measurement errors) seems to be large. Leaf discs, which can
-target leaf lamina avoiding leaf veins, are useful and essential for
-biochemical determinations such as measurements of Rubisco activity
-(\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because the
-photosynthetic activity occurs most in lamina rather than in veins for
-C\textsubscript{3} plants (\protect\hyperlink{ref-Hibberd2002}{Hibberd
-and Quick, 2002}; \protect\hyperlink{ref-Gao2018}{Gao et al., 2018}).
-Leaf disc LMA is also the preferred method for quantifying leaf lamina
-density, which avoid effects of veins. However, if the objective is to
-use leaf disc LMA as an alternative for whole-leaf LMA, using an
-appropriate size of leaf punch is important for obtaining stable
-estimates of leaf disc LMA that matches well with whole-leaf LMA.
+Disc-based traits explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = , \emph{n} = ) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in Kraft et al.
+(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
+(\protect\hyperlink{ref-Onoda2011}{2011})).
+Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4\% differences) or large-leaved species were used (22.1\% differences).
+Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration.
+However, the strength of correlations highly depended on leaf area, thickness (Fig. 1) and sizes of leaf punches (Appendix S3 and S5).
+
+Larger leaves generally invest disproportionally more mass into dense midribs and major veins for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Sack2012}{Sack et al., 2012}), and thinner leaves have distinct veins and have kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}).
+As we predicted, thicker and/or smaller leaves tended to show greater \emph{R\textsuperscript{2}} values between whole-leaf and leaf disc estimates (Figs 1. and 2).
+Large-leaved species had greater whole-leaf LMA than leaf disc LMA (Table 1), which is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles.
+This is also supported by the subset of our dataset in which we measured leaf lamina and petiole dry mass separately.
+We confirmed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass, and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Appendix S6).
+
+Meanwhile, our results are seemingly inconsistent with a previous study that used thin and soft leaves and found high \emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92; Kraft et al.
+(\protect\hyperlink{ref-Kraft2008}{2008})).
+Kraft et al.
+(\protect\hyperlink{ref-Kraft2008}{2008}) used sapling leaves under closed canopy that are thinner than adult leaves (\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010}; \protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}).
+Shade leaves tend to have thinner leaves than sun leaves because of fewer layers of palisade mesophyll cells (\protect\hyperlink{ref-Terashima2001}{Terashima et al., 2001}; \protect\hyperlink{ref-Onoda2008}{Onoda et al., 2008}).
+The relatively low \emph{R\textsuperscript{2}} values for thin-leaved species and individuals in our study compared to the previous study may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Fig.
+2; Appendices S3), and thus thin-leaved species, which have smaller dry mass (Appendix S4), tended to showed the low \emph{R\textsuperscript{2}} values especially when we used a smaller leaf punch (diameter: 0.6 cm; Appendix S5).
+
+Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig.
+3; \emph{R\textsuperscript{2}} = 0.33).
+This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
+Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species \emph{Alocasia macrorrhiza}, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions (\protect\hyperlink{ref-Li2013a}{Li et al., 2013}).
+Because calculating the mean values generally diminishes the effect of within-sample variation, the relationship between disc-based estimates of individual mean LMA and its whole-leaf estimates will be stronger than the relationship between leaf disc CV and whole-leaf CV.
+Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
+This is consistent with the \emph{R\textsuperscript{2}} values in our results (Figs. 1-3).
+The mismatch of ITV between whole-leaf and disc-based estimate could be ignored in community-level ITV studies (i.e., \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), which quantify the total variance of ITV within communities.
+However, it is likely to change patterns for species-level ITV studies (i.e., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}), which quantify extents of ITV for each species, since species with high ITV based on leaf-disc estimates do not always have to show high ITV for whole-leaf estimates.
+This problem will be more obvious when one uses smaller leaf punches (Appendix S7).
+
+The present study was designed to examine the extent to which whole leaf and leaf disc LMA matched.
+Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA.
+However, larger and thinner leaves tended to show the large discrepancies between the leaf disc and whole-leaf estimates, and thus when one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis), appropriate calibrations are necessary.
+Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches are also the important sources of variance between whole-leaf and leaf disc LMA.
+This is probably because small dry mass inflates measurement errors and small leaf disc size inflates trait variation within leaves.
+Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be large.
+Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity (\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because the photosynthetic activity occurs most in lamina rather than in veins for C\textsubscript{3} plants (\protect\hyperlink{ref-Hibberd2002}{Hibberd and Quick, 2002}; \protect\hyperlink{ref-Gao2018}{Gao et al., 2018}).
+Leaf disc LMA is also the preferred method for quantifying leaf lamina density, which avoid effects of veins.
+However, if the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
 
@@
 
-The authors thank Lian-Bin Tao and Peng-Yun Yan for field work. This
-work was funded by the National Natural Science Foundation of China
-(41861144016, 32071735, 31570406, 32171507), the CAS `Light of West
-China' Program, Yunnan Provincial Science and Technology Department
-(2018HB068). PM was supported by financial support from CAS-TWAS
-President's Fellowship for International Doctoral Students. MK was
-supported by CAS President's International Fellowship Initiative
-(2020FYB0003).
+The authors thank Lian-Bin Tao and Peng-Yun Yan for field work.
+This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).
+PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.
+MK was supported by CAS President's International Fellowship Initiative (2020FYB0003).
 
@@
 
-PM, MK, and YJC conceived the study; PM, YO, and YJC collected data; MK
-and CZ performed the analysis; MK and YJC led the writing of the paper;
-and all authors contributed to revisions.
+PM, MK, and YJC conceived the study;
+PM, YO, and YJC collected data;
+MK and CZ performed the analysis;
+MK and YJC led the writing of the paper; and
+all authors contributed to revisions.
 
 \hypertarget{data-availability-statement}{%
-\section{DATA AVAILABILITY
-STATEMENT}\label{data-availability-statement}}
-
-Data and codes for this manuscript are archived and available on Zenodo
-(XXX).
+\section{DATA AVAILABILITY STATEMENT}\label{data-availability-statement}}
+
+Data and codes for this manuscript are archived and available on Zenodo (XXX).
 
@@
 
-Additional supporting information may be found online in the Supporting
-Information section at the end of the article.
-
-\textbf{APPENDIX S1.} Site information.
-
-\textbf{APPENDIX S2.} Generalization for a relationship between ratios
-of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf
-tissue density (LD), and leaf thickness (LT).
-
-\textbf{APPENDIX S3.} Relationships between whole-leaf LMA : disc leaf
-LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and
-(c) leaf area.
-
-\textbf{APPENDIX S4.} Summary of multiple regression for log-transformed
-total dry mass of leaf discs.
-
-\textbf{APPENDIX S5.} Relationships between species mean leaf mass per
-area (LMA) determined by using whole leaves and leaf discs.
-
-\textbf{APPENDIX S6.} Relationships between petiole to leaf dry mass
-ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
-
-\textbf{APPENDIX S7.} Relationships between coefficient of variation
-(CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm
-diameter leaf punch, and (b) 1.0 cm diameter leaf punch.
+Additional supporting information may be found online in the Supporting Information section at the end of the article.
+
+\textbf{APPENDIX S1.}
+Site information.
+
+\textbf{APPENDIX S2.}
+Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
+
+\textbf{APPENDIX S3.}
+Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and (c) leaf area.
+
+\textbf{APPENDIX S4.}
+Summary of multiple regression for log-transformed total dry mass of leaf discs.
+
+\textbf{APPENDIX S5.}
+Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
+
+\textbf{APPENDIX S6.}
+Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
+
+\textbf{APPENDIX S7.}
+Relationships between coefficient of variation (CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and (b) 1.0 cm diameter leaf punch.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Albert2010a}{}}%
-Albert, C. H., W. Thuiller, N. G. Yoccoz, A. Soudant, F. Boucher, P.
-Saccone, and S. Lavorel. 2010.
-\href{https://doi.org/10.1111/j.1365-2745.2010.01651.x}{Intraspecific
-functional variability: {Extent}, structure and sources of variation}.
+Albert, C.
+H., W.
+Thuiller, N.
+G.
+Yoccoz, A.
+Soudant, F.
+Boucher, P.
+Saccone, and S.
+Lavorel.
+2010.
+\href{https://doi.org/10.1111/j.1365-2745.2010.01651.x}{Intraspecific functional variability: {Extent}, structure and sources of variation}.
 \emph{Journal of Ecology} 98: 604--613.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
-Carpenter, B., A. Gelman, M. D. Hoffman, D. Lee, B. Goodrich, M.
-Betancourt, M. Brubaker, et al. 2017.
-\href{https://doi.org/10.18637/jss.v076.i01}{Stan : {A Probabilistic
-Programming Language}}. \emph{Journal of Statistical Software} 76:
-1--32.
+Carpenter, B., A.
+Gelman, M.
+D.
+Hoffman, D.
+Lee, B.
+Goodrich, M.
+Betancourt, M.
+Brubaker, et al.
+2017.
+\href{https://doi.org/10.18637/jss.v076.i01}{Stan : {A Probabilistic Programming Language}}.
+\emph{Journal of Statistical Software} 76: 1--32.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Diaz2004}{}}%
-Díaz, S., J. G. Hodgson, K. Thompson, M. Cabido, J. H. C. Cornelissen,
-A. Jalili, G. Montserrat-Martí, et al. 2004.
-\href{https://doi.org/10.1658/1100-9233(2004)015\%5B0295:TPTTDE\%5D2.0.CO;2}{The
-plant traits that drive ecosystems: {Evidence} from three continents}.
+Díaz, S., J.
+G.
+Hodgson, K.
+Thompson, M.
+Cabido, J.
+H.
+C.
+Cornelissen, A.
+Jalili, G.
+Montserrat-Martí, et al.
+2004.
+\href{https://doi.org/10.1658/1100-9233(2004)015\%5B0295:TPTTDE\%5D2.0.CO;2}{The plant traits that drive ecosystems: {Evidence} from three continents}.
 \emph{Journal of Vegetation Science} 15: 295.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Diaz2016}{}}%
-Díaz, S., J. Kattge, J. H. C. Cornelissen, I. J. Wright, S. Lavorel, S.
-Dray, B. Reu, et al. 2016.
-\href{https://doi.org/10.1038/nature16489}{The global spectrum of plant
-form and function}. \emph{Nature} 529: 167--171.
+Díaz, S., J.
+Kattge, J.
+H.
+C.
+Cornelissen, I.
+J.
+Wright, S.
+Lavorel, S.
+Dray, B.
+Reu, et al.
+2016.
+\href{https://doi.org/10.1038/nature16489}{The global spectrum of plant form and function}.
+\emph{Nature} 529: 167--171.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Evans1972}{}}%
-Evans, G. C. 1972. The quantitative analysis of plant growth. {Univ of
-California Press}.
+Evans, G. C. 1972. The quantitative analysis of plant growth. {Univ of California Press}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Falster2018}{}}%
-Falster, D. S., R. A. Duursma, and R. G. FitzJohn. 2018.
-\href{https://doi.org/10.1073/pnas.1714044115}{How functional traits
-influence plant growth and shade tolerance across the life cycle}.
-\emph{Proceedings of the National Academy of Sciences} 115:
-E6789--E6798.
+Falster, D.
+S., R.
+A.
+Duursma, and R.
+G.
+FitzJohn.
+2018.
+\href{https://doi.org/10.1073/pnas.1714044115}{How functional traits influence plant growth and shade tolerance across the life cycle}.
+\emph{Proceedings of the National Academy of Sciences} 115: E6789--E6798.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gao2018}{}}%
-Gao, Z., W. Shen, and G. Chen. 2018.
-\href{https://doi.org/10.1093/jxb/ery155}{Uncovering {C4-like}
-photosynthesis in {C3} vascular cells}. \emph{Journal of Experimental
-Botany} 69: 3531--3540.
+Gao, Z., W. Shen, and G. Chen. 2018. \href{https://doi.org/10.1093/jxb/ery155}{Uncovering {C4-like} photosynthesis in {C3} vascular cells}. \emph{Journal of Experimental Botany} 69: 3531--3540.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Garnier1994}{}}%
-Garnier, E., and G. Laurent. 1994.
-\href{https://doi.org/10.1111/j.1469-8137.1994.tb04036.x}{Leaf anatomy,
-specific mass and water content in congeneric annual and perennial grass
-species}. \emph{New Phytologist} 128: 725--736.
+Garnier, E., and G.
+Laurent.
+1994.
+\href{https://doi.org/10.1111/j.1469-8137.1994.tb04036.x}{Leaf anatomy, specific mass and water content in congeneric annual and perennial grass species}.
+\emph{New Phytologist} 128: 725--736.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gelman2013}{}}%
-Gelman, A., J. B. Carlin, H. S. Stern, D. B. Dunson, A. Vehtari, and D.
-B. Rubin. 2013. Bayesian {Data Analysis}, {Third Edition}. {Taylor \&
-Francis}.
+Gelman, A., J. B. Carlin, H. S. Stern, D. B. Dunson, A. Vehtari, and D. B. Rubin. 2013. Bayesian {Data Analysis}, {Third Edition}. {Taylor \& Francis}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gelman2008}{}}%
-Gelman, A., A. Jakulin, M. G. Pittau, and Y. S. Su. 2008.
-\href{https://doi.org/10.1214/08-AOAS191}{A weakly informative default
-prior distribution for logistic and other regression models}.
+Gelman, A., A.
+Jakulin, M.
+G.
+Pittau, and Y.
+S.
+Su.
+2008.
+\href{https://doi.org/10.1214/08-AOAS191}{A weakly informative default prior distribution for logistic and other regression models}.
 \emph{Annals of Applied Statistics} 2: 1360--1383.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Grubb1986}{}}%
-Grubb, P. 1986. Sclerophylls, pachyphylls, and pycnophylls: {The} nature
-and significance of hard leaf surface. \emph{Insects and the Plant
-Surface}: 137--150.
+Grubb, P. 1986. Sclerophylls, pachyphylls, and pycnophylls: {The} nature and significance of hard leaf surface. \emph{Insects and the Plant Surface}: 137--150.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hanson1917}{}}%
-Hanson, H. C. 1917. Leaf-structure as related to environment.
-\emph{American Journal of Botany}: 533--560.
+Hanson, H. C. 1917. Leaf-structure as related to environment. \emph{American Journal of Botany}: 533--560.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hibberd2002}{}}%
-Hibberd, J. M., and W. P. Quick. 2002.
-\href{https://doi.org/10.1038/415451a}{Characteristics of {C4}
-photosynthesis in stems and petioles of {C3} flowering plants}.
-\emph{Nature} 415: 451--454.
+Hibberd, J. M., and W. P. Quick. 2002. \href{https://doi.org/10.1038/415451a}{Characteristics of {C4} photosynthesis in stems and petioles of {C3} flowering plants}. \emph{Nature} 415: 451--454.
 
 \leavevmode\vadjust pre{\hypertarget{ref-John2017}{}}%
-John, G. P., C. Scoffoni, T. N. Buckley, R. Villar, H. Poorter, and L.
-Sack. 2017. \href{https://doi.org/10.1111/ele.12739}{The anatomical and
-compositional basis of leaf mass per area}. \emph{Ecology Letters} 20:
-412--425.
+John, G.
+P., C.
+Scoffoni, T.
+N.
+Buckley, R.
+Villar, H.
+Poorter, and L.
+Sack.
+2017.
+\href{https://doi.org/10.1111/ele.12739}{The anatomical and compositional basis of leaf mass per area}.
+\emph{Ecology Letters} 20: 412--425.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Katabuchi2015}{}}%
-Katabuchi, M. 2015.
-\href{https://doi.org/10.1007/s11284-015-1307-x}{{LeafArea}: An {R}
-package for rapid digital image analysis of leaf area}. \emph{Ecological
-Research} 30: 1073--1077.
+Katabuchi, M. 2015. \href{https://doi.org/10.1007/s11284-015-1307-x}{{LeafArea}: An {R} package for rapid digital image analysis of leaf area}. \emph{Ecological Research} 30: 1073--1077.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kattge2020}{}}%
-Kattge, J., G. Bönisch, S. Díaz, S. Lavorel, I. C. Prentice, P. Leadley,
-S. Tautenhahn, et al. 2020.
-\href{https://doi.org/10.1111/gcb.14904}{{TRY} plant trait database
-\textendash{} enhanced coverage and open access}. \emph{Global Change
-Biology} 26: 119--188.
+Kattge, J., G.
+Bönisch, S.
+Díaz, S.
+Lavorel, I.
+C.
+Prentice, P.
+Leadley, S.
+Tautenhahn, et al.
+2020.
+\href{https://doi.org/10.1111/gcb.14904}{{TRY} plant trait database \textendash{} enhanced coverage and open access}.
+\emph{Global Change Biology} 26: 119--188.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kichenin2013}{}}%
-Kichenin, E., D. A. Wardle, D. A. Peltzer, C. W. Morse, and G. T.
-Freschet. 2013.
-\href{https://doi.org/10.1111/1365-2435.12116}{Contrasting effects of
-plant inter- and intraspecific variation on community-level trait
-measures along an environmental gradient}. \emph{Functional Ecology} 27:
-1254--1261.
+Kichenin, E., D.
+A.
+Wardle, D.
+A.
+Peltzer, C.
+W.
+Morse, and G.
+T.
+Freschet.
+2013.
+\href{https://doi.org/10.1111/1365-2435.12116}{Contrasting effects of plant inter- and intraspecific variation on community-level trait measures along an environmental gradient}.
+\emph{Functional Ecology} 27: 1254--1261.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kitajima2010}{}}%
-Kitajima, K., and L. Poorter. 2010.
-\href{https://doi.org/10.1111/j.1469-8137.2010.03212.x}{Tissue-level
-leaf toughness, but not lamina thickness, predicts sapling leaf lifespan
-and shade tolerance of tropical tree species}. \emph{New Phytologist}
-186: 708--721.
+Kitajima, K., and L.
+Poorter.
+2010.
+\href{https://doi.org/10.1111/j.1469-8137.2010.03212.x}{Tissue-level leaf toughness, but not lamina thickness, predicts sapling leaf lifespan and shade tolerance of tropical tree species}.
+\emph{New Phytologist} 186: 708--721.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kraft2008}{}}%
-Kraft, N. J. B., R. Valencia, and D. D. Ackerly. 2008.
-\href{https://doi.org/10.1126/science.1160662}{Functional {Traits} and
-{Niche-Based Tree Community Assembly} in an {Amazonian Forest}}.
+Kraft, N.
+J.
+B., R.
+Valencia, and D.
+D.
+Ackerly.
+2008.
+\href{https://doi.org/10.1126/science.1160662}{Functional {Traits} and {Niche-Based Tree Community Assembly} in an {Amazonian Forest}}.
 \emph{Science} 322: 580--582.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Li2013a}{}}%
-Li, S., Y.-J. Zhang, L. Sack, C. Scoffoni, A. Ishida, Y.-J. Chen, and
-K.-F. Cao. 2013. \href{https://doi.org/10.1371/journal.pone.0066016}{The
-heterogeneity and spatial patterning of structure and physiology across
-the leaf surface in giant leaves of alocasia macrorrhiza}. \emph{PLOS
-ONE} 8: 1--10.
+Li, S., Y.-J.
+Zhang, L.
+Sack, C.
+Scoffoni, A.
+Ishida, Y.-J.
+Chen, and K.-F.
+Cao.
+2013.
+\href{https://doi.org/10.1371/journal.pone.0066016}{The heterogeneity and spatial patterning of structure and physiology across the leaf surface in giant leaves of alocasia macrorrhiza}.
+\emph{PLOS ONE} 8: 1--10.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Messier2017}{}}%
-Messier, J., B. J. McGill, B. J. Enquist, and M. J. Lechowicz. 2017.
-\href{https://doi.org/10.1111/ecog.02006}{Trait variation and
-integration across scales: Is the leaf economic spectrum present at
-local scales?} \emph{Ecography} 40: 685--697.
+Messier, J., B.
+J.
+McGill, B.
+J.
+Enquist, and M.
+J.
+Lechowicz.
+2017.
+\href{https://doi.org/10.1111/ecog.02006}{Trait variation and integration across scales: Is the leaf economic spectrum present at local scales?} \emph{Ecography} 40: 685--697.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Messier2010}{}}%
-Messier, J., B. J. McGill, and M. J. Lechowicz. 2010.
-\href{https://doi.org/10.1111/j.1461-0248.2010.01476.x}{How do traits
-vary across ecological scales? {A} case for trait-based ecology}.
+Messier, J., B.
+J.
+McGill, and M.
+J.
+Lechowicz.
+2010.
+\href{https://doi.org/10.1111/j.1461-0248.2010.01476.x}{How do traits vary across ecological scales?
+{A} case for trait-based ecology}.
 \emph{Ecology Letters} 13: 838--848.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Niinemets2007}{}}%
-Niinemets, Ü., A. Portsmuth, D. Tena, M. Tobias, S. Matesanz, and F.
-Valladares. 2007. \href{https://doi.org/10.1093/aob/mcm107}{Do we
-underestimate the importance of leaf size in plant economics?
-{Disproportional} scaling of support costs within the spectrum of leaf
-physiognomy}. \emph{Annals of Botany} 100: 283--303.
+Niinemets, Ü., A.
+Portsmuth, D.
+Tena, M.
+Tobias, S.
+Matesanz, and F.
+Valladares.
+2007.
+\href{https://doi.org/10.1093/aob/mcm107}{Do we underestimate the importance of leaf size in plant economics?
+{Disproportional} scaling of support costs within the spectrum of leaf physiognomy}.
+\emph{Annals of Botany} 100: 283--303.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Niinemets2006}{}}%
-Niinemets, Ü., A. Portsmuth, and M. Tobias. 2006.
-\href{https://doi.org/10.1111/j.1469-8137.2006.01741.x}{Leaf size
-modifies support biomass distribution among stems, petioles and mid-ribs
-in temperate plants}. \emph{New Phytologist} 171: 91--104.
+Niinemets, Ü., A.
+Portsmuth, and M.
+Tobias.
+2006.
+\href{https://doi.org/10.1111/j.1469-8137.2006.01741.x}{Leaf size modifies support biomass distribution among stems, petioles and mid-ribs in temperate plants}.
+\emph{New Phytologist} 171: 91--104.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Oktavia2020}{}}%
-Oktavia, D., and G. Jin. 2020.
-\href{https://doi.org/10.1016/j.baae.2020.09.010}{Variations in leaf
-morphological and chemical traits in response to life stages, plant
-functional types, and habitat types in an old-growth temperate forest}.
+Oktavia, D., and G.
+Jin.
+2020.
+\href{https://doi.org/10.1016/j.baae.2020.09.010}{Variations in leaf morphological and chemical traits in response to life stages, plant functional types, and habitat types in an old-growth temperate forest}.
 \emph{Basic and Applied Ecology} 49: 22--33.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Onoda2008}{}}%
-Onoda, Y., F. Schieving, and N. P. R. Anten. 2008.
-\href{https://doi.org/10.1093/aob/mcn013}{Effects of light and nutrient
-availability on leaf mechanical properties of {Plantago} major: {A}
-conceptual approach}. \emph{Annals of Botany} 101: 727--736.
+Onoda, Y., F.
+Schieving, and N.
+P.
+R.
+Anten.
+2008.
+\href{https://doi.org/10.1093/aob/mcn013}{Effects of light and nutrient availability on leaf mechanical properties of {Plantago} major: {A} conceptual approach}.
+\emph{Annals of Botany} 101: 727--736.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Onoda2011}{}}%
-Onoda, Y., M. Westoby, P. B. Adler, A. M. F. Choong, F. J. Clissold, J.
-H. C. Cornelissen, S. Díaz, et al. 2011.
-\href{https://doi.org/10.1111/j.1461-0248.2010.01582.x}{Global patterns
-of leaf mechanical properties}. \emph{Ecology Letters} 14: 301--312.
+Onoda, Y., M.
+Westoby, P.
+B.
+Adler, A.
+M.
+F.
+Choong, F.
+J.
+Clissold, J.
+H.
+C.
+Cornelissen, S.
+Díaz, et al.
+2011.
+\href{https://doi.org/10.1111/j.1461-0248.2010.01582.x}{Global patterns of leaf mechanical properties}.
+\emph{Ecology Letters} 14: 301--312.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Onoda2017}{}}%
-Onoda, Y., I. J. Wright, J. R. Evans, K. Hikosaka, K. Kitajima, Ü.
-Niinemets, H. Poorter, et al. 2017.
-\href{https://doi.org/10.1111/nph.14496}{Physiological and structural
-tradeoffs underlying the leaf economics spectrum}. \emph{New
-Phytologist} 214: 1447--1463.
+Onoda, Y., I.
+J.
+Wright, J.
+R.
+Evans, K.
+Hikosaka, K.
+Kitajima, Ü.
+Niinemets, H.
+Poorter, et al.
+2017.
+\href{https://doi.org/10.1111/nph.14496}{Physiological and structural tradeoffs underlying the leaf economics spectrum}.
+\emph{New Phytologist} 214: 1447--1463.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Parry2002}{}}%
-Parry, M. A., P. J. Andralojc, S. Khan, P. J. Lea, and A. J. Keys. 2002.
-Rubisco activity: Effects of drought stress. \emph{Annals of Botany} 89:
-833--839.
+Parry, M. A., P. J. Andralojc, S. Khan, P. J. Lea, and A. J. Keys. 2002. Rubisco activity: Effects of drought stress. \emph{Annals of Botany} 89: 833--839.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Perez-Harguindeguy2013}{}}%
-Pérez-Harguindeguy, N., S. Díaz, E. Garnier, S. Lavorel, H. Poorter, P.
-Jaureguiberry, M. S. Bret-Harte, et al. 2013.
-\href{https://doi.org/10.1071/BT12225}{New handbook for standardised
-measurement of plant functional traits worldwide}. \emph{Australian
-Journal of Botany} 61: 167--234.
+Pérez-Harguindeguy, N., S.
+Díaz, E.
+Garnier, S.
+Lavorel, H.
+Poorter, P.
+Jaureguiberry, M.
+S.
+Bret-Harte, et al.
+2013.
+\href{https://doi.org/10.1071/BT12225}{New handbook for standardised measurement of plant functional traits worldwide}.
+\emph{Australian Journal of Botany} 61: 167--234.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poorter2014}{}}%
-Poorter, H., H. Lambers, and J. R. Evans. 2014.
-\href{https://doi.org/10.1111/nph.12547}{Trait correlation networks: {A}
-whole-plant perspective on the recently criticized leaf economic
-spectrum}. \emph{New Phytologist} 201: 378--382.
+Poorter, H., H.
+Lambers, and J.
+R.
+Evans.
+2014.
+\href{https://doi.org/10.1111/nph.12547}{Trait correlation networks: {A} whole-plant perspective on the recently criticized leaf economic spectrum}.
+\emph{New Phytologist} 201: 378--382.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Poorter2009}{}}%
-Poorter, H., Ü. Niinemets, L. Poorter, I. J. Wright, and R. Villar.
-2009. \href{https://doi.org/10.1111/j.1469-8137.2009.02830.x}{Causes and
-consequences of variation in leaf mass per area ({LMA}): {A}
-meta-analysis}. \emph{New Phytologist} 182: 565--588.
+Poorter, H., Ü.
+Niinemets, L.
+Poorter, I.
+J.
+Wright, and R.
+Villar.
+2009.
+\href{https://doi.org/10.1111/j.1469-8137.2009.02830.x}{Causes and consequences of variation in leaf mass per area ({LMA}): {A} meta-analysis}.
+\emph{New Phytologist} 182: 565--588.
 
 \leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
-R Core Team. 2022. R: {A} language and environment for statistical
-computing. {R Foundation for Statistical Computing}, {Vienna, Austria}.
+R Core Team. 2022. R: {A} language and environment for statistical computing. {R Foundation for Statistical Computing}, {Vienna, Austria}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Reich2014}{}}%
-Reich, P. B. 2014. \href{https://doi.org/10.1111/1365-2745.12211}{The
-world-wide 'fast-slow' plant economics spectrum: {A} traits manifesto}.
-\emph{Journal of Ecology} 102: 275--301.
+Reich, P. B. 2014. \href{https://doi.org/10.1111/1365-2745.12211}{The world-wide 'fast-slow' plant economics spectrum: {A} traits manifesto}. \emph{Journal of Ecology} 102: 275--301.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Sack2012}{}}%
-Sack, L., C. Scoffoni, A. D. McKown, K. Frole, M. Rawls, J. C. Havran,
-H. Tran, and T. Tran. 2012. Developmentally based scaling of leaf
-venation architecture explains global ecological patterns. \emph{Nature
-Communications} 3: 1--10.
+Sack, L., C.
+Scoffoni, A.
+D.
+McKown, K.
+Frole, M.
+Rawls, J.
+C.
+Havran, H.
+Tran, and T.
+Tran.
+2012.
+Developmentally based scaling of leaf venation architecture explains global ecological patterns.
+\emph{Nature Communications} 3: 1--10.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Siefert2015}{}}%
-Siefert, A., C. Violle, L. Chalmandrier, C. H. Albert, A. Taudiere, A.
-Fajardo, L. W. Aarssen, et al. 2015.
-\href{https://doi.org/10.1111/ele.12508}{A global meta-analysis of the
-relative extent of intraspecific trait variation in plant communities}.
+Siefert, A., C.
+Violle, L.
+Chalmandrier, C.
+H.
+Albert, A.
+Taudiere, A.
+Fajardo, L.
+W.
+Aarssen, et al.
+2015.
+\href{https://doi.org/10.1111/ele.12508}{A global meta-analysis of the relative extent of intraspecific trait variation in plant communities}.
 \emph{Ecology Letters} 18: 1406--1419.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Terashima2001}{}}%
-Terashima, I., S.-I. Miyazawa, and Y. T. Hanba. 2001.
-\href{https://doi.org/10.1007/PL00013972}{Why are {Sun Leaves Thicker}
-than {Shade Leaves}? \textemdash{} {Consideration} based on {Analyses}
-of {CO2 Diffusion} in the {Leaf}}. \emph{Journal of Plant Research} 114:
-93--105.
+Terashima, I., S.-I.
+Miyazawa, and Y.
+T.
+Hanba.
+2001.
+\href{https://doi.org/10.1007/PL00013972}{Why are {Sun Leaves Thicker} than {Shade Leaves}?
+\textemdash{} {Consideration} based on {Analyses} of {CO2 Diffusion} in the {Leaf}}.
+\emph{Journal of Plant Research} 114: 93--105.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Warton2012a}{}}%
-Warton, D. I., R. A. Duursma, D. S. Falster, and S. Taskinen. 2012.
-\href{https://doi.org/10.1111/j.2041-210X.2011.00153.x}{Smatr
-3\textendash{} an {R} package for estimation and inference about
-allometric lines}. \emph{Methods in Ecology and Evolution} 3: 257--259.
+Warton, D.
+I., R.
+A.
+Duursma, D.
+S.
+Falster, and S.
+Taskinen.
+2012.
+\href{https://doi.org/10.1111/j.2041-210X.2011.00153.x}{Smatr 3\textendash{} an {R} package for estimation and inference about allometric lines}.
+\emph{Methods in Ecology and Evolution} 3: 257--259.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Warton2006}{}}%
-Warton, D. I., I. J. Wright, D. S. Falster, and M. Westoby. 2006.
-\href{https://doi.org/10.1017/S1464793106007007}{Bivariate line-fitting
-methods for allometry}. \emph{Biological Reviews of the Cambridge
-Philosophical Society} 81: 259--291.
+Warton, D.
+I., I.
+J.
+Wright, D.
+S.
+Falster, and M.
+Westoby.
+2006.
+\href{https://doi.org/10.1017/S1464793106007007}{Bivariate line-fitting methods for allometry}.
+\emph{Biological Reviews of the Cambridge Philosophical Society} 81: 259--291.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wright2004a}{}}%
-Wright, I. J., P. B. Reich, M. Westoby, D. D. Ackerly, Z. Baruch, F.
-Bongers, J. Cavender-Bares, et al. 2004.
-\href{https://doi.org/10.1038/nature02403}{The worldwide leaf economics
-spectrum}. \emph{Nature} 428: 821--827.
+Wright, I.
+J., P.
+B.
+Reich, M.
+Westoby, D.
+D.
+Ackerly, Z.
+Baruch, F.
+Bongers, J.
+Cavender-Bares, et al.
+2004.
+\href{https://doi.org/10.1038/nature02403}{The worldwide leaf economics spectrum}.
+\emph{Nature} 428: 821--827.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wright2010}{}}%
-Wright, S. J., K. Kitajima, N. J. B. Kraft, P. B. Reich, I. J. Wright,
-D. E. Bunker, R. Condit, et al. 2010.
-\href{https://doi.org/10.1890/09-2335.1}{Functional traits and the
-growth-mortality trade-off in tropical trees}. \emph{Ecology} 91:
-3664--3674.
+Wright, S.
+J., K.
+Kitajima, N.
+J.
+B.
+Kraft, P.
+B.
+Reich, I.
+J.
+Wright, D.
+E.
+Bunker, R.
+Condit, et al.
+2010.
+\href{https://doi.org/10.1890/09-2335.1}{Functional traits and the growth-mortality trade-off in tropical trees}.
+\emph{Ecology} 91: 3664--3674.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Yang2020}{}}%
-Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020.
-Large {Underestimation} of {Intraspecific Trait Variation} and {Its
-Improvements}. \emph{Frontiers in Plant Science} 11.
+Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020. Large {Underestimation} of {Intraspecific Trait Variation} and {Its Improvements}. \emph{Frontiers in Plant Science} 11.
 
@@
 All & 0.97 {[}0.94, 1.01{]} & \textbf{0.09 {[}0.02, 0.16{]}} & 0.87 \\
-Thick-large & 0.93 {[}0.85, 1.03{]} & \textbf{0.19 {[}0.01, 0.37{]}} &
-0.86 \\
+Thick-large & 0.93 {[}0.85, 1.03{]} & \textbf{0.19 {[}0.01, 0.37{]}} & 0.86 \\
 Thick-small & 1.02 {[}0.97, 1.07{]} & 0 {[}-0.11, 0.11{]} & 0.93 \\
-Thin-large & 0.91 {[}0.82, 1.02{]} & \textbf{0.2 {[}0.02, 0.37{]}} &
-0.71 \\
+Thin-large & 0.91 {[}0.82, 1.02{]} & \textbf{0.2 {[}0.02, 0.37{]}} & 0.71 \\
 Thin-small & 0.93 {[}0.83, 1.03{]} & 0.16 {[}-0.02, 0.35{]} & 0.84 \\
@@
 
-\textbf{Table. 1.} Relationships between species mean leaf leaf mass per
-area (LMA) values determined by using whole leaves and leaf discs across
-all species and within species groups. Data are divided into four
-categories based on the quartiles: thin and small-leaved, thin and
-large-leaved, thick and small-leaved, and thick and large-leaved
-species. SMA slope (95\% CI), intercepts (95\% CI), and
-\emph{R\textsuperscript{2}} values are reported. Statistically
-significant differences (\emph{P} \textless{} 0.05) in slopes and
-intercepts are highlighted in bold.
+\textbf{Table. 1.}
+Relationships between species mean leaf leaf mass per area (LMA) values determined by using whole leaves and leaf discs across all species and within species groups.
+Data are divided into four categories based on the quartiles:
+thin and small-leaved,
+thin and large-leaved,
+thick and small-leaved,
+and thick and large-leaved species.
+SMA slope (95\% CI), intercepts (95\% CI), and \emph{R\textsuperscript{2}} values are reported.
+Statistically significant differences (\emph{P} \textless{} 0.05) in slopes and intercepts are highlighted in bold.
 
@@
 
-\textbf{Fig. 1.} Relationships between species mean leaf mass per area
-(LMA) determined by using whole leaves and leaf discs. Species groups
-are divided into four categories on the basis of the medians of the leaf
-size and leaf thickness across all the species. Dashed lines indicate
-1:1 lines. Blue solid lines indicate standardized major axis
-regressions. The 95\% confidence intervals are presented as the shaded
-area. All the correlations are significant (\emph{P} \textless{} 0.001).
+\textbf{Fig. 1.}
+Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
+Species groups are divided into four categories on the basis of the medians of the leaf size and leaf thickness across all the species.
+Dashed lines indicate 1:1 lines.
+Blue solid lines indicate standardized major axis regressions.
+The 95\% confidence intervals are presented as the shaded area.
+All the correlations are significant (\emph{P} \textless{} 0.001).
 
@@
 
-\textbf{Fig. 2.} Relationships between individual leaf mass per area
-(LMA) determined by using whole leaves and leaf discs. Individual groups
-are divided into four categories based on the basis of the medians of
-the leaf size and leaf thickness across all the individuals. All the
-correlations are significant (\emph{P} \textless{} 0.001). Details as in
-Fig. 1.
+\textbf{Fig. 2.}
+Relationships between individual leaf mass per area (LMA) determined by using whole leaves and leaf discs.
+Individual groups are divided into four categories based on the basis of the medians of the leaf size and leaf thickness across all the individuals.
+All the correlations are significant (\emph{P} \textless{} 0.001).
+Details as in Fig. 1.
 
@@
 
-\textbf{Fig. 3.} Relationships between coefficient of variation (CV) in
-leaf trait values determined by using whole leaves and leaf discs: (a)
-leaf mass per area (LMA). The correlation is significant (\emph{P}
-\textless{} 0.001). Details as in Fig. 1. Note that the axes are square
-root scales.
+\textbf{Fig. 3.}
+Relationships between coefficient of variation (CV) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
+The correlation is significant (\emph{P} \textless{} 0.001).
+Details as in Fig. 1.
+Note that the axes are square root scales.
 

### 2022-04-26 ms/LMA_method.Rmd
update

@@
 
-*Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA*
+*Effects of leaf area and thickness on the relationship between whole-leaf and leaf disc LMA*
 
@@
 
-where $LMA_{Wi}$, $LMA_{Di}$, $LA_{i}$, $LT_{i}$ are the whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree *i*, respectively.
+where $LMA_{Wi}$, $LA_{i}$, $LT_{i}$ are the observed whole-leaf LMA, leaf area and leaf thickness for tree *i*, respectively,
+$LMA_{Di}$ is the true unobserved value of leaf disc LMA for tree *i*, which can be modeled using the observed leaf disc LMA.
 $\tilde{\mu_i}$ is the effect of leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree *i*, and $\sigma_i$ is the variance of whole-leaf LMA for tree *i*, and $\beta$ are coefficients.

### 2022-04-27 ms/response_letter.Rmd
stan
add subsection for Bayes
update

@@
 
+Thank you.
+This is an important thing to clarify.
+Leaf thickness and leaf area effect not only the mean LMA but also the variance of LMA, and that is why R2 values changed among the four groups (thin vs. think and small vs. large leaves).
+
 > 3.
@@
 I think this metric needs to either be excluded entirely or significantly expanded upon.
+
+Thank you.
+We now use Bao's CV estimator (CV4) instead of  coefficient of variation of log-normally distributed data ($CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$).
+The pattern didn't change qualitatively.
+
+- Added Bao
 
@@
 
+- making stan
+
 > L154-160 see major comment 3
@@
 I would therefore remove the species level results form the manuscript, and instead only report on the individual level data.
+
+- need to think this
 

### 2022-04-27 R/data_clean.R

@@ -1,0 +1,432 @@
+#' @title CV
+cv <- \(x, na.rm = TRUE) sd(log(x), na.rm = TRUE) / mean(log(x), na.rm = TRUE)
+
+#' @title Bao's CV with log-transformation
+cv4 <- function(x, log = TRUE) {
+  x <- x[!is.na(x)]
+  if (log) x <- log(x)
+  n <- length(x)
+  mu <- mean(x)
+  sig <- sd(x)
+  cv1 <- sig / mu
+  gamma1 <- sum(((x - mu) / sig)^3) / n
+  gamma2 <- sum(((x - mu) / sig)^4) / n
+  cv4 <- cv1 - cv1^3 / n + cv1 / (4 * n)
+        + cv1^2 * gamma1 / (2 * n) + cv1 * gamma2 / (8 * n)
+  cv4
+}
+
+
+clean_lma_yaku <- function(lma_yaku) {
+  d3 <- read_csv(lma_yaku) |>
+    clean_names(abbreviations = c("LMA", "LD", "LDMC", "LT"))
+
+  yaku <- d3 |>
+    filter(growthform != "H") |>
+    mutate(location = "Yakushima") |>
+    mutate(biomes = "ST2") |>
+    mutate(garden = "NO") |>
+    mutate(mat = NA) |>
+    mutate(map = NA) |>
+    mutate(contributor = "Onoda Yusuke") |>
+    mutate(growthform = ifelse(growthform == "W", "Trees", growthform)) |>
+    rename(
+      lt = lamina_thickness,
+      la = la_mean_leaf_let,
+      data_contributor = contributor,
+      growth_form = growthform,
+      lma_leaf = whole_leaf_lma,
+      lma_disc = ld_lma,
+      ldmc_leaf = ldmc,
+      ld_disc = td) |>
+    mutate(ld_leaf = lma_leaf / lt * 10^-3) %>%
+    mutate(ldmc_disc = NA) |>
+    mutate(lt_disc = NA) |>
+    mutate(petiole_ratio = petiole_dw / scanned_leaf_dw)
+  yaku
+}
+
+clean_lma_raw <- function(lma_raw) {
+  d <- read_csv(lma_raw) |>
+    clean_names(abbreviations = c("LMA", "LD", "LDMC", "LT"))
+
+  d |>
+    mutate(location = ifelse(location == "Ailao_underground", "Ailao_understory", location)) |>
[…]

### 2022-04-27 R/ind_analysis.R

@@ -139,3 +139,48 @@ dm_lm <- function(tree) {
   rownames(tb)[4] <- "Large leaf punch"
   tb
 }
+
+create_cv_fit <- function(tree, k = 10, seed = 123)  {
+  set.seed(seed)
+  cv <- crossv_kfold(tree, k = k)
+  y_bar <- mean(log(tree$lma_leaf))
+
+  models1 <- map(cv$train,
+    ~lm(log(lma_leaf) ~ log(lma_disc), data = .))
+  models2 <- map(cv$train,
+    ~lm(log(lma_leaf) ~ log(la) + log(lt),
+        offset = log(lma_disc), data = .))
+  models3  <- map(cv$train,
+    ~lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt),
+        data = .))
+  fit1 <- lm(log(lma_leaf) ~ log(lma_disc), data = tree)
+  fit2 <- lm(log(lma_leaf) ~ log(la) + log(lt),
+        offset = log(lma_disc), data = tree)
+  fit3 <- lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt), data = tree)
+
+  get_pred  <- function(model, test_data){
+    data  <- as.data.frame(test_data)
+    pred  <- add_predictions(data, model)
+    return(pred)
+  }
+
+  pred <- map(list(models1, models2, models3),
+    \(x) map2_df(x, cv$test, get_pred, .id = "Run"))
+
+  tmp_fun <- function(x) {
+    x |>
+    group_by(Run) |>
+    summarise(
+      MSE = mean((log(lma_leaf) - pred)^2),
+      R2 = 1 - sum((log(lma_leaf) - pred)^2) / sum((log(lma_leaf) - y_bar)^2) )
+  }
+
+  mse_dat <- map(pred, tmp_fun)
+  r2 <- map_dbl(mse_dat, \(x)mean(x$R2))
+  mse_ <- map_dbl(mse_dat, \(x)mean(x$MSE))
+  list(
+    table = tibble(model = paste("fit", 1:3), r2 = r2, mse = mse_),
+    fit1 = fit1,
+    fit2 = fit2,
+    fit3 = fit3)
+}

### 2022-04-27 _targets.R

@@ -22,7 +22,9 @@ tar_option_set(packages = c(
   "smatr",
   "parallel",
   "janitor",
-  "extrafont"
+  "extrafont",
+  "modelr",
+  "performance"
 ))
 
 # check if it's inside a container
@@ -207,6 +209,20 @@ list(
     seed = 123
    ),
   tar_stan_mcmc(
+    fit_tree_7,
+    "stan/sma_full.stan",
+    data = clean_stan_data(tree,
+      interaction = FALSE, dry_mass = FALSE, scale = TRUE),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 4000,
+    iter_sampling = 4000,
+    adapt_delta = 0.99,
+    max_treedepth = 15,
+    seed = 123
+   ),
+  tar_stan_mcmc(
     fit_sp_1,
     "stan/model.stan",
     data = clean_stan_data(sp_mean,
@@ -230,6 +246,18 @@ list(
     iter_sampling = 2000,
     seed = 123
   ),
+  tar_stan_mcmc(
+    fit_sp_6,
+    "stan/sma.stan",
+    data = clean_stan_data(sp_mean,
+      interaction = FALSE, dry_mass = FALSE, scale = TRUE),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    seed = 123
+   ),
 
   # coef for OLS stan
   tar_target(
@@ -295,6 +323,29 @@ list(
     format = "file"
   ),
 
+  tar_target(
+    coef_tree_sma_full_tab,
+    create_stan_tab(fit_tree_7_draws_sma_full)
+  ),
+
+  tar_target(
+    cv_tree,
+    create_cv_fit(tree, k = 10, seed = 123)
+  ),
+  tar_target(
+    cv_sp,
+    create_cv_fit(sp_mean, k = 10, seed = 123)
+  ),
+
+  # coef for SMA stan for sp
+  tar_target(
+    coef_sp_sma_tab,
+    create_stan_tab(fit_sp_6_draws_sma)
+  ),
+  tar_target(
+    coef_sp_sma_plot,
+    coef_pointrange(coef_sp_sma_tab)
+  ),
   # tar_stan_mcmc(
   # tar_stan_mcmc(
   #   fit_sp_1,

### 2022-04-27 _targets_packages.R

@@ -2,13 +2,14 @@
 library(clustermq)
 library(extrafont)
 library(fst)
-library(future)
 library(ggpubr)
 library(ggsma)
 library(janitor)
 library(markdown)
+library(modelr)
 library(parallel)
 library(patchwork)
+library(performance)
 library(qs)
 library(smatr)
 library(tibble)

### 2022-04-28 report.Rmd
udpate make
sma table for tree
dens leaf

@@
 
+<!-- I put tar_load to use {{targets}} -->
+
 ```{r, include=FALSE}
@@
 
-# SMA table (species-level)
+# SMA table
+
+## species
 
 ```{r}
-tar_load(sma_tab)
-sma_tab |>
+tar_load(sma_sp_tab)
+sma_sp_tab |>
+  kable() |>
+  kable_styling()
+```
+
+## tree
+
+```{r}
+tar_load(sma_tree_tab)
+sma_tree_tab |>
+  kable() |>
+  kable_styling()
+```
+
+## tree LD
+
+```{r}
+tar_load(sma_tree_ld_tab)
+sma_tree_ld_tab |>
   kable() |>

### 2022-04-28 R/data_clean.R

@@ -379,6 +379,7 @@ tree_dat_clean <- function(tree_data_csv) {
 
   la_mid_tree <- median(tree$la, na.rm = TRUE)
   lt_mid_tree <- median(tree$lt, na.rm = TRUE)
+  ld_mid_tree <- median(tree$ld_leaf, na.rm = TRUE)
 
   tree <- tree |>
     mutate(lt_gr = case_when(
@@ -405,7 +406,18 @@ tree_dat_clean <- function(tree_data_csv) {
     mutate(la_gr2 = ifelse(la < la_mid_tree, "Small-leaved~individuals",
                            "Large-leaved~individuals")) |>
     mutate(lt_gr2 = ifelse(lt < lt_mid_tree, "Thin-leaved~individuals",
-                           "Thick-leaved~individuals"))
+                           "Thick-leaved~individuals")) |>
+    mutate(ld_gr = ifelse(ld_leaf < ld_mid_tree, "Dense",
+                           "Nondense")) |>
+    mutate(ld_gr2 = ifelse(ld_leaf < ld_mid_tree, "Dense-leaved~individuals",
+                           "Nondense-leaved~individuals")) |>
+    mutate(la_gr2 = factor(la_gr2, levels = c("Small-leaved~individuals",
+                           "Large-leaved~individuals"))) |>
+    mutate(lt_gr2 = factor(lt_gr2, levels = c("Thin-leaved~individuals",
+                           "Thick-leaved~individuals"))) |>
+    mutate(ld_gr2 = factor(ld_gr2, levels = c("Nondense-leaved~individuals",
+                           "Dense-leaved~individuals")))
+
 
   tree
 }

### 2022-04-28 R/ind_analysis.R

@@ -1,5 +1,7 @@
 lalt_tree_grid <- function(tree) {
   tree |>
+    mutate(la_gr2 = factor(la_gr2, levels = c("Small-leaved~individuals",
+                           "Large-leaved~individuals") |> rev())) |>
     ggplot(aes(x = lma_disc, y = lma_leaf, col = dry_mass_disc)) +
     geom_point(alpha = 0.8) +
     scale_color_viridis_c(
@@ -23,7 +25,7 @@ lalt_tree_grid <- function(tree) {
     theme_bw() +
     theme(
       text = element_text(family = "Arial"),
-      legend.position = c(0.39, 0.15),
+      legend.position = "none",
       legend.key.size = unit(0.5, "cm"),
       legend.spacing.y = unit(0.1, "cm"),
       legend.text.align = 0,
@@ -33,6 +35,21 @@ lalt_tree_grid <- function(tree) {
     )
 }
 
+lalt_tree_grid_dense <- function(tree) {
+  p1 <- tree |>
+      filter(ld_gr2 == "Nondense-leaved~individuals") |>
+      lalt_tree_grid() +
+      ggtitle("Nondense-leaved individuals") +
+      theme(legend.position = c(0.88, 0.65))
+  p2 <- tree |>
+      filter(ld_gr2 == "Dense-leaved~individuals") |>
+      lalt_tree_grid() +
+      ggtitle("Dense-leaved individuals")
+  p1 + p2 +
+    plot_annotation(tag_levels = "a") &
+    theme(
+      text = element_text(family = "Arial"))
+}
 
 ratio_combine <- function(tree) {
   my_col <- RColorBrewer::brewer.pal(4, "RdBu")
@@ -152,11 +169,13 @@ create_cv_fit <- function(tree, k = 10, seed = 123)  {
         offset = log(lma_disc), data = .))
   models3  <- map(cv$train,
     ~lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt),
+        offset = log(lma_disc),
         data = .))
   fit1 <- lm(log(lma_leaf) ~ log(lma_disc), data = tree)
   fit2 <- lm(log(lma_leaf) ~ log(la) + log(lt),
         offset = log(lma_disc), data = tree)
-  fit3 <- lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt), data = tree)
+  fit3 <- lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt),
[…]

### 2022-04-28 R/sp_analysis.R

@@ -140,6 +140,43 @@ generate_sma_tab <- function(sp_mean) {
   tb
 }
 
+#' @title SMA table (species-level)
+generate_sma_ld_tab <- function(sp_mean) {
+  sp_mean <- sp_mean |>
+    mutate(lalt_gr = paste(ld_gr, "~", lalt_gr))
+
+  sma_lma <- sma(log10(lma_leaf) ~ log10(lma_disc),
+    data = sp_mean,
+    elev.test = 0,
+    slope.test = 1
+  )
+
+  sma_lma_lalt_gr <- sma(log10(lma_leaf) ~ log10(lma_disc) * lalt_gr,
+    data = sp_mean,
+    elev.test = 0,
+    slope.test = 1
+  )
+
+  # we don't need leaf density
+  tb0 <- lapply(
+    list(
+      lma = sma_lma,
+      lma_gr = sma_lma_lalt_gr
+    ),
+    extract_sma
+  )
+
+  tb <- rbind(tb0$lma[[2]], tb0$lma_gr[[2]])
+  tb <- cbind(c("All", tb0$lma_gr$group), tb) |>
+    as_tibble() |>
+    rename(Slope = slope, Intercept = intercept)
+
+  colnames(tb)[1] <- "Data"
+
+  tb
+}
+
+
 #' @title LMA and LD (species-level)
 lma_ld_wrap_point <- function(sp_mean) {
   d_leaf <- sp_mean |>

### 2022-04-28 R/stan.R

@@ -1,13 +1,19 @@
-clean_stan_data <- function(sp_mean, interaction = TRUE, dry_mass = TRUE, scale = FALSE) {
+clean_stan_data <- function(sp_mean, dry_mass = TRUE, scale = FALSE, ld = FALSE) {
   x <- cbind(
     intercept = rep(1, nrow(sp_mean)),
-    la = sp_mean$la |> log(),
-    lt = sp_mean$lt |> log()
+    lma_disc = sp_mean$lma_disc,
+    la = sp_mean$la,
+    lt = sp_mean$lt
   )
+  if (ld) {
+    # unit doesn't matter after scaling but I'll use /1000 anyway
+    x[,2] <- sp_mean$lma_disc / sp_mean$lt / 1000
+  }
+
+  x[, 2:4] <- apply(x[, 2:4], 2, \(x)log(x))
 
   if (scale) {
-    x[, 2] <- x[, 2] |> exp() |> log() |> scale() |> as.numeric()
-    x[ ,3] <- x[, 3] |> exp() |> log() |> scale() |> as.numeric()
+    x[, 2:4] <- apply(x[, 2:4], 2, \(x)scale(x))
   }
 
   if (dry_mass) {
@@ -17,13 +23,8 @@ clean_stan_data <- function(sp_mean, interaction = TRUE, dry_mass = TRUE, scale 
   }
 
   if (scale && dry_mass) {
-    x2[, 4] <- x2[, 4] |> exp() |> log() |> scale() |> as.numeric()
+    x2[, 5] <- x2[, 5] |> exp() |> log() |> scale() |> as.numeric()
  }
-
-  if (interaction){
-    x <- cbind(x, x[, 2] * x[, 3])
-    colnames(x) <- c("intercept", "la", "lt", "lalt")
-  }
 
   # use non-scaled value for LMA
   log_lma_disc <- sp_mean$lma_disc |> log()
@@ -71,7 +72,6 @@ create_dummy_data <- function(n) {
     x = x)
 }
 
-
 create_stan_tab <- function(draws) {
   tmp <- draws |>
     dplyr::select(contains(c("beta", "gamma")))
@@ -83,50 +83,68 @@ create_stan_tab <- function(draws) {
   tibble(para = names(mean_), mean_, lwr2_5, lwr5, upr95, upr97_5)
 }
 
-coef_pointrange <- function(data) {
+coef_pointrange <- function(data, ld = FALSE) {
   data2 <- data |>
[…]

### 2022-04-28 _targets.R

@@ -108,18 +108,6 @@ list(
     stan_sp_dat,
     clean_stan_data(sp_mean, dry_mass = FALSE)
   ),
-  tar_target(
-    stan_tree_dat,
-    clean_stan_data(tree, interaction = FALSE, dry_mass = TRUE, scale = TRUE)
-  ),
-  tar_target(
-    stan_tree_dat_noint,
-    clean_stan_data(tree, interaction = TRUE, dry_mass = FALSE, scale = TRUE)
-  ),
-  tar_target(
-    stan_tree_dat_simple,
-    clean_stan_data(tree, interaction = FALSE, dry_mass = FALSE, scale = TRUE)
-  ),
   # tar_target(
   #   stan_sp_dat_noint,
   #   clean_stan_data(sp_mean, interaction = FALSE)
@@ -139,67 +127,19 @@ list(
     fit_tree_1,
     "stan/model.stan",
     data = clean_stan_data(tree,
-      interaction = FALSE, dry_mass = FALSE, scale = TRUE),
+      dry_mass = FALSE, scale = TRUE),
     refresh = 0,
     chains = 4,
     parallel_chains = getOption("mc.cores", 4),
-    iter_warmup = 2000,
-    iter_sampling = 2000,
+    iter_warmup = 1000,
+    iter_sampling = 1000,
     seed = 123
    ),
-  tar_stan_mcmc(
+   tar_stan_mcmc(
     fit_tree_2,
-    "stan/model.stan",
-    data = clean_stan_data(tree,
-      interaction = TRUE, dry_mass = FALSE, scale = TRUE),
-    refresh = 0,
-    chains = 4,
-    parallel_chains = getOption("mc.cores", 4),
-    iter_warmup = 2000,
-    iter_sampling = 2000,
-    seed = 123
-   ),
-  tar_stan_mcmc(
-    fit_tree_3,
-    "stan/punch.stan",
-    data = clean_stan_data(tree,
-      interaction = FALSE, dry_mass = TRUE, scale = TRUE),
-    refresh = 0,
-    chains = 4,
-    parallel_chains = getOption("mc.cores", 4),
-    iter_warmup = 2000,
-    iter_sampling = 2000,
-    seed = 123
-   ),
-  tar_stan_mcmc(
-    fit_tree_4,
-    "stan/model.stan",
-    data = clean_stan_data(tree,
[…]

### 2022-04-29 R/data_clean.R
sp analysis

@@ -315,6 +315,7 @@ sp_dat_mean <- function(full_data_csv){
 
   la_mid <- median(d$la)
   lt_mid <- median(d$lt, na.rm = TRUE)
+  ld_mid <- median(d$ld_leaf, na.rm = TRUE)
 
   d <- d |>
     mutate(lt_gr = case_when(
@@ -341,7 +342,18 @@ sp_dat_mean <- function(full_data_csv){
     mutate(la_gr2 = ifelse(la < la_mid, "Small-leaved~species",
                            "Large-leaved~species")) |>
     mutate(lt_gr2 = ifelse(lt < lt_mid, "Thin-leaved~species",
-                           "Thick-leaved~species"))
+                           "Thick-leaved~species")) |>
+    mutate(ld_gr = ifelse(ld_leaf < ld_mid, "Dense",
+                           "Nondense")) |>
+    mutate(ld_gr2 = ifelse(ld_leaf < ld_mid, "Dense-leaved~species",
+                           "Nondense-leaved~species")) |>
+    mutate(la_gr2 = factor(la_gr2, levels = c("Small-leaved~species",
+                           "Large-leaved~species"))) |>
+    mutate(lt_gr2 = factor(lt_gr2, levels = c("Thin-leaved~species",
+                           "Thick-leaved~species"))) |>
+    mutate(ld_gr2 = factor(ld_gr2, levels = c("Nondense-leaved~species",
+                           "Dense-leaved~species")))
+
   d
 }
 

### 2022-04-29 R/sp_analysis.R

@@ -2,6 +2,8 @@
 #' @title Leaf disc vs whole-leaf LMA (pooled species-level)
 lalt_pool_grid_point <- function(data) {
   data |>
+    mutate(la_gr2 = factor(la_gr2, levels = c("Small-leaved~species",
+                           "Large-leaved~species") |> rev())) |>
     ggplot(aes(x = lma_disc, y = lma_leaf)) +
     geom_point(alpha = 0.8) +
     scale_x_log10() +
@@ -23,6 +25,21 @@ lalt_pool_grid_point <- function(data) {
     theme(text = element_text(family = "Arial"))
 }
 
+lalt_sp_grid_dense <- function(data) {
+  p1 <- data |>
+      filter(ld_gr2 == "Nondense-leaved~species") |>
+      lalt_pool_grid_point() +
+      ggtitle("Nondense-leaved species") +
+      theme(legend.position = c(0.88, 0.65))
+  p2 <- data |>
+      filter(ld_gr2 == "Dense-leaved~species") |>
+      lalt_pool_grid_point() +
+      ggtitle("Dense-leaved species")
+  p1 + p2 +
+    plot_annotation(tag_levels = "a") &
+    theme(
+      text = element_text(family = "Arial"))
+}
 
 #' @title Leaf disc vs whole-leaf LMA (separted species-level)
 lalt_sep_grid_point <- function(data) {

### 2022-04-29 R/stan.R

@@ -148,3 +148,113 @@ coef_pointrange <- function(data, ld = FALSE) {
     }
     p
 }
+
+coef_pointrange2 <- function(data, ld = FALSE) {
+
+  data1 <- data |>
+    filter(para != "gamma[1]") |>
+    filter(str_detect(para, "beta")) |>
+    mutate(para = case_when(
+      para == "beta[1]" ~ "Intercept for mean",
+      para == "beta[2]" ~ "Effect of disc LMA on mean",
+      para == "beta[3]" ~ "Effect of LA on mean",
+      para == "beta[4]" ~ "Effect of LT on mean"
+    )) |>
+    mutate(para = factor(para,
+      levels = c(
+      "Intercept for mean",
+      "Effect of disc LMA on mean",
+      "Effect of LA on mean",
+      "Effect of LT on mean"
+    ) |> rev()))
+
+  data2 <- data |>
+    filter(para != "gamma[1]") |>
+    filter(str_detect(para, "gamma")) |>
+    mutate(para = case_when(
+      para == "gamma[2]" ~ "Effect of disc LMA on variance",
+      para == "gamma[3]" ~ "Effect of LA on variance",
+      para == "gamma[4]" ~ "Effect of LT on variance"
+    )) |>
+    mutate(para = factor(para,
+      levels = c(
+      "Effect of disc LMA on variance",
+      "Effect of LA on variance",
+      "Effect of LT on variance"
+    ) |> rev()))
+
+
+    p1 <- data1 |>
+      ggplot(aes(y = para)) +
+      geom_vline(xintercept = 0, lty  = 2, color = "grey60") +
+      geom_linerange(
+        aes(xmin = lwr2_5, xmax = upr97_5),
+        color = "#3366FF") +
+      geom_linerange(
+        aes(xmin = lwr5, xmax = upr95),
+        size = 1.5,
+        color = "#3366FF") +
+      geom_point(
+        aes(x = mean_),
+        color = "#3366FF",
+        fill =  "#33CCFF",
+        shape = 21,
+        size = 3) +
+      ylab("") +
+      xlab("Standardized coefficients") +
+      scale_y_discrete(labels = c(
+        "Intercept for mean" = expression(Intercept~of~mean~(beta[0])),
+        "Effect of disc LMA on mean" = expression(Effect~of~LMA~on~mean~(beta[1])),
+        "Effect of LA on mean" = expression(Effect~of~LA~on~mean~(beta[2])),
[…]

### 2022-04-29 _targets.R

@@ -201,7 +201,7 @@ list(
     iter_sampling = 1000,
     seed = 123
    ),
-  tar_stan_mcmc(
+   tar_stan_mcmc(
     fit_sp_2,
     "stan/sma.stan",
     data = clean_stan_data(sp_mean,
@@ -209,8 +209,38 @@ list(
     refresh = 0,
     chains = 4,
     parallel_chains = getOption("mc.cores", 4),
-    iter_warmup = 1000,
-    iter_sampling = 1000,
+    iter_warmup = 4000,
+    iter_sampling = 4000,
+    adapt_delta = 0.99,
+    max_treedepth = 15,
+    seed = 123
+   ),
+   tar_stan_mcmc(
+    fit_sp_3,
+    "stan/sma.stan",
+    data = clean_stan_data(sp_mean,
+      dry_mass = FALSE, scale = TRUE, ld = TRUE),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 4000,
+    iter_sampling = 4000,
+    adapt_delta = 0.99,
+    max_treedepth = 15,
+    seed = 123
+   ),
+   tar_stan_mcmc(
+    fit_sp_4,
+    "stan/sma.stan",
+    data = clean_stan_data(sp_mean,
+      dry_mass = FALSE, scale = FALSE, ld = TRUE),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    adapt_delta = 0.99,
+    max_treedepth = 15,
     seed = 123
    ),
 
@@ -343,8 +373,41 @@ list(
   ),
   tar_target(
     coef_sp_sma_plot,
-    coef_pointrange(coef_sp_sma_tab)
+    coef_pointrange2(coef_sp_sma_tab)
   ),
+
+  tar_target(
+    coef_sp_sma_png,
+    ggsave(
+      "figs/coef_sp_sma.png",
+      coef_sp_sma_plot,
+      dpi = 300,
+      width = 8,
+      height = 4
+    ),
+    format = "file"
+  ),
+
+  tar_target(
+    coef_sp_ld_sma_tab,
+    create_stan_tab(fit_sp_3_draws_sma)
+  ),
+  tar_target(
+    coef_sp_ld_sma_plot,
[…]

### 2022-04-29 R/ind_analysis.R
cv

@@ -168,13 +168,13 @@ create_cv_fit <- function(tree, k = 10, seed = 123)  {
     ~lm(log(lma_leaf) ~ log(la) + log(lt),
         offset = log(lma_disc), data = .))
   models3  <- map(cv$train,
-    ~lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt),
+    ~lm(log(lma_leaf) ~ log(ld_leaf) + log(la) + log(lt),
         offset = log(lma_disc),
         data = .))
   fit1 <- lm(log(lma_leaf) ~ log(lma_disc), data = tree)
   fit2 <- lm(log(lma_leaf) ~ log(la) + log(lt),
         offset = log(lma_disc), data = tree)
-  fit3 <- lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt),
+  fit3 <- lm(log(lma_leaf) ~ log(ld_leaf) + log(la) + log(lt),
           offset = log(lma_disc), data = tree)
 
   get_pred  <- function(model, test_data){

### 2022-05-01 report.Rmd
sp analysis
cv
update

--- 2022-04-06 report.Rmd
@@
 
-![](figs/lalt_sep_grid.png)
-
-# SMA table (species-level)
+## MCMC check
 
 ```{r}
-tar_load(sma_tab)
-sma_tab |>
+targets::tar_load("fit_sp_0_summary_simple")
+targets::tar_load("fit_sp_1_summary_model")
+targets::tar_load("fit_sp_2_summary_model")
+targets::tar_load("fit_sp_3_summary_model")
+targets::tar_load("fit_sp_4_summary_sma")
+# targets::tar_load("fit_sp_5_summary_sma")
+targets::tar_load("fit_sp_6_summary_sma_err")
+
+targets::tar_load("fit_sp_0_diagnostics_simple")
+targets::tar_load("fit_sp_1_diagnostics_model")
+targets::tar_load("fit_sp_2_diagnostics_model")
+targets::tar_load("fit_sp_3_diagnostics_model")
+targets::tar_load("fit_sp_4_diagnostics_sma")
+# targets::tar_load("fit_sp_5_diagnostics_sma")
+targets::tar_load("fit_sp_6_diagnostics_sma_err")
+```
+
+```{r}
+fit_sp_0_summary_simple |> filter(rhat > 1.1)
+fit_sp_1_summary_model |> filter(rhat > 1.1)
+fit_sp_2_summary_model |> filter(rhat > 1.1)
+fit_sp_3_summary_model |> filter(rhat > 1.1)
+fit_sp_4_summary_sma |> filter(rhat > 1.1)
+# fit_sp_5_summary_sma |> filter(rhat > 1.1)
+fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
+```
+
+It is difficult to model heteroskedasticity and measurement errors at the same time.
+
+```{r}
+div_check(fit_sp_0_diagnostics_simple)
+div_check(fit_sp_1_diagnostics_model)
+div_check(fit_sp_2_diagnostics_model)
+div_check(fit_sp_3_diagnostics_model)
+div_check(fit_sp_4_diagnostics_sma)
+# div_check(fit_sp_5_diagnostics_sma)
+div_check(fit_sp_6_diagnostics_sma_err)
+```
+
+```{r}
+targets::tar_load(loo_model)
+loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]])
+```
+
+```{r}
+tar_read(cv_sp)
+```
+
+## coef
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png)
+```
+
+![](figs/coef_sp.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png2)
+```
+
+![](figs/coef_sp2.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png3)
+```
+
+![](figs/coef_sp3.png)
+
+# SMA table
+
+## species
+
+```{r, eval=TRUE}
+tar_load(sma_sp_tab)
+sma_sp_tab |>
   kable() |>
   kable_styling()
+```
+
+## species LD
+
+```{r, eval=TRUE}
+tar_load(sma_sp_ld_tab)
+sma_sp_ld_tab |>
+  kable() |>
+  kable_styling()
+```
+
+## tree
+
+```{r, eval=TRUE}
+tar_load(sma_tree_tab)
+sma_tree_tab |>
+  kable() |>
+  kable_styling()
+```
+
+## tree LD
+
+```{r, eval=TRUE}
+tar_load(sma_tree_ld_tab)
+sma_tree_ld_tab |>
+  kable() |>
+  kable_styling()
+```
+
+# Validation
+
+```{r}
+tar_load(cv_sp)
+cv_sp
+```
+
+```{r}
+tar_load(cv_tree)
+cv_tree
 ```

### 2022-05-01 R/ind_analysis.R

@@ -171,11 +171,17 @@ create_cv_fit <- function(tree, k = 10, seed = 123)  {
     ~lm(log(lma_leaf) ~ log(ld_leaf) + log(la) + log(lt),
         offset = log(lma_disc),
         data = .))
+  models4 <- map(cv$train,
+    ~lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt),
+        data = .))
+
   fit1 <- lm(log(lma_leaf) ~ log(lma_disc), data = tree)
   fit2 <- lm(log(lma_leaf) ~ log(la) + log(lt),
         offset = log(lma_disc), data = tree)
   fit3 <- lm(log(lma_leaf) ~ log(ld_leaf) + log(la) + log(lt),
           offset = log(lma_disc), data = tree)
+  fit4 <- lm(log(lma_leaf) ~ log(lma_disc) + log(la) + log(lt),
+          data = tree)
 
   get_pred  <- function(model, test_data){
     data  <- as.data.frame(test_data)
@@ -183,7 +189,7 @@ create_cv_fit <- function(tree, k = 10, seed = 123)  {
     return(pred)
   }
 
-  pred <- map(list(models1, models2, models3),
+  pred <- map(list(models1, models2, models3, models4),
     \(x) map2_df(x, cv$test, get_pred, .id = "Run"))
 
   tmp_fun <- function(x) {
@@ -198,8 +204,10 @@ create_cv_fit <- function(tree, k = 10, seed = 123)  {
   r2 <- map_dbl(mse_dat, \(x)mean(x$R2))
   mse_ <- map_dbl(mse_dat, \(x)mean(x$MSE))
   list(
-    table = tibble(model = paste("fit", 1:3), r2 = r2, mse = mse_),
+    table = tibble(model = paste("fit", 1:4), r2 = r2, mse = mse_),
     fit1 = fit1,
     fit2 = fit2,
-    fit3 = fit3)
+    fit3 = fit3,
+    fit4 = fit4
+    )
 }

### 2022-05-01 R/stan.R

@@ -1,10 +1,51 @@
-clean_stan_data <- function(sp_mean, dry_mass = TRUE, scale = FALSE, ld = FALSE) {
+clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD")) {
+  if (model == "no") {
+    x <- cbind(
+      intercept = rep(1, nrow(sp_mean)),
+      la = sp_mean$la,
+      lt = sp_mean$lt
+    )
+  } else if (model == "LMA") {
+    x <- cbind(
+      intercept = rep(1, nrow(sp_mean)),
+      lma_disc = sp_mean$lma_disc,
+      la = sp_mean$la,
+      lt = sp_mean$lt
+    )
+  } else {
+    x <- cbind(
+      intercept = rep(1, nrow(sp_mean)),
+      lma_disc = sp_mean$lma_disc / sp_mean$lt / 1000,
+      la = sp_mean$la,
+      lt = sp_mean$lt
+    )
+  }
+
+  x[, -1] <- apply(x[, -1], 2, \(x)scale(log(x)))
+
+  # use non-scaled value for LMA
+  log_lma_disc <- sp_mean$lma_disc |> log()
+  log_lma_leaf <- sp_mean$lma_leaf |> log()
+
+  list(
+    N = nrow(sp_mean),
+    K = ncol(x),
+    J = unique(sp_mean$species) |> length(),
+    sp = sp_mean$species |> as.factor() |> as.numeric(),
+    log_y = log_lma_leaf,
+    log_lma_disc = log_lma_disc,
+    x = x)
+
+}
+
+clean_stan_data2 <- function(sp_mean, dry_mass = TRUE, scale = FALSE, ld = FALSE) {
   x <- cbind(
     intercept = rep(1, nrow(sp_mean)),
     lma_disc = sp_mean$lma_disc,
     la = sp_mean$la,
     lt = sp_mean$lt
   )
+
   if (ld) {
     # unit doesn't matter after scaling but I'll use /1000 anyway
     x[,2] <- sp_mean$lma_disc / sp_mean$lt / 1000
@@ -52,7 +93,6 @@ clean_stan_data <- function(sp_mean, dry_mass = TRUE, scale = FALSE, ld = FALSE)
       x = x)
   }
 }
-
 create_dummy_data <- function(n) {
   xx1 <- rnorm(n)
   xx2 <- rnorm(n)
@@ -253,8 +293,17 @@ coef_pointrange2 <- function(data, ld = FALSE) {
[…]

### 2022-05-01 _targets.R

@@ -104,10 +104,6 @@ list(
     stan_sim_dat,
     create_dummy_data(100)
   ),
-  tar_target(
-    stan_sp_dat,
-    clean_stan_data(sp_mean, dry_mass = FALSE)
-  ),
   # tar_target(
   #   stan_sp_dat_noint,
   #   clean_stan_data(sp_mean, interaction = FALSE)
@@ -123,141 +119,171 @@ list(
     iter_sampling = 1000,
     seed = 123
    ),
-  tar_stan_mcmc(
-    fit_tree_1,
+
+  # tar_stan_mcmc(
+  #   fit_tree_1,
+  #   "stan/model.stan",
+  #   data = clean_stan_data(tree,
+  #     dry_mass = FALSE, scale = TRUE),
+  #   refresh = 0,
+  #   chains = 4,
+  #   parallel_chains = getOption("mc.cores", 4),
+  #   iter_warmup = 1000,
+  #   iter_sampling = 1000,
+  #   seed = 123
+  #  ),
+  #  tar_stan_mcmc(
+  #   fit_tree_2,
+  #   "stan/sma.stan",
+  #   data = clean_stan_data(tree,
+  #     dry_mass = FALSE, scale = TRUE),
+  #   refresh = 0,
+  #   chains = 4,
+  #   parallel_chains = getOption("mc.cores", 4),
+  #   iter_warmup = 4000,
+  #   iter_sampling = 4000,
+  #   adapt_delta = 0.99,
+  #   max_treedepth = 15,
+  #   seed = 123
+  #  ),
+  #  tar_stan_mcmc(
+  #   fit_tree_3,
+  #   "stan/sma.stan",
+  #   data = clean_stan_data(tree,
+  #     dry_mass = FALSE, scale = TRUE, ld = TRUE),
+  #   refresh = 0,
+  #   chains = 4,
+  #   parallel_chains = getOption("mc.cores", 4),
+  #   iter_warmup = 4000,
+  #   iter_sampling = 4000,
+  #   adapt_delta = 0.99,
+  #   max_treedepth = 15,
+  #   seed = 123
+  #  ),
+  #  tar_stan_mcmc(
+  #   fit_tree_4,
+  #   "stan/sma.stan",
+  #   data = clean_stan_data(tree,
+  #     dry_mass = FALSE, scale = FALSE, ld = TRUE),
+  #   refresh = 0,
+  #   chains = 4,
+  #   parallel_chains = getOption("mc.cores", 4),
[…]

### 2022-05-02 report.Rmd
sma update

--- 2022-04-06 report.Rmd
@@
 
-![](figs/lalt_sep_grid.png)
-
-# SMA table (species-level)
+## MCMC check
 
 ```{r}
-tar_load(sma_tab)
-sma_tab |>
+targets::tar_load("fit_sp_0_summary_simple")
+targets::tar_load("fit_sp_1_summary_model")
+targets::tar_load("fit_sp_2_summary_model")
+targets::tar_load("fit_sp_3_summary_model")
+targets::tar_load("fit_sp_4_summary_sma")
+targets::tar_load("fit_sp_5_summary_sma")
+targets::tar_load("fit_sp_6_summary_sma_err")
+
+targets::tar_load("fit_sp_0_diagnostics_simple")
+targets::tar_load("fit_sp_1_diagnostics_model")
+targets::tar_load("fit_sp_2_diagnostics_model")
+targets::tar_load("fit_sp_3_diagnostics_model")
+targets::tar_load("fit_sp_4_diagnostics_sma")
+targets::tar_load("fit_sp_5_diagnostics_sma")
+targets::tar_load("fit_sp_6_diagnostics_sma_err")
+```
+
+```{r}
+fit_sp_0_summary_simple |> filter(rhat > 1.1)
+fit_sp_1_summary_model |> filter(rhat > 1.1)
+fit_sp_2_summary_model |> filter(rhat > 1.1)
+fit_sp_3_summary_model |> filter(rhat > 1.1)
+fit_sp_4_summary_sma |> filter(rhat > 1.1)
+fit_sp_5_summary_sma |> filter(rhat > 1.1)
+fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
+```
+
+It is difficult to model heteroskedasticity and measurement errors at the same time.
+
+```{r}
+div_check(fit_sp_0_diagnostics_simple)
+div_check(fit_sp_1_diagnostics_model)
+div_check(fit_sp_2_diagnostics_model)
+div_check(fit_sp_3_diagnostics_model)
+div_check(fit_sp_4_diagnostics_sma)
+div_check(fit_sp_5_diagnostics_sma)
+div_check(fit_sp_6_diagnostics_sma_err)
+```
+
+```{r}
+targets::tar_load(loo_model)
+loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]])
+```
+
+```{r}
+tar_read(cv_sp)
+```
+
+## coef
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png)
+```
+
+![](figs/coef_sp.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png2)
+```
+
+![](figs/coef_sp2.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png3)
+```
+
+![](figs/coef_sp3.png)
+
+# SMA table
+
+## species
+
+```{r, eval=TRUE}
+tar_load(sma_sp_tab)
+sma_sp_tab |>
   kable() |>
   kable_styling()
+```
+
+## species LD
+
+```{r, eval=TRUE}
+tar_load(sma_sp_ld_tab)
+sma_sp_ld_tab |>
+  kable() |>
+  kable_styling()
+```
+
+## tree
+
+```{r, eval=TRUE}
+tar_load(sma_tree_tab)
+sma_tree_tab |>
+  kable() |>
+  kable_styling()
+```
+
+## tree LD
+
+```{r, eval=TRUE}
+tar_load(sma_tree_ld_tab)
+sma_tree_ld_tab |>
+  kable() |>
+  kable_styling()
+```
+
+# Validation
+
+```{r}
+tar_load(cv_sp)
+cv_sp
+```
+
+```{r}
+tar_load(cv_tree)
+cv_tree
 ```

### 2022-05-02 R/stan.R

@@ -93,6 +93,7 @@ clean_stan_data2 <- function(sp_mean, dry_mass = TRUE, scale = FALSE, ld = FALSE
       x = x)
   }
 }
+
 create_dummy_data <- function(n) {
   xx1 <- rnorm(n)
   xx2 <- rnorm(n)
@@ -110,6 +111,24 @@ create_dummy_data <- function(n) {
     log_y = yy,
     log_lma_disc = xx1,
     x = x)
+}
+
+create_dummy_sma_data <- function(n, seed = 123) {
+  set.seed(seed)
+  beta1 <- 1
+  beta2 <- 1.5
+  x_true <- rnorm(n)
+  sig_x <- 0.4
+  sig <- 0.8
+  x <- rnorm(n, x_true, sig_x)
+  y <- rnorm(n, beta1 + beta2 * x_true, sig)
+
+  list(
+    N = n,
+    y = y,
+    x = x,
+    x_true = x_true
+    )
 }
 
 create_stan_tab <- function(draws) {

### 2022-05-02 _targets.R

@@ -108,6 +108,7 @@ list(
   #   stan_sp_dat_noint,
   #   clean_stan_data(sp_mean, interaction = FALSE)
   # ),
+
   tar_stan_mcmc(
     fit_sim,
     "stan/model.stan",
@@ -117,6 +118,20 @@ list(
     parallel_chains = getOption("mc.cores", 4),
     iter_warmup = 1000,
     iter_sampling = 1000,
+    seed = 123
+   ),
+
+  tar_stan_mcmc(
+    fit_sim_sma,
+    "stan/test.stan",
+    data = create_dummy_sma_data(300),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    adapt_delta = 0.99,
+    max_treedepth = 15,
     seed = 123
    ),
 
@@ -237,25 +252,26 @@ list(
     chains = 4,
     parallel_chains = getOption("mc.cores", 4),
     iter_warmup = 2000,
-    iter_sampling = 4000,
-    adapt_delta = 0.95,
+    iter_sampling = 2000,
+    adapt_delta = 0.99,
     max_treedepth = 15,
     seed = 123
    ),
 
-  #  tar_stan_mcmc(
-  #   fit_sp_5,
-  #   "stan/sma.stan",
-  #   data = clean_stan_data(sp_mean, model = "LMA"),
-  #   refresh = 0,
-  #   chains = 4,
-  #   parallel_chains = getOption("mc.cores", 4),
-  #   iter_warmup = 2000,
-  #   iter_sampling = 2000,
-  #   adapt_delta = 0.99,
-  #   max_treedepth = 15,
-  #   seed = 123
-  #  ),
+   tar_stan_mcmc(
+    fit_sp_5,
+    "stan/sma.stan",
+    data = clean_stan_data(sp_mean, model = "LMA"),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    adapt_delta = 0.99,
+    max_treedepth = 15,
+    seed = 123
+   ),
+
    tar_stan_mcmc(
     fit_sp_6,
     "stan/sma_err.stan",
@@ -265,7 +281,7 @@ list(
     parallel_chains = getOption("mc.cores", 4),
     iter_warmup = 2000,
[…]

### 2022-05-02 report.Rmd
int

--- 2022-04-28 report.Rmd
@@
 
-![](figs/lalt_sep_grid.png)
+## MCMC check
+
+```{r}
+targets::tar_load("fit_sp_0_summary_simple")
+targets::tar_load("fit_sp_1_summary_model")
+targets::tar_load("fit_sp_11_summary_model")
+targets::tar_load("fit_sp_2_summary_model")
+targets::tar_load("fit_sp_3_summary_model")
+targets::tar_load("fit_sp_4_summary_sma")
+targets::tar_load("fit_sp_5_summary_sma")
+targets::tar_load("fit_sp_6_summary_sma_err")
+
+targets::tar_load("fit_sp_0_diagnostics_simple")
+targets::tar_load("fit_sp_1_diagnostics_model")
+targets::tar_load("fit_sp_11_diagnostics_model")
+targets::tar_load("fit_sp_2_diagnostics_model")
+targets::tar_load("fit_sp_3_diagnostics_model")
+targets::tar_load("fit_sp_4_diagnostics_sma")
+targets::tar_load("fit_sp_5_diagnostics_sma")
+targets::tar_load("fit_sp_6_diagnostics_sma_err")
+```
+
+```{r}
+fit_sp_0_summary_simple |> filter(rhat > 1.1)
+fit_sp_1_summary_model |> filter(rhat > 1.1)
+fit_sp_11_summary_model |> filter(rhat > 1.1)
+fit_sp_2_summary_model |> filter(rhat > 1.1)
+fit_sp_3_summary_model |> filter(rhat > 1.1)
+fit_sp_4_summary_sma |> filter(rhat > 1.1)
+fit_sp_5_summary_sma |> filter(rhat > 1.1)
+fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
+```
+
+It is difficult to model heteroskedasticity and measurement errors at the same time.
+
+```{r}
+div_check(fit_sp_0_diagnostics_simple)
+div_check(fit_sp_1_diagnostics_model)
+div_check(fit_sp_11_diagnostics_model)
+div_check(fit_sp_2_diagnostics_model)
+div_check(fit_sp_3_diagnostics_model)
+div_check(fit_sp_4_diagnostics_sma)
+div_check(fit_sp_5_diagnostics_sma)
+div_check(fit_sp_6_diagnostics_sma_err)
+```
+
+```{r}
+targets::tar_load(loo_model)
+loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]], loo_model[[5]])
+```
+
+```{r}
+tar_read(cv_sp)
+```
+
+## coef
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png)
+```
+
+![](figs/coef_sp.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png2)
+```
+
+![](figs/coef_sp2.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png3)
+```
+
+![](figs/coef_sp3.png)
 
@@
 
-```{r}
+```{r, eval=TRUE}
 tar_load(sma_sp_tab)
@@
 
+## species LD
+
+```{r, eval=TRUE}
+tar_load(sma_sp_ld_tab)
+sma_sp_ld_tab |>
+  kable() |>
+  kable_styling()
+```
+
 ## tree
 
-```{r}
+```{r, eval=TRUE}
 tar_load(sma_tree_tab)
@@
 
-```{r}
+```{r, eval=TRUE}
 tar_load(sma_tree_ld_tab)
@@
   kable_styling()
+```
+
+# Validation
+
+```{r}
+tar_load(cv_sp)
+cv_sp
+```
+
+```{r}
+tar_load(cv_tree)
+cv_tree
 ```

### 2022-05-02 R/stan.R

@@ -1,4 +1,4 @@
-clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD")) {
+clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD"), int = FALSE) {
   if (model == "no") {
     x <- cbind(
       intercept = rep(1, nrow(sp_mean)),
@@ -22,6 +22,10 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD")) {
   }
 
   x[, -1] <- apply(x[, -1], 2, \(x)scale(log(x)))
+
+  if (int) {
+   x <- cbind(x, lalt = x[,2] * x[,3])
+  }
 
   # use non-scaled value for LMA
   log_lma_disc <- sp_mean$lma_disc |> log()

### 2022-05-02 _targets.R

@@ -203,6 +203,21 @@ list(
     # max_treedepth = 15,
     seed = 123
    ),
+
+   tar_stan_mcmc(
+    fit_sp_11,
+    "stan/model.stan",
+    data = clean_stan_data(sp_mean, model = "no", int = TRUE),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    # adapt_delta = 0.99,
+    # max_treedepth = 15,
+    seed = 123
+   ),
+
    tar_stan_mcmc(
     fit_sp_2,
     "stan/model.stan",
@@ -521,6 +536,7 @@ list(
       list(
         fit_sp_0 = fit_sp_0_mcmc_simple,
         fit_sp_1 = fit_sp_1_mcmc_model,
+        fit_sp_11 = fit_sp_11_mcmc_model,
         fit_sp_2 = fit_sp_2_mcmc_model,
         fit_sp_3 = fit_sp_3_mcmc_model
         ),

### 2022-05-02 report.Rmd
fit_sp_6

--- 2022-05-02 report.Rmd
@@
 targets::tar_load("fit_sp_1_summary_model")
+targets::tar_load("fit_sp_11_summary_model")
 targets::tar_load("fit_sp_2_summary_model")
 targets::tar_load("fit_sp_3_summary_model")
+targets::tar_load("fit_sp_33_summary_model")
 targets::tar_load("fit_sp_4_summary_sma")
@@
 targets::tar_load("fit_sp_1_diagnostics_model")
+targets::tar_load("fit_sp_11_diagnostics_model")
 targets::tar_load("fit_sp_2_diagnostics_model")
 targets::tar_load("fit_sp_3_diagnostics_model")
+targets::tar_load("fit_sp_33_diagnostics_model")
 targets::tar_load("fit_sp_4_diagnostics_sma")
@@
 fit_sp_1_summary_model |> filter(rhat > 1.1)
+fit_sp_11_summary_model |> filter(rhat > 1.1)
 fit_sp_2_summary_model |> filter(rhat > 1.1)
 fit_sp_3_summary_model |> filter(rhat > 1.1)
+fit_sp_33_summary_model |> filter(rhat > 1.1)
 fit_sp_4_summary_sma |> filter(rhat > 1.1)
@@
 div_check(fit_sp_1_diagnostics_model)
+div_check(fit_sp_11_diagnostics_model)
 div_check(fit_sp_2_diagnostics_model)
 div_check(fit_sp_3_diagnostics_model)
+div_check(fit_sp_33_diagnostics_model)
 div_check(fit_sp_4_diagnostics_sma)
@@
 targets::tar_load(loo_model)
-loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]])
+loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]],
+  loo_model[[4]], loo_model[[5]], loo_model[[6]])
 ```

### 2022-05-02 R/sp_analysis.R

@@ -41,6 +41,124 @@ lalt_sp_grid_dense <- function(data) {
       text = element_text(family = "Arial"))
 }
 
+
+# ldlalt_sp_col <- function(data) {
+
+  # tar_load(sp_mean)
+  # data <- sp_mean
+  # data <- data |>
+  #   mutate(la_gr3 = ifelse(str_detect(la_gr2, "Large"), "Large", "Small")) |>
+  #   mutate(lt_gr3 = ifelse(str_detect(lt_gr2, "Thick"), "Thick", "Thin")) |>
+  #   mutate(ld_gr3 = ifelse(str_detect(ld_gr2, "Dense"), "Dense", "Less dense"))
+
+  # my_col <- RColorBrewer::brewer.pal(4, "RdBu")
+
+  # p1 <- data |>
+  #   ggplot(aes(x = lma_disc, y = lma_leaf, col = ld_gr3)) +
+  #   geom_point(alpha = 0.6) +
+  #   scale_x_log10() +
+  #   scale_y_log10() +
+  #   geom_abline(slope = 1, intercept = 0, lty = 2) +
+  #   geom_sma(se = FALSE) +
+  #   scale_color_manual(
+  #     values = my_col[c(2, 4)],
+  #     name = "Diameter of the leaf punch"
+  #   ) +
+  #   xlab(expression(Leaf ~ disc ~ LMA ~ (g ~ m^{
+  #     -2
+  #   }))) +
+  #   ylab(expression(Whole - leaf ~ LMA ~ (g ~ m^{
+  #     -2
+  #   }))) +
+  #   stat_cor(
+  #     aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial"),
+  #     show.legend = FALSE
+  #   ) +
+  #   theme_bw() +
+  #   theme(
+  #     text = element_text(family = "Arial"),
+  #     legend.position = c(0.3, 0.1),
+  #     legend.key.size = unit(0.5, "cm"),
+  #     legend.spacing.y = unit(0.1, "cm"),
+  #     legend.text.align = 0,
+  #     legend.key.height = unit(0.2, "cm"),
+  #     legend.text = element_text(size = 9),
+  #     legend.title = element_text(size = 9)
+  #   )
+
+  # p2 <- data |>
+  #   ggplot(aes(x = lma_disc, y = lma_leaf, col = la_gr3)) +
+  #   geom_point(alpha = 0.6) +
+  #   scale_x_log10() +
[…]

### 2022-05-02 R/stan.R

@@ -1,4 +1,4 @@
-clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD"), int = FALSE) {
+clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = FALSE) {
   if (model == "no") {
     x <- cbind(
       intercept = rep(1, nrow(sp_mean)),
@@ -12,12 +12,22 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD"), int = FALSE) 
       la = sp_mean$la,
       lt = sp_mean$lt
     )
-  } else {
+  } else if (model == "LD") {
     x <- cbind(
       intercept = rep(1, nrow(sp_mean)),
-      lma_disc = sp_mean$lma_disc / sp_mean$lt / 1000,
+      lma_disc = sp_mean$ld_leaf,
       la = sp_mean$la,
       lt = sp_mean$lt
+    )
+  } else if (model == "LD2") {
+    x <- cbind(
+      intercept = rep(1, nrow(sp_mean)),
+      lma_disc = sp_mean$ld_leaf,
+      la = sp_mean$la,
+      lt = sp_mean$lt,
+      int1 = sp_mean$ld_leaf * sp_mean$la,
+      int2 = sp_mean$ld_leaf * sp_mean$lt,
+      int3 = sp_mean$la * sp_mean$lt
     )
   }
 

### 2022-05-02 _targets.R

@@ -231,10 +231,24 @@ list(
     # max_treedepth = 15,
     seed = 123
    ),
+
    tar_stan_mcmc(
     fit_sp_3,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "LD"),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    # adapt_delta = 0.99,
+    # max_treedepth = 15,
+    seed = 123
+   ),
+   tar_stan_mcmc(
+    fit_sp_33,
+    "stan/model.stan",
+    data = clean_stan_data(sp_mean, model = "LD2"),
     refresh = 0,
     chains = 4,
     parallel_chains = getOption("mc.cores", 4),
@@ -538,7 +552,8 @@ list(
         fit_sp_1 = fit_sp_1_mcmc_model,
         fit_sp_11 = fit_sp_11_mcmc_model,
         fit_sp_2 = fit_sp_2_mcmc_model,
-        fit_sp_3 = fit_sp_3_mcmc_model
+        fit_sp_3 = fit_sp_3_mcmc_model,
+        fit_sp_33 = fit_sp_33_mcmc_model
         ),
     \(x)x$loo(cores = parallel::detectCores())
     )

### 2022-05-03 R/stan.R
update figs

@@ -29,6 +29,13 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = 
       int2 = sp_mean$ld_leaf * sp_mean$lt,
       int3 = sp_mean$la * sp_mean$lt
     )
+  } else if (model == "LM") {
+    x <- cbind(
+      intercept = rep(1, nrow(sp_mean)),
+      lma_disc = sp_mean$ld_leaf * sp_mean$lt,
+      la = sp_mean$la,
+      lt = sp_mean$lt
+    )
   }
 
   x[, -1] <- apply(x[, -1], 2, \(x)scale(log(x)))
@@ -219,10 +226,21 @@ coef_pointrange <- function(data, ld = FALSE) {
         "Effect of LT on variance" = expression(Effect~of~LT~on~variance~(gamma[3]))
       ))
     }
+    if(ld) {
+      p <- p + scale_y_discrete(labels = c(
+        "Intercept for mean" = expression(Intercept~of~mean~(beta[0])),
+        "Effect of disc LMA on mean" = expression(Effect~of~LD~on~mean~(beta[1])),
+        "Effect of LA on mean" = expression(Effect~of~LA~on~mean~(beta[2])),
+        "Effect of LT on mean" = expression(Effect~of~LT~on~mean~(beta[3])),
+        "Effect of disc LMA on variance" = expression(Effect~of~LD~on~variance~(gamma[1])),
+        "Effect of LA on variance" = expression(Effect~of~LA~on~variance~(gamma[2])),
+        "Effect of LT on variance" = expression(Effect~of~LT~on~variance~(gamma[3]))
+      ))
+    }
     p
 }
 
-coef_pointrange2 <- function(data, ld = FALSE) {
+coef_pointrange2 <- function(data, ld = FALSE, lm = FALSE, lalt = FALSE) {
 
   data1 <- data |>
     filter(para != "gamma[1]") |>
@@ -325,6 +343,31 @@ coef_pointrange2 <- function(data, ld = FALSE) {
         "Effect of disc LMA on variance" = expression(Effect~of~LD~on~variance~(gamma[1])),
         "Effect of LA on variance" = expression(Effect~of~LA~on~variance~(gamma[2])),
         "Effect of LT on variance" = expression(Effect~of~LT~on~variance~(gamma[3]))
+      ))
+    }
+    if(lm) {
+      p1 <- p1 + scale_y_discrete(labels = c(
[…]

### 2022-05-03 report.Rmd
update figs
update ld_disc

--- 2022-05-02 report.Rmd
@@
 targets::tar_load("fit_sp_1_summary_model")
+targets::tar_load("fit_sp_11_summary_model")
 targets::tar_load("fit_sp_2_summary_model")
+targets::tar_load("fit_sp_21_summary_model2")
 targets::tar_load("fit_sp_3_summary_model")
-targets::tar_load("fit_sp_4_summary_sma")
-targets::tar_load("fit_sp_5_summary_sma")
-targets::tar_load("fit_sp_6_summary_sma_err")
+targets::tar_load("fit_sp_31_summary_model")
+targets::tar_load("fit_sp_32_summary_model")
+# targets::tar_load("fit_sp_4_summary_sma")
+# targets::tar_load("fit_sp_5_summary_sma")
+# targets::tar_load("fit_sp_6_summary_sma_err")
 
@@
 targets::tar_load("fit_sp_1_diagnostics_model")
+targets::tar_load("fit_sp_11_diagnostics_model")
 targets::tar_load("fit_sp_2_diagnostics_model")
+targets::tar_load("fit_sp_21_diagnostics_model2")
 targets::tar_load("fit_sp_3_diagnostics_model")
-targets::tar_load("fit_sp_4_diagnostics_sma")
-targets::tar_load("fit_sp_5_diagnostics_sma")
-targets::tar_load("fit_sp_6_diagnostics_sma_err")
+targets::tar_load("fit_sp_31_diagnostics_model")
+targets::tar_load("fit_sp_32_diagnostics_model")
+# targets::tar_load("fit_sp_4_diagnostics_sma")
+# targets::tar_load("fit_sp_5_diagnostics_sma")
+# targets::tar_load("fit_sp_6_diagnostics_sma_err")
 ```
@@
 fit_sp_1_summary_model |> filter(rhat > 1.1)
+fit_sp_11_summary_model |> filter(rhat > 1.1)
 fit_sp_2_summary_model |> filter(rhat > 1.1)
+fit_sp_21_summary_model2 |> filter(rhat > 1.1)
 fit_sp_3_summary_model |> filter(rhat > 1.1)
-fit_sp_4_summary_sma |> filter(rhat > 1.1)
-fit_sp_5_summary_sma |> filter(rhat > 1.1)
-fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
+fit_sp_31_summary_model |> filter(rhat > 1.1)
+fit_sp_32_summary_model |> filter(rhat > 1.1)
+# fit_sp_4_summary_sma |> filter(rhat > 1.1)
+# fit_sp_5_summary_sma |> filter(rhat > 1.1)
+# fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
 ```
@@
 div_check(fit_sp_1_diagnostics_model)
+div_check(fit_sp_11_diagnostics_model)
 div_check(fit_sp_2_diagnostics_model)
+div_check(fit_sp_21_diagnostics_model2)
 div_check(fit_sp_3_diagnostics_model)
-div_check(fit_sp_4_diagnostics_sma)
-div_check(fit_sp_5_diagnostics_sma)
-div_check(fit_sp_6_diagnostics_sma_err)
+div_check(fit_sp_31_diagnostics_model)
+div_check(fit_sp_32_diagnostics_model)
+# div_check(fit_sp_4_diagnostics_sma)
+# div_check(fit_sp_5_diagnostics_sma)
+# div_check(fit_sp_6_diagnostics_sma_err)
 ```
@@
 targets::tar_load(loo_model)
-loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]])
+loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]],
+  loo_model[[4]], loo_model[[5]], loo_model[[6]], loo_model[[7]], loo_model[[8]])
 ```
@@
 ```{r, eval=TRUE}
+tar_load(coef_sp_png1)
+```
+
+![](figs/coef_sp1.png)
+
+```{r, eval=TRUE}
 tar_load(coef_sp_png3)
@@
 ![](figs/coef_sp3.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png31)
+```
+
+![](figs/coef_sp31.png)
+
+```{r, eval=TRUE}
+tar_load(coef_sp_png333)
+```
+
+![](figs/coef_sp333.png)
 

### 2022-05-03 R/stan.R

@@ -19,6 +19,14 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = 
       la = sp_mean$la,
       lt = sp_mean$lt
     )
+  } else if (model == "LD3") {
+    x <- cbind(
+      intercept = rep(1, nrow(sp_mean)),
+      #lma_disc = sp_mean$lma_disc / sp_mean$lt,
+      lma_disc = sp_mean$ld_disc,
+      la = sp_mean$la,
+      lt = sp_mean$lt
+    )
   } else if (model == "LD2") {
     x <- cbind(
       intercept = rep(1, nrow(sp_mean)),
@@ -55,7 +63,9 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = 
     sp = sp_mean$species |> as.factor() |> as.numeric(),
     log_y = log_lma_leaf,
     log_lma_disc = log_lma_disc,
-    x = x)
+    x = x,
+    x2 = x[,-2]
+    )
 
 }
 

### 2022-05-03 _targets.R

@@ -231,6 +231,19 @@ list(
     # max_treedepth = 15,
     seed = 123
    ),
+   tar_stan_mcmc(
+    fit_sp_21,
+    "stan/model2.stan",
+    data = clean_stan_data(sp_mean, model = "LMA"),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    # adapt_delta = 0.99,
+    # max_treedepth = 15,
+    seed = 123
+   ),
 
    tar_stan_mcmc(
     fit_sp_3,
@@ -246,7 +259,21 @@ list(
     seed = 123
    ),
    tar_stan_mcmc(
-    fit_sp_33,
+    fit_sp_31,
+    "stan/model.stan",
+    data = clean_stan_data(sp_mean, model = "LD3"),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    # adapt_delta = 0.99,
+    # max_treedepth = 15,
+    seed = 123
+   ),
+
+   tar_stan_mcmc(
+    fit_sp_32,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "LD2"),
     refresh = 0,
@@ -287,47 +314,48 @@ list(
     seed = 123
    ),
 
-   tar_stan_mcmc(
-    fit_sp_4,
-    "stan/sma.stan",
-    data = clean_stan_data(sp_mean, model = "no"),
-    refresh = 0,
-    chains = 4,
-    parallel_chains = getOption("mc.cores", 4),
-    iter_warmup = 2000,
-    iter_sampling = 2000,
-    adapt_delta = 0.99,
-    max_treedepth = 15,
-    seed = 123
-   ),
+  # sma works but error models do not work
+  #  tar_stan_mcmc(
+  #   fit_sp_4,
+  #   "stan/sma.stan",
+  #   data = clean_stan_data(sp_mean, model = "no"),
+  #   refresh = 0,
+  #   chains = 4,
+  #   parallel_chains = getOption("mc.cores", 4),
+  #   iter_warmup = 2000,
+  #   iter_sampling = 2000,
+  #   adapt_delta = 0.99,
+  #   max_treedepth = 15,
+  #   seed = 123
[…]

### 2022-05-03 ms/LMA_method.Rmd
update ms

--- 2022-04-26 ms/LMA_method.Rmd
@@
 
-*Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA*
+*Effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA*
 
-To quantify the effect of leaf area and thickness on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
-The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf area and leaf thickness on the log-scale;
+To quantify the effect of leaf morphology on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
+The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf tissue density, leaf area and leaf thickness on the log-scale;
 
 \begin{align}
-\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i) (\#eq:LMA)\\
-\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i}) (\#eq:mu)
+\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i^2) (\#eq:LMA)\\
+\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LD_{i}) + \beta_2 \mathrm{ln}(LA_{i}) + \beta_3 \mathrm{ln}(LT_{i}) (\#eq:mu)
 \end{align}
 
-where $LMA_{Wi}$, $LMA_{Di}$, $LA_{i}$, $LT_{i}$ are the whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree *i*, respectively.
-$\tilde{\mu_i}$ is the effect of leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree *i*, and $\sigma_i$ is the variance of whole-leaf LMA for tree *i*, and $\beta$ are coefficients.
-
-The variance of whole-leaf LMA ($\sigma_i$) was assumed to follow a normal distribution;
+where $LMA_{Wi}$, $LMA_{Di}$, $LD_{i}$, $LA_{i}$, $LT_{i}$ are the observed whole-leaf LMA, leaf disc LMA, leaf tissue density, leaf area and leaf thickness for tree *i*, respectively,
+$\tilde{\mu_i}$ is the effect of leaf tissue density, leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree *i*, and $\sigma_i^2$ is the variance of whole-leaf LMA for tree *i*, and $\beta$ are coefficients.
+The standard deviation of whole-leaf LMA ($\sigma_i$) was assumed to follow a normal distribution;
 
 \begin{align}
-\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega) (\#eq:ln-sigma) \\
-\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i}) (\#eq:tilde-sigma)
+\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega^2) (\#eq:ln-sigma) \\
+\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LD_{i}) + \gamma_2 \mathrm{ln}(LA_{i}) + \gamma_3 \mathrm{ln}(LT_{i}) (\#eq:tilde-sigma)
 \end{align}
@@
 where $\tilde{\sigma_i}$ is the effect of leaf area and leaf thickness on the variance of whole-leaf LMA,
-$\omega$ is a scaling hyperparameter, and $\gamma$ are coefficients.
-To allow comparisons among parameter estimates, $\mathrm{ln}(LA)$ and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
+$\omega^2$ is a scaling hyperparameter, and $\gamma$ are coefficients.
+To allow comparisons among parameter estimates, $\mathrm{ln}(LD)$, $\mathrm{ln}(LA)$ and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
+Note that this model does not include measurement errors of leaf disc LMA implemented in the following analysis, because there are too many scaling parameters
 
@@
 
-Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the samples and different leaf area and thickness groups.
-Species and individual groups were divided into four categories based on the medians of leaf area and leaf thickness across all species and all individuals, respectively:
-thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species (individuals).
+Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were further summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the samples and different leaf area and thickness groups.
+
+Species groups were divided into four categories based on the medians of leaf area and leaf thickness across all species:
+thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species.
 Median values are as following:
 small-leaved species (LA < `r val$LA_mid` cm^2^),
-thin-leaved species (LT < `r val$LT_mid` mm),
-small-leaved individuals (LA < `r val$LA_mid2` cm^2^),
-and thin-leaved individuals (LT < `r val$LT_mid2` mm).
+and thin-leaved species (LT < `r val$LT_mid` mm).
 
@@
 
-Disc-based estimates of species mean LMA matched well whole-leaf estimates (Table 1; *R^2^* = `r val$r2_LMA` for all species).
-Species with thicker and smaller leaves had stronger correlations between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
-There was a negative correlation between species mean leaf area and leaf thickness (*r* = `r val$LA_LT_r`, *P* `r val$LA_LT_p`, *n* = `r val$LA_LT_n`).
+Leaf tissue density, leaf area and leaf thickness influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 1).
+Specifically, species with greater leaf tissue density (Fig. 1a, $\beta_1$), and larger (Fig. 1a, $\beta_2$) and thicker leaves (Fig. 1a, $\beta_3$) had greater whole-leaf LMA than leaf disc LMA.
+Species with lower leaf tissue density (Fig.
+1b, $\gamma_1$), larger leaf area (Fig.
+1b, $\gamma_2$), and thinner leaves (Fig.
+1b, $\gamma_3$) had larger variance in the relationship between the whole-leaf LMA and leaf disc LMA.
+
 When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4% greater than disc-based estimates in the arithmetic scale.
@@
 
-Disc-based estimates of individual mean LMA also showed positive correlations with whole-leaf estimates but their *R^2^* values were smaller than those for the species means (Fig. 2).
-Similar to the species-level pattern, individuals with thicker and smaller leaves had stronger correlations (Fig. 2).
+Species with less dense, thicker and smaller leaves had stronger correlations between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
+
+There was a negative correlation between species mean leaf area and leaf thickness (*r* = `r val$LA_LT_r`, *P* `r val$LA_LT_p`, *n* = `r val$LA_LT_n`).
+
 The relationships of the whole-leaf LMA : disc leaf LMA ratio with total dry mass for the leaf disc (we weighted 2-3 discs together), with leaf thickness, and with leaf area were heteroscedastic (unequal variance, *P* < 0.001; Appendix S3).
@@
 **Fig. 1.**
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
-Species groups are divided into four categories on the basis of the medians of the leaf size and leaf thickness across all the species.
+Standardized regression coefficients modelig
+(a) the effects of leaf tissue density (LD; $\beta_1$),
+leaf area (LA; $\beta_2$),
+leaf thickness (LT; $\beta_3$)
+on the mean estimates of whole-leaf LMA, and
+(b) the effects of leaf tissue density ($\gamma_1$),
+leaf area ($\gamma_2$), and
+leaf thickness ($\gamma_3$)
+on the estimated variance of whole-leaf LMA.
+The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
+Circles show posterior means of coefficients.
+Thick and thin lines indicate 90% and 95% credible intervals, respectively.
+
+![](../figs/coef_sp3.png)
+
+\newpage
+
+**Fig. 2.**
+Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs for (a) nondense-leave species and (b) dense-leaved species.
+Species groups are divided into eight categories on the basis of the medians of the leaf tissue density, leaf area and leaf thickness across all the species.
 Dashed lines indicate 1:1 lines.
@@
 
-![](../figs/lalt_pool_grid.png)
-
-\newpage
-
-**Fig. 2.**
-Relationships between individual leaf mass per area (LMA) determined by using whole leaves and leaf discs.
-Individual groups are divided into four categories based on the basis of the medians of the leaf size and leaf thickness across all the individuals.
-All the correlations are significant (*P* < 0.001).
-Details as in Fig. 1.
-
-![](../figs/lalt_tree_grid.png)
+![](../figs/lalt_sp_grid_dense.png)
 

### 2022-05-03 ms/LMA_method.tex
update ms

@@
 
-\emph{Effects of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA}
-
-To quantify the effect of leaf sizes and thicknesses on the relationship between whole-leaf and leaf disc LMA, we built hierarchical Bayes models.
-The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of leaf size and leaf thickness on the log-scale;
+\emph{Effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA}
+
+To quantify the effect of leaf morphology on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
+The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of leaf tissue density, leaf area and leaf thickness on the log-scale;
 
 \begin{align}
-\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i) \label{eq:LMA}\\
-\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LA_{i}) + \beta_2 \mathrm{ln}(LT_{i}) \label{eq:mu}
+\mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i^2) \label{eq:LMA}\\
+\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LD_{i}) + \beta_2 \mathrm{ln}(LA_{i}) + \beta_3 \mathrm{ln}(LT_{i}) \label{eq:mu}
 \end{align}
 
-where \(LMA_{Wi}\), \(LMA_{Di}\), \(LA_{i}\), \(LT_{i}\) are the whole-leaf LMA, leaf disc LMA, leaf area and leaf thickness for tree \emph{i}, respectively.
-\(\tilde{\mu_i}\) is the effect of leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree \emph{i}, and \(\sigma_i\) is the variance of whole-leaf LMA for tree \emph{i}, and \(\beta\) are coefficients.
-
-The variance of whole-leaf LMA (\(\sigma_i\)) was assumed to follow a normal distribution;
+where \(LMA_{Wi}\), \(LD_{i}\), \(LA_{i}\), \(LT_{i}\) are the observed whole-leaf LMA, leaf tissue density, leaf area and leaf thickness for tree \emph{i}, respectively,
+\(LMA_{Di}\) is the true unobserved value of leaf disc LMA for tree \emph{i}, which can be modeled using the observed leaf disc LMA.
+\(\tilde{\mu_i}\) is the effect of leaf tissue density, leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree \emph{i}, and \(\sigma_i^2\) is the variance of whole-leaf LMA for tree \emph{i}, and \(\beta\) are coefficients.
+
+The standard deviation of whole-leaf LMA (\(\sigma_i\)) was assumed to follow a normal distribution;
 
 \begin{align}
-\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega) \label{eq:ln-sigma} \\
-\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LA_{i}) + \gamma_2 \mathrm{ln}(LT_{i}) \label{eq:tilde-sigma}
+\mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega^2) \label{eq:ln-sigma} \\
+\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LD_{i}) + \gamma_2 \mathrm{ln}(LA_{i}) + \gamma_3 \mathrm{ln}(LT_{i}) \label{eq:tilde-sigma}
 \end{align}
@@
 where \(\tilde{\sigma_i}\) is the effect of leaf area and leaf thickness on the variance of whole-leaf LMA,
-\(\omega\) is a scaling hyperparameter, and \(\gamma\) are coefficients.
-To allow comparisons among parameter estimates, \(\mathrm{ln}(LA)\) and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
+\(\omega^2\) is a scaling hyperparameter, and \(\gamma\) are coefficients.
+To allow comparisons among parameter estimates, \(\mathrm{ln}(LD)\), \(\mathrm{ln}(LA)\) and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
 
@@
 
-\emph{Bivariate trait relationships}
+\emph{Bivariate trait relationships for mean and CV}
 
@@
 and thin-leaved individuals (LT \textless{} mm).
-
-\emph{Intraspecifc variation}
 

### 2022-05-03 report.Rmd
clean names

--- 2022-05-02 report.Rmd
@@
 
-```{r}
-targets::tar_load("fit_sp_0_summary_simple")
-targets::tar_load("fit_sp_1_summary_model")
-targets::tar_load("fit_sp_11_summary_model")
-targets::tar_load("fit_sp_2_summary_model")
-targets::tar_load("fit_sp_3_summary_model")
-targets::tar_load("fit_sp_4_summary_sma")
-targets::tar_load("fit_sp_5_summary_sma")
-targets::tar_load("fit_sp_6_summary_sma_err")
+```{r,eval=TRUE}
 
-targets::tar_load("fit_sp_0_diagnostics_simple")
-targets::tar_load("fit_sp_1_diagnostics_model")
-targets::tar_load("fit_sp_11_diagnostics_model")
-targets::tar_load("fit_sp_2_diagnostics_model")
-targets::tar_load("fit_sp_3_diagnostics_model")
-targets::tar_load("fit_sp_4_diagnostics_sma")
-targets::tar_load("fit_sp_5_diagnostics_sma")
-targets::tar_load("fit_sp_6_diagnostics_sma_err")
+targets::tar_load(fit_sp_no_lma_summary_model)
+targets::tar_load(fit_sp_no_lma_int_summary_model)
+targets::tar_load(fit_sp_lma_summary_model)
+targets::tar_load(fit_sp_lma2_summary_model2)
+targets::tar_load(fit_sp_ld_summary_model)
+targets::tar_load(fit_sp_ld2_summary_model)
+targets::tar_load(fit_sp_ld3_summary_model)
+targets::tar_load(fit_sp_lm_summary_model)
+targets::tar_load(fit_sp_lma0_summary_simple)
+
+targets::tar_load(fit_sp_no_lma_diagnostics_model)
+targets::tar_load(fit_sp_no_lma_int_diagnostics_model)
+targets::tar_load(fit_sp_lma_diagnostics_model)
+targets::tar_load(fit_sp_lma2_diagnostics_model2)
+targets::tar_load(fit_sp_ld_diagnostics_model)
+targets::tar_load(fit_sp_ld2_diagnostics_model)
+targets::tar_load(fit_sp_ld3_diagnostics_model)
+targets::tar_load(fit_sp_lm_diagnostics_model)
+targets::tar_load(fit_sp_lma0_diagnostics_simple)
+
 ```
 
-```{r}
-fit_sp_0_summary_simple |> filter(rhat > 1.1)
-fit_sp_1_summary_model |> filter(rhat > 1.1)
-fit_sp_11_summary_model |> filter(rhat > 1.1)
-fit_sp_2_summary_model |> filter(rhat > 1.1)
-fit_sp_3_summary_model |> filter(rhat > 1.1)
-fit_sp_4_summary_sma |> filter(rhat > 1.1)
-fit_sp_5_summary_sma |> filter(rhat > 1.1)
-fit_sp_6_summary_sma_err |> filter(rhat > 1.1)
+```{r,eval=TRUE}
+fit_sp_no_lma_summary_model  |> filter(rhat > 1.1)
+fit_sp_no_lma_int_summary_model |> filter(rhat > 1.1)
+fit_sp_lma_summary_model |> filter(rhat > 1.1)
+fit_sp_lma2_summary_model2 |> filter(rhat > 1.1)
+fit_sp_ld_summary_model |> filter(rhat > 1.1)
+fit_sp_ld2_summary_model |> filter(rhat > 1.1)
+fit_sp_ld3_summary_model |> filter(rhat > 1.1)
+fit_sp_lm_summary_model |> filter(rhat > 1.1)
+fit_sp_lma0_summary_simple |> filter(rhat > 1.1)
 ```
@@
 
-```{r}
-div_check(fit_sp_0_diagnostics_simple)
-div_check(fit_sp_1_diagnostics_model)
-div_check(fit_sp_11_diagnostics_model)
-div_check(fit_sp_2_diagnostics_model)
-div_check(fit_sp_3_diagnostics_model)
-div_check(fit_sp_4_diagnostics_sma)
-div_check(fit_sp_5_diagnostics_sma)
-div_check(fit_sp_6_diagnostics_sma_err)
+```{r,eval=TRUE}
+div_check(fit_sp_no_lma_diagnostics_model)
+div_check(fit_sp_no_lma_int_diagnostics_model)
+div_check(fit_sp_lma_diagnostics_model)
+div_check(fit_sp_lma2_diagnostics_model2)
+div_check(fit_sp_ld_diagnostics_model)
+div_check(fit_sp_ld2_diagnostics_model)
+div_check(fit_sp_ld3_diagnostics_model)
+div_check(fit_sp_lm_diagnostics_model)
+div_check(fit_sp_lma0_diagnostics_simple)
 ```
@@
 targets::tar_load(loo_model)
-loo::loo_compare(loo_model[[1]], loo_model[[2]], loo_model[[3]], loo_model[[4]], loo_model[[5]])
+loo::loo_compare(
+  loo_model[[1]], loo_model[[2]], loo_model[[3]],
+  loo_model[[4]], loo_model[[5]], loo_model[[6]],
+  loo_model[[7]], loo_model[[8]], loo_model[[9]])
 ```
@@
 sma_sp_ld_tab |>
+  kable() |>
+  kable_styling()
+```
+
+## species simple
+
+```{r, eval=TRUE}
+tar_load(sma_sp_2_tab)
+sma_sp_2_tab |>
   kable() |>

### 2022-05-03 R/sp_analysis.R

@@ -277,6 +277,7 @@ generate_sma_tab <- function(sp_mean) {
 
 #' @title SMA table (species-level)
 generate_sma_ld_tab <- function(sp_mean) {
+
   sp_mean <- sp_mean |>
     mutate(lalt_gr = paste(ld_gr, "~", lalt_gr))
 
@@ -303,6 +304,56 @@ generate_sma_ld_tab <- function(sp_mean) {
 
   tb <- rbind(tb0$lma[[2]], tb0$lma_gr[[2]])
   tb <- cbind(c("All", tb0$lma_gr$group), tb) |>
+    as_tibble() |>
+    rename(Slope = slope, Intercept = intercept)
+
+  colnames(tb)[1] <- "Data"
+
+  tb
+}
+
+#' @title SMA table (species-level)
+generate_sma_2_tab <- function(sp_mean) {
+  sp_mean <- sp_mean |>
+     mutate(la_gr3 = ifelse(str_detect(la_gr2, "Large"), "Large", "Small")) |>
+     mutate(lt_gr3 = ifelse(str_detect(lt_gr2, "Thick"), "Thick", "Thin")) |>
+     mutate(ld_gr3 = ifelse(str_detect(ld_gr2, "Dense"), "Dense", "Less dense"))
+
+  sma_lma <- sma(log10(lma_leaf) ~ log10(lma_disc),
+    data = sp_mean,
+    elev.test = 0,
+    slope.test = 1
+  )
+
+  sma_la <- sma(log10(lma_leaf) ~ log10(lma_disc) * la_gr3,
+    data = sp_mean,
+    elev.test = 0,
+    slope.test = 1
+  )
+  sma_ld <- sma(log10(lma_leaf) ~ log10(lma_disc) * ld_gr3,
+    data = sp_mean,
+    elev.test = 0,
+    slope.test = 1
+  )
+  sma_lt <- sma(log10(lma_leaf) ~ log10(lma_disc) * lt_gr3,
+    data = sp_mean,
+    elev.test = 0,
+    slope.test = 1
+  )
+
+  # we don't need leaf density
+  tb0 <- lapply(
+    list(
+      lma = sma_lma,
+      ld_gr = sma_ld,
+      la_gr = sma_la,
+      lt_gr = sma_lt
+    ),
+    extract_sma
+  )
+
[…]

### 2022-05-03 R/stan.R

@@ -30,11 +30,11 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = 
   } else if (model == "LD2") {
     x <- cbind(
       intercept = rep(1, nrow(sp_mean)),
-      lma_disc = sp_mean$ld_leaf,
+      lma_disc = sp_mean$ld_disc,
       la = sp_mean$la,
       lt = sp_mean$lt,
-      int1 = sp_mean$ld_leaf * sp_mean$la,
-      int2 = sp_mean$ld_leaf * sp_mean$lt,
+      int1 = sp_mean$ld_disc * sp_mean$la,
+      int2 = sp_mean$ld_disc * sp_mean$lt,
       int3 = sp_mean$la * sp_mean$lt
     )
   } else if (model == "LM") {

### 2022-05-03 _targets.R

@@ -191,7 +191,7 @@ list(
   #  ),
 
    tar_stan_mcmc(
-    fit_sp_1,
+    fit_sp_no_lma,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "no"),
     refresh = 0,
@@ -205,7 +205,7 @@ list(
    ),
 
    tar_stan_mcmc(
-    fit_sp_11,
+    fit_sp_no_lma_int,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "no", int = TRUE),
     refresh = 0,
@@ -219,7 +219,7 @@ list(
    ),
 
    tar_stan_mcmc(
-    fit_sp_2,
+    fit_sp_lma,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "LMA"),
     refresh = 0,
@@ -232,7 +232,7 @@ list(
     seed = 123
    ),
    tar_stan_mcmc(
-    fit_sp_21,
+    fit_sp_lma2,
     "stan/model2.stan",
     data = clean_stan_data(sp_mean, model = "LMA"),
     refresh = 0,
@@ -246,7 +246,7 @@ list(
    ),
 
    tar_stan_mcmc(
-    fit_sp_3,
+    fit_sp_ld,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "LD"),
     refresh = 0,
@@ -259,7 +259,7 @@ list(
     seed = 123
    ),
    tar_stan_mcmc(
-    fit_sp_31,
+    fit_sp_ld3,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "LD3"),
     refresh = 0,
@@ -273,7 +273,7 @@ list(
    ),
 
    tar_stan_mcmc(
-    fit_sp_32,
+    fit_sp_ld2,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "LD2"),
     refresh = 0,
@@ -286,7 +286,7 @@ list(
     seed = 123
    ),
    tar_stan_mcmc(
-    fit_sp_333,
+    fit_sp_lm,
     "stan/model.stan",
     data = clean_stan_data(sp_mean, model = "LM"),
     refresh = 0,
@@ -301,7 +301,7 @@ list(
 
 
    tar_stan_mcmc(
-    fit_sp_0,
+    fit_sp_lma0,
     "stan/simple.stan",
[…]

### 2022-05-03 report.Rmd
add tab

@@
 ```
+```{r}
+sma_sp_tab |>
+  write_csv("data/sma_sp_tab.csv")
+```
 
@@
 
+```{r}
+sma_sp_ld_tab |>
+  write_csv("data/sma_sp_ld_tab.csv")
+```
+
 ## species simple
@@
   kable_styling()
+```
+
+```{r}
+sma_sp_2_tab |>
+  write_csv("data/sma_sp_2_tab.csv")
 ```

### 2022-05-03 _targets.R

@@ -748,6 +748,7 @@ list(
     generate_sma_ld_tab(sp_mean)
   ),
 
+
   tar_target(
     sma_sp_2_tab,
     generate_sma_2_tab(sp_mean)

### 2022-05-03 ms/LMA_method.Rmd
update ms

@@
 Leaf tissue density, leaf area and leaf thickness influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 1).
-Specifically, species with greater leaf tissue density (Fig. 1a, $\beta_1$), and larger (Fig. 1a, $\beta_2$) and thicker leaves (Fig. 1a, $\beta_3$) had greater whole-leaf LMA than leaf disc LMA.
-Species with lower leaf tissue density (Fig.
-1b, $\gamma_1$), larger leaf area (Fig.
-1b, $\gamma_2$), and thinner leaves (Fig.
-1b, $\gamma_3$) had larger variance in the relationship between the whole-leaf LMA and leaf disc LMA.
+Specifically, species with lower leaf tissue density (Fig. 1a, $\beta_1$) and larger leaves (Fig. 1a, $\beta_2$) had greater whole-leaf LMA than leaf disc LMA.
+Species with lower leaf tissue density (Fig. 1b, $\gamma_1$) and larger larger leaves (Fig. 1b, $\gamma_2$) also had larger variance in the relationship between the whole-leaf LMA and leaf disc LMA.
+Thinner-leaved species (Fig. 1b, $\gamma_3$) tended to have larger variance in the relationship (i.e., the 90% credible interval did not include zero).
 
 When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4% greater than disc-based estimates in the arithmetic scale.
+
 Large-leaved species also had significant positive intercepts, suggesting that whole-leaf estimates of LMA were 22.1% greater than disc-based estimates in the arithmetic scale (Table 1).
@@
 
-![](../figs/coef_sp3.png)
+![](../figs/coef_sp31.png)
 

### 2022-05-03 R/data_clean.R
add ldlalt.csv

@@ -352,7 +352,8 @@ sp_dat_mean <- function(full_data_csv){
     mutate(lt_gr2 = factor(lt_gr2, levels = c("Thin-leaved~species",
                            "Thick-leaved~species"))) |>
     mutate(ld_gr2 = factor(ld_gr2, levels = c("Nondense-leaved~species",
-                           "Dense-leaved~species")))
+                           "Dense-leaved~species"))) |>
+    mutate(ldlalt_gr = paste0(ld_gr, "~", lalt_gr))
 
   d
 }
@@ -428,8 +429,8 @@ tree_dat_clean <- function(tree_data_csv) {
     mutate(lt_gr2 = factor(lt_gr2, levels = c("Thin-leaved~individuals",
                            "Thick-leaved~individuals"))) |>
     mutate(ld_gr2 = factor(ld_gr2, levels = c("Nondense-leaved~individuals",
-                           "Dense-leaved~individuals")))
-
+                           "Dense-leaved~individuals"))) |>
+    mutate(ldlalt_gr = paste0(ld_gr, "~", lalt_gr))
 
   tree
 }

### 2022-05-03 R/sp_analysis.R

@@ -277,16 +277,13 @@ generate_sma_tab <- function(sp_mean) {
 
 #' @title SMA table (species-level)
 generate_sma_ld_tab <- function(sp_mean) {
-  sp_mean <- sp_mean |>
-    mutate(lalt_gr = paste0(ld_gr, "~", lalt_gr))
-
   sma_lma <- sma(log10(lma_leaf) ~ log10(lma_disc),
     data = sp_mean,
     elev.test = 0,
     slope.test = 1
   )
 
-  sma_lma_lalt_gr <- sma(log10(lma_leaf) ~ log10(lma_disc) * lalt_gr,
+  sma_lma_gr <- sma(log10(lma_leaf) ~ log10(lma_disc) * ldlalt_gr,
     data = sp_mean,
     elev.test = 0,
     slope.test = 1
@@ -296,7 +293,7 @@ generate_sma_ld_tab <- function(sp_mean) {
   tb0 <- lapply(
     list(
       lma = sma_lma,
-      lma_gr = sma_lma_lalt_gr
+      lma_gr = sma_lma_gr
     ),
     extract_sma
   )

### 2022-05-03 _targets.R

@@ -98,8 +98,8 @@ list(
     write_yml("values.yml",
       sp_mean, full_data_cv_csv, tree, lma_yaku_re)
   ),
-  # analyses and figs ---------------------------------------------
 
+  # analyses and figs ---------------------------------------------
   tar_target(
     stan_sim_dat,
     create_dummy_data(100)

### 2022-05-04 report.Rmd
add ldlalt.csv
update ldlalt
punch size

@@
 library(kableExtra)
+```
+
+```{r}
+tar_load(sp_mean)
+sp_mean |>
+  group_by(ldlalt_gr) |>
+  summarise(
+    lma_leaf = mean(lma_leaf) |> round(1),
+    lma_disc = mean(lma_disc) |> round(1)) |>
+  write_csv("data/ldlalt.csv")
 ```
@@
   loo_model[[4]], loo_model[[5]], loo_model[[6]],
-  loo_model[[7]], loo_model[[8]], loo_model[[9]])
+  loo_model[[7]], loo_model[[8]], loo_model[[9]],
+  loo_model[[10]], loo_model[[11]])
 ```

### 2022-05-04 R/stan.R

@@ -19,7 +19,7 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = 
       la = sp_mean$la,
       lt = sp_mean$lt
     )
-  } else if (model == "LD3") {
+  } else if (model == "LD3" | model == "punch" | model == "punch2") {
     x <- cbind(
       intercept = rep(1, nrow(sp_mean)),
       #lma_disc = sp_mean$lma_disc / sp_mean$lt,
@@ -45,7 +45,6 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = 
       lt = sp_mean$lt
     )
   }
-
   x2 <- cbind(
       intercept = rep(1, nrow(sp_mean)),
       lma_disc = sp_mean$ld_leaf,
@@ -55,6 +54,22 @@ clean_stan_data <- function(sp_mean, model = c("no", "LMA", "LD", "LD2"), int = 
 
   x2[, -1] <- apply(x2[, -1], 2, \(x)scale(log(x)))
   x[, -1] <- apply(x[, -1], 2, \(x)scale(log(x)))
+
+  if (model == "punch") {
+    yaku <- ifelse(sp_mean$location == "Yakushima", 0.5^2 * pi, 0.3^2*pi)
+    yaku <- scale(yaku) |> as.numeric()
+    x <- cbind(x,
+    punch = yaku,
+    int1 = x[,2] * yaku,
+    int2 = x[,3] * yaku,
+    int3 = x[,4] * yaku
+    )
+  } else if (model == "punch2") {
+    yaku <- ifelse(sp_mean$location == "Yakushima", 0, 1)
+    x <- cbind(x,
+    punch = yaku
+    )
+  }
 
   if (int) {
    x <- cbind(x, lalt = x[,2] * x[,3])
@@ -290,7 +305,6 @@ coef_pointrange <- function(data, ld = FALSE) {
 }
 
 coef_pointrange2 <- function(data, ld = FALSE, lm = FALSE, lalt = FALSE) {
-
   data1 <- data |>
     filter(para != "gamma[1]") |>
     filter(para != "beta[1]") |>
@@ -423,6 +437,99 @@ coef_pointrange2 <- function(data, ld = FALSE, lm = FALSE, lalt = FALSE) {
     p1 / p2 +
     plot_annotation(tag_levels = "a") &
     theme(
+      text = element_text(family = "Arial"))
+}
+
[…]

### 2022-05-04 _targets.R

@@ -272,6 +272,32 @@ list(
     # max_treedepth = 15,
     seed = 123
    ),
+   tar_stan_mcmc(
+    fit_sp_punch,
+    "stan/model.stan",
+    data = clean_stan_data(sp_mean, model = "punch"),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    # adapt_delta = 0.99,
+    # max_treedepth = 15,
+    seed = 123
+   ),
+   tar_stan_mcmc(
+    fit_sp_punch2,
+    "stan/model.stan",
+    data = clean_stan_data(sp_mean, model = "punch2"),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    # adapt_delta = 0.99,
+    # max_treedepth = 15,
+    seed = 123
+   ),
 
    tar_stan_mcmc(
     fit_sp_ld3_yaku,
@@ -384,6 +410,41 @@ list(
   #   max_treedepth = 15,
   #   seed = 123
   #  ),
+  tar_target(
+    coef_sp_tab_punch1,
+    create_stan_tab(fit_sp_punch_draws_model)
+  ),
+  tar_target(
+    coef_sp_tab_punch2,
+    create_stan_tab(fit_sp_punch2_draws_model)
+  ),
+
+  tar_target(
+    coef_sp_plot_punch1,
+    coef_pointrange3(coef_sp_tab_punch1)
+  ),
+  tar_target(
+    coef_sp_png_punch1,
+    ggsave(
+      "figs/coef_sp_punch1.png",
+      coef_sp_plot_punch1,
+      dpi = 300,
+      width = 6,
+      height = 6
+    ),
+    format = "file"
+  ),
+  tar_target(
+    coef_sp_pdf_punch1,
+    ggsave(
+      "figs/coef_sp_punch1.pdf",
+      coef_sp_plot,
+      device = cairo_pdf,
+      width = 6,
+      height = 6
+    ),
+    format = "file"
+  ),
 
   # coef for OLS stan
   tar_target(
@@ -692,7 +753,9 @@ list(
         fit_sp_ld2_mcmc_model2 = fit_sp_ld2_mcmc_model2,
[…]

### 2022-05-05 report.Rmd
update fig lab

@@
   loo_model[[7]], loo_model[[8]], loo_model[[9]],
-  loo_model[[10]], loo_model[[11]])
+  loo_model[[10]], loo_model[[11]],
+  loo_model[[12]], loo_model[[13]]
+  )
 ```

### 2022-05-05 _targets.R

@@ -311,6 +311,19 @@ list(
     # max_treedepth = 15,
     seed = 123
    ),
+   tar_stan_mcmc(
+    fit_sp_punch4,
+    "stan/model2.stan",
+    data = clean_stan_data(sp_mean, model = "punch"),
+    refresh = 0,
+    chains = 4,
+    parallel_chains = getOption("mc.cores", 4),
+    iter_warmup = 2000,
+    iter_sampling = 2000,
+    # adapt_delta = 0.99,
+    # max_treedepth = 15,
+    seed = 123
+   ),
 
    tar_stan_mcmc(
     fit_sp_ld3_yaku,
@@ -451,7 +464,7 @@ list(
       "figs/coef_sp_punch1.png",
       coef_sp_plot_punch1,
       dpi = 300,
-      width = 6,
+      width = 5,
       height = 6
     ),
     format = "file"
@@ -571,20 +584,20 @@ list(
 
   # coef for OLS stan 2
   tar_target(
-    coef_sp_tab3,
+    coef_sp_ld_tab,
     create_stan_tab(fit_sp_ld_draws_model)
   ),
   tar_target(
-    coef_sp_plot3,
-    coef_pointrange2(coef_sp_tab3, ld = TRUE)
+    coef_sp_ld_plot,
+    coef_pointrange2(coef_sp_ld_tab, ld = TRUE)
   ),
   tar_target(
-    coef_sp_png3,
+    coef_sp_ld_png,
     ggsave(
-      "figs/coef_sp3.png",
-      coef_sp_plot3,
+      "figs/coef_sp_ld.png",
+      coef_sp_ld_plot,
       dpi = 300,
-      width = 6,
+      width = 5,
       height = 6
     ),
     format = "file"
@@ -804,7 +817,8 @@ list(
         fit_sp_lma0_mcmc_simple = fit_sp_lma0_mcmc_simple,
         fit_sp_punch_mcmc_model = fit_sp_punch_mcmc_model,
         fit_sp_punch2_mcmc_model = fit_sp_punch2_mcmc_model,
-        fit_sp_punch3_mcmc_model2 = fit_sp_punch3_mcmc_model2
+        fit_sp_punch3_mcmc_model2 = fit_sp_punch3_mcmc_model2,
+        fit_sp_punch4_mcmc_model2 = fit_sp_punch4_mcmc_model2
         ),
     \(x)x$loo(cores = parallel::detectCores())
     )

### 2022-05-06 ms/LMA_method.Rmd
update ms

--- 2022-05-03 ms/LMA_method.Rmd
@@
 library(kableExtra)
-
 val <- yaml::yaml.load_file("../values.yml")
@@
 
-Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)
+Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per are (LMA)
 
@@
 
-To quantify the effect of leaf morphology on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
+To quantify the effect of leaf morphology and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
 The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf tissue density, leaf area and leaf thickness on the log-scale;
@@
 \mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i^2) (\#eq:LMA)\\
-\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LD_{i}) + \beta_2 \mathrm{ln}(LA_{i}) + \beta_3 \mathrm{ln}(LT_{i}) (\#eq:mu)
+\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LD_{i}) + \beta_2 \mathrm{ln}(LA_{i}) + \beta_3 \mathrm{ln}(LT_{i}) + \beta_4 PS_{i} \nonumber \\
+& + PS_{i} \times \bigl\{ \beta_5 \mathrm{ln}(LD_{i}) + \beta_6 \mathrm{ln}(LA_{i}) + \beta_7 \mathrm{ln}(LT_{i})\bigr\}(\#eq:mu)
 \end{align}
 
-where $LMA_{Wi}$, $LMA_{Di}$, $LD_{i}$, $LA_{i}$, $LT_{i}$ are the observed whole-leaf LMA, leaf disc LMA, leaf tissue density, leaf area and leaf thickness for tree *i*, respectively,
-$\tilde{\mu_i}$ is the effect of leaf tissue density, leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree *i*, and $\sigma_i^2$ is the variance of whole-leaf LMA for tree *i*, and $\beta$ are coefficients.
+where $LMA_{Wi}$, $LMA_{Di}$, $LD_{i}$, $LA_{i}$, and $LT_{i}$ are the observed whole-leaf LMA, leaf disc LMA, leaf tissue density, leaf area, and leaf thickness for species *i*, respectively,
+The dummy variable $PS_i$ is set to 1 for samples obtained with a small leaf punch (0.6-cm diameter) and 0 for samples obtained with a large leaf punch (1.0-cm diameter).
+$\tilde{\mu_i}$ is the effect of leaf tissue density, leaf area, leaf thickness and leaf punch size on the mean estimates for the whole-leaf LMA of species *i*, $\sigma_i^2$ is the variance of whole-leaf LMA for species *i*, and $\beta$ are coefficients.
 The standard deviation of whole-leaf LMA ($\sigma_i$) was assumed to follow a normal distribution;
@@
 \mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega^2) (\#eq:ln-sigma) \\
-\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LD_{i}) + \gamma_2 \mathrm{ln}(LA_{i}) + \gamma_3 \mathrm{ln}(LT_{i}) (\#eq:tilde-sigma)
+\mathrm{ln}(\tilde{\sigma_i}) & = \gamma_0 + \gamma_1 \mathrm{ln}(LD_{i}) + \gamma_2 \mathrm{ln}(LA_{i}) + \gamma_3 \mathrm{ln}(LT_{i}) + \gamma_4 PS_{i} \nonumber \\
+& + PS_{i} \times \bigl\{\gamma_5 \mathrm{ln}(LD_{i}) + \gamma_6 \mathrm{ln}(LA_{i}) + \gamma_7 \mathrm{ln}(LT_{i})\bigr\}(\#eq:tilde-sigma)
 \end{align}
 
-where $\tilde{\sigma_i}$ is the effect of leaf area and leaf thickness on the variance of whole-leaf LMA,
+where $\tilde{\sigma_i}$ is a hyperparameter for $\sigma_i$ ,
 $\omega^2$ is a scaling hyperparameter, and $\gamma$ are coefficients.
-To allow comparisons among parameter estimates, $\mathrm{ln}(LD)$, $\mathrm{ln}(LA)$ and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
+To allow comparisons among parameter estimates, $\mathrm{ln}(LD)$, $\mathrm{ln}(LA)$, and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
 Note that this model does not include measurement errors of leaf disc LMA implemented in the following analysis, because there are too many scaling parameters
@@
 
-Leaf tissue density, leaf area and leaf thickness influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 1).
-Specifically, species with greater leaf tissue density (Fig. 1a, $\beta_1$), and larger (Fig. 1a, $\beta_2$) and thicker leaves (Fig. 1a, $\beta_3$) had greater whole-leaf LMA than leaf disc LMA.
-Species with lower leaf tissue density (Fig.
-1b, $\gamma_1$), larger leaf area (Fig.
-1b, $\gamma_2$), and thinner leaves (Fig.
-1b, $\gamma_3$) had larger variance in the relationship between the whole-leaf LMA and leaf disc LMA.
-
-When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4% greater than disc-based estimates in the arithmetic scale.
-Large-leaved species also had significant positive intercepts, suggesting that whole-leaf estimates of LMA were 22.1% greater than disc-based estimates in the arithmetic scale (Table 1).
-Intercepts did not differ for small-leaved species (Table 1).
-
-Species with less dense, thicker and smaller leaves had stronger correlations between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
-
-There was a negative correlation between species mean leaf area and leaf thickness (*r* = `r val$LA_LT_r`, *P* `r val$LA_LT_p`, *n* = `r val$LA_LT_n`).
-
-The relationships of the whole-leaf LMA : disc leaf LMA ratio with total dry mass for the leaf disc (we weighted 2-3 discs together), with leaf thickness, and with leaf area were heteroscedastic (unequal variance, *P* < 0.001; Appendix S3).
-Samples with small total dry mass, thin leaves, and larger leaves tended to show greater variance (Fig. 2; Appendix S3).
-The total dry mass of leaf disc was positively correlated with both leaf thickness and leaf punch size (Appendix S4).
+There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: `r val$sma_slope_all_mean` [95%CI: `r val$sma_slope_all_lwr`, `r val$sma_slope_all_upr`], SMA intercept: `r val$sma_int_all_mean` [95%CI: `r val$sma_int_all_lwr`, `r val$sma_int_all_upr`]), suggesting that the whole-leaf estimates of LMA were `r val$sma_per_all_mean`% [95%CI: `r val$sma_per_all_lwr`, `r val$sma_per_all_upr`] greater than disc-based estimates in the arithmetic scale.
+Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2).
+When a large leaf punch was used, species with lower leaf tissue density had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a).
+Species with lower leaf tissue density had greater estimate whole-leaf to leaf disc LMA ratio when a small leaf punch was used (Fig. 2a).
+Species with larger leaves had greater estimate of the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2b), which was only significant for leaves obtained by a large punch.
+Species with thinner leaves had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
+Posteriors of coefficients are summarized in (Fig. SX).
+Leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
+3a).
+Large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Fig.
+3b).
 Amounts of intraspecific variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig. 3; *R^2^* = `r val$cv_r2`).
@@
 Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches are also the important sources of variance between whole-leaf and leaf disc LMA.
-This is probably because small dry mass inflates measurement errors and small leaf disc size inflates trait variation within leaves.
+This is probably because small dry mass inflates measurement errors and small leaf disc size inflates trait variation within leave.
 Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be large.
@@
 
-```{r tb1, echo=FALSE}
-tab1 <- read.csv("../data/tab1.csv")
+```{r tb1, echo=FALSE, eval=FALSE}
+tab1 <- read.csv("../data/sma_sp_ld_tab.csv")
 colnames(tab1) <- c("Data", "Slope", "Intercept", "*R^2^*")
@@
   mutate(Data = case_when(
-    Data == "Thick~Large" ~ "Thick-large",
-    Data == "Thick~Small" ~ "Thick-small",
-    Data == "Thin~Large" ~ "Thin-large",
-    Data == "Thin~Small" ~ "Thin-small",
+    Data == "Dense~Thick~Large" ~ "Dense-thick-large",
+    Data == "Dense~Thick~Small" ~ "Dense-thick-small",
+    Data == "Dense~Thin~Large" ~ "Dense-thin-large",
+    Data == "Dense~Thin~Small" ~ "Dense-thin-small",
+    Data == "Nondense~Thick~Large" ~ "Nondense-thick-large",
+    Data == "Nondense~Thick~Small" ~ "Nondense-thick-small",
+    Data == "Nondense~Thin~Large" ~ "Nondense-thin-large",
+    Data == "Nondense~Thin~Small" ~ "Nondense-thin-small",
     TRUE ~ Data
@@
 
-**Table. 1.**
-Relationships between species mean leaf leaf mass per area (LMA) values determined by using whole leaves and leaf discs across all species and within species groups.
-Data are divided into four categories based on the quartiles:
-thin and small-leaved,
-thin and large-leaved,
-thick and small-leaved,
-and thick and large-leaved species.
-SMA slope (95% CI), intercepts (95% CI), and *R^2^* values are reported.
-Statistically significant differences (*P* < 0.05) in slopes and intercepts are highlighted in bold.
+**Fig. 1.**
+Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs.
+Dashed lines indicate 1:1 lines.
+Blue solid lines indicate standardized major axis (SMA) regressions.
+The 95% confidence intervals are resented as the shaded area.
+The correlation is significant (*P* < 0.001).
 
-\newpage
-
-**Fig. 1.**
-Standardized regression coefficients modelig
-(a) the effects of leaf tissue density (LD; $\beta_1$),
-leaf area (LA; $\beta_2$),
-leaf thickness (LT; $\beta_3$)
-on the mean estimates of whole-leaf LMA, and
-(b) the effects of leaf tissue density ($\gamma_1$),
-leaf area ($\gamma_2$), and
-leaf thickness ($\gamma_3$)
-on the estimated variance of whole-leaf LMA.
-The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
-Circles show posterior means of coefficients.
-Thick and thin lines indicate 90% and 95% credible intervals, respectively.
-
-![](../figs/coef_sp3.png)
+![](../figs/sma.png)
 
@@
 **Fig. 2.**
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs for (a) nondense-leave species and (b) dense-leaved species.
-Species groups are divided into eight categories on the basis of the medians of the leaf tissue density, leaf area and leaf thickness across all the species.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis regressions.
-The 95% confidence intervals are presented as the shaded area.
-All the correlations are significant (*P* < 0.001).
+Model predictions of the whole-leaf to leaf disc LMA ratio as a function of leaf punch sizes and (a) leaf tissue density, (b) leaf area, and (c) leaf thickness.
+Dashed line indicates 1:1 ratio of leaf disc and whole-leaf estimates.
+Solid lines indicate the posterior means ($\tilde{\mu}$ in Eq. 1-2), and the shade regions shows $\pm$ the posterior means of standard deviations ($\tilde{\sigma}$ in Eq. 3-4).
 
-![](../figs/lalt_sp_grid_dense.png)
+![](../figs/pred_mcmc.png)
 
@@
 **Fig. 3.**
-Relationships between coefficient of variation (CV) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
+Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
+Blue solid lines indicate ordinary least squares (OLS) regressions.
+The 95% confidence intervals are presented as the shaded area.
+All the correlations are significant (P < 0.001).
+All the samples were obtained with a diameter 1.0-cm leaf punch.
+
+![](../figs/petiole.png)
+
+**Fig. 4.**
+Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
 The correlation is significant (*P* < 0.001).

### 2022-05-06 ms/LMA_method.tex
update ms

@@
 
-To quantify the effect of leaf morphology on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
+To quantify the effect of leaf morphology and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
 The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of leaf tissue density, leaf area and leaf thickness on the log-scale;
@@
 \mathrm{ln}(LMA_{Wi}) & \sim N(\mathrm{ln}(LMA_{Di}) + \tilde{\mu_i}, \sigma_i^2) \label{eq:LMA}\\
-\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LD_{i}) + \beta_2 \mathrm{ln}(LA_{i}) + \beta_3 \mathrm{ln}(LT_{i}) \label{eq:mu}
+\tilde{\mu_i} & = \beta_0 + \beta_1 \mathrm{ln}(LD_{i}) + \beta_2 \mathrm{ln}(LA_{i}) + \beta_3 \mathrm{ln}(LT_{i}) + \beta_4 PS_{i} \nonumber \\
+& + PS_{i} \times \bigl\{ \beta_5 \mathrm{ln}(LD_{i}) + \beta_6 \mathrm{ln}(LA_{i}) + \beta_7 \mathrm{ln}(LT_{i})\bigr\}\label{eq:mu}
 \end{align}
 
-where \(LMA_{Wi}\), \(LD_{i}\), \(LA_{i}\), \(LT_{i}\) are the observed whole-leaf LMA, leaf tissue density, leaf area and leaf thickness for tree \emph{i}, respectively,
-\(LMA_{Di}\) is the true unobserved value of leaf disc LMA for tree \emph{i}, which can be modeled using the observed leaf disc LMA.
-\(\tilde{\mu_i}\) is the effect of leaf tissue density, leaf area and leaf thickness on the mean estimates for the whole-leaf LMA of tree \emph{i}, and \(\sigma_i^2\) is the variance of whole-leaf LMA for tree \emph{i}, and \(\beta\) are coefficients.
-
+where \(LMA_{Wi}\), \(LMA_{Di}\), \(LD_{i}\), \(LA_{i}\), and \(LT_{i}\) are the observed whole-leaf LMA, leaf disc LMA, leaf tissue density, leaf area, and leaf thickness for species \emph{i}, respectively,
+The dummy variable \(PS_i\) is set to 1 for samples obtained with a small leaf punch (0.6-cm diameter) and 0 for samples obtained with a large leaf punch (1.0-cm diameter).
+\(\tilde{\mu_i}\) is the effect of leaf tissue density, leaf area, leaf thickness and leaf punch size on the mean estimates for the whole-leaf LMA of species \emph{i}, \(\sigma_i^2\) is the variance of whole-leaf LMA for species \emph{i}, and \(\beta\) are coefficients.
 The standard deviation of whole-leaf LMA (\(\sigma_i\)) was assumed to follow a normal distribution;
@@
 \mathrm{ln}(\sigma_i) & \sim N(\mathrm{ln}(\tilde{\sigma_i}), \omega^2) \label{eq:ln-sigma} \\
-\tilde{\sigma_i} & = \gamma_0 + \gamma_1 \mathrm{ln}(LD_{i}) + \gamma_2 \mathrm{ln}(LA_{i}) + \gamma_3 \mathrm{ln}(LT_{i}) \label{eq:tilde-sigma}
+\mathrm{ln}(\tilde{\sigma_i}) & = \gamma_0 + \gamma_1 \mathrm{ln}(LD_{i}) + \gamma_2 \mathrm{ln}(LA_{i}) + \gamma_3 \mathrm{ln}(LT_{i}) + \gamma_4 PS_{i} \nonumber \\
+& + PS_{i} \times \bigl\{\gamma_5 \mathrm{ln}(LD_{i}) + \gamma_6 \mathrm{ln}(LA_{i}) + \gamma_7 \mathrm{ln}(LT_{i})\bigr\}\label{eq:tilde-sigma}
 \end{align}
 
-where \(\tilde{\sigma_i}\) is the effect of leaf area and leaf thickness on the variance of whole-leaf LMA,
+where \(\tilde{\sigma_i}\) is a hyperparameter for \(\sigma_i\) ,
 \(\omega^2\) is a scaling hyperparameter, and \(\gamma\) are coefficients.
-To allow comparisons among parameter estimates, \(\mathrm{ln}(LD)\), \(\mathrm{ln}(LA)\) and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
+To allow comparisons among parameter estimates, \(\mathrm{ln}(LD)\), \(\mathrm{ln}(LA)\), and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
+Note that this model does not include measurement errors of leaf disc LMA implemented in the following analysis, because there are too many scaling parameters
 
@@
 
-Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with standardized major axis (SMA) regressions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the samples and different leaf area and thickness groups.
-Species and individual groups were divided into four categories based on the medians of leaf area and leaf thickness across all species and all individuals, respectively:
-thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species (individuals).
+Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were further summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with standardized major axis (SMA) regressions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the samples and different leaf area and thickness groups.
+
+Species groups were divided into four categories based on the medians of leaf area and leaf thickness across all species:
+thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species.
 Median values are as following:
 small-leaved species (LA \textless{} cm\textsuperscript{2}),
-thin-leaved species (LT \textless{} mm),
-small-leaved individuals (LA \textless{} cm\textsuperscript{2}),
-and thin-leaved individuals (LT \textless{} mm).
+and thin-leaved species (LT \textless{} mm).
 
@@
 
-Disc-based estimates of species mean LMA matched well whole-leaf estimates (Table 1; \emph{R\textsuperscript{2}} = for all species).
-Species with thicker and smaller leaves had stronger correlations between disc-based and whole-leaf estimates of LMA (Table 1, Fig. 1).
-There was a negative correlation between species mean leaf area and leaf thickness (\emph{r} = , \emph{P} , \emph{n} = ).
-When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4\% greater than disc-based estimates in the arithmetic scale.
-Large-leaved species also had significant positive intercepts, suggesting that whole-leaf estimates of LMA were 22.1\% greater than disc-based estimates in the arithmetic scale (Table 1).
-Intercepts did not differ for small-leaved species (Table 1).
-
-Disc-based estimates of individual mean LMA also showed positive correlations with whole-leaf estimates but their \emph{R\textsuperscript{2}} values were smaller than those for the species means (Fig.
-2).
-Similar to the species-level pattern, individuals with thicker and smaller leaves had stronger correlations (Fig. 2).
-The relationships of the whole-leaf LMA : disc leaf LMA ratio with total dry mass for the leaf disc (we weighted 2-3 discs together), with leaf thickness, and with leaf area were heteroscedastic (unequal variance, \emph{P} \textless{} 0.001; Appendix S3).
-Samples with small total dry mass, thin leaves, and larger leaves tended to show greater variance (Fig. 2; Appendix S3).
-The total dry mass of leaf disc was positively correlated with both leaf thickness and leaf punch size (Appendix S4).
+There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.69\% {[}95\%CI: 8.07, 11.4{]} greater than disc-based estimates in the arithmetic scale.
+
+Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2).
+When a large leaf punch was used, species with lower leaf tissue density had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a).
+Species with lower leaf tissue density had greater estimate whole-leaf to leaf disc LMA ratio when a small leaf punch was used (Fig. 2a).
+Species with larger leaves had greater estimate of the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2b), which was only significant for leaves obtained by a large punch.
+Species with thinner leaves had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
+Posteriors of coefficients are summarized in (Fig. SX).
+Leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
+3a).
+Large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Fig.
+3b).
+
 Amounts of intraspecific variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.33).
@@
 
-\begin{longtable}[]{@{}lllr@{}}
-\toprule()
-Data & Slope & Intercept & \emph{R\textsuperscript{2}} \\
-\midrule()
-\endhead
-All & 0.97 {[}0.94, 1.01{]} & \textbf{0.09 {[}0.02, 0.16{]}} & 0.87 \\
-Thick-large & 0.93 {[}0.85, 1.03{]} & \textbf{0.19 {[}0.01, 0.37{]}} & 0.86 \\
-Thick-small & 1.02 {[}0.97, 1.07{]} & 0 {[}-0.11, 0.11{]} & 0.93 \\
-Thin-large & 0.91 {[}0.82, 1.02{]} & \textbf{0.2 {[}0.02, 0.37{]}} & 0.71 \\
-Thin-small & 0.93 {[}0.83, 1.03{]} & 0.16 {[}-0.02, 0.35{]} & 0.84 \\
-\bottomrule()
-\end{longtable}
-
-\textbf{Table. 1.}
-Relationships between species mean leaf leaf mass per area (LMA) values determined by using whole leaves and leaf discs across all species and within species groups.
-Data are divided into four categories based on the quartiles:
-thin and small-leaved,
-thin and large-leaved,
-thick and small-leaved,
-and thick and large-leaved species.
-SMA slope (95\% CI), intercepts (95\% CI), and \emph{R\textsuperscript{2}} values are reported.
-Statistically significant differences (\emph{P} \textless{} 0.05) in slopes and intercepts are highlighted in bold.
+\textbf{Fig. 1.}
+Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs.
+Dashed lines indicate 1:1 lines.
+Blue solid lines indicate standardized major axis (SMA) regressions.
+The 95\% confidence intervals are resented as the shaded area.
+The correlation is significant (\emph{P} \textless{} 0.001).
+
+\includegraphics{../figs/sma.png}
 
@@
 
-\textbf{Fig. 1.}
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
-Species groups are divided into four categories on the basis of the medians of the leaf size and leaf thickness across all the species.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis regressions.
+\textbf{Fig. 2.}
+Model predictions of the whole-leaf to leaf disc LMA ratio as a function of leaf punch sizes and (a) leaf tissue density, (b) leaf area, and (c) leaf thickness.
+Dashed line indicates 1:1 ratio of leaf disc and whole-leaf estimates.
+Solid lines indicate the posterior means (\(\tilde{\mu}\) in Eq. 1-2), and the shade regions shows \(\pm\) the posterior means of standard deviations (\(\tilde{\sigma}\) in Eq. 3-4).
+
+\includegraphics{../figs/pred_mcmc.png}
+
+\newpage
+
+\textbf{Fig. 3.}
+Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
+Blue solid lines indicate ordinary least squares (OLS) regressions.
 The 95\% confidence intervals are presented as the shaded area.
-All the correlations are significant (\emph{P} \textless{} 0.001).
-
-\includegraphics{../figs/lalt_pool_grid.png}
-
-\newpage
-
-\textbf{Fig. 2.}
-Relationships between individual leaf mass per area (LMA) determined by using whole leaves and leaf discs.
-Individual groups are divided into four categories based on the basis of the medians of the leaf size and leaf thickness across all the individuals.
-All the correlations are significant (\emph{P} \textless{} 0.001).
-Details as in Fig. 1.
-
-\includegraphics{../figs/lalt_tree_grid.png}
-
-\newpage
-
-\textbf{Fig. 3.}
-Relationships between coefficient of variation (CV) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
+All the correlations are significant (P \textless{} 0.001).
+All the samples were obtained with a diameter 1.0-cm leaf punch.
+
+\includegraphics{../figs/petiole.png}
+
+\textbf{Fig. 4.}
+Relationships between coefficient of variation (Bao's CV estimator) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
 The correlation is significant (\emph{P} \textless{} 0.001).

### 2022-05-06 ms/SI.Rmd
update ms

@@
 
+**Fig. SX.**
+Standardized regression coefficients modelig the effects of leaf tissue density,
+leaf area,
+leaf thickness,
+punch size, and
+their interactios
+(a) on the mean estimates of whole-leaf LMA, and
+(b) on the estimated variance of whole-leaf LMA.
+The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
+Thick and thin lines indicate 90% and 95% credible intervals, respectively.
+Circles show posterior means of coefficients.
+Circles filled with blue indicate significant effects and white indicate non-significance effects.
+
+![](../figs/coef_sp_punch1_add.png)
+
+\newpage
+
 # Appendix S2:

### 2022-05-06 ms/LMA_method.Rmd
update result

@@
 
+*Relationship between whole-leaf and leaf disc LMA*
+
+A bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the species.
+
+SMA analyses were run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
+Confidence intervals of SMA estimates were based on 2000 bootstraps.
+
 *Effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA*
 
-To quantify the effect of leaf morphology and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
+To further quantify the effect of leaf morphology and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
 The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of  leaf tissue density, leaf area and leaf thickness on the log-scale;
@@
 
-*Bivariate trait relationships for mean and CV*
+We also perfomred ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
 
-Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were further summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the samples and different leaf area and thickness groups.
-
-Species groups were divided into four categories based on the medians of leaf area and leaf thickness across all species:
-thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species.
-Median values are as following:
-small-leaved species (LA < `r val$LA_mid` cm^2^),
-and thin-leaved species (LT < `r val$LT_mid` mm).
+*Relationship between disc-based and whole-leaf estiamtes of intraspecific variation*
 
@@
 
-SMA analyses were run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
-Confidence intervals of SMA estimates were based on 2000 bootstraps.
-All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022].
+SMA analyses were run as described above.
+All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2021].
 

### 2022-05-06 ms/LMA_method.Rmd
update method

@@
 
-*Data sources*
+*Study sites and plant materials*
 
-We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
-First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
+We conducted this study in four sites which cover a wide ranges of biomes to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits (see site details in Table S1).
+First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
 Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
+We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
 In total, we used `r val$all_sp` woody species and `r val$all_tree` individuals.

### 2022-05-06 ms/SI.Rmd
update method

@@
 
-# https://github.com/haozhu233/kableExtra/issues/477
+# https://github.com/haozhu233/kableExtra/issues/47
 options(kableExtra.auto_format = FALSE)
@@
 
-val <- yaml::yaml.load_file("values.yml")
+val <- yaml::yaml.load_file("../values.yml")
 ```
@@
 | Yakushima  | Warm-temperate forest        | 14 - 1748     | 30°38'N, 130°62'E  | 19.4    | 4477     | -                  |       -            | `r val$yaku_sp` |
+
+| Data name | Site name  | Vegetation                             | Elevation (m) | Locations          | MAT (℃) | MAP (mm) | Dry period (month) | Canopy height (m) | Leaf disc thickness | Leaf punch diameter (cm) | Number of species | Number of individuals |
+|-----------|------------|----------------------------------------|---------------|--------------------|---------|----------|--------------------|-------------------|---------------------|--------------------------|-------------------|-----------------------|
+| Yunnan    | Bubeng     | Tropical forest (TRF)                  | 780           | 21°37'N, 101°35' E | 21      | 1532     | 6                  | 35-45             | Measured            | 0.6                      | `r val$TRF`       | test                  |
+| Yunnan    | Ailao-shan | Subtropical evergreen wet forest (STF) | 2500          | 24°32'N,101°01'E   | 11.7    | 1931     | -                  | 25                | Measured            | 0.6                      | `r val$STF`       | test                  |
+| Yunnan    | Yuanjiang  | Hot-dry savanna  (HDS)                 | 480           | 23°28'N, 102°10'E  | 24.7    | 732.8    | 6                  | 4-6               | Measured            | 0.6                      | `r val$HDS`       | test                  |
+| Yakushima | Yakushima  | Warm-temperate forest                  | 14 - 1748     | 30°38'N, 130°62'E  | 19.4    | 4477     | -                  | -                 | Not-measured        | 1.0                      | `r val$TRF`       | test                  |
 
@@
 
-```{r, eval=TRUE, echo=FALSE}
+```{r, eval=FALSE, echo=FALSE}
 tar_load(dm_lm_tab)

### 2022-05-06 _targets.R
fix tar_make_clustermq
https://github.com/ropensci/targets/discussions/689

@@ -13,7 +13,7 @@ source("R/yml.R")
 source("R/stan.R")
 source("R/predictdf.R")
 
-options(clustermq.scheduler = "multiprocess")
+options(clustermq.scheduler = "multicore")
 
 tar_option_set(packages = c(
   "tidyverse",

### 2022-05-06 run.R

@@ -1,6 +1,6 @@
-# targets::tar_make_clustermq(
-#   workers = parallel::detectCores(),
-#   reporter = "silent"
-# )
+targets::tar_make_clustermq(
+  workers = parallel::detectCores(),
+  reporter = "silent"
+)
 
-targets::tar_make()
+#targets::tar_make()

### 2022-05-07 ms/SI.Rmd
fix tar_make_clustermq
https://github.com/ropensci/targets/discussions/689
add site

--- 2022-05-06 ms/SI.Rmd
@@
 SPEI: Standardized Precipitation Evapotranspiration Index.
+
+```{r}
+library(jsonlite)
+site <- fromJSON("../data/site_info.json")
+site |>
+  kable(format = "html") |>
+  kable_styling()
+```
 

### 2022-05-07 ms/SI.Rmd
clean
- use format = "file"
- add site_info.json

@@
 
-val <- yaml::yaml.load_file("../values.yml")
+#  for non-targets
+# val <- yaml::yaml.load_file("../values.yml")
+val <- yaml::yaml.load_file("values.yml")
 ```
@@
 
-```{r}
+`r val$TRF_sp`
+
+```{r, echo=TRUE}
 library(jsonlite)
-site <- fromJSON("../data/site_info.json")
+#site <- fromJSON("../data/site_info.json")
+site <- fromJSON("data/site_info.json")
 site |>

### 2022-05-07 report.Rmd
clean
- use format = "file"
- add site_info.json

@@
     lma_leaf = mean(lma_leaf) |> round(1),
-    lma_disc = mean(lma_disc) |> round(1)) |>
+    lma_disc = mean(lma_disc) |> round(1)
+  ) |>
   write_csv("data/ldlalt.csv")
@@
 targets::tar_load(fit_sp_ld_summary_model)
-targets::tar_load(fit_sp_ld2_summary_model)
+targets::tar_load(fit_sp_ld2_summary_model2)
 targets::tar_load(fit_sp_ld3_summary_model)
@@
 targets::tar_load(fit_sp_ld_diagnostics_model)
-targets::tar_load(fit_sp_ld2_diagnostics_model)
+targets::tar_load(fit_sp_ld2_diagnostics_model2)
 targets::tar_load(fit_sp_ld3_diagnostics_model)
@@
 targets::tar_load(fit_sp_lma0_diagnostics_simple)
-
 ```
@@
 fit_sp_ld_summary_model |> filter(rhat > 1.1)
-fit_sp_ld2_summary_model |> filter(rhat > 1.1)
+fit_sp_ld2_summary_model2 |> filter(rhat > 1.1)
 fit_sp_ld3_summary_model |> filter(rhat > 1.1)
@@
 div_check(fit_sp_ld_diagnostics_model)
-div_check(fit_sp_ld2_diagnostics_model)
+div_check(fit_sp_ld2_diagnostics_model2)
 div_check(fit_sp_ld3_diagnostics_model)
@@
 
-```{r, eval=TRUE}
-tar_load(coef_sp_png)
-```
-
-![](figs/coef_sp.png)
-
-```{r, eval=TRUE}
-tar_load(coef_sp_png2)
-```
-
-![](figs/coef_sp2.png)
-
-```{r, eval=TRUE}
-tar_load(coef_sp_png1)
-```
-
-![](figs/coef_sp1.png)
-
-```{r, eval=TRUE}
-tar_load(coef_sp_png3)
-```
-
-![](figs/coef_sp3.png)
-
-```{r, eval=TRUE}
-tar_load(coef_sp_png31)
-```
-
-![](figs/coef_sp31.png)
-
-```{r, eval=TRUE}
-tar_load(coef_sp_png333)
-```
-
-![](figs/coef_sp333.png)
+![](figs/coef_sp_punch1_add.png)
 

### 2022-05-07 R/data_clean.R

@@ -166,6 +166,7 @@ data_clean <- function(d, d2, d3) {
 
    new_dat3 |>
       write_csv("data/full_data.csv")
+   paste("data/full_data.csv")
 }
 
 data_clean_cv <- function(d, d3) {
@@ -241,6 +242,7 @@ data_clean_cv <- function(d, d3) {
 
   new_dat3 |>
     write_csv("data/full_data_cv.csv")
+  paste("data/full_data_cv.csv")
 }
 
 data_clean_tree <- function(d, d3) {
@@ -291,6 +293,7 @@ data_clean_tree <- function(d, d3) {
   )
 
   tree_data |> write_csv("data/tree_data.csv")
+  paste("data/tree_data.csv")
 }
 
 

### 2022-05-07 R/site_info.R

@@ -1,0 +1,21 @@
+update_site_info <- function(site_info_raw, yml) {
+  site <- fromJSON(site_info_raw)
+  val <- yaml::yaml.load_file(yml)
+  site2 <- site |>
+    mutate(`Number of species` = c(
+      val$TRF_sp,
+      val$STF_sp,
+      val$HDS_sp,
+      val$Yaku_sp
+    )) |>
+    mutate(`Number of individuals` = c(
+      val$TRF_ind,
+      val$STF_ind,
+      val$HDS_ind,
+      val$Yaku_ind
+    ))
+
+  write_json(site2, "data/site_info.json", pretty = TRUE)
+  # The return value must be a vector of paths to the files we write:
+  paste("data/site_info.json")
+}

### 2022-05-07 R/yml.R

@@ -1,4 +1,4 @@
-write_yml <- function(path, sp_mean, full_data_cv_csv, tree, lma_yaku_re, sma_sp_ld_tab) {
+write_yml <- function(path, sp_mean, full_data_cv_csv, tree, lma_yaku_re, boot_fit_dat) {
   r2_lma <- cor.test(log(sp_mean$lma_leaf), log(sp_mean$lma_disc))$estimate^2 |> round(2)
   r2_ld <- cor.test(log(sp_mean$ld_leaf), log(sp_mean$ld_disc))$estimate^2 |> round(2)
 
@@ -81,13 +81,62 @@ write_yml <- function(path, sp_mean, full_data_cv_csv, tree, lma_yaku_re, sma_sp
     round(mean_, 1)
   }
 
-  boot_fit_dat <- boot_fit(sp_mean)
+  #boot_fit_dat <- boot_fit(sp_mean)
   lma_mean_per <- ((boot_fit_dat$conf_mean / boot_fit_dat$xseq) - 1) * 100
   lma_lwr_per <- ((boot_fit_dat$conf_low / boot_fit_dat$xseq) - 1) * 100
   lma_upr_per <- ((boot_fit_dat$conf_high / boot_fit_dat$xseq) - 1) * 100
 
+  # library(tidyverse)
+  # library(targets)
+  # tar_load(sp_mean)
+  # tar_load(tree)
+  n_sp <- table(sp_mean$location)
+  n_ind <- table(tree$location)
+
   output <- path
   out <- file(paste(output), "w") # write
+  writeLines(
+    paste0("TRF_sp: ",
+           n_sp["Mengla_Bubeng"]),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("STF_sp: ",
+           n_sp["Ailao_understory"]),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("HDS_sp: ",
+           n_sp["Yuanjiang_Savanna"]),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("Yaku_sp: ",
+           n_sp["Yakushima"]),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("TRF_ind: ",
+           n_ind["Mengla_Bubeng"]),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("STF_ind: ",
+           n_ind["Ailao_understory"]),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("HDS_ind: ",
[…]

### 2022-05-07 _targets.R

@@ -11,6 +11,7 @@ source("R/ind_analysis.R")
 source("R/fig_write.R")
 source("R/yml.R")
 source("R/stan.R")
+source("R/site_info.R")
 source("R/predictdf.R")
 
 options(clustermq.scheduler = "multicore")
@@ -26,7 +27,8 @@ tar_option_set(packages = c(
   "extrafont",
   "loo",
   "modelr",
-  "performance"
+  "performance",
+  "jsonlite"
 ))
 
 # check if it's inside a container
@@ -55,6 +57,11 @@ list(
     format = "file"
   ),
   tar_target(
+    site_info_raw,
+    "data-raw/site_info_raw.json",
+    format = "file"
+  ),
+  tar_target(
     lma_raw_re,
     clean_lma_raw(lma_raw)
   ),
@@ -68,36 +75,63 @@ list(
   ),
   tar_target(
     full_data_csv,
-    data_clean(lma_raw_re, lma_la_re, lma_yaku_re)
+    data_clean(lma_raw_re, lma_la_re, lma_yaku_re),
+    format = "file"
+  ),
+  tar_target(
+    full_data,
+    read_csv(full_data_csv)
   ),
   tar_target(
     full_data_cv_csv,
-    data_clean_cv(lma_raw_re, lma_yaku_re)
+    data_clean_cv(lma_raw_re, lma_yaku_re),
+    format = "file"
+  ),
+  tar_target(
+    full_data_cv,
+    read_csv(full_data_cv_csv)
   ),
   tar_target(
     tree_data_csv,
-    data_clean_tree(lma_raw_re, lma_yaku_re)
+    data_clean_tree(lma_raw_re, lma_yaku_re),
+    format = "file"
+  ),
+  tar_target(
+    tree_data,
+    read_csv(tree_data_csv)
   ),
   tar_target(
     sp_mean,
-    sp_dat_mean(full_data_csv)
+    sp_dat_mean(full_data)
   ),
   tar_target(
     sp_cv,
-    sp_dat_cv(full_data_cv_csv)
+    sp_dat_cv(full_data_cv)
   ),
   tar_target(
     tree,
-    tree_dat_clean(tree_data_csv)
+    tree_dat_clean(tree_data)
   ),
   tar_target(
     yaku_sp,
     create_yaku_sp(lma_yaku_re)
   ),
+
+  tar_target(
+    boot_fit_dat,
[…]

### 2022-05-07 _targets_packages.R

@@ -5,6 +5,7 @@ library(fst)
 library(ggpubr)
 library(ggsma)
 library(janitor)
+library(jsonlite)
 library(loo)
 library(markdown)
 library(modelr)

### 2022-05-07 run.R

@@ -3,4 +3,6 @@ targets::tar_make_clustermq(
   reporter = "silent"
 )
 
-#targets::tar_make()
+# targets::tar_make(
+#   reporter = "silent"
+# )

### 2022-05-07 ms/SI.Rmd
update

--- 2022-05-07 ms/SI.Rmd
@@
 
-val <- yaml::yaml.load_file("../values.yml")
+# for dependency
+targets::tar_load(yml)
+#  for non-targets
+# val <- yaml::yaml.load_file("../values.yml")
+val <- yaml::yaml.load_file("values.yml")
 ```
@@
 
-```{r}
+```{r, echo=TRUE}
 library(jsonlite)
-site <- fromJSON("../data/site_info.json")
+# for dependency
+targets::tar_load(site_info)
+#site <- fromJSON("../data/site_info.json")
+site <- fromJSON("data/site_info.json")
 site |>
@@
 
+```{r, incude=FALSE}
+targets::tar_load(coef_sp_punch1_add_plot)
+```
+
 ![](../figs/coef_sp_punch1_add.png)
@@
 Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.
+
+```{r, include=FALSE}
+targets::tar_load(lma_ld_png)
+```
 

### 2022-05-07 ms/SI.Rmd
update

@@
 
-```{r, echo=TRUE}
+```{r, echo=FALSE}
 library(jsonlite)
@@
 ```
-
-| Site name  | Vegetation                             | Elevation (m) | Locations          | MAT (℃) | MAP (mm) | Dry period (month) | Canopy height (m) | Species number  |
-|------------|----------------------------------------|---------------|--------------------|---------|----------|--------------------|-------------------|-----------------|
-| Bubeng     | Tropical forest (TRF)                  | 780           | 21°37'N, 101°35' E | 21      | 1532     | 6                  | 35-45             | `r val$TRF`     |
-| Ailao-shan | Subtropical evergreen wet forest (STF) | 2500          | 24°32'N,101°01'E   | 11.7    | 1931     | -                  | 25                | `r val$STF`     |
-| Yuanjiang  | Hot-dry savanna  (HDS)                 | 480           | 23°28'N, 102°10'E  | 24.7    | 732.8    | 6                  | 4-6               | `r val$HDS`     |
-| Yakushima  | Warm-temperate forest        | 14 - 1748     | 30°38'N, 130°62'E  | 19.4    | 4477     | -                  |       -            | `r val$yaku_sp` |
 

### 2022-05-09 ms/response_letter.Rmd
update ms
update method
update

@@
 
+Thank you.
+(different levels of organization?)
+We have added columns to explain the number of species, the number of individuals, whether leaf thickness was measured, and leaf punch size in Table S1.
+
 > L148-151 why were the species divided at all?
@@
 
-- making stan
+Thank you.
+We now only report the linear model that used leaf area and leaf thickness as covariates as noted above.
 
@@
 I'm therefore confused as to how the authors are interpreting the effect of "leaf punch size" in their models: could this not simply be a reflection of the different species represented in the different datasets?
+
+- caveate
 
@@
 
+Thank you.
+We have added MAT and MAP in the main text to support that our dataset covers the wide climate ranges in the distribution of broad-leaved tree species.
+
 > Lines 124 and 125: Why did you maintain leaf petiole in calculating LMA?
@@
 
+The main function of leaves is to deliver a profitable return on the investment that has been made in constructing the leaf (Westoby, Reich and Wright 2013), and thus it is also natural to include leaf petiole in LMA.
+According to the trait hand book (Perez-Harguindeguy 2013), either including or excluding petiole will fine.
+As long as we checked the TRY data that we have now, the numbers of LMA records for those two measurements are very similar:
+the number of records of LMA (or 1/SLA) including petiole is 57,033, and
+the number of records of LMA (or 1/SLA) excluding petiole is 59,103.
+(add conclusion).
+
+Thank you.
+We now more clearly explain that thick veins are secondary order veins.
+We have also added detailed LMA measurement protocol in Fig. SX.
+
 > Lines 129-131: Can you class the leaf shapes of 334 woody species you have used? It will affect your sampling positions you are describing here.
 
-> Lines 151-153: I think, a frequency of LA is needed as a supplementary figure to show the feasibility of such divisions.
+We have added detailed LMA measurement protocol in Fig. SX as note above.
+
+> Lines 151-153: I think, a frequency of LA is needed as a supplementary figure to show the feasibility of such division.
 

### 2022-05-09 ms/LMA_method.Rmd
update ms

@@
 
-*Study sites and plant materials*
+*Data sources*
 
-We conducted this study in four sites which cover a wide ranges of biomes to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits (see site details in Table S1).
+We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
 First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
 Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
-We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
-In total, we used `r val$all_sp` woody species and `r val$all_tree` individuals.
+In total, our data set comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from xxx to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Table S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
 The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.
@@
 *Measurements of leaf disc and whole-leaf LMA*
+
+We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
 

### 2022-05-09 ms/SI.Rmd
update ms

@@
 site <- fromJSON("data/site_info.json")
-site |>
+site >
   kable(format = "html") |>

### 2022-05-10 ms/response_letter.Rmd
update ms

@@
 
-test
+We thank the reviewer for the encouraging comments and helpful critiques.
 
@@
 
+- record and requests
+
 > 2.
@@
 This is an important thing to clarify.
-Leaf thickness and leaf area effect not only the mean LMA but also the variance of LMA, and that is why R2 values changed among the four groups (thin vs. think and small vs. large leaves).
+We now use a linear model that used leaf area and leaf thickness as covariates but we suggest OLS models without covariates for the conversion of LMA because leaf thickness and leaf area affect not only the mean but also the variance in the relationship between the leaf disc and whole-leaf estimates, and that is why R2 values changed among the four groups (thin vs.
+think and small vs.
+large leaves) and it is not to practical to convert LMA using leaf area or leaf thickness.
+We also present a practical guideline for conversion of LMA.
 
@@
 
+Thank you.
+We have updated the line 26 but key the line 51 as "the key trait" because xxx
+
 > Line 57: I think that the following reference helps to support this statement, because LMA values were found to vary across leaf age, and LMA also exhibits a plasticity to climate when leaves enter the maturation stage (Jiao et al., 2022).

### 2022-05-10 ms/LMA_method.Rmd
update ms

@@
 **PREMISE:**
-Leaf mass per area (LMA), which is the key trait in leaf economic spectrum and plant growth analysis, is measured from leaf discs or whole leaves.
+Leaf mass per area (LMA), which is an important functional trait in leaf economic spectrum and plant growth analysis, is measured from leaf discs or whole leaves.
 These differences in the measurement methods may lead to large differences in the estimates of LMA values.
@@
 
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area thus reflecting a cost for light interception, which is the key trait of the leaf economic spectrum (LES) [@Wright2004a; @Poorter2009; @Onoda2017].
+The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf [@Westoby2013], which is inherently economic in nature [i.e., leaf economic spectrum, @Wright2004a].
+Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is the key trait of the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
 Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover [@Wright2004a].
@@
 Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago [@Hanson1917].
+Actually, LMA was the most often requested leaf trait in the TRY plant data database (2,977 out of 7,330 requests), followed by leaf nitrogen contents per leaf dry mass [1,938 requests, @Kattge2020 [status October 1 2019]].
 
 LMA values can be determined by either
-1) a whole leaf including or excluding petioles, and
-2) a leaf disc excluding all major veins or petioles [@Perez-Harguindeguy2013; @Kattge2020].
-Although some studies do not make clear what protocol was followed, these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
+1) a whole leaf including (88,490 observations and 7,068 species) or excluding petioles (64,838 observations and 7,558 species), and
+2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) [@Perez-Harguindeguy2013; @Kattge2020 [TRY version 5]].
+Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
+
 Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.

### 2022-05-10 ms/response_letter.Rmd
remove ITV

@@
 
-- Added Bao
+- remove?
 
@@
 
+Thank you.
+We now introduce the LES in the first sentence so that the readers can understand the role of LMA in LES more clearly.
+
 > L69-73 This sentence is crucial for your hypotheses but is buried in the middle of this paragraph.
@@
 The second paragraph can get into which leaf types are likely to give similar or different estimates based on the two metrics and why.
+
+Thank you.
+We now break up the paragraph into two sections: the first describing the different methods and their record numbers in TRY, and previous works that compared them, and the second describing the expected effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA.
 
@@
 
+We have removed XXX.
+
 > Line 157: Are you that the unit of CV is not a percentage? In general, an unitless variable, we usually use its percentage.

### 2022-05-10 ms/LMA_method.Rmd
remove ITV

@@
 
-The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf [@Westoby2013], which is inherently economic in nature [i.e., leaf economic spectrum, @Wright2004a].
+The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf [i.e., leaf economic spectrum, @Wright2004a; @Westoby2013].
 Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is the key trait of the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
@@
 LMA values can be determined by either
-1) a whole leaf including (88,490 observations and 7,068 species) or excluding petioles (64,838 observations and 7,558 species), and
+1) a whole leaf including (88,490 observations and 7,068 species) or excluding petioles (64,838 observations and 7,558 species; note that this could include leaf disc samples), and
 2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) [@Perez-Harguindeguy2013; @Kattge2020 [TRY version 5]].
 Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
+Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two [*R^2^* = 0.92 for whole-leaves  in @Kraft2008, *R^2^* = 0.92 for leaf laminas in @Onoda2011], but the comparisons between the two estimates in other biomes have rarely been examined.
 
 Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
-If leaf disc LMA largely and consistently underestimates whole-leaf LMA, some calibrations may be required to combine or compare those different estimates [@Kraft2008; @Onoda2011].
-If divergencies between the estimates based on the different methods are large and inconsistent (i.e., low *R^2^* values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
+(**add leaf density**)
+If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates [@Kraft2008; @Onoda2011].
+If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low *R^2^* values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
 To date, however, only a database from a single region, Panama Plant Traits Database [@Wright2010], is available in the TRY [@Kattge2020] that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.
 
-Given that leaf disc samples have more sources of intraspecific trait variation (ITV) than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified as a coefficient of variance (CV).
-Sources of ITV for whole-leaf samples is variation among individuals within the same species and variation among leaves within the same individuals [@Messier2010; @Messier2017].
-An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
-Thus, extents of ITV for each species based on whole-leaf and leaf discs samples may not match.
-Despite the importance of ITV in community ecology [@Kichenin2013; @Siefert2015], the effect of different measurement methods on the extent of ITV has been largely ignored.
-
-In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf thicknesses, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
+In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf tissue density, leaf area and leaf thickness, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
 We collected a total of `r val$all_sp` woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
@@
 We also perfomred ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
-
-*Relationship between disc-based and whole-leaf estiamtes of intraspecific variation*
-
-The amount of intraspecific variation (ITV) was calculated using Bao's CV estimator [@Yang2020];
-
-\begin{align}
-CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} (\#eq:CV)
-\end{align}
-
-where $CV_1 = s/\bar{x}$, $s$ is the sample standard deviation and $\bar{x}$ is the sample mean, *N* is the sample size, and $\gamma_1$ and $\gamma_2$ are the skewness and kurtosis of the trait distribution.
-Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small [@Yang2020].
-
-SMA analyses were run as described above.
 All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2021].
@@
 3b).
-Amounts of intraspecific variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig. 3; *R^2^* = `r val$cv_r2`).
 

### 2022-05-10 ms/LMA_method.tex
remove ITV

@@
 \textbf{PREMISE:}
-Leaf mass per area (LMA), which is the key trait in leaf economic spectrum and plant growth analysis, is measured from leaf discs or whole leaves.
+Leaf mass per area (LMA), which is an important functional trait in leaf economic spectrum and plant growth analysis, is measured from leaf discs or whole leaves.
 These differences in the measurement methods may lead to large differences in the estimates of LMA values.
@@
 
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area thus reflecting a cost for light interception, which is the key trait of the leaf economic spectrum (LES) (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
+The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf (i.e., leaf economic spectrum, \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Westoby2013}{Westoby et al., 2013}).
+Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is the key trait of the leaf economic spectrum (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
 Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}).
@@
 Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago (\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
+Actually, LMA was the most often requested leaf trait in the TRY plant data database (2,977 out of 7,330 requests), followed by leaf nitrogen contents per leaf dry mass (1,938 requests, \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}status October 1 2019{]}).
 
 LMA values can be determined by either
-1) a whole leaf including or excluding petioles, and
-2) a leaf disc excluding all major veins or petioles (\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}).
-Although some studies do not make clear what protocol was followed, these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}).
+1) a whole leaf including (88,490 observations and 7,068 species) or excluding petioles (64,838 observations and 7,558 species; note that this could include leaf disc samples), and
+2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) (\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5{]}).
+Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}).
+Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two Onoda et al.
+(\protect\hyperlink{ref-Onoda2011}{2011}), but the comparisons between the two estimates in other biomes have rarely been examined.
+
 Since larger leaves tend to invest more of their mass into dense midribs and petiole for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
-If leaf disc LMA largely and consistently underestimates whole-leaf LMA, some calibrations may be required to combine or compare those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
-If divergencies between the estimates based on the different methods are large and inconsistent (i.e., low \emph{R\textsuperscript{2}} values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
+(\textbf{add leaf density})
+If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
+If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low \emph{R\textsuperscript{2}} values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
 To date, however, only a database from a single region, Panama Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.
 
-Given that leaf disc samples have more sources of intraspecific trait variation (ITV) than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified as a coefficient of variance (CV).
-Sources of ITV for whole-leaf samples is variation among individuals within the same species and variation among leaves within the same individuals (\protect\hyperlink{ref-Messier2010}{Messier et al., 2010}, \protect\hyperlink{ref-Messier2017}{2017}).
-An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
-Thus, extents of ITV for each species based on whole-leaf and leaf discs samples may not match.
-Despite the importance of ITV in community ecology (\protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013}; \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), the effect of different measurement methods on the extent of ITV has been largely ignored.
-
-In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf sizes and leaf thicknesses, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
+In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf tissue density, leaf area and leaf thickness, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
 We collected a total of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
@@
 We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
-First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
+First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
 Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
-In total, we used 334 woody species and individuals.
+In total, our data set comprised 334 woody species and 1365 individual that ranged from xxx to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Table S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
+(\protect\hyperlink{ref-Song2017}{2017}); Fei et al.
+(\protect\hyperlink{ref-Fei2018}{2018}){]}, which covers the wide climate ranges in the distribution of broad-leaved tree species.
 The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.
@@
 \emph{Measurements of leaf disc and whole-leaf LMA}
+
+We excluded species that had tiny leaves or leaflets (length \textless1 cm) because it was not practical to measure leaf disc LMA.
 
@@
 Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a precision at 0.0001 g.
-In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (86 out of 193 species) to quantify leaf support costs.
+In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (80 out of 193 species) to quantify leaf support costs.
 Dry mass for leaf discs were recorded 2-3 discs together for each leaf.
@@
 
+\emph{Relationship between whole-leaf and leaf disc LMA}
+
+A bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with standardized major axis (SMA) regressions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the species.
+
+SMA analyses were run using the R package \emph{smatr} (\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
+Confidence intervals of SMA estimates were based on 2000 bootstraps.
+
 \emph{Effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA}
 
-To quantify the effect of leaf morphology and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
+To further quantify the effect of leaf morphology and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we built a hierarchical Bayesian model.
 The whole-leaf LMA was assumed to follow a normal distribution (N) with the mean of leaf disc LMA and covariates of leaf tissue density, leaf area and leaf thickness on the log-scale;
@@
 
-\emph{Bivariate trait relationships for mean and CV}
-
-Bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were further summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with standardized major axis (SMA) regressions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the samples and different leaf area and thickness groups.
-
-Species groups were divided into four categories based on the medians of leaf area and leaf thickness across all species:
-thin and small-leaved, thin and large-leaved, thick and small-leaved, thick and large-leaved species.
-Median values are as following:
-small-leaved species (LA \textless{} cm\textsuperscript{2}),
-and thin-leaved species (LT \textless{} mm).
-
-The amount of intraspecific variation (ITV) was calculated using Bao's CV estimator (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020});
-
-\begin{align}
-CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} \label{eq:CV}
-\end{align}
-
-where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and \(\bar{x}\) is the sample mean, \emph{N} is the sample size, and \(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait distribution.
-Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
-
-SMA analyses were run using the R package \emph{smatr} (\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
-Confidence intervals of SMA estimates were based on 2000 bootstraps.
-All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}).
+We also perfomred ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
+All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2021}{\textbf{RCoreTeam2021?}}).
 
@@
 
-There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.69\% {[}95\%CI: 8.07, 11.4{]} greater than disc-based estimates in the arithmetic scale.
-
+There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.68\% {[}95\%CI: 8.05, 11.4{]} greater than disc-based estimates in the arithmetic scale.
 Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2).
@@
 3b).
-
-Amounts of intraspecific variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig. 3; \emph{R\textsuperscript{2}} = 0.33).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Eguchi2006}{}}%
+Eguchi, T. 2006. Climate. Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in Japanese)}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Evans1972}{}}%
@@
 \emph{Proceedings of the National Academy of Sciences} 115: E6789--E6798.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
+Fei, X., Q.
+Song, Y.
+Zhang, Y.
+Liu, L.
+Sha, G.
+Yu, L.
+Zhang, et al.
+2018.
+\href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon exchanges and their responses to temperature and precipitation in forest ecosystems in {Yunnan}, {Southwest China}}.
+\emph{Science of The Total Environment} 616--617: 824--840.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kichenin2013}{}}%
-Kichenin, E., D.
-A.
-Wardle, D.
-A.
-Peltzer, C.
-W.
-Morse, and G.
-T.
-Freschet.
-2013.
-\href{https://doi.org/10.1111/1365-2435.12116}{Contrasting effects of plant inter- and intraspecific variation on community-level trait measures along an environmental gradient}.
-\emph{Functional Ecology} 27: 1254--1261.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Kitajima2010}{}}%
@@
 \emph{PLOS ONE} 8: 1--10.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Messier2017}{}}%
-Messier, J., B.
-J.
-McGill, B.
-J.
-Enquist, and M.
-J.
-Lechowicz.
-2017.
-\href{https://doi.org/10.1111/ecog.02006}{Trait variation and integration across scales: Is the leaf economic spectrum present at local scales?} \emph{Ecography} 40: 685--697.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Messier2010}{}}%
-Messier, J., B.
-J.
-McGill, and M.
-J.
-Lechowicz.
-2010.
-\href{https://doi.org/10.1111/j.1461-0248.2010.01476.x}{How do traits vary across ecological scales?
-{A} case for trait-based ecology}.
-\emph{Ecology Letters} 13: 838--848.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
-R Core Team. 2022. R: {A} language and environment for statistical computing. {R Foundation for Statistical Computing}, {Vienna, Austria}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Reich2014}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
+Song, Q.-H., Y.-P.
+Zhang, L.-Q.
+Sha, X.-B.
+Deng, Y.
+Deng, C.-S.
+Wu, Z.-Y.
+Lu, et al.
+2017.
+\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature variability in a tropical rainforest, subtropical evergreen forest, and savanna forest in {Southwest China}}.
+\emph{iForest - Biogeosciences and Forestry} 10: 611.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Terashima2001}{}}%
@@
 \emph{Biological Reviews of the Cambridge Philosophical Society} 81: 259--291.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Westoby2013}{}}%
+Westoby, M., P.
+B.
+Reich, and I.
+J.
+Wright.
+2013.
+\href{https://doi.org/10.1111/nph.12345}{Understanding ecological variation across species: {Area-based} vs mass-based expression of leaf traits}.
+\emph{New Phytologist} 199: 322--323.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Yang2020}{}}%
-Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020. Large {Underestimation} of {Intraspecific Trait Variation} and {Its Improvements}. \emph{Frontiers in Plant Science} 11.
-
 \end{CSLReferences}
@@
 \textbf{Fig. 4.}
-Relationships between coefficient of variation (Bao's CV estimator) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
+Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
 The correlation is significant (\emph{P} \textless{} 0.001).

### 2022-05-11 R/data_clean.R
add cv analysis

@@ -196,7 +196,7 @@ data_clean_cv <- function(d, d3) {
   yaku_sp_n <- d3 |>
     group_by(species, location) |>
     summarize(n = n()) |>
-    filter(n >= 3)
+    filter(n >= 5)
 
   yaku_sp <- d3 |>
     group_by(species) |>

### 2022-05-11 R/sp_analysis.R

@@ -502,26 +502,35 @@ lma_ld_wrap_point <- function(sp_mean) {
 
 
 #' @title CV
-cv_pool_point <- function(sp_cv) {
-  sp_cv |>
+cv_pool_point <- function(sp_cv, remove_outliers = FALSE) {
+  if (remove_outliers) {
+  sp_cv <- sp_cv |>
+    filter(lma_leaf_cv < 0.09)
+  }
+  p <- sp_cv |>
     ggplot(aes(x = lma_disc_cv, y = lma_leaf_cv)) +
     geom_abline(intercept = 0, slope = 1, lty = 2) +
     geom_point(alpha = 0.6) +
-    scale_x_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
-    scale_y_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1)) +
+    scale_x_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1, 0.15)) +
+    scale_y_continuous(trans = "sqrt", breaks = c(0.001, 0.01, 0.05, 0.1, 0.15)) +
     geom_sma(se = TRUE, nboot = 2000) +
     ylab("CV of whole-leaf LMA") +
     xlab("CV of leaf disc LMA") +
-    coord_fixed() +
+    coord_fixed(xlim = c(0.005, 0.15), ylim = c(0.005, 0.15)) +
     stat_cor(
-      label.x.npc = 0.3,
-      label.y.npc = 0,
+      label.x.npc = 0,
+      label.y.npc = 0.99,
       vjust = 1.5,
       aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
     ) +
     theme_bw() +
     theme(
       text = element_text(family = "Arial"))
+  if (remove_outliers) {
+    p <- p +
+      coord_fixed(xlim = c(0.005, 0.1), ylim = c(0.005, 0.1))
+  }
+  p
 }
 
 cv_sep_point <- function(sp_cv) {

### 2022-05-11 R/yml.R

@@ -1,4 +1,4 @@
-write_yml <- function(path, sp_mean, full_data_cv_csv, tree, lma_yaku_re, boot_fit_dat) {
+write_yml <- function(path, sp_mean, full_data_cv_csv, tree, lma_yaku_re, sp_cv, boot_fit_dat) {
   r2_lma <- cor.test(log(sp_mean$lma_leaf), log(sp_mean$lma_disc))$estimate^2 |> round(2)
   r2_ld <- cor.test(log(sp_mean$ld_leaf), log(sp_mean$ld_disc))$estimate^2 |> round(2)
 
@@ -94,6 +94,12 @@ write_yml <- function(path, sp_mean, full_data_cv_csv, tree, lma_yaku_re, boot_f
   n_sp <- table(sp_mean$location)
   n_ind <- table(tree$location)
 
+  sp_cv2 <- sp_cv |>
+    dplyr::filter(lma_leaf_cv < 0.09)
+  t_test <- t.test(log10(sp_cv$lma_leaf_cv), log10(sp_cv$lma_disc_cv))
+  sma_cv <- sma(log(lma_leaf_cv) ~ log(lma_disc_cv), sp_cv)
+  sma_cv2 <- sma(log(lma_leaf_cv) ~ log(lma_disc_cv), sp_cv2)
+
   output <- path
   out <- file(paste(output), "w") # write
   writeLines(
@@ -137,6 +143,43 @@ write_yml <- function(path, sp_mean, full_data_cv_csv, tree, lma_yaku_re, boot_f
     out,
     sep = "\n")
 
+  writeLines(
+    paste0("sma_slope_cv_mean: ",
+           sma_cv$groupsummary$Slope |> round(3)
+           ),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("sma_slope_cv_lwr: ",
+           sma_cv$groupsummary$Slope_lowCI |> round(3)
+           ),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("sma_slope_cv_upr: ",
+           sma_cv$groupsummary$Slope_highCI |> round(3)
+           ),
+    out,
+    sep = "\n")
+
+  writeLines(
+    paste0("sma_int_cv_mean: ",
+           sma_cv$groupsummary$Int |> round(3)|> format(nsmall = 3)
+           ),
+    out,
+    sep = "\n")
+  writeLines(
+    paste0("sma_int_cv_lwr: ",
[…]

### 2022-05-11 _targets.R

@@ -125,7 +125,7 @@ list(
   tar_target(
     yml,
     write_yml("values.yml",
-      sp_mean, full_data_cv, tree, lma_yaku_re, boot_fit_dat),
+      sp_mean, full_data_cv, tree, lma_yaku_re, sp_cv, boot_fit_dat),
     format = "file"
   ),
   tar_target(
@@ -746,28 +746,49 @@ list(
     },
     format = "file"
   ),
-
   tar_target(
-    cv_sep_plot, {
-      p <- cv_sep_point(sp_cv)
+    cv_pool_plot_rm, {
+      p <- cv_pool_point(sp_cv, remove_outliers = TRUE)
       ggsave(
-        "figs/cv_sep.png",
+        "figs/cv_pool_rm.png",
         p,
         dpi = 300,
-        width = 6,
+        width = 3,
         height = 3
       )
       ggsave(
-        "figs/cv_sep.pdf",
+        "figs/cv_pool_rm.pdf",
         p,
         device = cairo_pdf,
-        width = 6,
+        width = 3,
         height = 3
       )
-      paste0("figs/cv_sep", c(".png", ".pdf"))
+      paste0("figs/cv_pool_rm", c(".png", ".pdf"))
     },
     format = "file"
   ),
+
+  # tar_target(
+  #   cv_sep_plot, {
+  #     p <- cv_sep_point(sp_cv)
+  #     ggsave(
+  #       "figs/cv_sep.png",
+  #       p,
+  #       dpi = 300,
+  #       width = 6,
+  #       height = 3
+  #     )
+  #     ggsave(
+  #       "figs/cv_sep.pdf",
+  #       p,
+  #       device = cairo_pdf,
+  #       width = 6,
+  #       height = 3
+  #     )
+  #     paste0("figs/cv_sep", c(".png", ".pdf"))
+  #   },
+  #   format = "file"
+  # ),
 
   tar_target(
     petiole_plot, {

### 2022-05-11 ms/LMA_method.Rmd
update itv text

@@
 Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago [@Hanson1917].
-Actually, LMA was the most often requested leaf trait in the TRY plant data database (2,977 out of 7,330 requests), followed by leaf nitrogen contents per leaf dry mass [1,938 requests, @Kattge2020 [status October 1 2019]].
+Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass [12,238 species, 1,938 requests, @Kattge2020 [TRY version 5, status October 1 2019]]
 
-LMA values can be determined by either
+LMA values can be determined by either measuring whole-leaf (including or excluding petioles) or leaf disc samples [@Perez-Harguindeguy2013].
+According to the TRY database version 5, recorded numbers of observations and species are as follows:
 1) a whole leaf including (88,490 observations and 7,068 species) or excluding petioles (64,838 observations and 7,558 species; note that this could include leaf disc samples), and
-2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) [@Perez-Harguindeguy2013; @Kattge2020 [TRY version 5]].
+2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) [@Kattge2020 [TRY version 5]].
 Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
-Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two [*R^2^* = 0.92 for whole-leaves  in @Kraft2008, *R^2^* = 0.92 for leaf laminas in @Onoda2011], but the comparisons between the two estimates in other biomes have rarely been examined.
+Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two [*R^2^* = 0.92 for whole-leaves in @Kraft2008; *R^2^* = 0.92 for leaf laminas in @Onoda2011], but the comparisons between the two estimates in other biomes have rarely been examined.
 
@@
 
-In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf tissue density, leaf area and leaf thickness, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
+Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions (REF).
+The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation [e.g., @Messier2010; @Kichenin2013; @Fajarado2018].
+The coefficient of variation (CV) is often used for quantifying the extent of ITV for each species [@Yang2020; @Westerband2021].
+Sources of ITV for whole-leaf samples are variation among individuals within the same species and variation among leaves within the same individuals [@Messier2010; @Messier2017].
+An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
+Given that leaf disc samples have more sources of ITV than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified based on CV.
+Despite the importance of ITV in community ecology [@Siefert2015; @Westerband2021], the effect of different measurement methods on the extent of ITV has been largely ignored.
+
+In this study, we aimed to investigate the relationship between whole-leaf (including petiole) LMA and leaf disc LMA,
+whether the relationship varied with leaf tissue density, leaf area and leaf thickness, and
+whether the extent of ITV for each species match between whole-leaf and leaf disc based estimates.
 We collected a total of `r val$all_sp` woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
-We predicted that the overall relationship between whole-leaf LMA and disc LMA would be weaker than previous reported LMA data (*R^2^* = 0.92 for whole-leaves in @Kraft2008, *R^2^* = 0.92 for leaf laminas in @Onoda2011) because we collected data with various leaf sizes from a wide range of climates.
-We also predicted that species with larger and/or thinner leaves would show weaker correlations.
-Finally, we predicted that amounts of intraspecifc variations for each species do not match well between whole-leaf and leaf disc based estimates.
+We predicted that whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas [@Niinemets2007].
+
+We also predicted that species with larger and/or thinner leaves would show weaker correlations and larger differences in LMA estimates.
+(**add leaf density**)
+
+Finally, we predicted that the extent of ITV do not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
 
@@
 Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
-In total, our data set comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from xxx to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Table S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
+In total, our data set comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Table S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
 The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.
@@
 *Measurements of leaf disc and whole-leaf LMA*
-
-We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
 
@@
 At least six sun-exposed healthy leaves were sampled from each of 3 to 6 individuals for each species.
-Trait values were averaged at the species- and individual-level for the analyses.
+Trait values were averaged at the species-level for the analyses.
 For compound-leaved species, we referred a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
+We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
 
@@
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset.
+Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Fig. S1 for more details).
 Fresh leaf area (LA; cm^-2^) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package *LeafArea* [@Katabuchi2015].
@@
 We also perfomred ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
+
+*Relationship between disc-based and whole-leaf estiamtes of intraspecific variation*
+
+The extent of intraspecific variation (ITV) was calculated using Bao's CV estimator [@Yang2020];
+
+\begin{align}
+CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} (\#eq:CV)
+\end{align}
+
+where $CV_1 = s/\bar{x}$, $s$ is the sample standard deviation and $\bar{x}$ is the sample mean, *N* is the sample size, and $\gamma_1$ and $\gamma_2$ are the skewness and kurtosis of the trait distribution.
+Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small [@Yang2020].
+We calulcated CV for species that have at least 5 indivdiuals as recommended in @Westerband2021.
+Ideally, 20 individuals for each species are required for robust estimation of CV [i.e., <5% differences from the true ITV; @Yang2020].
+
+SMA analyses were run as described above.
+We also perfmoed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
 All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2021].
@@
 3b).
+
+The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4)
+Altough there were no stiatical differences in the SMA slope or elevation(SMA slope: `r val$sma_slope_cv_mean` [95%CI: `r val$sma_slope_cv_lwr`, `r val$sma_slope_cv_upr`], SMA intercept: `r val$sma_int_cv_mean` [95%CI: `r val$sma_int_cv_lwr`, `r val$sma_int_cv_upr`]), leaf disc LMA had greater CV than whole-leaf LMA (*t* = `r val$t_test_t`, *d.f.* = `r val$t_test_df`, *P* < 0.001).
 
@@
 Details as in Fig. 1.
-Note that the axes are square root scales.
 

### 2022-05-11 ms/LMA_method.Rmd
update result

@@
 Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions (REF).
-The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation [e.g., @Messier2010; @Kichenin2013; @Fajarado2018].
+The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation [e.g., @Messier2010; @Kichenin2013; @Fajardo2018].
 The coefficient of variation (CV) is often used for quantifying the extent of ITV for each species [@Yang2020; @Westerband2021].
@@
 We also perfmoed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
-All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2021].
+All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022].
 
@@
 There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: `r val$sma_slope_all_mean` [95%CI: `r val$sma_slope_all_lwr`, `r val$sma_slope_all_upr`], SMA intercept: `r val$sma_int_all_mean` [95%CI: `r val$sma_int_all_lwr`, `r val$sma_int_all_upr`]), suggesting that the whole-leaf estimates of LMA were `r val$sma_per_all_mean`% [95%CI: `r val$sma_per_all_lwr`, `r val$sma_per_all_upr`] greater than disc-based estimates in the arithmetic scale.
-Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2).
-When a large leaf punch was used, species with lower leaf tissue density had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a).
-Species with lower leaf tissue density had greater estimate whole-leaf to leaf disc LMA ratio when a small leaf punch was used (Fig. 2a).
+
+Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
+Species with lower leaf tissue density had greater variance in the estiamte of whole-leaf to leaf disc LMA ratio (Fig. 2a).
+When a small leaf punch was used, this pattern was more pronounced and leaf disc and whole-leaf LMA estimate diverged for species with higher leaf tissue density (Fig. 2a).
 Species with larger leaves had greater estimate of the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2b), which was only significant for leaves obtained by a large punch.
 Species with thinner leaves had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
-Posteriors of coefficients are summarized in (Fig. SX).
+A small punch also inflated variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a-c and Appendix SX).
 Leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
@@
 
-The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4)
-Altough there were no stiatical differences in the SMA slope or elevation(SMA slope: `r val$sma_slope_cv_mean` [95%CI: `r val$sma_slope_cv_lwr`, `r val$sma_slope_cv_upr`], SMA intercept: `r val$sma_int_cv_mean` [95%CI: `r val$sma_int_cv_lwr`, `r val$sma_int_cv_upr`]), leaf disc LMA had greater CV than whole-leaf LMA (*t* = `r val$t_test_t`, *d.f.* = `r val$t_test_df`, *P* < 0.001).
+The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4).
+Altough there were no stiatical differences in the SMA slope or elevation (SMA slope: `r val$sma_slope_cv_mean` [95%CI: `r val$sma_slope_cv_lwr`, `r val$sma_slope_cv_upr`], SMA intercept: `r val$sma_int_cv_mean` [95%CI: `r val$sma_int_cv_lwr`, `r val$sma_int_cv_upr`]), leaf disc LMA had greater CVs than whole-leaf LMA (*t* = `r val$t_test_t`, *d.f.* = `r val$t_test_df`, *P* < 0.001).
 

### 2022-05-11 ms/LMA_method.tex
update result

@@
 Thin and large leaves had weaker correlations between leaf disc and whole-leaf estimates.
-Variability of LMA estimates within species (i.e., amount of intraspecific variation) only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.33).
+Variability of LMA estimates within species (i.e., amount of intraspecific variation) only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.09).
 We also found that sample with small total dry mass of leaf discs tended to show greater differences between leaf disc and whole-leaf LMA.
@@
 Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago (\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
-Actually, LMA was the most often requested leaf trait in the TRY plant data database (2,977 out of 7,330 requests), followed by leaf nitrogen contents per leaf dry mass (1,938 requests, \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}status October 1 2019{]}).
-
-LMA values can be determined by either
+Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass (12,238 species, 1,938 requests, \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5, status October 1 2019{]})
+
+LMA values can be determined by either measuring whole-leaf (including or excluding petioles) or leaf disc samples (\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et al., 2013}).
+According to the TRY database version 5, recorded numbers of observations and species are as follows:
 1) a whole leaf including (88,490 observations and 7,068 species) or excluding petioles (64,838 observations and 7,558 species; note that this could include leaf disc samples), and
-2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) (\protect\hyperlink{ref-Perez-Harguindeguy2013}{Pérez-Harguindeguy et al., 2013}; \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5{]}).
+2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) (\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5{]}).
 Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}).
-Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two Onoda et al.
-(\protect\hyperlink{ref-Onoda2011}{2011}), but the comparisons between the two estimates in other biomes have rarely been examined.
+Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two (\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}), but the comparisons between the two estimates in other biomes have rarely been examined.
 
@@
 
-In this study, we aimed to investigate what extent whole-leaf (including petiole) and leaf disc LMA match, whether the relationships between whole-leaf LMA and leaf disc LMA varied in leaf tissue density, leaf area and leaf thickness, and whether amounts of intraspecifc variations for each match between whole-leaf and leaf disc based estimates.
+Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions (REF).
+The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013}; \protect\hyperlink{ref-Fajardo2018}{Fajardo and Siefert, 2018}).
+The coefficient of variation (CV) is often used for quantifying the extent of ITV for each species (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}; \protect\hyperlink{ref-Westerband2021}{Westerband et al., 2021}).
+Sources of ITV for whole-leaf samples are variation among individuals within the same species and variation among leaves within the same individuals (\protect\hyperlink{ref-Messier2010}{Messier et al., 2010}, \protect\hyperlink{ref-Messier2017}{2017}).
+An additional source of trait variation for leaf disc samples is variation among leaf discs within the same leaves.
+Given that leaf disc samples have more sources of ITV than whole-leaf samples, the effects of discrepancies between whole-leaf LMA and leaf disc LMA might be large when ITV is quantified based on CV.
+Despite the importance of ITV in community ecology (\protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}; \protect\hyperlink{ref-Westerband2021}{Westerband et al., 2021}), the effect of different measurement methods on the extent of ITV has been largely ignored.
+
+In this study, we aimed to investigate the relationship between whole-leaf (including petiole) LMA and leaf disc LMA,
+whether the relationship varied with leaf tissue density, leaf area and leaf thickness, and
+whether the extent of ITV for each species match between whole-leaf and leaf disc based estimates.
 We collected a total of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
-We predicted that the overall relationship between whole-leaf LMA and disc LMA would be weaker than previous reported LMA data (\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} = 0.92 for leaf laminas in Onoda et al.
-(\protect\hyperlink{ref-Onoda2011}{2011})) because we collected data with various leaf sizes from a wide range of climates.
-We also predicted that species with larger and/or thinner leaves would show weaker correlations.
-Finally, we predicted that amounts of intraspecifc variations for each species do not match well between whole-leaf and leaf disc based estimates.
+We predicted that whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}).
+
+We also predicted that species with larger and/or thinner leaves would show weaker correlations and larger differences in LMA estimates.
+(\textbf{add leaf density})
+
+Finally, we predicted that the extent of ITV do not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
 
@@
 Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
-In total, our data set comprised 334 woody species and 1365 individual that ranged from xxx to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Table S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
+In total, our data set comprised 334 woody species and 1365 individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Table S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
 (\protect\hyperlink{ref-Song2017}{2017}); Fei et al.
@@
 \emph{Measurements of leaf disc and whole-leaf LMA}
-
-We excluded species that had tiny leaves or leaflets (length \textless1 cm) because it was not practical to measure leaf disc LMA.
 
@@
 At least six sun-exposed healthy leaves were sampled from each of 3 to 6 individuals for each species.
-Trait values were averaged at the species- and individual-level for the analyses.
+Trait values were averaged at the species-level for the analyses.
 For compound-leaved species, we referred a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
+We excluded species that had tiny leaves or leaflets (length \textless1 cm) because it was not practical to measure leaf disc LMA.
 
@@
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset.
+Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Fig. S1 for more details).
 Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
@@
 We also perfomred ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
-All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2021}{\textbf{RCoreTeam2021?}}).
+
+\emph{Relationship between disc-based and whole-leaf estiamtes of intraspecific variation}
+
+The extent of intraspecific variation (ITV) was calculated using Bao's CV estimator (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020});
+
+\begin{align}
+CV = CV_1 - \frac{CV_1^3}{N} + \frac{CV_1}{4N} + \frac{CV_1^2 \gamma_1}{2N} + \frac{CV_1 \gamma_2}{8N} \label{eq:CV}
+\end{align}
+
+where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and \(\bar{x}\) is the sample mean, \emph{N} is the sample size, and \(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait distribution.
+Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
+We calulcated CV for species that have at least 5 indivdiuals as recommended in Westerband et al. (\protect\hyperlink{ref-Westerband2021}{2021}).
+Ideally, 20 individuals for each species are required for robust estimation of CV {[}i.e., \textless5\% differences from the true ITV; Yang et al. (\protect\hyperlink{ref-Yang2020}{2020}){]}.
+
+SMA analyses were run as described above.
+We also perfmoed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
+All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}).
 
@@
 There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.68\% {[}95\%CI: 8.05, 11.4{]} greater than disc-based estimates in the arithmetic scale.
-Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2).
-When a large leaf punch was used, species with lower leaf tissue density had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a).
-Species with lower leaf tissue density had greater estimate whole-leaf to leaf disc LMA ratio when a small leaf punch was used (Fig. 2a).
+
+Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
+Species with lower leaf tissue density had greater variance in the estiamte of whole-leaf to leaf disc LMA ratio (Fig. 2a).
+When a small leaf punch was used, this pattern was more pronounced and leaf disc and whole-leaf LMA estimate diverged for species with higher leaf tissue density (Fig. 2a).
 Species with larger leaves had greater estimate of the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2b), which was only significant for leaves obtained by a large punch.
 Species with thinner leaves had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
-Posteriors of coefficients are summarized in (Fig. SX).
+A small punch also inflated variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a-c and Appendix SX).
 Leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
@@
 3b).
+
+The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4).
+Altough there were no stiatical differences in the SMA slope or elevation (SMA slope: 1.116 {[}95\%CI: 0.954, 1.304{]}, SMA intercept: 0.102 {[}95\%CI: -0.174, 0.377{]}), leaf disc LMA had greater CVs than whole-leaf LMA (\emph{t} = -3.19, \emph{d.f.} = 144, \emph{P} \textless{} 0.001).
 
@@
 Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig.
-3; \emph{R\textsuperscript{2}} = 0.33).
+3; \emph{R\textsuperscript{2}} = 0.09).
 This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Fajardo2018}{}}%
+Fajardo, A., and A.
+Siefert.
+2018.
+\href{https://doi.org/10.1002/ecy.2194}{Intraspecific trait variation and the leaf economics spectrum across resource gradients and levels of organization}.
+\emph{Ecology} 99: 1024--1030.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Falster2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kichenin2013}{}}%
+Kichenin, E., D.
+A.
+Wardle, D.
+A.
+Peltzer, C.
+W.
+Morse, and G.
+T.
+Freschet.
+2013.
+\href{https://doi.org/10.1111/1365-2435.12116}{Contrasting effects of plant inter- and intraspecific variation on community-level trait measures along an environmental gradient}.
+\emph{Functional Ecology} 27: 1254--1261.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Kitajima2010}{}}%
@@
 \emph{PLOS ONE} 8: 1--10.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Messier2017}{}}%
+Messier, J., B.
+J.
+McGill, B.
+J.
+Enquist, and M.
+J.
+Lechowicz.
+2017.
+\href{https://doi.org/10.1111/ecog.02006}{Trait variation and integration across scales: Is the leaf economic spectrum present at local scales?} \emph{Ecography} 40: 685--697.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Messier2010}{}}%
+Messier, J., B.
+J.
+McGill, and M.
+J.
+Lechowicz.
+2010.
+\href{https://doi.org/10.1111/j.1461-0248.2010.01476.x}{How do traits vary across ecological scales?
+{A} case for trait-based ecology}.
+\emph{Ecology Letters} 13: 838--848.
 
@@
 \emph{New Phytologist} 182: 565--588.
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCoreTeam2022}{}}%
+R Core Team. 2022. R: {A} language and environment for statistical computing. {R Foundation for Statistical Computing}, {Vienna, Austria}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Westerband2021}{}}%
+Westerband, A.
+C., J.
+L.
+Funk, and K.
+E.
+Barton.
+2021.
+\href{https://doi.org/10.1093/aob/mcab011}{Intraspecific trait variation in plants: A renewed focus on its role in ecological processes}.
+\emph{Annals of Botany} 127: 397--410.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Westoby2013}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Yang2020}{}}%
+Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020. Large {Underestimation} of {Intraspecific Trait Variation} and {Its Improvements}. \emph{Frontiers in Plant Science} 11.
+
 \end{CSLReferences}

### 2022-05-11 ms/response_letter.Rmd
update itv text
update ms

@@
 Thank you.
-We now use Bao's CV estimator (CV4) instead of  coefficient of variation of log-normally distributed data ($CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$).
-The pattern didn't change qualitatively.
-
-- remove?
+We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA.
+We now use Bao's CV estimator (CV4) instead of the coefficient of variation of log-normally distributed data ($CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$).
+We also limited to the analysis for species that have at least 5 individuals.
+The relationship between the two estimates became much weaker (Fig. 4).
 
@@
 
+Thank you.
+As noted above, We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA.
+
 > L99-100 It may bear repeating here why you expect the estimates to match up better for smaller and/or thicker leaves
 
+Thank you.
+We have repeated our expectations here.
+
 > L101-102 again, might be worth stating why (even if it is discussed above)
+
+Thank you.
+We have repeated our expectations here.
 
@@
 
+Thank you.
+We now use Bao's CV as noted above.
+
 > L169-172 This is the major result of the paper.
 I suggest making it the first line of the results section (however I would modify it to fit the individual, rather than species-mean, level data: see below).
+
+Thank you.
+We have started the result section with the shift in elevation between whole-leaf and leaf disc LMA (i.e., whole-leaf LMA is greater than leaf disc LMA) .
+Please see our response for using species- vs. individual-level data below.
 
@@
 
-- need to think this
+Thank you.
+We agree that using both species- and individual-level data in the same statistical framework is confusing and not appropriate.
+Instead of using individual-level data, we now only use the species-level data
+For individual-level data, variance among species are not independent, and thus SMA or OLS regressions are not appropriate.
+Analyses of individual-level data requires mixed linear models with species-level errors, but this is not useful for the context of our paper.
+We therefore only report species-level results.
 
@@
 
-- caveate
+Thank you.
+We now include other continuous variables (leaf tissue density, leaf area, and leaf thickness) as covariates in our model, and thus we have some confidence in the effect of leaf punch.
+However, as the reviewer pointed out, we should have used the same leaf punch size or repeated measurements using different leaf punch sizes.
+We consider this as a limitation of our study and explain this in the discussion.
 
 > L183-184 Which metric had higher ITV? That is a more relevant result than simply the R2 value.
+
+Leaf disc LMA had higher ITV.
+We have added the paired t-test for this in the results section.
 
@@
 
+Thank you.
+We have included this in the results section.
+
 > L247 is this reported in the results somewhere? I thought the multiple discs/leaf were measured together?
 
+- working
+
 > Appendix S2 seems to be missing the x axis titles
+
+- working
 
@@
 
+???
+
 > The authors had better explain why they used the LMA values with leaf petioles mass.
+
+Thank you.
+We have added the records of TRY database that shows LMA including petioles are very common.
 
@@
 
+Thank you.
+We keep the original title as recommended by the editor.
+
 > Lines 26 and 51: Change "the key trait" to "an important functional trait".
@@
 Thank you.
-We have updated the line 26 but key the line 51 as "the key trait" because xxx
+We have updated the first one but keep the second one as "a key trait" because we have added the explanation on why LMA is considered as "a key trait" in the LES at the beginning of the introduction.
 
@@
 > Jiao, Y., Niklas, K.J., Wang, L., Yu, K., Li, Y., Shi, P. 2022. Influence of leaf age on the scaling relationships of lamina biomass vs. area. Frontiers in Plant Science In press.
+
+Thank you.
+** this should be somewhere else and not line 57**.
+We have cited it in XX.
 
@@
 
+Thank you.
+We have cited these now.
+
 > Lines 97 and 98: Drop the numerical values of R squared. There is no need to exhibit the results here.
+
+Thank you, but to make the statement of "good correlations" more quantitative, we do feel showing *R^2^* values is still useful.
+We, therefore, kept the *R^2^* values in the introduction.
 
@@
 
+Thank you.
 The main function of leaves is to deliver a profitable return on the investment that has been made in constructing the leaf (Westoby, Reich and Wright 2013), and thus it is also natural to include leaf petiole in LMA.
-According to the trait hand book (Perez-Harguindeguy 2013), either including or excluding petiole will fine.
-As long as we checked the TRY data that we have now, the numbers of LMA records for those two measurements are very similar:
-the number of records of LMA (or 1/SLA) including petiole is 57,033, and
-the number of records of LMA (or 1/SLA) excluding petiole is 59,103.
-(add conclusion).
+As noted above, we have added the records of TRY database that shows LMA including petioles are actually very common.
 
-Thank you.
 We now more clearly explain that thick veins are secondary order veins.
-We have also added detailed LMA measurement protocol in Fig. SX.
 
@@
 
-We have added detailed LMA measurement protocol in Fig. SX as note above.
+Thank you.
+It is hard to classify the leaf shapes of each species.
+Instead, we have added the detailed LMA measurement protocol including sampling positions for different types of leaf shapes in Appendix S2.
 
@@
 
-We have removed XXX.
+Thank you.
+As noted above, we have removed the analysis grouping species into the different categories.
 
@@
 
+Thank you.
+We have changed the unit of CV to percentage.
+
 > Line 163: It is incorrect to use 1000 bootstrap replates to calculate a confidence interval!
 In general, >= 30 replates are enough for calculating a standard deviation, and >= 2000 replates to calculate a confidence interval.
+
+Thank you.
+We now use 2000 replicates.
 
@@
 If possible, I suggest adding several sentences to discuss the reasons for the pooled data in the Discussion section.
+
+Thank you.
+We originally had this result to support grouping species into four categories, because if the correlation between leaf area and leaf thickness are too strong, we cannot group species into four categories based on median values of traits.
+As noted above, we removed the analysis of grouping species, and thus we also removed this result.
 
@@
 > Line 171: "… were 9.4% greater than disc-based estimates …" Can you provide a standard deviation or a confidence interval for 9.4%? In general, we can use the bootstrap method to get it.
+
+Thank you.
+We have added confidence intervals using bootstraps.

### 2022-05-11 ms/LMA_method.Rmd
update ms

@@
 The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf [i.e., leaf economic spectrum, @Wright2004a; @Westoby2013].
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is the key trait of the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
+Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
 Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover [@Wright2004a].
@@
 
-Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
+Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007; @Li2022; @Li2022a], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
 (**add leaf density**)
@@
 
-A bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (*R^2^*) based on Pearson correlations and with standardized major axis (SMA) regressions [@Warton2006] across all the species.
+A bivariate trait relationship between disc-based and whole-leaf log-transformed LMA was summarized with variance explained (*R^2^*) based on Pearson correlations and with a standardized major axis (SMA) regression [@Warton2006] across all the species.
 
-SMA analyses were run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
+A SMA analysis was run using the R package *smatr* [@Warton2012a]; this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
 Confidence intervals of SMA estimates were based on 2000 bootstraps.
@@
 To allow comparisons among parameter estimates, $\mathrm{ln}(LD)$, $\mathrm{ln}(LA)$, and $\mathrm{ln}(LT)$ were scaled to a mean of 0 and standard deviation of 1.
-Note that this model does not include measurement errors of leaf disc LMA implemented in the following analysis, because there are too many scaling parameters
+Note that this model does not include measurement errors of leaf disc LMA implemented in the previous SMA analysis, because there are too many scaling parameters
 
 Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan [@Carpenter2017] using the weakly-informative priors [@Gelman2008].
-See supplement XXXX for more detail.
+See Appendix SX for more detail.
 The Stan code use to fit models is available from Github at: [https://github.com/mattocci27/leaf-disc](https://github.com/mattocci27/leaf-disc).
@@
 where $CV_1 = s/\bar{x}$, $s$ is the sample standard deviation and $\bar{x}$ is the sample mean, *N* is the sample size, and $\gamma_1$ and $\gamma_2$ are the skewness and kurtosis of the trait distribution.
-Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small [@Yang2020].
+Bao's CV estimator is a robust method to quantify ITV based on a coefficient of variation (CV) when sample size is small [@Yang2020].
 We calulcated CV for species that have at least 5 indivdiuals as recommended in @Westerband2021.
@@
 
+\newpage
+
 **Fig. 4.**
-Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
+Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in LMA values determined by using whole leaves and leaf discs.
 The correlation is significant (*P* < 0.001).

### 2022-05-11 ms/LMA_method.tex
update ms

@@
 The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf (i.e., leaf economic spectrum, \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Westoby2013}{Westoby et al., 2013}).
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is the key trait of the leaf economic spectrum (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
+Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
 Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}).
@@
 
-Since larger leaves tend to invest more of their mass into dense midribs and petiole for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}), and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
+Since larger leaves tend to invest more of their mass into dense midribs and petiole for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}; \protect\hyperlink{ref-Li2022a}{Li, Zheng, et al., 2022}), and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
 (\textbf{add leaf density})
@@
 
-A bivariate trait relationships between disc-based and whole-leaf log-transformed LMA were summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with standardized major axis (SMA) regressions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the species.
-
-SMA analyses were run using the R package \emph{smatr} (\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
+A bivariate trait relationship between disc-based and whole-leaf log-transformed LMA was summarized with variance explained (\emph{R\textsuperscript{2}}) based on Pearson correlations and with a standardized major axis (SMA) regression (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}) across all the species.
+
+A SMA analysis was run using the R package \emph{smatr} (\protect\hyperlink{ref-Warton2012a}{Warton et al., 2012}); this included tests for slope heterogeneity and elevation differences between disc-based and whole-leaf estimates of LMA values.
 Confidence intervals of SMA estimates were based on 2000 bootstraps.
@@
 To allow comparisons among parameter estimates, \(\mathrm{ln}(LD)\), \(\mathrm{ln}(LA)\), and \(\mathrm{ln}(LT)\) were scaled to a mean of 0 and standard deviation of 1.
-Note that this model does not include measurement errors of leaf disc LMA implemented in the following analysis, because there are too many scaling parameters
+Note that this model does not include measurement errors of leaf disc LMA implemented in the previous SMA analysis, because there are too many scaling parameters
 
 Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}) using the weakly-informative priors (\protect\hyperlink{ref-Gelman2008}{Gelman et al., 2008}).
-See supplement XXXX for more detail.
+See Appendix SX for more detail.
 The Stan code use to fit models is available from Github at: \url{https://github.com/mattocci27/leaf-disc}.
@@
 where \(CV_1 = s/\bar{x}\), \(s\) is the sample standard deviation and \(\bar{x}\) is the sample mean, \emph{N} is the sample size, and \(\gamma_1\) and \(\gamma_2\) are the skewness and kurtosis of the trait distribution.
-Bao's CV estimator is a robust method to quantify ITV based on coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
+Bao's CV estimator is a robust method to quantify ITV based on a coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
 We calulcated CV for species that have at least 5 indivdiuals as recommended in Westerband et al. (\protect\hyperlink{ref-Westerband2021}{2021}).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Li2022}{}}%
+Li, Y., P.
+Shi, Ü.
+Niinemets, Y.
+Song, K.
+Yu, J.
+Schrader, and K.
+J.
+Niklas.
+2022.
+\href{https://doi.org/10.1002/ajb2.1812}{Diminishing returns among lamina fresh and dry mass, surface area, and petiole fresh mass among nine {Lauraceae} species}.
+\emph{American Journal of Botany} 109: 377--392.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Li2022a}{}}%
+Li, Y., Y.
+Zheng, D.
+A.
+Ratkowsky, H.
+Wei, and P.
+Shi.
+2022.
+\href{https://doi.org/10.3389/fpls.2021.822907}{Application of an {Ovate Leaf Shape Model} to {Evaluate Leaf Bilateral Asymmetry} and {Calculate Lamina Centroid Location}}.
+\emph{Frontiers in Plant Science} 12: 822907.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Messier2017}{}}%
@@
 
+\newpage
+
 \textbf{Fig. 4.}
-Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in leaf trait values determined by using whole leaves and leaf discs: (a) leaf mass per area (LMA).
+Relationships between coefficient of variation (Bao's CV estimator, Eq. 5) in LMA values determined by using whole leaves and leaf discs.
 The correlation is significant (\emph{P} \textless{} 0.001).

### 2022-05-11 ms/LMA_method.Rmd
update ms

@@
 
-Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per are (LMA)
+Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)
 
@@
 
-We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
+We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
 First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
 Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
-In total, our data set comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Table S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
+In total, our data set comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
 The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.

### 2022-05-11 ms/LMA_method.tex
update ms

@@
 
-We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Table S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
+We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
 First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
 Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
-In total, our data set comprised 334 woody species and 1365 individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Table S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
+In total, our data set comprised 334 woody species and 1365 individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
 (\protect\hyperlink{ref-Song2017}{2017}); Fei et al.

### 2022-05-12 ms/LMA_method.Rmd
update leaf disc intro

@@
 The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf [i.e., leaf economic spectrum, @Wright2004a; @Westoby2013].
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
+Leaf mass per area (LMA or 1/SLA [specific leaf area]), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum [@Wright2004a; @Poorter2009; @Onoda2017].
 Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover [@Wright2004a].
@@
 2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) [@Kattge2020 [TRY version 5]].
+There are not many records that explicitly indicate leaf disc LMA in the TRY database, but leaf disc LMA has been used for ecological studies as well as physiological studies [e.g., @Kraft2008; @Poorter2009a; @Onoda2011; @Serbin2019; @Campany2021].
+@Poorter2009a found that leaf disc LMA showed stronger correlations with shade tolerance than whole-leaf LMA, suggesting that lamina traits are more important whole-leaf traits in certain ecological contexts
 Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
@@
 At least six sun-exposed healthy leaves were sampled from each of 3 to 6 individuals for each species.
-Trait values were averaged at the species-level for the analyses.
+Trait values were averaged at the species- and individual-level for the analyses.
 For compound-leaved species, we referred a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
@@
 
-To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins.
+To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins (first to second veins).
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Fig. S1 for more details).
+Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Appendix S2 for more details).
 Fresh leaf area (LA; cm^-2^) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package *LeafArea* [@Katabuchi2015].
@@
 Based on those measurements of whole-leaf and leaf disc samples, LMA (g m^-2^) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
-We do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S2).
 

### 2022-05-12 ms/response_letter.Rmd
update leaf disc intro
update intro

@@
 
-- record and requests
+Thank you.
+We note that a key difference between leaf disc and whole-leaf LMA is that leaf disc LMA focuses on lamina rather than whole-leaf and usages depend on ecological contexts.
 
@@
 Thank you.
-This is an important thing to clarify.
-We now use a linear model that used leaf area and leaf thickness as covariates but we suggest OLS models without covariates for the conversion of LMA because leaf thickness and leaf area affect not only the mean but also the variance in the relationship between the leaf disc and whole-leaf estimates, and that is why R2 values changed among the four groups (thin vs.
+This is a good point and an important thing to clarify.
+We now use a linear model that includes leaf area and leaf thickness as covariates but we suggest OLS models without covariates for the conversion of LMA because leaf thickness and leaf area affect not only the mean but also the variance in the relationship between the leaf disc and whole-leaf estimates, and that is why R2 values changed among the four groups (thin vs.
 think and small vs.
@@
 Thank you.
-As noted above, We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA.
+As noted above, we have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA.
 
@@
 
-???
+Thank you.
+We have mentioned several ecological studies that used leaf disc LMA in the introduction.
 

### 2022-05-12 ms/LMA_method.Rmd
update intro

@@
 2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) [@Kattge2020 [TRY version 5]].
-There are not many records that explicitly indicate leaf disc LMA in the TRY database, but leaf disc LMA has been used for ecological studies as well as physiological studies [e.g., @Kraft2008; @Poorter2009a; @Onoda2011; @Serbin2019; @Campany2021].
-@Poorter2009a found that leaf disc LMA showed stronger correlations with shade tolerance than whole-leaf LMA, suggesting that lamina traits are more important whole-leaf traits in certain ecological contexts
-Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
-Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two [*R^2^* = 0.92 for whole-leaves in @Kraft2008; *R^2^* = 0.92 for leaf laminas in @Onoda2011], but the comparisons between the two estimates in other biomes have rarely been examined.
+There are not many records that explicitly indicate leaf disc LMA in the TRY database, but leaf disc LMA has been commonly used for ecological studies as well as biochemical studies [e.g., @Kraft2008; @Poorter2009a; @Onoda2011; @Osada2014; @Sastry2017; @Serbin2019; @Campany2021].
+Although using whole-leaf traits seems to be more straightforward in the logic of investment costs and returns on investment [@Westoby2013], @Poorter2009a found that leaf disc LMA showed stronger correlations with shade tolerance than whole-leaf LMA, suggesting that lamina traits are more important than whole-leaf traits in certain ecological contexts.
+Many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), but these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA [@John2017].
+Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two [*R^2^* = 0.92 for whole-leaves in @Kraft2008; *R^2^* = 0.92 for leaf laminas in @Onoda2011].
+However, the comparisons between the two estimates in other biomes have rarely been examined, even though LMA responses to climate [@Poorter2009a] .
 
 Since larger leaves tend to invest more of their mass into dense midribs and petiole for support [@Niinemets2006; @Niinemets2007; @Li2022; @Li2022a], and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; [@Grubb1986]), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
-(**add leaf density**)
+Higher leaf density (and LMA) is associated with higher vein density [@John2017; @Sancho-Knapik2020], and thus leaf disc LMA avoiding major veins might also underestimate whole-leaf LMA for species with higher leaf tissue density.
 If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates [@Kraft2008; @Onoda2011].
@@
 
-Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions (REF).
+Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions [@Westerband2021].
 The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation [e.g., @Messier2010; @Kichenin2013; @Fajardo2018].
@@
 We collected a total of `r val$all_sp` woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
-We predicted that whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas [@Niinemets2007].
-
-We also predicted that species with larger and/or thinner leaves would show weaker correlations and larger differences in LMA estimates.
-(**add leaf density**)
-
-Finally, we predicted that the extent of ITV do not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
+We evaluate the following hypotheses:
+(1) whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas [@Niinemets2007],
+(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles that are likely to be ignored in leaf disc samples, and
+(3) the extent of ITV does not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
+In addition to leaf morphology, we also investigate the effects of leaf punch size on the relationship between whole-leaf and leaf disc LMA.
 

### 2022-05-12 ms/LMA_method.tex
update intro

@@
 The primary function of leaves is to return photosynthetic revenue on the investment that has been made in constructing the leaf (i.e., leaf economic spectrum, \protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Westoby2013}{Westoby et al., 2013}).
-Leaf mass per area (LMA), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
+Leaf mass per area (LMA or 1/SLA {[}specific leaf area{]}), determined by lamina thickness and leaf tissue density (LD), describes how much biomass is invested into given photosynthetic leaf area, which is a key trait in the leaf economic spectrum (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}; \protect\hyperlink{ref-Poorter2009}{Poorter et al., 2009}; \protect\hyperlink{ref-Onoda2017}{Onoda et al., 2017}).
 Generally, resource-acquisitive species (fast-growing species) tend to have low LMA values, showing high photosynthesis, high nutrients, and often have fast leaf turnover (\protect\hyperlink{ref-Wright2004a}{Wright et al., 2004}).
@@
 2) a leaf disc excluding all major veins or petioles (645 observations and 403 species) (\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5{]}).
-Although many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}).
+There are not many records that explicitly indicate leaf disc LMA in the TRY database, but leaf disc LMA has been commonly used for ecological studies as well as biochemical studies (e.g., \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Poorter2009a}{Poorter, 2009}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}; \protect\hyperlink{ref-Osada2014}{Osada et al., 2014}; \protect\hyperlink{ref-Sastry2017}{Sastry and Barua, 2017}; \protect\hyperlink{ref-Serbin2019}{Serbin et al., 2019}; \protect\hyperlink{ref-Campany2021}{Campany et al., 2021}).
+Although using whole-leaf traits seems to be more straightforward in the logic of investment costs and returns on investment (\protect\hyperlink{ref-Westoby2013}{Westoby et al., 2013}), Poorter (\protect\hyperlink{ref-Poorter2009a}{2009}) found that leaf disc LMA showed stronger correlations with shade tolerance than whole-leaf LMA, suggesting that lamina traits are more important than whole-leaf traits in certain ecological contexts.
+Many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), but these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}).
 Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two (\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}), but the comparisons between the two estimates in other biomes have rarely been examined.
@@
 Since larger leaves tend to invest more of their mass into dense midribs and petiole for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}; \protect\hyperlink{ref-Li2022a}{Li, Zheng, et al., 2022}), and thinner leaves have clearly visible and large-diameter veins with less uniform leaf structure (i.e., kite-type leaves; (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986})), discrepancies in the estimates of whole-leaf LMA and leaf disc LMA might be greater for larger and thinner leaves.
-(\textbf{add leaf density})
+Higher leaf density (and LMA) is associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}), and thus leaf disc LMA avoiding major veins might also underestimate whole-leaf LMA for species with higher leaf tissue density.
 If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
@@
 
-Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions (REF).
+Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions (\protect\hyperlink{ref-Westerband2021}{Westerband et al., 2021}).
 The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013}; \protect\hyperlink{ref-Fajardo2018}{Fajardo and Siefert, 2018}).
@@
 We collected a total of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
-We predicted that whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}).
-
-We also predicted that species with larger and/or thinner leaves would show weaker correlations and larger differences in LMA estimates.
-(\textbf{add leaf density})
-
-Finally, we predicted that the extent of ITV do not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
+We evaluate the following hypotheses:
+(1) whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}),
+(2) species with higher leaf tissue density, larger and/or thinner leaves would show weaker correlations and larger differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles that are likely to be ignored in leaf disc samples, and
+(3) the extent of ITV does not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
+In addition to leaf morphology, we also investigate the effects of leaf punch size on the relationship between whole-leaf and leaf disc LMA.
 
@@
 
-To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins.
+To determine what extent LMA values were affected by the different methods, LMA were determined (i) LMA based on a whole leaf including petioles and (ii) LMA based on leaf disc avoiding thick veins (first to second veins).
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Fig. S1 for more details).
+Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Appendix S2 for more details).
 Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
@@
 Based on those measurements of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
-We do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S2).
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Campany2021}{}}%
+Campany, C.
+E., J.
+Pittermann, A.
+Baer, H.
+Holmlund, E.
+Schuettpelz, K.
+Mehltreter, and J.
+E.
+Watkins Jr.
+2021.
+\href{https://doi.org/10.1111/pce.14042}{Leaf water relations in epiphytic ferns are driven by drought avoidance rather than tolerance mechanisms}.
+\emph{Plant, Cell \& Environment} 44: 1741--1755.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Osada2014}{}}%
+Osada, N., Y.
+Yasumura, and A.
+Ishida.
+2014.
+\href{https://doi.org/10.1007/s00442-014-2966-y}{Leaf nitrogen distribution in relation to crown architecture in the tall canopy species, {Fagus} crenata}.
+\emph{Oecologia} 175: 1093--1106.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Parry2002}{}}%
@@
 \emph{New Phytologist} 182: 565--588.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Poorter2009a}{}}%
+Poorter, L.
+2009.
+\href{https://doi.org/10.1111/j.1469-8137.2008.02715.x}{Leaf traits show different relationships with shade tolerance in moist versus dry tropical forests}.
+\emph{New Phytologist} 181: 890--900.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Sancho-Knapik2020}{}}%
+Sancho-Knapik, D., A.
+Escudero, S.
+Mediavilla, C.
+Scoffoni, J.
+Zailaa, J.
+Cavender-Bares, T.
+Gómez Álvarez-Arenas, et al.
+2020.
+Deciduous and evergreen oaks show contrasting adaptive responses in leaf mass per area across environments.
+\emph{New Phytologist}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sastry2017}{}}%
+Sastry, A., and D.
+Barua.
+2017.
+\href{https://doi.org/10.1038/s41598-017-11343-5}{Leaf thermotolerance in tropical trees from a seasonally dry climate varies along the slow-fast resource acquisition spectrum}.
+\emph{Scientific Reports} 7: 11246.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Serbin2019}{}}%
+Serbin, S.
+P., J.
+Wu, K.
+S.
+Ely, E.
+L.
+Kruger, P.
+A.
+Townsend, R.
+Meng, B.
+T.
+Wolfe, et al.
+2019.
+\href{https://doi.org/10.1111/nph.16123}{From the {Arctic} to the tropics: Multi-biome prediction of leaf mass per area using leaf reflectance}.
+\emph{New Phytologist} 224: 1557--1568.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Siefert2015}{}}%

### 2022-05-12 ms/LMA_method.Rmd
update discussion

@@
 First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
-Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
-In total, our data set comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
+Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
+In total, our dataset comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
 The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.
@@
 $\tilde{\mu_i}$ is the effect of leaf tissue density, leaf area, leaf thickness and leaf punch size on the mean estimates for the whole-leaf LMA of species *i*, $\sigma_i^2$ is the variance of whole-leaf LMA for species *i*, and $\beta$ are coefficients.
+Since leaf disc LMA is used as an offset, this model can be used to see the realtionship between whole-leaf to leaf disc LMA ratio and predictors.
 The standard deviation of whole-leaf LMA ($\sigma_i$) was assumed to follow a normal distribution;
@@
 
-Disc-based traits explained interspecific variations in whole-leaf LMA (*R^2^* = `r val$r2_LMA`, *n* = `r val$N3`) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported  (*R^2^* = 0.92, *n* = 409,  for whole-leaves in @Kraft2008, *R^2^* = 0.92, *n* = 364 for leaf laminas in @Onoda2011).
-Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4% differences) or large-leaved species were used (22.1% differences).
-Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration.
-However, the strength of correlations highly depended on leaf area, thickness (Fig. 1) and sizes of leaf punches (Appendix S3 and S5).
+Leaf disc LMA explained interspecific variations in whole-leaf LMA (*R^2^* = `r val$r2_lma`, *n* = `r val$all_sp`) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported  [*R^2^* = 0.92, *n* = 409, for whole-leaves in @Kraft2008; *R^2^* = 0.92, *n* = 364 for leaf laminas in @Onoda2011].
+Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4% differences).
+Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration
+(
+OLS regressions:
+log~10~LMA~w~ = `r val$ols_int_log10` + `r val$ols_slope` $\times$ log~10~LMA~d~ or
+log~10~LMA~d~ = `r val$ols_slope_inv` $\times$ log~10~LMA~w~,
+where LMA~w~ and LMA~d~ are the whole-leaf and leaf disc LMA, respectively
+).
+However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
 
-Larger leaves generally invest disproportionally more mass into dense midribs and major veins for support [@Niinemets2006; @Niinemets2007; @Sack2012], and thinner leaves have distinct veins and have kite-type appearances [@Grubb1986].
-As we predicted, thicker and/or smaller leaves tended to show greater *R^2^* values between whole-leaf and leaf disc estimates (Figs 1. and 2).
-Large-leaved species had greater whole-leaf LMA than leaf disc LMA (Table 1), which is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles.
-This is also supported by the subset of our dataset in which we measured leaf lamina and petiole dry mass separately.
-We confirmed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass, and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Appendix S6).
+The effect of leaf punch size was the most important source of the variation (Fig.
+2, Appendix SX), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
+Small leaf disc size inflates trait variation within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
+Species with lower leaf tissue density and thin leaves showed greater variance in whole-leaf to leaf disc LMA ratio especially when a small punch was used (Fig.2ac: small leaf punch, Fig.
+2a: large leaf punch), suggesting that simple conversion between whole-leaf and leaf disc LMA is difficult for those species.
+@Kraft2008 found high *R^2^* values (*R^2^* = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves [@Kitajima2010; @Oktavia2020].
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
+The relatively low *R^2^* values for species with lower leaf tissue density and thin leaves in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset, may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendices SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
-Meanwhile, our results are seemingly inconsistent with a previous study that used thin and soft leaves and found high *R^2^* values (*R^2^* = 0.92; @Kraft2008).
-@Kraft2008 used sapling leaves under closed canopy that are thinner than adult leaves [@Kitajima2010; @Oktavia2020].
-Shade leaves tend to have thinner leaves than sun leaves because of fewer layers of palisade mesophyll cells [@Onoda2008; @Terashima2001].
-The relatively low *R^2^* values for thin-leaved species and individuals in our study compared to the previous study may suggest not only the effect of distinct veins on variance in LMA [@John2017] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Fig.
-2; Appendices S3), and thus thin-leaved species, which have smaller dry mass (Appendix S4), tended to showed the low *R^2^* values especially when we used a smaller leaf punch (diameter: 0.6 cm; Appendix S5).
+Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig.
+2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
+We also observed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
+3a), and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Fig.
+3b).
+This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles [@Niinemets2006; @Niinemets2007; @Sack2012] and the pattern of higher leaf tissue density associated with higher vein density [@John2017; @Sancho-Knapik2020] because those driving factors of LMA are likely to be ignored in leaf disc samples.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appdendix SX), but those effects were not significant.
+This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates ($\beta$ in Eq.
+2) when a small leaf punch was used.
 

### 2022-05-12 ms/LMA_method.tex
update discussion

@@
 Many studies do not make clear what protocol was followed (146,315 observations and 13,101 species), but these differences in the measurement methods may lead to large discrepancies in the estimates of LMA values because the major vein allocation (major vein, which includes first to second or third-order veins, volume per area) has been reported to be one of the main determinants for the variation in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}).
-Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two (\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}), but the comparisons between the two estimates in other biomes have rarely been examined.
+Previous works that compared estimates of whole-leaf LMA and leaf disc LMA using tropical tree species showed good correlations between the two (\emph{R\textsuperscript{2}} = 0.92 for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
+However, the comparisons between the two estimates in other biomes have rarely been examined, even though LMA responses to climate (\protect\hyperlink{ref-Poorter2009a}{Poorter, 2009}) .
 
@@
 (1) whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}),
-(2) species with higher leaf tissue density, larger and/or thinner leaves would show weaker correlations and larger differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles that are likely to be ignored in leaf disc samples, and
+(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles that are likely to be ignored in leaf disc samples, and
 (3) the extent of ITV does not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
@@
 \(\tilde{\mu_i}\) is the effect of leaf tissue density, leaf area, leaf thickness and leaf punch size on the mean estimates for the whole-leaf LMA of species \emph{i}, \(\sigma_i^2\) is the variance of whole-leaf LMA for species \emph{i}, and \(\beta\) are coefficients.
+Since leaf disc LMA is used as an offset, this model can be used to see the realtionship between whole-leaf to leaf disc LMA ratio and predictors.
 The standard deviation of whole-leaf LMA (\(\sigma_i\)) was assumed to follow a normal distribution;
@@
 
-Disc-based traits explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = , \emph{n} = ) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in Kraft et al.
+Leaf disc LMA explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in Kraft et al.
 (\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
 (\protect\hyperlink{ref-Onoda2011}{2011})).
-Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4\% differences) or large-leaved species were used (22.1\% differences).
-Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration.
-However, the strength of correlations highly depended on leaf area, thickness (Fig. 1) and sizes of leaf punches (Appendix S3 and S5).
-
+Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4\% differences).
+Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration
+(
+OLS regressions:
+log\textsubscript{10}LMA\textsubscript{w} = 0.211 + 0.911 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
+log\textsubscript{10}LMA\textsubscript{d} = 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{w},
+where LMA\textsubscript{w} and LMA\textsubscript{d} are the whole-leaf and leaf disc LMA, respectively
+).
+However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
+Higher leaf tissue density is associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}), but this effect might be ignored in leaf disc LMA.
 Larger leaves generally invest disproportionally more mass into dense midribs and major veins for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Sack2012}{Sack et al., 2012}), and thinner leaves have distinct veins and have kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}).
-As we predicted, thicker and/or smaller leaves tended to show greater \emph{R\textsuperscript{2}} values between whole-leaf and leaf disc estimates (Figs 1. and 2).
-Large-leaved species had greater whole-leaf LMA than leaf disc LMA (Table 1), which is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles.
-This is also supported by the subset of our dataset in which we measured leaf lamina and petiole dry mass separately.
-We confirmed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass, and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Appendix S6).
-
-Meanwhile, our results are seemingly inconsistent with a previous study that used thin and soft leaves and found high \emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92; Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008})).
+The effects of leaf morphology on the relationship between the whole-leaf LMA and leaf disc LMA were generally matched with our hyptheses, but the actual patterns were more complicated.
+
+The effect of leaf punch size was the most important source of the variation (Fig.
+2, Appendix SX), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
+Small leaf disc size inflates trait variation within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
+Species with lower leaf tissue density and thin leaves showed greater variance in whole-leaf to leaf disc LMA ratio especially when a small punch was used (Fig.2ac: small leaf punch, Fig.
+2a: large leaf punch), suggesting that simple conversion between whole-leaf and leaf disc LMA is difficult for those species.
 Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}) used sapling leaves under closed canopy that are thinner than adult leaves (\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010}; \protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}).
-Shade leaves tend to have thinner leaves than sun leaves because of fewer layers of palisade mesophyll cells (\protect\hyperlink{ref-Terashima2001}{Terashima et al., 2001}; \protect\hyperlink{ref-Onoda2008}{Onoda et al., 2008}).
-The relatively low \emph{R\textsuperscript{2}} values for thin-leaved species and individuals in our study compared to the previous study may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+(\protect\hyperlink{ref-Kraft2008}{2008}) found high \emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves (\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010}; \protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}).
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
+The relatively low \emph{R\textsuperscript{2}} values for species with lower leaf tissue density and thin leaves in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset, may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
 We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Fig.
-2; Appendices S3), and thus thin-leaved species, which have smaller dry mass (Appendix S4), tended to showed the low \emph{R\textsuperscript{2}} values especially when we used a smaller leaf punch (diameter: 0.6 cm; Appendix S5).
+2; Appendices SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+
+Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig.
+2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
+We also observed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
+3a), and large-leaved species tended to have greater investment for petiole dry mass than small-leaved species (Fig.
+3b).
+This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}) and the pattern of higher leaf tissue density associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}) because those driving factors of LMA are likely to be ignored in leaf disc samples.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appdendix SX), but those effects were not significant.
+This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates (\(\beta\)) when use a small leaf punch.
 
@@
 \emph{Basic and Applied Ecology} 49: 22--33.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Onoda2008}{}}%
-Onoda, Y., F.
-Schieving, and N.
-P.
-R.
-Anten.
-2008.
-\href{https://doi.org/10.1093/aob/mcn013}{Effects of light and nutrient availability on leaf mechanical properties of {Plantago} major: {A} conceptual approach}.
-\emph{Annals of Botany} 101: 727--736.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Terashima2001}{}}%
-Terashima, I., S.-I.
-Miyazawa, and Y.
-T.
-Hanba.
-2001.
-\href{https://doi.org/10.1007/PL00013972}{Why are {Sun Leaves Thicker} than {Shade Leaves}?
-\textemdash{} {Consideration} based on {Analyses} of {CO2 Diffusion} in the {Leaf}}.
-\emph{Journal of Plant Research} 114: 93--105.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Warton2012a}{}}%

### 2022-05-12 ms/LMA_method.Rmd
add ITV

@@
 This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
+On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA.
 Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species *Alocasia macrorrhiza*, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions [@Li2013a].
@@
 Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
-This is consistent with the *R^2^* values in our results (Figs. 1-3).
-The mismatch of ITV between whole-leaf and disc-based estimate could be ignored in community-level ITV studies [i.e., @Siefert2015], which quantify the total variance of ITV within communities.
-However, it is likely to change patterns for species-level ITV studies [i.e., @Albert2010a], which quantify extents of ITV for each species, since species with high ITV based on leaf-disc estimates do not always have to show high ITV for whole-leaf estimates.
-This problem will be more obvious when one uses smaller leaf punches (Appendix S7).
+The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to detemine sources of trait variation (e.g., site, across species, within species) which often use mixed linear modles and variance partitioning [e.g., @Messier2010; @Leps2011; @Siefert2015].
+However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV [i.g., @Albert2010a; @Bastias2017a; @Yang2020].
+This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estiamtes but those two estiamtes are usually not clarifeind in trait databases (e.g., TRY).
+Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV [@Yang2020].
+Future studies should include more samples to improve the comparisons of leaf disc and whole-leaf based ITV.
 

### 2022-05-13 ms/response_letter.Rmd
update ms

@@
 Thank you.
-We note that a key difference between leaf disc and whole-leaf LMA is that leaf disc LMA focuses on lamina rather than whole-leaf and usages depend on ecological contexts.
+We now note that a key difference between leaf disc and whole-leaf LMA is that leaf disc LMA focuses on lamina rather than whole-leaf and usages depend on ecological contexts.
+We also have mentioned the TRY database to explain LMA is the most often used leaf trait in TRY.
 
@@
 Thank you.
-(different levels of organization?)
 We have added columns to explain the number of species, the number of individuals, whether leaf thickness was measured, and leaf punch size in Table S1.
+We have also added detailed sampling protocol in Appendix S2.
 
@@
 
-- working
+Thank you.
+That is not a result but an explanation.
+Since we only measured 3 discs for each leaf in the Yunnan dataset, which is a common protocol, we cannot avoid the effect of variance within leaves.
+We have updated the text.
 
@@
 
-- working
+Thank you.
+The two panels share the x axis.
+Units are in the strip.
 
@@
 Thank you.
-** this should be somewhere else and not line 57**.
-We have cited it in XX.
+We have cited it in the context of "diminishing returns" in the discussion.
 
@@
 
-Thank you.
-We originally had this result to support grouping species into four categories, because if the correlation between leaf area and leaf thickness are too strong, we cannot group species into four categories based on median values of traits.
-As noted above, we removed the analysis of grouping species, and thus we also removed this result.
-
 > Lin, S., Shao, L., Hui, C., Song, Y., Reddy, G.V.P., Gielis, J., Li, F., Ding, Y., Wei, Q., Shi, P.
@@
 
+Thank you.
+We originally had this result to support grouping species into four categories, because if the correlation between leaf area and leaf thickness are too strong, we cannot group species into four categories based on median values of traits.
+As noted above, we removed the analysis of grouping species, and thus we also removed this result.
+
 > Line 171: "… were 9.4% greater than disc-based estimates …" Can you provide a standard deviation or a confidence interval for 9.4%? In general, we can use the bootstrap method to get it.
@@
 Thank you.
-We have added confidence intervals using bootstraps.
+We have added confidence intervals using bootstraps in the result section.

### 2022-05-13 ms/LMA_method.Rmd
update ms

@@
 
-# ABSTRACT
+# ABSTRACT (< 250 words, we need to remove 47 words!)
 
@@
 **METHODS:**
-We determined LMA using leaf discs and whole-leaf (including petiole) for `r val$all_sp` woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match, whether the differences in the estimates are associated with leaf size and thickness, and whether intraspecifc variation for each species match.
+We determined LMA using leaf discs and whole-leaf (including petiole) for `r val$all_sp` woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match,
+whether the relationship varied with leaf tissue density, leaf area, leaf thickness and leaf punch size (0.6-cm and 1.0-cm in diameter),
+and whether the extent of intraspecifc variation (ITV) for each species matches.
 
 **RESULTS:**
-Disc-based estimates of species and individual mean LMA matched well whole-leaf estimates.
-Thin and large leaves had weaker correlations between leaf disc and whole-leaf estimates.
-Variability of LMA estimates within species (i.e., amount of intraspecific variation) only weakly matched between whole-leaf and disc-based estimates (*R^2^* = `r val$cv_r2`).
-We also found that sample with small total dry mass of leaf discs tended to show greater differences between leaf disc and whole-leaf LMA.
+Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be higher than leaf disc LMA.
+The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
+Small leaf punch also inflated the whole-leaf to leaf disc LMA ratio.
+Variability of LMA estimates within species (i.e., extent of ITV) only weakly matched between whole-leaf and disc-based estimates (*R^2^* = `r val$cv_r2`).
 
 **CONCLUSIONS:**
-Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (9.4% differences in our samples), but their accuracy depends on leaf size, leaf thickness, and sizes of leaf punch.
-Therefore, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
-Quantifying trait variation using leaf disc should be considered with caution.
+Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (`r val$sma_per_all_mean`% differences in our samples), but their accuracy depends on leaf morphology, and sizes of leaf punch.
+Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
+Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
+Quantifying trait variation using leaf disc should be also considered with caution.
 
@@
 Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions [@Westerband2021].
+For example, shade leaves tend to have lower LMA than sun leaves because of fewer layers of palisade mesophyll cells [@Terashima2001; @Onoda2008].
 The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation [e.g., @Messier2010; @Kichenin2013; @Fajardo2018].
@@
 Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4% differences).
-Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration
-(
-OLS regressions:
-log~10~LMA~w~ = `r val$ols_int_log10` + `r val$ols_slope` $\times$ log~10~LMA~d~ or
-log~10~LMA~d~ = `r val$ols_slope_inv` $\times$ log~10~LMA~w~,
-where LMA~w~ and LMA~d~ are the whole-leaf and leaf disc LMA, respectively
-).
+Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
 However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
+
+*Effects of leaf punch size and leaf morphology*
 
@@
 2, Appendix SX), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
-Small leaf disc size inflates trait variation within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
+Small leaf disc size inflates trait varition within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
 Species with lower leaf tissue density and thin leaves showed greater variance in whole-leaf to leaf disc LMA ratio especially when a small punch was used (Fig.2ac: small leaf punch, Fig.
-2a: large leaf punch), suggesting that simple conversion between whole-leaf and leaf disc LMA is difficult for those species.
+2a: large leaf punch).
 @Kraft2008 found high *R^2^* values (*R^2^* = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves [@Kitajima2010; @Oktavia2020].
 Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
-The relatively low *R^2^* values for species with lower leaf tissue density and thin leaves in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset, may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendices SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance [@Poorter2009a], suggesting that leaf disc LMA and whole-leaf LMA can be inheretly different when small disc samples were used.
+The relatively low *R^2^* values in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
-Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig.
-2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
+Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig. 2ab: large leaf punch).
 We also observed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
@@
 
+*Conversion between whole-leaf and leaf disc LMA*
+
+When the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch (e.g., 1.0-cm in diameter) is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
+Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
+The effects of leaf tissue density and leaf area are predictable when we used a large leaf punch (Fig.
+2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
+OLS regressions with leaf area as a covariate as follwoing:
+(1) log~10~LMA~w~ = `r val$yaku2_slope_disc` $\times$ log~10~LMA~d~ + `r val$yaku2_slope_area` $\times$ log~10~LA,
+(2) log~10~LMA~d~ = `r val$yaku2_int_inv_log10` + `r val$yaku2_slope_inv_leaf` $\times$ log~10~LMA~w~  - 0.063  $\times$ log~10~LA (*R^2^* = `r val$yaku_r2_area`, *AIC* = `r val$yaku_aic_area`, *n* = `r val$yaku_sp`),
+where LMA~w~, LMA~d~, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
+OLS regressions without leaf area as a covariate as follwoing:
+(3) log~10~LMA~w~ = `r val$yaku_int_log10` + `r val$yaku_slope_disc` $\times$ log~10~LMA~d~ or
+(4) log~10~LMA~d~ = `r val$yaku_slope_inv_leaf` $\times$ log~10~LMA~w~
+(*R^2^* = `r val$yaku_r2_simple`, *AIC* = `r val$yaku_aic_simple`, *n* = `r val$yaku_sp`).
+Nonetheless, including leaf area only slighlty imporves the *R^2^* values for the Yakushima dataset where a large punch was used.
+This is because the large descripancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called "dimishing returns" [@Niklas2007] which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles [@Li2022], which is strong for mature leaves [@Jiao2022].
+The "dimishing returns" can be either descirbed as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
+When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to covert LMA values using one of the models above.
+
+*Intraspecific variation*
+
 Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig.
@@
 This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
-On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA.
+On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA as we expected.
 Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species *Alocasia macrorrhiza*, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions [@Li2013a].
@@
 However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV [i.g., @Albert2010a; @Bastias2017a; @Yang2020].
-This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estiamtes but those two estiamtes are usually not clarifeind in trait databases (e.g., TRY).
+This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarifeind in trait databases (e.g., TRY).
 Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV [@Yang2020].
@@
 
+*Conclusions*
+
 The present study was designed to examine the extent to which whole leaf and leaf disc LMA matched.
-Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA.
-However, larger and thinner leaves tended to show the large discrepancies between the leaf disc and whole-leaf estimates, and thus when one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis), appropriate calibrations are necessary.
-Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches are also the important sources of variance between whole-leaf and leaf disc LMA.
-This is probably because small dry mass inflates measurement errors and small leaf disc size inflates trait variation within leave.
-Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be large.
+Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches as well as leaf morphology are the important sources of variance between whole-leaf and leaf disc LMA.
+Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA when an appropriate size of leaf punch (e.g., 1.0-cm in diameter) was used.
+Thhose LMA values can be converted using OLS regressions.
+Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be considerably large but cannot be avoid for typical sampling numbers (2-3 discs per leaf).
 Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity [@Parry2002], because the photosynthetic activity occurs most in lamina rather than in veins for C~3~ plants [@Hibberd2002; @Gao2018].
 Leaf disc LMA is also the preferred method for quantifying leaf lamina density, which avoid effects of veins.
-However, if the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
+Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
 

### 2022-05-13 ms/LMA_method.tex
update ms

@@
 
-\hypertarget{abstract}{%
-\section{ABSTRACT}\label{abstract}}
+\hypertarget{abstract-250-words-we-need-to-remove-47-words}{%
+\section{ABSTRACT (\textless{} 250 words, we need to remove 47 words!)}\label{abstract-250-words-we-need-to-remove-47-words}}
 
@@
 \textbf{METHODS:}
-We determined LMA using leaf discs and whole-leaf (including petiole) for 334 woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match, whether the differences in the estimates are associated with leaf size and thickness, and whether intraspecifc variation for each species match.
+We determined LMA using leaf discs and whole-leaf (including petiole) for 334 woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match,
+whether the relationship varied with leaf tissue density, leaf area, leaf thickness and leaf punch size (0.6-cm and 1.0-cm in diameter),
+and whether the extent of intraspecifc variation (ITV) for each species matches.
 
 \textbf{RESULTS:}
-Disc-based estimates of species and individual mean LMA matched well whole-leaf estimates.
-Thin and large leaves had weaker correlations between leaf disc and whole-leaf estimates.
-Variability of LMA estimates within species (i.e., amount of intraspecific variation) only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.09).
-We also found that sample with small total dry mass of leaf discs tended to show greater differences between leaf disc and whole-leaf LMA.
+Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be higher than leaf disc LMA.
+The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
+Small leaf punch also inflated the whole-leaf to leaf disc LMA ratio.
+Variability of LMA estimates within species (i.e., extent of ITV) only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.09).
 
 \textbf{CONCLUSIONS:}
-Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (9.4\% differences in our samples), but their accuracy depends on leaf size, leaf thickness, and sizes of leaf punch.
-Therefore, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
-Quantifying trait variation using leaf disc should be considered with caution.
+Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (9.68\% differences in our samples), but their accuracy depends on leaf morphology, and sizes of leaf punch.
+Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
+Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
+Quantifying trait variation using leaf disc should be also considered with caution.
 
@@
 Intraspecific trait variation (ITV), which reflects both heritable genetic variation and phenotypic plasticity, influences plant responses to abiotic and biotic interactions (\protect\hyperlink{ref-Westerband2021}{Westerband et al., 2021}).
+For example, shade leaves tend to have lower LMA than sun leaves because of fewer layers of palisade mesophyll cells (\protect\hyperlink{ref-Terashima2001}{Terashima et al., 2001}; \protect\hyperlink{ref-Onoda2008}{Onoda et al., 2008}).
 The extent of ITV within and among communities for LMA can be similar to or greater than interspecific trait variation (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Kichenin2013}{Kichenin et al., 2013}; \protect\hyperlink{ref-Fajardo2018}{Fajardo and Siefert, 2018}).
@@
 First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
-Second, the Yakushima data is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
-In total, our data set comprised 334 woody species and 1365 individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
+Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
+In total, our dataset comprised 334 woody species and 1365 individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
 (\protect\hyperlink{ref-Song2017}{2017}); Fei et al.
@@
 
-Leaf disc LMA explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in Kraft et al.
-(\protect\hyperlink{ref-Kraft2008}{2008}), \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in Onoda et al.
-(\protect\hyperlink{ref-Onoda2011}{2011})).
+Leaf disc LMA explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
 Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4\% differences).
-Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration
-(
-OLS regressions:
-log\textsubscript{10}LMA\textsubscript{w} = 0.211 + 0.911 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
-log\textsubscript{10}LMA\textsubscript{d} = 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{w},
-where LMA\textsubscript{w} and LMA\textsubscript{d} are the whole-leaf and leaf disc LMA, respectively
-).
+Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
 However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
-Higher leaf tissue density is associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}), but this effect might be ignored in leaf disc LMA.
-Larger leaves generally invest disproportionally more mass into dense midribs and major veins for support (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Sack2012}{Sack et al., 2012}), and thinner leaves have distinct veins and have kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}).
-The effects of leaf morphology on the relationship between the whole-leaf LMA and leaf disc LMA were generally matched with our hyptheses, but the actual patterns were more complicated.
+
+\emph{Effects of leaf punch size and leaf morphology}
 
@@
 2, Appendix SX), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
-Small leaf disc size inflates trait variation within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
+Small leaf disc size inflates trait varition within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
 Species with lower leaf tissue density and thin leaves showed greater variance in whole-leaf to leaf disc LMA ratio especially when a small punch was used (Fig.2ac: small leaf punch, Fig.
-2a: large leaf punch), suggesting that simple conversion between whole-leaf and leaf disc LMA is difficult for those species.
+2a: large leaf punch).
 Kraft et al.
@@
 Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
-The relatively low \emph{R\textsuperscript{2}} values for species with lower leaf tissue density and thin leaves in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset, may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Fig.
-2; Appendices SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
-
-Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig.
-2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
+On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance (\protect\hyperlink{ref-Poorter2009a}{Poorter, 2009}), suggesting that leaf disc LMA and whole-leaf LMA can be inheretly different when small disc samples were used.
+The relatively low \emph{R\textsuperscript{2}} values in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) or distinct veins with kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+
+Species with higher leaf tissue density and large leaves showed greater whole-leaf LMA than leaf disc LMA (Fig. 2ab: large leaf punch).
 We also observed that leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
@@
 3b).
-This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}) and the pattern of higher leaf tissue density associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}) because those driving factors of LMA are likely to be ignored in leaf disc samples.
+This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Sack2012}{Sack et al., 2012}) and the pattern of higher leaf tissue density associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}) because those driving factors of LMA are likely to be ignored in leaf disc samples.
 The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appdendix SX), but those effects were not significant.
-This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates (\(\beta\)) when use a small leaf punch.
+This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates (\(\beta\) in Eq.
+2) when a small leaf punch was used.
+
+\emph{Conversion between whole-leaf and leaf disc LMA}
+
+When the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch (e.g., 1.0-cm in diameter) is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
+Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
+The effects of leaf tissue density and leaf area are predictable when we used a large leaf punch (Fig.
+2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
+OLS regressions with leaf area as a covariate as follwoing:
+(1) log\textsubscript{10}LMA\textsubscript{w} = 0.997 \(\times\) log\textsubscript{10}LMA\textsubscript{d} + 0.0589 \(\times\) log\textsubscript{10}LA,
+(2) log\textsubscript{10}LMA\textsubscript{d} = 0.15 + 0.945 \(\times\) log\textsubscript{10}LMA\textsubscript{w} - 0.063 \(\times\) log\textsubscript{10}LA (\emph{R\textsuperscript{2}} = 0.94, \emph{AIC} = -321.7, \emph{n} = 193),
+where LMA\textsubscript{w}, LMA\textsubscript{d}, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
+OLS regressions without leaf area as a covariate as follwoing:
+(3) log\textsubscript{10}LMA\textsubscript{w} = 0.124 + 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
+(4) log\textsubscript{10}LMA\textsubscript{d} = 0.973 \(\times\) log\textsubscript{10}LMA\textsubscript{w}
+(\emph{R\textsuperscript{2}} = 0.93, \emph{AIC} = -284.2, \emph{n} = 193).
+Nonetheless, including leaf area only slighlty imporves the \emph{R\textsuperscript{2}} values for the Yakushima dataset where a large punch was used.
+This is because the large descripancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called ``dimishing returns'' (\protect\hyperlink{ref-Niklas2007}{Niklas et al., 2007}) which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles (\protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}), which is strong for mature leaves (\protect\hyperlink{ref-Jiao2022}{Jiao et al., 2022}).
+The ``dimishing returns'' can be either descirbed as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
+When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to covert LMA values using one of the models above.
+
+\emph{Intraspecific variation}
 
@@
 This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
+On average, ITV based on leaf disc LMA was greater than ITV based on whole-leaf LMA as we expected.
 Although there are not many studies that quantified trait variation within a single leaf, a previous study that used a giant leaved species \emph{Alocasia macrorrhiza}, suggests that LMA varied within leaves due to reduced water supply and demand from midrib to outer regions (\protect\hyperlink{ref-Li2013a}{Li et al., 2013}).
@@
 Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
-This is consistent with the \emph{R\textsuperscript{2}} values in our results (Figs. 1-3).
-The mismatch of ITV between whole-leaf and disc-based estimate could be ignored in community-level ITV studies (i.e., \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}), which quantify the total variance of ITV within communities.
-However, it is likely to change patterns for species-level ITV studies (i.e., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}), which quantify extents of ITV for each species, since species with high ITV based on leaf-disc estimates do not always have to show high ITV for whole-leaf estimates.
-This problem will be more obvious when one uses smaller leaf punches (Appendix S7).
+The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to detemine sources of trait variation (e.g., site, across species, within species) which often use mixed linear modles and variance partitioning (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Leps2011}{Lepš et al., 2011}; \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}).
+However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV (i.g., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}; \protect\hyperlink{ref-Bastias2017a}{Bastias et al., 2017}; \protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
+This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarifeind in trait databases (e.g., TRY).
+Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
+Future studies should include more samples to improve the comparisons of leaf disc and whole-leaf based ITV.
+
+\emph{Conclusions}
 
 The present study was designed to examine the extent to which whole leaf and leaf disc LMA matched.
-Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA.
-However, larger and thinner leaves tended to show the large discrepancies between the leaf disc and whole-leaf estimates, and thus when one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis), appropriate calibrations are necessary.
-Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches are also the important sources of variance between whole-leaf and leaf disc LMA.
-This is probably because small dry mass inflates measurement errors and small leaf disc size inflates trait variation within leave.
-Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be large.
+Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches as well as leaf morphology are the important sources of variance between whole-leaf and leaf disc LMA.
+Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA when an appropriate size of leaf punch (e.g., 1.0-cm in diameter) was used.
+Thhose LMA values can be converted using OLS regressions.
+Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be considerably large but cannot be avoid for typical sampling numbers (2-3 discs per leaf).
 Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity (\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because the photosynthetic activity occurs most in lamina rather than in veins for C\textsubscript{3} plants (\protect\hyperlink{ref-Hibberd2002}{Hibberd and Quick, 2002}; \protect\hyperlink{ref-Gao2018}{Gao et al., 2018}).
 Leaf disc LMA is also the preferred method for quantifying leaf lamina density, which avoid effects of veins.
-However, if the objective is to use leaf disc LMA as an alternative for whole-leaf LMA, using an appropriate size of leaf punch is important for obtaining stable estimates of leaf disc LMA that matches well with whole-leaf LMA.
+Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Bastias2017a}{}}%
+Bastias, C.
+C., C.
+Fortunel, F.
+Valladares, C.
+Baraloto, R.
+Benavides, W.
+Cornwell, L.
+Markesteijn, et al.
+2017.
+\href{https://doi.org/10.1371/journal.pone.0172495}{Intraspecific leaf trait variability along a boreal-to-tropical community diversity gradient}.
+\emph{PLOS ONE} 12: 1--16.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Campany2021}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Jiao2022}{}}%
+Jiao, Y., K.
+J.
+Niklas, L.
+Wang, K.
+Yu, Y.
+Li, and P.
+Shi.
+2022.
+Influence of leaf age on the scaling relationships of lamina biomass vs.
+Area in {Photinia}\texttimes{} fraseri'{Red Robin}'.
+\emph{Frontiers in Plant Science} 13: 860206.
+
 \leavevmode\vadjust pre{\hypertarget{ref-John2017}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Leps2011}{}}%
+Lepš, J., F.
+de Bello, P.
+Šmilauer, and J.
+Doležal.
+2011.
+\href{https://doi.org/10.1111/j.1600-0587.2010.06904.x}{Community trait response to environment: {Disentangling} species turnover vs intraspecific trait variability effects}.
+\emph{Ecography} 34: 856--863.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Li2013a}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Niklas2007}{}}%
+Niklas, K.
+J., E.
+D.
+Cobb, Ü.
+Niinemets, P.
+B.
+Reich, A.
+Sellin, B.
+Shipley, and Ian J.
+Wright.
+2007.
+\href{https://doi.org/10.1073/pnas.0701135104}{"{Diminishing} returns" in the scaling of functional leaf traits across and within species groups}.
+\emph{Proceedings of the National Academy of Sciences} 104: 8891--8896.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Oktavia2020}{}}%
@@
 \emph{Basic and Applied Ecology} 49: 22--33.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Onoda2008}{}}%
+Onoda, Y., F.
+Schieving, and N.
+P.
+R.
+Anten.
+2008.
+\href{https://doi.org/10.1093/aob/mcn013}{Effects of light and nutrient availability on leaf mechanical properties of {Plantago} major: {A} conceptual approach}.
+\emph{Annals of Botany} 101: 727--736.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Terashima2001}{}}%
+Terashima, I., S.-I.
+Miyazawa, and Y.
+T.
+Hanba.
+2001.
+\href{https://doi.org/10.1007/PL00013972}{Why are {Sun Leaves Thicker} than {Shade Leaves}?
+\textemdash{} {Consideration} based on {Analyses} of {CO2 Diffusion} in the {Leaf}}.
+\emph{Journal of Plant Research} 114: 93--105.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Warton2012a}{}}%

### 2022-05-13 ms/LMA_method.Rmd
fix typo

@@
 If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates [@Kraft2008; @Onoda2011].
-If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low *R^2^* values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
+If divergences between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low *R^2^* values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
 To date, however, only a database from a single region, Panama Plant Traits Database [@Wright2010], is available in the TRY [@Kattge2020] that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.
@@
 
-We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
-First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
+We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
+First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
 Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
 In total, our dataset comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
-The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.
+The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe below.
 
@@
 In the HDS, and STF sites, we used a 12-m long pruner to collect samples for most of the target species.
-In case of tall individuals that out of the reach of pruner, we used a rope climbing to reach the canopy, then sampled branches with the long pruner.
+In the case of tall individuals that were out of the reach of pruners, we used rope climbing to reach the canopy, then sampled branches with the long pruner.
 In Yakushima, we used 15-m poles for our leaf sampling.
@@
 Trait values were averaged at the species- and individual-level for the analyses.
-For compound-leaved species, we referred a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
+For compound-leaved species, we referred to a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
 We excluded species that had tiny leaves or leaflets (length <1 cm) because it was not practical to measure leaf disc LMA.
@@
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Appendix S2 for more details).
+Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S2 for more details).
 Fresh leaf area (LA; cm^-2^) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package *LeafArea* [@Katabuchi2015].
@@
 
-We also perfomred ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
+We also performed ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
 
-*Relationship between disc-based and whole-leaf estiamtes of intraspecific variation*
+*Relationship between disc-based and whole-leaf estimates of intraspecific variation*
 
@@
 Bao's CV estimator is a robust method to quantify ITV based on a coefficient of variation (CV) when sample size is small [@Yang2020].
-We calulcated CV for species that have at least 5 indivdiuals as recommended in @Westerband2021.
+We calculated CV for species that have at least 5 individuals as recommended in @Westerband2021.
 Ideally, 20 individuals for each species are required for robust estimation of CV [i.e., <5% differences from the true ITV; @Yang2020].
@@
 SMA analyses were run as described above.
-We also perfmoed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
+We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
 All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022].
@@
 Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
-Species with lower leaf tissue density had greater variance in the estiamte of whole-leaf to leaf disc LMA ratio (Fig. 2a).
+Species with lower leaf tissue density had greater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a).
 When a small leaf punch was used, this pattern was more pronounced and leaf disc and whole-leaf LMA estimate diverged for species with higher leaf tissue density (Fig. 2a).
-Species with larger leaves had greater estimate of the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2b), which was only significant for leaves obtained by a large punch.
-Species with thinner leaves had grater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
+Species with larger leaves had greater estimate for the whole-leaf to leaf disc LMA ratio (Fig. 2b), which was only significant for leaves obtained by a large punch.
+Species with thinner leaves had greater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
 A small punch also inflated variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a-c and Appendix SX).
@@
 The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4).
-Altough there were no stiatical differences in the SMA slope or elevation (SMA slope: `r val$sma_slope_cv_mean` [95%CI: `r val$sma_slope_cv_lwr`, `r val$sma_slope_cv_upr`], SMA intercept: `r val$sma_int_cv_mean` [95%CI: `r val$sma_int_cv_lwr`, `r val$sma_int_cv_upr`]), leaf disc LMA had greater CVs than whole-leaf LMA (*t* = `r val$t_test_t`, *d.f.* = `r val$t_test_df`, *P* < 0.001).
+Although there were no statistical differences in the SMA slope or elevation (SMA slope: `r val$sma_slope_cv_mean` [95%CI: `r val$sma_slope_cv_lwr`, `r val$sma_slope_cv_upr`], SMA intercept: `r val$sma_int_cv_mean` [95%CI: `r val$sma_int_cv_lwr`, `r val$sma_int_cv_upr`]), leaf disc LMA had greater CVs than whole-leaf LMA (*t* = `r val$t_test_t`, *d.f.* = `r val$t_test_df`, *P* < 0.001).
 
@@
 @Kraft2008 found high *R^2^* values (*R^2^* = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves [@Kitajima2010; @Oktavia2020].
-Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
-On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance [@Poorter2009a], suggesting that leaf disc LMA and whole-leaf LMA can be inheretly different when small disc samples were used.
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Appendix SX).
+On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance [@Poorter2009a], suggesting that leaf disc LMA and whole-leaf LMA can be inherently different when small disc samples were used.
 The relatively low *R^2^* values in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
@@
 This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles [@Niinemets2006; @Niinemets2007; @Sack2012] and the pattern of higher leaf tissue density associated with higher vein density [@John2017; @Sancho-Knapik2020] because those driving factors of LMA are likely to be ignored in leaf disc samples.
-The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appdendix SX), but those effects were not significant.
-This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates ($\beta$ in Eq.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix SX), but those effects were not significant.
+This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean estimates ($\beta$ in Eq.
 2) when a small leaf punch was used.
@@
 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
-OLS regressions with leaf area as a covariate as follwoing:
+OLS regressions with leaf area as a covariate as following:
 (1) log~10~LMA~w~ = `r val$yaku2_slope_disc` $\times$ log~10~LMA~d~ + `r val$yaku2_slope_area` $\times$ log~10~LA,
@@
 where LMA~w~, LMA~d~, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
-OLS regressions without leaf area as a covariate as follwoing:
+OLS regressions without leaf area as a covariate as following:
 (3) log~10~LMA~w~ = `r val$yaku_int_log10` + `r val$yaku_slope_disc` $\times$ log~10~LMA~d~ or
@@
 (*R^2^* = `r val$yaku_r2_simple`, *AIC* = `r val$yaku_aic_simple`, *n* = `r val$yaku_sp`).
-Nonetheless, including leaf area only slighlty imporves the *R^2^* values for the Yakushima dataset where a large punch was used.
-This is because the large descripancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called "dimishing returns" [@Niklas2007] which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles [@Li2022], which is strong for mature leaves [@Jiao2022].
-The "dimishing returns" can be either descirbed as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
-When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to covert LMA values using one of the models above.
+Nonetheless, including leaf area only slightly improves the *R^2^* values for the Yakushima dataset where a large punch was used.
+This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called "diminishing returns" [@Niklas2007] which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles [@Li2022], which is strong for mature leaves [@Jiao2022].
+The "diminishing returns" can be either described as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
+When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to convert LMA values using one of the models above.
 
@@
 Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
-The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to detemine sources of trait variation (e.g., site, across species, within species) which often use mixed linear modles and variance partitioning [e.g., @Messier2010; @Leps2011; @Siefert2015].
+The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to determine sources of trait variation (e.g., site, across species, within species) which often use mixed linear models and variance partitioning [e.g., @Messier2010; @Leps2011; @Siefert2015].
 However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV [i.g., @Albert2010a; @Bastias2017a; @Yang2020].
-This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarifeind in trait databases (e.g., TRY).
+This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarified in trait databases (e.g., TRY).
 Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV [@Yang2020].
@@
 Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA when an appropriate size of leaf punch (e.g., 1.0-cm in diameter) was used.
-Thhose LMA values can be converted using OLS regressions.
-Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be considerably large but cannot be avoid for typical sampling numbers (2-3 discs per leaf).
+Those LMA values can be converted using OLS regressions.
+Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be considerably large but cannot be avoided with the typical sampling numbers (2-3 discs per leaf).
 Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity [@Parry2002], because the photosynthetic activity occurs most in lamina rather than in veins for C~3~ plants [@Hibberd2002; @Gao2018].

### 2022-05-13 ms/LMA_method.tex
fix typo

@@
 If leaf disc LMA largely and consistently underestimates whole-leaf LMA (i.e., differences in means), some calibrations may be required to combine or compare those different estimates (\protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
-If divergencies between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low \emph{R\textsuperscript{2}} values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
+If divergences between the estimates based on the different methods are large and inconsistent (i.e., differences in variances and low \emph{R\textsuperscript{2}} values), this is difficult to calibrate and should inflate errors in the subsequent analyses.
 To date, however, only a database from a single region, Panama Plant Traits Database (\protect\hyperlink{ref-Wright2010}{Wright et al., 2010}), is available in the TRY (\protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020}) that have both estimates of LMA from small leaf discs and whole leaves including petioles, limiting of our understanding of under what conditions estimates of LMA from leaf discs are reliable estimates of whole-leaf LMA.
@@
 
-We used newly compiled individual-level plant datasets form a wide ranges of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
-First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rain forest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
+We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
+First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
 Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
@@
 (\protect\hyperlink{ref-Fei2018}{2018}){]}, which covers the wide climate ranges in the distribution of broad-leaved tree species.
-The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe bellow.
+The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe below.
 
@@
 Trait values were averaged at the species- and individual-level for the analyses.
-For compound-leaved species, we referred a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
+For compound-leaved species, we referred to a leaflet (the minimum photosynthetic unit) as a single leaf in our study.
 We excluded species that had tiny leaves or leaflets (length \textless1 cm) because it was not practical to measure leaf disc LMA.
@@
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf were in the Yakushima dataset (see Appendix S2 for more details).
+Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S2 for more details).
 Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
@@
 
-We also perfomred ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
-
-\emph{Relationship between disc-based and whole-leaf estiamtes of intraspecific variation}
+We also performed ordinary least-squares (OLS) regressions to see the relationship between whole-leaf to leaf disc LMA ratio and petiole to leaf dry mass ratio and between leaf area petiole to leaf dry mass ratio, using a subset of the dataset in which we measured leaf lamina and petiole dry mass separately.
+
+\emph{Relationship between disc-based and whole-leaf estimates of intraspecific variation}
 
@@
 Bao's CV estimator is a robust method to quantify ITV based on a coefficient of variation (CV) when sample size is small (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
-We calulcated CV for species that have at least 5 indivdiuals as recommended in Westerband et al. (\protect\hyperlink{ref-Westerband2021}{2021}).
+We calculated CV for species that have at least 5 individuals as recommended in Westerband et al. (\protect\hyperlink{ref-Westerband2021}{2021}).
 Ideally, 20 individuals for each species are required for robust estimation of CV {[}i.e., \textless5\% differences from the true ITV; Yang et al. (\protect\hyperlink{ref-Yang2020}{2020}){]}.
@@
 SMA analyses were run as described above.
-We also perfmoed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
+We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
 All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}).
@@
 The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4).
-Altough there were no stiatical differences in the SMA slope or elevation (SMA slope: 1.116 {[}95\%CI: 0.954, 1.304{]}, SMA intercept: 0.102 {[}95\%CI: -0.174, 0.377{]}), leaf disc LMA had greater CVs than whole-leaf LMA (\emph{t} = -3.19, \emph{d.f.} = 144, \emph{P} \textless{} 0.001).
+Although there were no statistical differences in the SMA slope or elevation (SMA slope: 1.116 {[}95\%CI: 0.954, 1.304{]}, SMA intercept: 0.102 {[}95\%CI: -0.174, 0.377{]}), leaf disc LMA had greater CVs than whole-leaf LMA (\emph{t} = -3.19, \emph{d.f.} = 144, \emph{P} \textless{} 0.001).
 
@@
 (\protect\hyperlink{ref-Kraft2008}{2008}) found high \emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves (\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010}; \protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}).
-Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardress of leaf tissue density or leaf thickness (Appendix SX).
-On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance (\protect\hyperlink{ref-Poorter2009a}{Poorter, 2009}), suggesting that leaf disc LMA and whole-leaf LMA can be inheretly different when small disc samples were used.
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Appendix SX).
+On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance (\protect\hyperlink{ref-Poorter2009a}{Poorter, 2009}), suggesting that leaf disc LMA and whole-leaf LMA can be inherently different when small disc samples were used.
 The relatively low \emph{R\textsuperscript{2}} values in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) or distinct veins with kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
@@
 This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Sack2012}{Sack et al., 2012}) and the pattern of higher leaf tissue density associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}) because those driving factors of LMA are likely to be ignored in leaf disc samples.
-The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appdendix SX), but those effects were not significant.
-This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean etimates (\(\beta\) in Eq.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix SX), but those effects were not significant.
+This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean estimates (\(\beta\) in Eq.
 2) when a small leaf punch was used.
@@
 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
-OLS regressions with leaf area as a covariate as follwoing:
+OLS regressions with leaf area as a covariate as following:
 (1) log\textsubscript{10}LMA\textsubscript{w} = 0.997 \(\times\) log\textsubscript{10}LMA\textsubscript{d} + 0.0589 \(\times\) log\textsubscript{10}LA,
@@
 where LMA\textsubscript{w}, LMA\textsubscript{d}, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
-OLS regressions without leaf area as a covariate as follwoing:
+OLS regressions without leaf area as a covariate as following:
 (3) log\textsubscript{10}LMA\textsubscript{w} = 0.124 + 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
@@
 (\emph{R\textsuperscript{2}} = 0.93, \emph{AIC} = -284.2, \emph{n} = 193).
-Nonetheless, including leaf area only slighlty imporves the \emph{R\textsuperscript{2}} values for the Yakushima dataset where a large punch was used.
-This is because the large descripancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called ``dimishing returns'' (\protect\hyperlink{ref-Niklas2007}{Niklas et al., 2007}) which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles (\protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}), which is strong for mature leaves (\protect\hyperlink{ref-Jiao2022}{Jiao et al., 2022}).
-The ``dimishing returns'' can be either descirbed as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
-When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to covert LMA values using one of the models above.
+Nonetheless, including leaf area only slightly improves the \emph{R\textsuperscript{2}} values for the Yakushima dataset where a large punch was used.
+This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called ``diminishing returns'' (\protect\hyperlink{ref-Niklas2007}{Niklas et al., 2007}) which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles (\protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}), which is strong for mature leaves (\protect\hyperlink{ref-Jiao2022}{Jiao et al., 2022}).
+The ``diminishing returns'' can be either described as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
+When one needs to mix leaf disc LMA and whole-leaf LMA in a single analysis (e.g., meta-analysis) or quickly measure leaf disc LMA as a proxy for whole-leaf LMA, we recommend to convert LMA values using one of the models above.
 
@@
 Thus, leaf disc and whole-leaf estimates of species means will show the strongest relationship.
-The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to detemine sources of trait variation (e.g., site, across species, within species) which often use mixed linear modles and variance partitioning (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Leps2011}{Lepš et al., 2011}; \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}).
+The mismatch of ITV between whole-leaf and disc-based estimates could be ignored in the type of ITV studies that attempt to determine sources of trait variation (e.g., site, across species, within species) which often use mixed linear models and variance partitioning (e.g., \protect\hyperlink{ref-Messier2010}{Messier et al., 2010}; \protect\hyperlink{ref-Leps2011}{Lepš et al., 2011}; \protect\hyperlink{ref-Siefert2015}{Siefert et al., 2015}).
 However, it is likely to change patterns significantly in the type of ITV studies that attempt to quantify the extent of ITV which usually use CV (i.g., \protect\hyperlink{ref-Albert2010a}{Albert et al., 2010}; \protect\hyperlink{ref-Bastias2017a}{Bastias et al., 2017}; \protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
-This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarifeind in trait databases (e.g., TRY).
+This caveat might apply to other leaf chemical traits such as leaf N contents because those traits have both disc and whole-leaf based estimates but those two estimates are usually not clarified in trait databases (e.g., TRY).
 Since we used limited sample numbers (at least 5 samples per species) and most of them were obtained with a small punch, our study design may inflate errors in estimating ITV (\protect\hyperlink{ref-Yang2020}{Yang et al., 2020}).
@@
 Our study shows that mean values of leaf disc LMA is generally a good proxy for mean values of whole-leaf LMA when an appropriate size of leaf punch (e.g., 1.0-cm in diameter) was used.
-Thhose LMA values can be converted using OLS regressions.
-Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be considerably large but cannot be avoid for typical sampling numbers (2-3 discs per leaf).
+Those LMA values can be converted using OLS regressions.
+Additionally, although the mean values of leaf disc and whole-leaf LMA matched well, quantifying trait variation using leaf discs should be considered with caution, because variation among leaf discs within the same leaves (including measurement errors) seems to be considerably large but cannot be avoided with the typical sampling numbers (2-3 discs per leaf).
 Leaf discs, which can target leaf lamina avoiding leaf veins, are useful and essential for biochemical determinations such as measurements of Rubisco activity (\protect\hyperlink{ref-Parry2002}{Parry et al., 2002}), because the photosynthetic activity occurs most in lamina rather than in veins for C\textsubscript{3} plants (\protect\hyperlink{ref-Hibberd2002}{Hibberd and Quick, 2002}; \protect\hyperlink{ref-Gao2018}{Gao et al., 2018}).

### 2022-05-13 ms/SI.Rmd
add cv analysis
add ratio_dm

--- 2022-05-07 ms/SI.Rmd
@@
 MAP: mean annual precipitation,
-SPEI: Standardized Precipitation Evapotranspiration Index.
+CV: coefficient variance
 
@@
 
-The site information and climate data referred to @Fei2018 and @Song2017.
-The 6-month-SPEI data were extracted from the Global SPEI database (http://spei.csic.es/map/maps.html#months=1#month=7#year=2019).
-
-\newpage
-
-**Fig. SX.**
-Standardized regression coefficients modelig the effects of leaf tissue density,
-leaf area,
-leaf thickness,
-punch size, and
-their interactios
-(a) on the mean estimates of whole-leaf LMA, and
-(b) on the estimated variance of whole-leaf LMA.
-The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
-Thick and thin lines indicate 90% and 95% credible intervals, respectively.
-Circles show posterior means of coefficients.
-Circles filled with blue indicate significant effects and white indicate non-significance effects.
-
-```{r, incude=FALSE}
-targets::tar_load(coef_sp_punch1_add_plot)
-```
-
-![](../figs/coef_sp_punch1_add.png)
+The site information and climate data in Yunnan, referred to @Fei2018, and @Song2017.
+MAT and MAP at the lower elevation (37 m) on Yakushima were obtained from the Yakushima meteorological stationj.
+MAT at the higher elevation (1800 m) on Yakushima was obtained from @Eguchi2006.
 
@@
 # Appendix S2:
+
+Detailed sampling protocol for whole-leaf and leaf disc LMA.
+
+![](../figs/S2.jpeg)
+
+\newpage
+
+# Appendix S3:
 
@@
 
-# Appendix S3:
+# Appendix S4:
 
-Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and (c) leaf area.
-(b) and (c) follow the same legend.
-All the relationships were heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together in (a)).
-Samples with small total dry mass, thin leaves, and larger leaves tended to show greater variance.
+Standardized regression coefficients modelig the effects of leaf tissue density,
+leaf area,
+leaf thickness,
+punch size, and
+their interactios
+(a) on the mean estimates of whole-leaf LMA, and
+(b) on the estimated variance of whole-leaf LMA.
+The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
+Thick and thin lines indicate 90% and 95% credible intervals, respectively.
+Circles show posterior means of coefficients.
+Circles filled with blue indicate significant effects and white indicate non-significance effects.
+
+```{r, incude=FALSE}
+targets::tar_load(coef_sp_punch1_add_plot)
+```
+
+![](../figs/coef_sp_punch1_add.png)
+
+\newpage
+
+# Appendix S5:
+
+Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
+The relationships was heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together).
+Samples with small total dry mass tended to show greater variance.
 
@@
 
-# Appendix S4:
+# Appendix S6:
 
-Summary of multiple regression for log-transformed total dry mass of leaf discs.
-The leaf punch size is described as an effect of '1.0 cm diameter' compared with '0.6 cm diameter'.
+Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
+Species was used as a random intercept.
+The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter.
 
-```{r, eval=FALSE, echo=FALSE}
-tar_load(dm_lm_tab)
-dm_lm_tab |>
+```{r, eval=TRUE, echo=FALSE}
+tar_load(dm_glmm_tab)
+dm_glmm_tab |>
   kable(format = "html") |>
@@
 
-# Appendix S5:
+# Appendix S7:
 
@@
 
-![](../figs/lalt_sep_grid.png){ width="600" style="display: block; margin: 0 auto" }
-
-# Appendix S6:
-
-Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
-Blue solid lines indicate ordinary least squares (OLS) regressions.
-The 95% confidence intervals are presented as the shaded area.
-All the correlations are significant (*P* < 0.001).
-
-![](../figs/petiole.png){ width="600" style="display: block; margin: 0 auto" }
-
-\newpage
-
-# Appendix S7:
-
-Relationships between coefficient of variation (CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and (b) 1.0 cm diameter leaf punch.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis regressions.
-The 95% confidence intervals are presented as the shaded area.
-All the correlations are significant (*P* < 0.01).
-Note that the axes are square root scales.
-
-![](../figs/cv_sep.png){ width="600" style="display: block; margin: 0 auto" }
+![](../figs/sma_grid_col3.png){ width="600" style="display: block; margin: 0 auto" }
 

### 2022-05-13 _targets.R

@@ -28,7 +28,8 @@ tar_option_set(packages = c(
   "loo",
   "modelr",
   "performance",
-  "jsonlite"
+  "jsonlite",
+  "lmtest"
 ))
 
 # check if it's inside a container
@@ -780,6 +781,20 @@ list(
     },
     format = "file"
   ),
+  tar_target(
+    ratio_dm_plot, {
+      p <- ratio_dm(tree)
+      ggsave(
+        "figs/ratio_dm.png",
+        p,
+        dpi = 300,
+        width = 3,
+        height = 3
+      )
+      paste0("figs/ratio_dm", c(".png"))
+    },
+    format = "file"
+  ),
 
   tar_target(
     lma_ld_plot, {
@@ -883,8 +898,8 @@ list(
   ),
 
   tar_target(
-    dm_lm_tab,
-    dm_lm(tree)
+    dm_glmm_tab,
+    dm_glmm(tree)
   ),
   tar_render(
     report,

### 2022-05-13 report.Rmd
add ratio_dm
add table

@@
 
+## punch
+
+```{r, eval=TRUE}
+tar_load(sma_tab_large)
+sma_tab_large |>
+  kable() |>
+  kable_styling()
+```
+
+```{r, eval=TRUE}
+tar_load(sma_tab_small)
+sma_tab_small |>
+  kable() |>
+  kable_styling()
+```
+
 ## species
@@
 ```
+
 ```{r}
@@
 
+# DM and HDK
+
+```{r}
+tar_load(tree)
+fit <- lm(log(lma_leaf / lma_disc) ~ log(dry_mass_disc), tree)
+lmtest::bptest(fit)
+```
+
 # Computing Environment

### 2022-05-13 _targets.R

@@ -26,8 +26,6 @@ tar_option_set(packages = c(
   "janitor",
   "extrafont",
   "loo",
-  "modelr",
-  "performance",
   "jsonlite",
   "lmtest"
 ))
@@ -677,6 +675,19 @@ list(
       paste0("figs/sma", c(".png"))
     },
     format = "file"
+  ),
+
+  tar_target(
+    sma_tab_large,
+    generate_sma_2_tab(
+      sp_mean |> filter(location == "Yakushima")
+    )
+  ),
+  tar_target(
+    sma_tab_small,
+    generate_sma_2_tab(
+      sp_mean |> filter(location != "Yakushima")
+    )
   ),
 
 

### 2022-05-13 ms/SI.Rmd
add table
update SI

@@
 
+Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
+Dashed lines indicate 1:1 lines.
+Blue solid lines indicate standardized major axis (SMA) regressions.
+The 95% confidence intervals are resented as the shaded area.
+The correlation is significant (*P* < 0.001).
+
+![](../figs/sma_sep.png){ width="400" style="display: block; margin: 0 auto" }
+
+\newpage
+
+# Appendix S6:
+
 Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
@@
 
-![](../figs/ratio.png){style="display: block; margin: 0 auto" }
+![](../figs/ratio_dm.png){ width="400" style="display: block; margin: 0 auto" }
 
@@
 
-# Appendix S6:
+# Appendix S7:
 
@@
 \newpage
-
-# Appendix S7:
-
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
-Species groups are divided into four categories on the basis of the medians of the leaf size and leaf thickness across all the species.
-Estimates obtained by different leaf punches are plotted separately in different colors.
-All the correlations are significant (*P* < 0.001).
-
-![](../figs/sma_grid_col3.png){ width="600" style="display: block; margin: 0 auto" }
-
-\newpage
 # LITERATURE CITED

### 2022-05-13 R/ind_analysis.R

@@ -63,7 +63,7 @@ ratio_dm <- function(tree) {
     geom_hline(yintercept = 1) +
     scale_color_manual(
       values = my_col[c(2, 4)],
-      name = "Diameter of the leaf punch"
+      name = "Leaf punch diameter"
     ) +
     xlab("Total dry mass of leaf disc (g)") +
     ylab("Whole-leaf LMA / leaf disc LMA") +

### 2022-05-13 _targets.R

@@ -676,6 +676,20 @@ list(
     },
     format = "file"
   ),
+  tar_target(
+    sma_sep_plot, {
+      p <- sma_point_sep(sp_mean)
+      ggsave(
+        "figs/sma_sep.png",
+        p,
+        dpi = 300,
+        width = 4,
+        height = 4
+      )
+      paste0("figs/sma_sep", c(".png"))
+    },
+    format = "file"
+  ),
 
   tar_target(
     sma_tab_large,

### 2022-05-13 ms/SI.Rmd
typo

@@
 MAP: mean annual precipitation,
-CV: coefficient variance
+CV: coefficient of variation
 
@@
 Species was used as a random intercept.
-The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter.
+The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
 

### 2022-05-13 ms/LMA_method.Rmd

@@
 
-# ABSTRACT (< 250 words, we need to remove 47 words!)
+# ABSTRACT
 
@@
 **METHODS:**
-We determined LMA using leaf discs and whole-leaf (including petiole) for `r val$all_sp` woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match,
-whether the relationship varied with leaf tissue density, leaf area, leaf thickness and leaf punch size (0.6-cm and 1.0-cm in diameter),
-and whether the extent of intraspecifc variation (ITV) for each species matches.
+We examined to what extent whole-leaf and disc-based LMA match using 334 woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate),
+whether the relationship varied by leaf morphology (tissue density, leaf area, leaf thickness), puncher size (0.6- and 1.0-cm diameter), and
+whether the extent of intraspecifc variation (ITV) for each species matches.
 
 **RESULTS:**
-Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be higher than leaf disc LMA.
+Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be `r val$sma_per_all_mean`% higher than leaf disc LMA.
 The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
-Small leaf punch also inflated the whole-leaf to leaf disc LMA ratio.
-Variability of LMA estimates within species (i.e., extent of ITV) only weakly matched between whole-leaf and disc-based estimates (*R^2^* = `r val$cv_r2`).
+Small leaf punch also inflated the ratio.
+The extent of ITV only weakly matched between whole-leaf and disc-based estimates (*R^2^* = `r val$cv_r2`).
 
 **CONCLUSIONS:**
-Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (`r val$sma_per_all_mean`% differences in our samples), but their accuracy depends on leaf morphology, and sizes of leaf punch.
-Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
+Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch, but it should be possible for species obtained with a large leaf punch.
 Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
-Quantifying trait variation using leaf disc should be also considered with caution.
+Quantifying ITV using leaf disc should be also considered with caution.
 
@@
 Based on those measurements of whole-leaf and leaf disc samples, LMA (g m^-2^) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
+We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S3).
 
@@
 Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan [@Carpenter2017] using the weakly-informative priors [@Gelman2008].
-See Appendix SX for more detail.
 The Stan code use to fit models is available from Github at: [https://github.com/mattocci27/leaf-disc](https://github.com/mattocci27/leaf-disc).
@@
 
-Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
+Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S4).
 Species with lower leaf tissue density had greater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a).
@@
 Species with thinner leaves had greater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
-A small punch also inflated variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a-c and Appendix SX).
+A small punch also inflated variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a-c and Appendix S4).
 Leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
@@
 Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
-However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix SX).
+However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S4).
 
@@
 The effect of leaf punch size was the most important source of the variation (Fig.
-2, Appendix SX), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
+2, Appendix S4), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
 Small leaf disc size inflates trait varition within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
@@
 @Kraft2008 found high *R^2^* values (*R^2^* = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves [@Kitajima2010; @Oktavia2020].
-Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Appendix SX).
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Fig.
+2ac).
 On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance [@Poorter2009a], suggesting that leaf disc LMA and whole-leaf LMA can be inherently different when small disc samples were used.
-The relatively low *R^2^* values in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+The relatively low *R^2^* values in the Yunnan dataset (Appendix S5) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S6), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S7), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
@@
 This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles [@Niinemets2006; @Niinemets2007; @Sack2012] and the pattern of higher leaf tissue density associated with higher vein density [@John2017; @Sancho-Knapik2020] because those driving factors of LMA are likely to be ignored in leaf disc samples.
-The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix SX), but those effects were not significant.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix S4), but those effects were not significant.
 This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean estimates ($\beta$ in Eq.
@@
 **APPENDIX S2.**
+Detailed sampling protocol for whole-leaf and leaf disc LMA.
+
+**APPENDIX S3.**
 Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
 
-**APPENDIX S3.**
-Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and (c) leaf area.
-
 **APPENDIX S4.**
-Summary of multiple regression for log-transformed total dry mass of leaf discs.
+Standardized regression coefficients modelig the effects of leaf tissue density, leaf area, leaf thickness, punch size, and their interactios (a) on the mean estimates of whole-leaf LMA, and (b) on the estimated variance of whole-leaf LMA.
 
 **APPENDIX S5.**
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
+Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
 
 **APPENDIX S6.**
-Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
+Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
 
 **APPENDIX S7.**
-Relationships between coefficient of variation (CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and (b) 1.0 cm diameter leaf punch.
+Summary of a linear mixed model for log-transformed total dry mass of leaf discs.
 

### 2022-05-13 ms/LMA_method.tex

@@
 
-\hypertarget{abstract-250-words-we-need-to-remove-47-words}{%
-\section{ABSTRACT (\textless{} 250 words, we need to remove 47 words!)}\label{abstract-250-words-we-need-to-remove-47-words}}
+\hypertarget{abstract}{%
+\section{ABSTRACT}\label{abstract}}
 
@@
 \textbf{METHODS:}
-We determined LMA using leaf discs and whole-leaf (including petiole) for 334 woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate) to examine what extent whole-leaf and leaf disc LMA match,
-whether the relationship varied with leaf tissue density, leaf area, leaf thickness and leaf punch size (0.6-cm and 1.0-cm in diameter),
-and whether the extent of intraspecifc variation (ITV) for each species matches.
+We examined to what extent whole-leaf and disc-based LMA match using 334 woody species from a wide range of biomes (tropics, subtropics, savanna, and temperate),
+whether the relationship varied by leaf morphology (tissue density, leaf area, leaf thickness), puncher size (0.6- and 1.0-cm diameter), and
+whether the extent of intraspecifc variation (ITV) for each species matches.
 
 \textbf{RESULTS:}
-Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be higher than leaf disc LMA.
+Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be 9.68\% higher than leaf disc LMA.
 The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
-Small leaf punch also inflated the whole-leaf to leaf disc LMA ratio.
-Variability of LMA estimates within species (i.e., extent of ITV) only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.09).
+Small leaf punch also inflated the ratio.
+The extent of ITV only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.09).
 
 \textbf{CONCLUSIONS:}
-Mean values of leaf disc LMA are generally good proxies for mean values of whole-leaf LMA with appropriate calibration (9.68\% differences in our samples), but their accuracy depends on leaf morphology, and sizes of leaf punch.
-Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch.
+Our results suggest that simple conversion between whole-leaf and leaf disc LMA is difficult for species obtained with a small leaf punch, but it should be possible for species obtained with a large leaf punch.
 Accurately representing leaf traits will probably require careful selection between leaf disc and whole-leaf traits depending on the objectives.
-Quantifying trait variation using leaf disc should be also considered with caution.
+Quantifying ITV using leaf disc should be also considered with caution.
 
@@
 Based on those measurements of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
+We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S3).
 
@@
 Posterior distributions of all parameters were estimated using the Hamiltonian Monte Carlo algorithm (HMC) implemented in Stan (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}) using the weakly-informative priors (\protect\hyperlink{ref-Gelman2008}{Gelman et al., 2008}).
-See Appendix SX for more detail.
 The Stan code use to fit models is available from Github at: \url{https://github.com/mattocci27/leaf-disc}.
@@
 (\protect\hyperlink{ref-Kraft2008}{2008}) found high \emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves (\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010}; \protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}).
-Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Appendix SX).
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Fig.
+2ac).
 On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance (\protect\hyperlink{ref-Poorter2009a}{Poorter, 2009}), suggesting that leaf disc LMA and whole-leaf LMA can be inherently different when small disc samples were used.
-The relatively low \emph{R\textsuperscript{2}} values in the Yunnan dataset (Appendix SX) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) or distinct veins with kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix SX), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix SX), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+The relatively low \emph{R\textsuperscript{2}} values in the Yunnan dataset (Appendix S5) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) or distinct veins with kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S6), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S7), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
@@
 This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Sack2012}{Sack et al., 2012}) and the pattern of higher leaf tissue density associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}) because those driving factors of LMA are likely to be ignored in leaf disc samples.
-The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix SX), but those effects were not significant.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix S4), but those effects were not significant.
 This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean estimates (\(\beta\) in Eq.
@@
 \textbf{APPENDIX S2.}
+Detailed sampling protocol for whole-leaf and leaf disc LMA.
+
+\textbf{APPENDIX S3.}
 Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
 
-\textbf{APPENDIX S3.}
-Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry mass for the leaf disc, (b) leaf thickness, and (c) leaf area.
-
 \textbf{APPENDIX S4.}
-Summary of multiple regression for log-transformed total dry mass of leaf discs.
+Standardized regression coefficients modelig the effects of leaf tissue density, leaf area, leaf thickness, punch size, and their interactios (a) on the mean estimates of whole-leaf LMA, and (b) on the estimated variance of whole-leaf LMA.
 
 \textbf{APPENDIX S5.}
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
+Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
 
 \textbf{APPENDIX S6.}
-Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
+Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
 
 \textbf{APPENDIX S7.}
-Relationships between coefficient of variation (CV) in LMA determined by using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and (b) 1.0 cm diameter leaf punch.
+Summary of a linear mixed model for log-transformed total dry mass of leaf discs.
 

### 2022-05-13 ms/response_letter.Rmd
add lines

@@
 
+Dear Editors,
+
+We hereby resubmit the manuscript (AJB-D-21-00391), “Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)” (Phisamai Maenpuen, Masatoshi Katabuchi, Yusuke Onoda, Cong Zhou, Jiao-Lin Zhang, Ya-Jun Chen).
+We thank the associate editor and the reviewers for their careful attention to detail in our manuscript and for providing comments that have greatly improved the study.
+
+Based on the comments, we have updated the manuscript to reflect the following:
+
+1.
+To quantify the effect of leaf morphology (leaf tissue density, leaf area, leaf thickness) and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we have built a hierarchical Bayesian model.
+This allows to quantify when the whole-leaf LMA to leaf disc LMA ratio become large and in which direction the relationship is changing.
+
+2. We also removed the analysis that grouped species into four categories based on medians of leaf area and leaf thickness because it is somewhat arbitral as pointed by the reviewer.
+Instead, the above Bayesian model can was used to test our hypotheses.
+
+3.
+We have removed the individual-based analysis from the main text because variance among species are not independent in the individual-level data, and thus SMA or OLS regressions are not appropriate.
+Analyses of individual-level data requires mixed linear models with species-level errors, but this is not useful for the context of our paper.
+We therefore only report species-level results.
+
+The programming code and the data supporting the findings of this study will be deposited at Zenodo (https://zenodo.org) and Github (https://github.com/mattocci27/leaf-disc).
+At the moment, we have attached the stan code for our Bayesian model.
+
+Below we provide detailed responses.
+The editing history is recorded in a separate pdf file.
+
+We appreciate the opportunity to revise and improve our manuscript, and we thank the editors and reviewers for their time and consideration.
+
+Sincerely,
+
+Masatoshi Katabuchi
+
+Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences
+
+(on behalf of coauthors: Phisamai Maenpuen,Yusuke Onoda, Cong Zhou, Jiao-Lin Zhang, and Ya-Jun Chen)
+
+\newpage
+
 > AE comments: Thanks for the submission.
@@
 I think the existing title is fine if you prefer to keep that but would ask you to carefully consider all other comments carefully.
+
+We appreciate the positive comments, and thank you for the opportunity to revise the manuscript.
+We have carefully detailed our responses to each point below.
 
@@
 Thank you.
-We now note that a key difference between leaf disc and whole-leaf LMA is that leaf disc LMA focuses on lamina rather than whole-leaf and usages depend on ecological contexts.
-We also have mentioned the TRY database to explain LMA is the most often used leaf trait in TRY.
+We now note that a key difference between leaf disc and whole-leaf LMA is that leaf disc LMA focuses on lamina rather than whole-leaf and usages depend on ecological contexts (Line 75-77).
+We also have mentioned the TRY database to explain LMA is the most often used leaf trait in TRY (Line 59-63).
 
@@
 Thank you.
-We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA.
+We have cited the recent review by Westerband et al. as well as other works to explain ITV, its importance and the extent of ITV for LMA (Line 104-111).
 We now use Bao's CV estimator (CV4) instead of the coefficient of variation of log-normally distributed data ($CV = \sqrt{exp(s_{\mathrm{ln}}^2) - 1}$).
@@
 Thank you.
-We now break up the paragraph into two sections: the first describing the different methods and their record numbers in TRY, and previous works that compared them, and the second describing the expected effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA.
+We now break up the paragraph into two sections: the first describing the different methods and their record numbers in TRY, and previous works that compared them (Line 64-86), and the second describing the expected effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA (Lin 87-103).
 
@@
 Thank you.
-We have repeated our expectations here.
+We have repeated our expectations here (Line 125-132).
 
@@
 Thank you.
-We have repeated our expectations here.
+Please see our response above.
 
@@
 Thank you.
-We have started the result section with the shift in elevation between whole-leaf and leaf disc LMA (i.e., whole-leaf LMA is greater than leaf disc LMA) .
+We have started the result section with the shift in elevation between whole-leaf and leaf disc LMA (i.e., whole-leaf LMA is greater than leaf disc LMA).
 Please see our response for using species- vs. individual-level data below.
@@
 However, as the reviewer pointed out, we should have used the same leaf punch size or repeated measurements using different leaf punch sizes.
-We consider this as a limitation of our study and explain this in the discussion.
+We have discussed the effects of leaf punch size more carefully (Line 273-282).
 
@@
 Leaf disc LMA had higher ITV.
-We have added the paired t-test for this in the results section.
+We have added the paired t-test for this in the results section (Line 251-255).
 
 > L193 you mention "appropriate calibration": it would be extremely useful if the authors were to report an equation (or several) for converting LMA measured by one metric to the other, ideally that incorporate leaf area and thickness (see major comment).
+
+Thank you.
+Now we have the subsection for conversion between the two LMA estimates in the discussion.
 
@@
 Thank you.
-We have included this in the results section.
+We have included this in the results section (Fig. 3).
 
@@
 Since we only measured 3 discs for each leaf in the Yunnan dataset, which is a common protocol, we cannot avoid the effect of variance within leaves.
-We have updated the text.
+We have updated the text (Line 364-365).
 
@@
 Thank you.
-The two panels share the x axis.
-Units are in the strip.
+The two panels share the same x axis, and the units are in the strip.
 
@@
 Thank you.
-We have mentioned several ecological studies that used leaf disc LMA in the introduction.
+We have mentioned several ecological studies that used leaf disc LMA in the introduction (Line 70-77).
 
@@
 Thank you.
-We have added the records of TRY database that shows LMA including petioles are very common.
+We have added the records of TRY database that shows LMA including petioles are very common (Line 64-70).
 
@@
 Thank you.
-We have cited it in the context of "diminishing returns" in the discussion.
+We have cited it in the context of "diminishing returns" in the discussion (Line 322-323).
 
@@
 Thank you.
-We have added MAT and MAP in the main text to support that our dataset covers the wide climate ranges in the distribution of broad-leaved tree species.
+We have added MAT and MAP in the main text to support that our dataset covers the wide climate ranges in the distribution of broad-leaved tree species (Line 143-147).
 
@@
 
-We now more clearly explain that thick veins are secondary order veins.
+We now more clearly explain that thick veins are first to secondary order veins (Line 163).
 

### 2022-05-13 ms/LMA_method.Rmd
add lines

@@
 Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago [@Hanson1917].
-Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass [12,238 species, 1,938 requests, @Kattge2020 [TRY version 5, status October 1 2019]]
+Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and has been also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass [12,238 species, 1,938 requests, @Kattge2020 [TRY version 5, status October 1 2019]]
 
@@
 (1) whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas [@Niinemets2007],
-(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles that are likely to be ignored in leaf disc samples, and
+(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles , whereas those effects are likely to be ignored in leaf disc samples, and
 (3) the extent of ITV does not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
@@
 
-There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: `r val$sma_slope_all_mean` [95%CI: `r val$sma_slope_all_lwr`, `r val$sma_slope_all_upr`], SMA intercept: `r val$sma_int_all_mean` [95%CI: `r val$sma_int_all_lwr`, `r val$sma_int_all_upr`]), suggesting that the whole-leaf estimates of LMA were `r val$sma_per_all_mean`% [95%CI: `r val$sma_per_all_lwr`, `r val$sma_per_all_upr`] greater than disc-based estimates in the arithmetic scale.
+There was a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: `r val$sma_slope_all_mean` [95%CI: `r val$sma_slope_all_lwr`, `r val$sma_slope_all_upr`], SMA intercept: `r val$sma_int_all_mean` [95%CI: `r val$sma_int_all_lwr`, `r val$sma_int_all_upr`]), suggesting that the whole-leaf estimates of LMA were `r val$sma_per_all_mean`% [95%CI: `r val$sma_per_all_lwr`, `r val$sma_per_all_upr`] greater than disc-based estimates in the arithmetic scale.
 
@@
 Leaf disc LMA explained interspecific variations in whole-leaf LMA (*R^2^* = `r val$r2_lma`, *n* = `r val$all_sp`) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported  [*R^2^* = 0.92, *n* = 409, for whole-leaves in @Kraft2008; *R^2^* = 0.92, *n* = 364 for leaf laminas in @Onoda2011].
-Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4% differences).
+Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (`r val$sma_per_all_mean`% differences).
 Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
@@
 @Kraft2008 found high *R^2^* values (*R^2^* = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves [@Kitajima2010; @Oktavia2020].
-Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Fig.
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the variance in the whole-leaf to leaf disc LMA ratio were small for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Fig.
 2ac).
@@
 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
-OLS regressions with leaf area as a covariate as following:
+The ordinary least-squares (OLS) regressions with leaf area as a covariate as following:
 (1) log~10~LMA~w~ = `r val$yaku2_slope_disc` $\times$ log~10~LMA~d~ + `r val$yaku2_slope_area` $\times$ log~10~LA,
@@
 where LMA~w~, LMA~d~, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
-OLS regressions without leaf area as a covariate as following:
+Thej OLS regressions without leaf area as a covariate as following:
 (3) log~10~LMA~w~ = `r val$yaku_int_log10` + `r val$yaku_slope_disc` $\times$ log~10~LMA~d~ or
@@
 Nonetheless, including leaf area only slightly improves the *R^2^* values for the Yakushima dataset where a large punch was used.
-This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called "diminishing returns" [@Niklas2007] which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles [@Li2022], which is strong for mature leaves [@Jiao2022].
+This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called "diminishing returns" [@Niklas2007] which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles [@Li2022].
+This effect is generally strong for mature leaves [@Jiao2022].
 The "diminishing returns" can be either described as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
@@
 
-*Conclusions*
+# Conclusions
 

### 2022-05-13 ms/LMA_method.tex
add lines

@@
 Therefore, LMA has been of interests to ecologists and widely used since the first report more than a century ago (\protect\hyperlink{ref-Hanson1917}{Hanson, 1917}).
-Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and was also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass (12,238 species, 1,938 requests, \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5, status October 1 2019{]})
+Actually, LMA has one of the best species coverage in leaf traits of the TRY plant data database (16,460 species) and has been also the most often requested leaf trait (2,977 out of 7,330 requests), followed by leaf by leaf nitrogen (N) contents per leaf dry mass (12,238 species, 1,938 requests, \protect\hyperlink{ref-Kattge2020}{Kattge et al., 2020} {[}TRY version 5, status October 1 2019{]})
 
@@
 (1) whole-leaf LMA would be greater than leaf disc LMA because whole-leaf LMA includes petioles and midribs that have greater dry mass per unit area than laminas (\protect\hyperlink{ref-Niinemets2007}{Niinemets et al., 2007}),
-(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles that are likely to be ignored in leaf disc samples, and
+(2) species with higher leaf tissue density, larger and/or thinner leaves would show larger variance and differences in LMA estimates because whole-leaf LMA should be driven more in those species by veins and petioles , whereas those effects are likely to be ignored in leaf disc samples, and
 (3) the extent of ITV does not match well between whole-leaf and leaf disc based estimates because leaf disc samples have more sources of variation than whole-leaf samples.
@@
 
-There were a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.68\% {[}95\%CI: 8.05, 11.4{]} greater than disc-based estimates in the arithmetic scale.
+There was a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.68\% {[}95\%CI: 8.05, 11.4{]} greater than disc-based estimates in the arithmetic scale.
 
@@
 Leaf disc LMA explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
-Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.4\% differences).
+Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.68\% differences).
 Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
@@
 (\protect\hyperlink{ref-Kraft2008}{2008}) found high \emph{R\textsuperscript{2}} values (\emph{R\textsuperscript{2}} = 0.92) between whole-leaf and leaf disc LMA based on leaf discs of approximately 1.0-cm diameter for sapling leaves under closed canopy that are softer and thinner than adult leaves (\protect\hyperlink{ref-Kitajima2010}{Kitajima and Poorter, 2010}; \protect\hyperlink{ref-Oktavia2020}{Oktavia and Jin, 2020}).
-Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the correlations were also strong for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Fig.
+Altough a leaf punch of 1.0-cm diameter was used only in the Yakushima dataset in our study, the variance in the whole-leaf to leaf disc LMA ratio were small for the Yakushima dataset, regardless of leaf tissue density or leaf thickness (Fig.
 2ac).
@@
 2ab: large leaf punch), suggesting that conversion between leaf disc and whole-leaf LMA should be possible using leaf area as a covariate (measuring leaf tissue density requires whole-leaf LMA itself).
-OLS regressions with leaf area as a covariate as following:
+The ordinary least-squares (OLS) regressions with leaf area as a covariate as following:
 (1) log\textsubscript{10}LMA\textsubscript{w} = 0.997 \(\times\) log\textsubscript{10}LMA\textsubscript{d} + 0.0589 \(\times\) log\textsubscript{10}LA,
@@
 where LMA\textsubscript{w}, LMA\textsubscript{d}, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
-OLS regressions without leaf area as a covariate as following:
+Thej OLS regressions without leaf area as a covariate as following:
 (3) log\textsubscript{10}LMA\textsubscript{w} = 0.124 + 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
@@
 Nonetheless, including leaf area only slightly improves the \emph{R\textsuperscript{2}} values for the Yakushima dataset where a large punch was used.
-This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called ``diminishing returns'' (\protect\hyperlink{ref-Niklas2007}{Niklas et al., 2007}) which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles (\protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}), which is strong for mature leaves (\protect\hyperlink{ref-Jiao2022}{Jiao et al., 2022}).
+This is because the large discrepancy in the whole-leaf to leaf disc LMA for large leaves can be explained by scaling relationships between leaf mass and leaf area called ``diminishing returns'' (\protect\hyperlink{ref-Niklas2007}{Niklas et al., 2007}) which refers to increases in leaf dry mass including petioles do not result in the proportional increase in leaf area including petioles (\protect\hyperlink{ref-Li2022}{Li, Shi, et al., 2022}).
+This effect is generally strong for mature leaves (\protect\hyperlink{ref-Jiao2022}{Jiao et al., 2022}).
 The ``diminishing returns'' can be either described as the scaling slope of leaf area in the model 1 or the scaling slope of leaf-disc LMA and the intercept in the model 3.
@@
 
-\emph{Conclusions}
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 

### 2022-05-13 ms/response_letter.Rmd
add lines

@@
 To quantify the effect of leaf morphology (leaf tissue density, leaf area, leaf thickness) and leaf punch size on the relationship between whole-leaf and leaf disc LMA, we have built a hierarchical Bayesian model.
-This allows to quantify when the whole-leaf LMA to leaf disc LMA ratio become large and in which direction the relationship is changing.
+This allows us to quantify when the whole-leaf LMA to leaf disc LMA ratio become large and in which direction the relationship is changing.
 
-2. We also removed the analysis that grouped species into four categories based on medians of leaf area and leaf thickness because it is somewhat arbitral as pointed by the reviewer.
-Instead, the above Bayesian model can was used to test our hypotheses.
+2. We have removed the analysis that grouped species into four categories based on medians of leaf area and leaf thickness because it is somewhat arbitral as pointed by the reviewer.
+Instead, the above Bayesian model was used to test our hypotheses.
 
 3.
-We have removed the individual-based analysis from the main text because variance among species are not independent in the individual-level data, and thus SMA or OLS regressions are not appropriate.
+We have also removed the individual-based analysis from the main text because variance among species are not independent in the individual-level data, and thus SMA or OLS regressions are not appropriate.
 Analyses of individual-level data requires mixed linear models with species-level errors, but this is not useful for the context of our paper.
@@
 \newpage
+
+# Responses
 
@@
 This is a good point and an important thing to clarify.
-We now use a linear model that includes leaf area and leaf thickness as covariates but we suggest OLS models without covariates for the conversion of LMA because leaf thickness and leaf area affect not only the mean but also the variance in the relationship between the leaf disc and whole-leaf estimates, and that is why R2 values changed among the four groups (thin vs.
-think and small vs.
-large leaves) and it is not to practical to convert LMA using leaf area or leaf thickness.
-We also present a practical guideline for conversion of LMA.
+We now use a Bayesian model that includes leaf area and leaf thickness as covariates for both mean and variance.
+However, we report several OLS models with and without leaf area in a practical guideline for LMA conversion (Line 303 - 323).
 
@@
 Thank you.
-We now introduce the LES in the first sentence so that the readers can understand the role of LMA in LES more clearly.
+We now introduce the LES in the first sentence so that the readers can understand the role of LMA in LES more clearly (Line 44-46).
 
@@
 Thank you.
-We have started the result section with the shift in elevation between whole-leaf and leaf disc LMA (i.e., whole-leaf LMA is greater than leaf disc LMA).
+We have started the result section with the shift in elevation between whole-leaf and leaf disc LMA (i.e., whole-leaf LMA is greater than leaf disc LMA) (Line 234-).
 Please see our response for using species- vs. individual-level data below.
@@
 Thank you.
-We have added confidence intervals using bootstraps in the result section.
+We have added confidence intervals using bootstraps in the result section (Line 252-255).

### 2022-05-13 ms/response_letter.Rmd
typo

@@
 Thank you.
-We now break up the paragraph into two sections: the first describing the different methods and their record numbers in TRY, and previous works that compared them (Line 64-86), and the second describing the expected effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA (Lin 87-103).
+We now break up the paragraph into two sections: the first describing the different methods and their record numbers in TRY, and previous works that compared them (Line 64-86), and the second describing the expected effects of leaf morphology on the relationship between whole-leaf and leaf disc LMA (Line 87-103).
 

### 2022-05-18 report.Rmd
clean al

--- 2022-05-07 report.Rmd
@@
 
-```{r}
-tar_load(sp_mean)
-sp_mean |>
-  group_by(ldlalt_gr) |>
-  summarise(
-    lma_leaf = mean(lma_leaf) |> round(1),
-    lma_disc = mean(lma_disc) |> round(1)
-  ) |>
-  write_csv("data/ldlalt.csv")
-```
-
-# Leaf disc vs whole-leaf LMA (species-level)
-
-## Pooled
-
-<!-- I put tar_load to use {{targets}} -->
-
-```{r, include=FALSE}
-tar_load(lalt_pool_grid_png)
-```
-
-![](figs/lalt_pool_grid.png)
-
-## Seprated
-
-```{r, include=FALSE}
-tar_load(lalt_sep_grid_png)
-```
-
-## MCMC check
+# MCMC check
 
 ```{r,eval=TRUE}
-
 targets::tar_load(fit_sp_no_lma_summary_model)
@@
 targets::tar_load(fit_sp_ld_summary_model)
-targets::tar_load(fit_sp_ld2_summary_model2)
 targets::tar_load(fit_sp_ld3_summary_model)
@@
 targets::tar_load(fit_sp_ld_diagnostics_model)
-targets::tar_load(fit_sp_ld2_diagnostics_model2)
 targets::tar_load(fit_sp_ld3_diagnostics_model)
@@
 fit_sp_ld_summary_model |> filter(rhat > 1.1)
-fit_sp_ld2_summary_model2 |> filter(rhat > 1.1)
 fit_sp_ld3_summary_model |> filter(rhat > 1.1)
@@
 div_check(fit_sp_ld_diagnostics_model)
-div_check(fit_sp_ld2_diagnostics_model2)
 div_check(fit_sp_ld3_diagnostics_model)
@@
   loo_model[[7]], loo_model[[8]], loo_model[[9]],
-  loo_model[[10]], loo_model[[11]],
-  loo_model[[12]], loo_model[[13]]
-)
+  loo_model[[10]], loo_model[[11]])
 ```
@@
 
-# SMA table
-
-## species
-
-```{r, eval=TRUE}
-tar_load(sma_sp_tab)
-sma_sp_tab |>
-  kable() |>
-  kable_styling()
-```
-```{r}
-sma_sp_tab |>
-  write_csv("data/sma_sp_tab.csv")
-```
-
-## species LD
-
-```{r, eval=TRUE}
-tar_load(sma_sp_ld_tab)
-sma_sp_ld_tab |>
-  kable() |>
-  kable_styling()
-```
-
-```{r}
-sma_sp_ld_tab |>
-  write_csv("data/sma_sp_ld_tab.csv")
-```
-
-## species simple
-
-```{r, eval=TRUE}
-tar_load(sma_sp_2_tab)
-sma_sp_2_tab |>
-  kable() |>
-  kable_styling()
-```
-
-```{r}
-sma_sp_2_tab |>
-  write_csv("data/sma_sp_2_tab.csv")
-```
-
-## tree
-
-```{r, eval=TRUE}
-tar_load(sma_tree_tab)
-sma_tree_tab |>
-  kable() |>
-  kable_styling()
-```
-
-## tree LD
-
-```{r, eval=TRUE}
-tar_load(sma_tree_ld_tab)
-sma_tree_ld_tab |>
-  kable() |>
-  kable_styling()
-```
+``
 
@@
 
-```{r}
-tar_load(cv_tree)
-cv_tree
-```
-
-# Leaf disc vs whole-leaf LMA (individual-level)
-
-```{r, include=FALSE}
-tar_load(lalt_tree_grid_png)
-```
-
-![](figs/lalt_tree_grid.png)
-
-# Divergence (species-level)
-
-```{r, include=FALSE}
-tar_load(ratio_png)
-```
-
-![](figs/ratio.png)
-
 # LMA and LD (species-level)
@@
 ```{r, include=FALSE}
-tar_load(lma_ld_png)
+tar_load(lma_ld_plot)
 ```
@@
 ```{r, include=FALSE}
-tar_load(cv_pool_png)
+tar_load(cv_pool_plot)
 ```
@@
 
-```{r, include=FALSE}
-tar_load(cv_sep_png)
-```
-
-![](figs/cv_sep.png)
-
 # Leaf support cost (species-level)
@@
 ```{r, include=FALSE}
-tar_load(petiole_png)
+tar_load(petiole_plot)
 ```
@@
 ![](figs/petiole.png)
+
+# DM and HDK
+
+```{r}
+tar_load(tree)
+fit <- lm(log(lma_leaf / lma_disc) ~ log(dry_mass_disc), tree)
+lmtest::bptest(fit)
+```
+
+# {targets} pipepline
+
+```{r}
+targets::tar_visnetwork()
+```
 
@@
 ```
-
-```{r}
-tar_visnetwork()
-```

### 2022-05-18 R/data_clean.R

@@ -124,7 +124,18 @@ data_clean_tree <- function(lma_raw_re, lma_yaku_re) {
      location == "Yakushima" ~ lma_disc * 1.57 * 10^-4,
      # disc size for lma_disc in lma_raw_re is 0.899
      TRUE ~ lma_disc * 0.889 * 10^-4
-                  ))
+                  )) |>
+    mutate(growth_form = case_when(
+      growth_form == "T" ~ "tree",
+      growth_form == "S" ~ "shrub",
+      growth_form == "L" ~ "liana",
+      growth_form == "Trees" ~ "tree"
+    )) |>
+    mutate(leaf_habit = case_when(
+      leaf_habit == "E" ~ "evergreen",
+      leaf_habit == "D" ~ "deciduous",
+      leaf_habit == "ED" ~ "semi-deciduous"
+    ))
 
   tree_data |> write_csv("data/tree_data.csv")
   paste("data/tree_data.csv")
@@ -134,9 +145,9 @@ data_clean_tree <- function(lma_raw_re, lma_yaku_re) {
 data_clean_mean <- function(tree) {
   sp_dat <- tree |>
     # to calculate means, we use samples that have both LMAw and LMAd
-    filter(!is.na(lma_disc)) |>
-    filter(!is.na(lma_leaf)) |>
-    filter(!is.na(lt)) |>
+    # filter(!is.na(lma_disc)) |>
+    # filter(!is.na(lma_leaf)) |>
+    # filter(!is.na(lt)) |>
     group_by(species, family, growth_form, leaf_habit, leaf_type,
     location, biomes, data_contributor) |>
     summarise_at(
@@ -152,6 +163,11 @@ data_clean_mean <- function(tree) {
       .funs = \(x)mean(x, na.rm = TRUE)
     ) |>
     arrange(location) |>
+    # to calculate means, we use all the samples even if that sample doesn't
+    # have the corresponding LMAw or LMAd
+    filter(!is.na(lma_disc)) |>
+    filter(!is.na(lma_leaf)) |>
+    filter(!is.na(lt)) |>
     mutate(lma_ratio = lma_leaf / lma_disc) |>
     mutate(ld_ratio = ld_leaf / ld_disc)
 
@@ -164,6 +180,9 @@ data_clean_mean <- function(tree) {
 data_clean_cv <- function(tree) {
   # sample with n > 5
   tree_n <- tree |>
[…]

### 2022-05-18 R/ind_analysis.R

@@ -1,56 +1,89 @@
-lalt_tree_grid <- function(tree) {
-  tree |>
-    mutate(la_gr2 = factor(la_gr2, levels = c("Small-leaved~individuals",
-                           "Large-leaved~individuals") |> rev())) |>
-    ggplot(aes(x = lma_disc, y = lma_leaf, col = dry_mass_disc)) +
-    geom_point(alpha = 0.8) +
-    scale_color_viridis_c(
-      trans = "log10",
-      name = "Total dry mass of \nleaf discs (g)"
-    ) +
-    scale_x_log10() +
-    scale_y_log10() +
-    geom_abline(slope = 1, intercept = 0, lty = 2) +
-    geom_sma(se = TRUE, nboot = 2000) +
-    facet_grid(la_gr2 ~ lt_gr2, scale = "free", labeller = label_parsed) +
-    xlab(expression(Leaf ~ disc ~ LMA ~ (g ~ m^{
-      -2
-    }))) +
-    ylab(expression(Whole - leaf ~ LMA ~ (g ~ m^{
-      -2
-    }))) +
-    stat_cor(
-      aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial")
-    ) +
-    theme_bw() +
-    theme(
-      text = element_text(family = "Arial"),
-      legend.position = "none",
-      legend.key.size = unit(0.5, "cm"),
-      legend.spacing.y = unit(0.1, "cm"),
-      legend.text.align = 0,
-      legend.key.height = unit(0.3, "cm"),
-      legend.text = element_text(size = 7),
-      legend.title = element_text(size = 7)
-    )
+#' @title Check heteroskedasticity
+check_hdk <- function(tree) {
+  fit <- lm(log(lma_leaf / lma_disc) ~ log(dry_mass_disc), tree)
+  lmtest::bptest(fit)
 }
 
-lalt_tree_grid_dense <- function(tree) {
-  p1 <- tree |>
-      filter(ld_gr2 == "Nondense-leaved~individuals") |>
-      lalt_tree_grid() +
-      ggtitle("Nondense-leaved individuals") +
-      theme(legend.position = c(0.88, 0.65))
-  p2 <- tree |>
-      filter(ld_gr2 == "Dense-leaved~individuals") |>
-      lalt_tree_grid() +
-      ggtitle("Dense-leaved individuals")
-  p1 + p2 +
[…]

### 2022-05-18 R/sp_analysis.R

@@ -20,6 +20,7 @@ sma_point <- function(data) {
     theme_bw() +
     theme(text = element_text(family = "Arial"))
 }
+
 #' @title Leaf disc vs whole-leaf LMA (simple)
 sma_point_sep <- function(data) {
   my_col <- RColorBrewer::brewer.pal(4, "RdBu")
@@ -60,565 +61,6 @@ sma_point_sep <- function(data) {
       legend.title = element_text(size = 9))
 }
 
-#' @title Leaf disc vs whole-leaf LMA (pooled species-level)
-lalt_pool_grid_point <- function(data) {
-  # data <- data |>
-  #   mutate(size_gr = ifelse(location == "Yakushima", "1.0-cm", "0.6-cm"))
-  data |>
-    mutate(la_gr2 = factor(la_gr2, levels = c("Small-leaved~species",
-                           "Large-leaved~species") |> rev())) |>
-    ggplot(aes(x = lma_disc, y = lma_leaf)) +
-    geom_point(alpha = 0.8) +
-    scale_x_log10() +
-    scale_y_log10() +
-    geom_abline(slope = 1, intercept = 0, lty = 2) +
-    geom_sma(se = TRUE, nboot = 2000) +
-    facet_grid(la_gr2 ~ lt_gr2, scale = "fixed", labeller = label_parsed) +
-    xlab(expression(Leaf ~ disc ~ LMA ~ (g ~ m^{
-      -2
-    }))) +
-    ylab(expression(Whole - leaf ~ LMA ~ (g ~ m^{
-      -2
-    }))) +
-    stat_cor(
-      aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"),
-          family = "Arial")
-    ) +
-    theme_bw() +
-    theme(text = element_text(family = "Arial"))
-}
-
-lalt_sp_grid_dense <- function(data) {
-  p1 <- data |>
-      filter(ld_gr2 == "Nondense-leaved~species") |>
-      lalt_pool_grid_point() +
-      ggtitle("Nondense-leaved species") +
-      theme(legend.position = c(0.88, 0.65))
-  p2 <- data |>
-      filter(ld_gr2 == "Dense-leaved~species") |>
-      lalt_pool_grid_point() +
-      ggtitle("Dense-leaved species")
-  p1 + p2 +
-    plot_annotation(tag_levels = "a") &
-    theme(
[…]

### 2022-05-18 _targets.R

@@ -27,7 +27,8 @@ tar_option_set(packages = c(
   "extrafont",
   "loo",
   "jsonlite",
-  "lmtest"
+  "lmtest",
+  "modelr"
 ))
 
 # check if it's inside a container
@@ -65,30 +66,8 @@ list(
     clean_lma_raw(lma_raw)
   ),
   tar_target(
-    lma_la_re,
-    clean_lma_la(lma_la)
-  ),
-  tar_target(
     lma_yaku_re,
     clean_lma_yaku(lma_yaku)
-  ),
-  tar_target(
-    full_data_csv,
-    data_clean(lma_raw_re, lma_la_re, lma_yaku_re),
-    format = "file"
-  ),
-  tar_target(
-    full_data,
-    read_csv(full_data_csv)
-  ),
-  tar_target(
-    full_data_cv_csv,
-    data_clean_cv(lma_raw_re, lma_yaku_re),
-    format = "file"
-  ),
-  tar_target(
-    full_data_cv,
-    read_csv(full_data_cv_csv)
   ),
   tar_target(
     tree_data_csv,
@@ -96,21 +75,30 @@ list(
     format = "file"
   ),
   tar_target(
-    tree_data,
+    tree,
     read_csv(tree_data_csv)
+  ),
+
+  tar_target(
+    sp_mean_file,
+    data_clean_mean(tree),
+    format = "file"
   ),
   tar_target(
     sp_mean,
-    sp_dat_mean(full_data)
+    read_csv(sp_mean_file)
+  ),
+
+  tar_target(
+    sp_cv_file,
+    data_clean_cv(tree),
+    format = "file"
   ),
   tar_target(
     sp_cv,
-    sp_dat_cv(full_data_cv)
+    read_csv(sp_cv_file)
   ),
-  tar_target(
-    tree,
-    tree_dat_clean(tree_data)
-  ),
+
   tar_target(
     yaku_sp,
     create_yaku_sp(lma_yaku_re)
@@ -124,7 +112,7 @@ list(
   tar_target(
     yml,
     write_yml("values.yml",
-      sp_mean, full_data_cv, tree, lma_raw_re, lma_yaku_re, sp_cv, boot_fit_dat),
+      sp_mean, sp_cv, tree, lma_raw_re, lma_yaku_re, boot_fit_dat),
     format = "file"
   ),
   tar_target(
@@ -132,6 +120,7 @@ list(
     update_site_info(site_info_raw, yml),
     format = "file"
   ),
+
 
[…]

### 2022-06-17 ms/LMA_method.Rmd
update MS according to the reviewer 1

@@
 whether the extent of ITV for each species match between whole-leaf and leaf disc based estimates.
-We collected a total of `r val$all_sp` woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
+We collected leaves from `r val$all_tree` individuals of `r val$all_sp` woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
 We evaluate the following hypotheses:
@@
 We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
-First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$sp1` species and `r val$tree1` individuals.
-Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$tree3` individuals.
-In total, our dataset comprised `r val$all_sp` woody species and `r val$all_tree` individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
+First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$TRF_sp + val$STF_sp + val$HDS_sp` species and `r val$TRF_ind + val$STF_ind + val$HDS_ind` individuals.
+Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$Yaku_ind` individuals.
+In total, our dataset comprised `r val$all_sp` woody species and `r val$all_tree` individuals that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
 The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe below.
@@
 Fresh leaf area (LA; cm^-2^) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package *LeafArea* [@Katabuchi2015].
-Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf using a micrometer (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
+Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
 Thickness of each leaf disc was also measured for the Yunnan dataset but not for the Yakushima dataset, which enables us to estimate whole-leaf and leaf disc leaf tissue density (LD; g cm^-3^) separately in the Yunnan dataset.
@@
 where LMA~w~, LMA~d~, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
-Thej OLS regressions without leaf area as a covariate as following:
+The OLS regressions without leaf area as a covariate as following:
 (3) log~10~LMA~w~ = `r val$yaku_int_log10` + `r val$yaku_slope_disc` $\times$ log~10~LMA~d~ or
@@
 (*R^2^* = `r val$yaku_r2_simple`, *AIC* = `r val$yaku_aic_simple`, *n* = `r val$yaku_sp`).
+[Note that OLS regressions minimize errors of either whole-leaf LMA or leaf disc LMA, and thus those four models are not identical, whereas SMA regressions are not appropriate for predictions [@Warton2006]]
 Nonetheless, including leaf area only slightly improves the *R^2^* values for the Yakushima dataset where a large punch was used.

### 2022-06-17 ms/LMA_method.Rmd
update main text

@@
 Thickness of each leaf disc was also measured for the Yunnan dataset but not for the Yakushima dataset, which enables us to estimate whole-leaf and leaf disc leaf tissue density (LD; g cm^-3^) separately in the Yunnan dataset.
-Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a precision at 0.0001 g.
+Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, Ohio, U.S.A.) with a precision at 0.0001 g.
 In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (`r val$pet_sp` out of `r val$yaku_sp` species) to quantify leaf support costs.
@@
 
-The authors thank Lian-Bin Tao and Peng-Yun Yan for field work.
+We thank the editors and two anonymous reviewers, whose comments greatly improved the manuscript.
+We also thank Lian-Bin Tao and Peng-Yun Yan for field work.
 This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).

### 2022-06-17 ms/LMA_method.tex
clean raw data

@@
 \textbf{RESULTS:}
-Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be 9.68\% higher than leaf disc LMA.
+Disc-based estimates of species mean LMA matched well whole-leaf estimates, and whole-leaf LMA tended to be 9.69\% higher than leaf disc LMA.
 The whole-leaf to leaf disc LMA ratio was higher for species with higher leaf tissue density and larger leaf, and their variance was greater for species with lower leaf tissue density and thinner leaves.
 Small leaf punch also inflated the ratio.
-The extent of ITV only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.09).
+The extent of ITV only weakly matched between whole-leaf and disc-based estimates (\emph{R\textsuperscript{2}} = 0.08).
 
@@
 whether the extent of ITV for each species match between whole-leaf and leaf disc based estimates.
-We collected a total of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
+We collected leaves from 1459 individuals of 334 woody species from four biomes (tropics, subtropics, savanna, and warm-temperate) to cover the wide range of geography.
 We evaluate the following hypotheses:
@@
 We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
-First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of species and individuals.
-Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and individuals.
-In total, our dataset comprised 334 woody species and 1365 individual that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
+First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of 141 species and 852 individuals.
+Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and 607 individuals.
+In total, our dataset comprised 334 woody species and 1459 individuals that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
 (\protect\hyperlink{ref-Song2017}{2017}); Fei et al.
@@
 Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
-Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf using a micrometer (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
+Fresh leaf thickness (LT; mm) was measured using a micrometer in three points at the base, middle and tip of the leaf (Mitutoyo 293-240, Mitutoyo Corporation, Kawasaki, Japan) with a precision at 0.001 mm.
 Thickness of each leaf disc was also measured for the Yunnan dataset but not for the Yakushima dataset, which enables us to estimate whole-leaf and leaf disc leaf tissue density (LD; g cm\textsuperscript{-3}) separately in the Yunnan dataset.
-Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, OH, U.S.A.) with a precision at 0.0001 g.
+Leaf dry mass (whole leaves including petioles and midribs, and leaf discs) was recorded after drying 80°C for over 48 h to constant weight using an electronic scale (Mettler-Toledo MS204TS, Columbus, Ohio, U.S.A.) with a precision at 0.0001 g.
 In the subset of Yakushima dataset, leaf lamina and petiole dry mass were also determined separately (80 out of 193 species) to quantify leaf support costs.
@@
 
-There was a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.68\% {[}95\%CI: 8.05, 11.4{]} greater than disc-based estimates in the arithmetic scale.
+There was a significant shift in elevation between whole-leaf and leaf disc LMA (Fig.1, SMA slope: 0.975 {[}95\%CI: 0.938, 1.013{]}, SMA intercept: 0.0881 {[}95\%CI: 0.016, 0.16{]}), suggesting that the whole-leaf estimates of LMA were 9.69\% {[}95\%CI: 8.06, 11.3{]} greater than disc-based estimates in the arithmetic scale.
 
@@
 The extent of intraspecific trait variation (CV; coefficient of variation) only weakly matched between whole-leaf and disc-based estimates (Fig.4).
-Although there were no statistical differences in the SMA slope or elevation (SMA slope: 1.116 {[}95\%CI: 0.954, 1.304{]}, SMA intercept: 0.102 {[}95\%CI: -0.174, 0.377{]}), leaf disc LMA had greater CVs than whole-leaf LMA (\emph{t} = -3.19, \emph{d.f.} = 144, \emph{P} \textless{} 0.001).
+Although there were no statistical differences in the SMA slope or elevation (SMA slope: 1.112 {[}95\%CI: 0.951, 1.302{]}, SMA intercept: 0.096 {[}95\%CI: -0.18, 0.372{]}), leaf disc LMA had greater CVs than whole-leaf LMA (\emph{t} = -3.2, \emph{d.f.} = 143, \emph{P} \textless{} 0.001).
 
@@
 Leaf disc LMA explained interspecific variations in whole-leaf LMA (\emph{R\textsuperscript{2}} = 0.87, \emph{n} = 334) quite well, and the strength of their relationship was approximately same or slightly weaker than previously reported (\emph{R\textsuperscript{2}} = 0.92, \emph{n} = 409, for whole-leaves in \protect\hyperlink{ref-Kraft2008}{Kraft et al., 2008}; \emph{R\textsuperscript{2}} = 0.92, \emph{n} = 364 for leaf laminas in \protect\hyperlink{ref-Onoda2011}{Onoda et al., 2011}).
-Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.68\% differences).
+Standardized major axis (SMA) regression analysis showed significantly greater intercepts when all the species were pooled (9.69\% differences).
 Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
@@
 where LMA\textsubscript{w}, LMA\textsubscript{d}, and LA are the whole-leaf LMA, leaf disc LMA and leaf area, respectively.
-Thej OLS regressions without leaf area as a covariate as following:
+The OLS regressions without leaf area as a covariate as following:
 (3) log\textsubscript{10}LMA\textsubscript{w} = 0.124 + 0.958 \(\times\) log\textsubscript{10}LMA\textsubscript{d} or
@@
 (\emph{R\textsuperscript{2}} = 0.93, \emph{AIC} = -284.2, \emph{n} = 193).
+{[}Note that OLS regressions minimize errors of either whole-leaf LMA or leaf disc LMA, and thus those four models are not identical, whereas SMA regressions are not appropriate for predictions (\protect\hyperlink{ref-Warton2006}{Warton et al., 2006}){]}
 Nonetheless, including leaf area only slightly improves the \emph{R\textsuperscript{2}} values for the Yakushima dataset where a large punch was used.
@@
 Even though we used the same species, the same individuals and the same trait (LMA) to estimate the extents of intraspecific trait variation (ITV), the explained variance of the relationship between whole-leaf and disc-based estimate was surprisingly small (Fig.
-3; \emph{R\textsuperscript{2}} = 0.09).
+3; \emph{R\textsuperscript{2}} = 0.08).
 This is probably because leaf disc samples have more sources of ITV than whole-leaf samples (i.e., variation among leaf discs within the same leaves).
@@
 
-The authors thank Lian-Bin Tao and Peng-Yun Yan for field work.
+We thank the editors and two anonymous reviewers, whose comments greatly improved the manuscript.
+We also thank Lian-Bin Tao and Peng-Yun Yan for field work.
 This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).

### 2022-06-17 R/data_clean.R

@@ -36,11 +36,11 @@ clean_lma_yaku <- function(lma_yaku) {
       growth_form = growthform,
       lma_leaf = whole_leaf_lma,
       lma_disc = ld_lma,
-      ldmc_leaf = ldmc,
+      # ldmc_leaf = ldmc,
       ld_disc = td) |>
     mutate(ld_leaf = lma_leaf / lt * 10^-3) %>%
     mutate(ld_disc = NA) |>
-    mutate(ldmc_disc = NA) |>
+    # mutate(ldmc_disc = NA) |>
     mutate(lt_disc = NA) |>
     mutate(petiole_ratio = petiole_dw / scanned_leaf_dw)
   yaku

### 2022-06-17 _targets.R

@@ -42,20 +42,25 @@ cmdstan_version()
 list(
   # data cleaning ----------------------------------
   tar_target(
+    lma_yaku,
+    "data-raw/yakushima_raw.csv",
+    format = "file"
+  ),
+  tar_target(
     lma_raw,
-    "data-raw/lma_raw.csv",
+    "data-raw/yunnan_lma.csv",
     format = "file"
   ),
   tar_target(
     lma_la,
-    "data-raw/lma_la.csv",
+    "data-raw/yunnan_la.csv",
     format = "file"
   ),
-  tar_target(
-    lma_yaku,
-    "data-raw/leaf_traits_for_katabuchi.csv",
-    format = "file"
-  ),
+  # tar_target(
+  #   lma_yaku,
+  #   "data-raw/leaf_traits_for_katabuchi.csv",
+  #   format = "file"
+  # ),
   tar_target(
     site_info_raw,
     "data-raw/site_info_raw.json",

### 2022-06-18 ms/LMA_method.Rmd
update appendix

@@
 
-We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
+We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1, Table S1 (see the Supplementary Data with this article)) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
 First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of `r val$TRF_sp + val$STF_sp + val$HDS_sp` species and `r val$TRF_ind + val$STF_ind + val$HDS_ind` individuals.
 Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of `r val$yaku_sp` species and `r val$Yaku_ind` individuals.
-In total, our dataset comprised `r val$all_sp` woody species and `r val$all_tree` individuals that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
+In total, our dataset comprised `r val$all_sp` woody species and `r val$all_tree` individuals that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) [Appendix S1, Table S1; @Eguchi2006; @Song2017; @Fei2018], which covers the wide climate ranges in the distribution of broad-leaved tree species.
 The methodologies for trait sampling and measurement are slightly different between the Yunnan and the Yakushima dataset, which we describe below.
@@
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S2 for more details).
+Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S1, Figure S1 for more details).
 Fresh leaf area (LA; cm^-2^) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package *LeafArea* [@Katabuchi2015].
@@
 Based on those measurements of whole-leaf and leaf disc samples, LMA (g m^-2^) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
-We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S3).
+We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S1, Figure S2).
 
@@
 
-Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S4).
+Leaf tissue density, leaf area, leaf thickness and leaf punch size influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S1, Figure S3).
 Species with lower leaf tissue density had greater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a).
@@
 Species with thinner leaves had greater variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2c), which was only significant for leaves obtained by a small punch.
-A small punch also inflated variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a-c and Appendix S4).
+A small punch also inflated variance in the estimate of whole-leaf to leaf disc LMA ratio (Fig. 2a-c and Appendix S1, Figure S3).
 Leaf disc and whole-leaf LMA estimate diverged for species with greater investment in petiole dry mass (Fig.
@@
 Together, these findings suggest that disc-based estimates can be generally used as good proxies for their whole-leaf estimates with appropriate calibration (see discussion below).
-However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S4).
+However, leaf tissue density, leaf area, leaf thickness and leaf punch size also influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 2 and Appendix S1, Figure S3).
 
@@
 The effect of leaf punch size was the most important source of the variation (Fig.
-2, Appendix S4), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
+2, Appendix S1, Figure S3), and samples obtained with a small leaf punch showed greater variance in whole-leaf to leaf disc LMA ratio.
 Small leaf disc size inflates trait varition within leaves because dry mass will be inflated when major veins are unintentionally included in the samples.
@@
 On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance [@Poorter2009a], suggesting that leaf disc LMA and whole-leaf LMA can be inherently different when small disc samples were used.
-The relatively low *R^2^* values in the Yunnan dataset (Appendix S5) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S6), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S7), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+The relatively low *R^2^* values in the Yunnan dataset (Appendix S1, Figure S4) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S1, Figure S5), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S1, Table S2), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
@@
 This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles [@Niinemets2006; @Niinemets2007; @Sack2012] and the pattern of higher leaf tissue density associated with higher vein density [@John2017; @Sancho-Knapik2020] because those driving factors of LMA are likely to be ignored in leaf disc samples.
-The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix S4), but those effects were not significant.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix S1, Figure S3), but those effects were not significant.
 This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean estimates ($\beta$ in Eq.
@@
 
-Data and codes for this manuscript are archived and available on Zenodo (XXX).
+Data and codes for this manuscript are archived on Zenodo (XXX) and also available at https://github.com/mattocci27/leaf-disc.
 
@@
 **APPENDIX S1.**
+Supplementary tables and figures, including Tables S1–S2 and Figures S1–S5.
+
+**Table S1.**
 Site information.
 
-**APPENDIX S2.**
+**Table S2.**
+Summary of a linear mixed model for log-transformed total dry mass of leaf discs.
+
+**Figure S1.**
 Detailed sampling protocol for whole-leaf and leaf disc LMA.
 
-**APPENDIX S3.**
+**Figure S2.**
 Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
 
-**APPENDIX S4.**
+**Figure S3.**
 Standardized regression coefficients modelig the effects of leaf tissue density, leaf area, leaf thickness, punch size, and their interactios (a) on the mean estimates of whole-leaf LMA, and (b) on the estimated variance of whole-leaf LMA.
 
-**APPENDIX S5.**
+**Figure S4.**
 Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
 
-**APPENDIX S6.**
+**Figure S5.**
 Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
-
-**APPENDIX S7.**
-Summary of a linear mixed model for log-transformed total dry mass of leaf discs.
 
@@
 
+\newpage
+
+# Figure legends
+
 **Fig. 1.**
@@
 Blue solid lines indicate standardized major axis (SMA) regressions.
-The 95% confidence intervals are resented as the shaded area.
+The 95% confidence intervals are represented as the shaded area.
 The correlation is significant (*P* < 0.001).
-
-![](../figs/sma.png)
-
-\newpage
 
@@
 Solid lines indicate the posterior means ($\tilde{\mu}$ in Eq. 1-2), and the shade regions shows $\pm$ the posterior means of standard deviations ($\tilde{\sigma}$ in Eq. 3-4).
-
-![](../figs/pred_mcmc.png)
-
-\newpage
 
@@
 
-![](../figs/petiole.png)
-
-\newpage
-
 **Fig. 4.**
@@
 Details as in Fig. 1.
-
-![](../figs/cv_pool.png)

### 2022-06-18 ms/LMA_method.tex
update appendix

@@
 \usepackage{footnotebackref}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
+We used newly compiled individual-level plant datasets from a wide range of biomes in China and Japan (Appendix S1, Table S1 (see the Supplementary Data with this article)) to examine the relationship between whole-leaf and leaf disc-based estimates of leaf traits.
 First, the Yunnan dataset is from three forest plots in Yunnan province, Southwest China, which includes a tropical rainforest (TRF), a tropical hot-dry savanna ecosystem (HDS), and a subtropical evergreen wet forest (STF), with a total of 141 species and 852 individuals.
 Second, the Yakushima dataset is from a warm-temperate forest in Yakushima island, Japan, with a total of 193 species and 607 individuals.
-In total, our dataset comprised 334 woody species and 1459 individuals that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
+In total, our dataset comprised 334 woody species and 1459 individuals that ranged from 8.1 to 24.7 °C in mean annual temperature (MAT) and 732.8 to 4477 mm in mean annual precipitation (MAP) {[}Appendix S1, Table S1; Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}); Song et al.
 (\protect\hyperlink{ref-Song2017}{2017}); Fei et al.
@@
 Three 0.6-cm diameter discs were taken from the base, middle and tip of each leaf using a hole punch in the Yunnan dataset.
-Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S2 for more details).
+Two 1.0-cm diameter discs were taken from each leaf in the Yakushima dataset (see Appendix S1, Figure S1 for more details).
 Fresh leaf area (LA; cm\textsuperscript{-2}) of leaf materials (whole leaves including petioles and midribs) was measured using a scanner and ImageJ software by the R package \emph{LeafArea} (\protect\hyperlink{ref-Katabuchi2015}{Katabuchi, 2015}).
@@
 Based on those measurements of whole-leaf and leaf disc samples, LMA (g m\textsuperscript{-2}) was calculated as the ratio of leaf dry mass to fresh leaf area, and LD was calculated as the ratio of LMA to LT.
-We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S3).
+We foucs on LMA in our study and we do not present results of LD in the main text, because differences between whole-leaf LD and leaf disc LD only depend on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness (Appendix S1, Figure S2).
 
@@
 On the other hand, a previous study found that leaf disc LMA obtained with a very small leaf punch (0.3-cm diameter) and whole-leaf LMA had different relationships between shade tolerance (\protect\hyperlink{ref-Poorter2009a}{Poorter, 2009}), suggesting that leaf disc LMA and whole-leaf LMA can be inherently different when small disc samples were used.
-The relatively low \emph{R\textsuperscript{2}} values in the Yunnan dataset (Appendix S5) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) or distinct veins with kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S6), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S7), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+The relatively low \emph{R\textsuperscript{2}} values in the Yunnan dataset (Appendix S1, Figure S4) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) or distinct veins with kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S1, Figure S5), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S1, Table S2), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
@@
 This is consistent with the pattern of large leaves disproportionately investing in more leaf veins and/or petioles (\protect\hyperlink{ref-Niinemets2006}{Niinemets et al., 2006}, \protect\hyperlink{ref-Niinemets2007}{2007}; \protect\hyperlink{ref-Sack2012}{Sack et al., 2012}) and the pattern of higher leaf tissue density associated with higher vein density (\protect\hyperlink{ref-John2017}{John et al., 2017}; \protect\hyperlink{ref-Sancho-Knapik2020}{Sancho-Knapik et al., 2020}) because those driving factors of LMA are likely to be ignored in leaf disc samples.
-The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix S4), but those effects were not significant.
+The estimated effects of leaf tissue density and leaf area was also positive for species obtained with a small leaf punch (Appendix S1, Figure S3), but those effects were not significant.
 This is probably because the variation in whole-leaf to leaf disc LMA ratio was too large to show clear effects of leaf tissue density and leaf area on the mean estimates (\(\beta\) in Eq.
@@
 
-Data and codes for this manuscript are archived and available on Zenodo (XXX).
+Data and codes for this manuscript are archived on Zenodo (XXX) and also available at \url{https://github.com/mattocci27/leaf-disc}.
 
@@
 \textbf{APPENDIX S1.}
+Supplementary tables and figures, including Tables S1--S2 and Figures S1--S5.
+
+\textbf{Table S1.}
 Site information.
 
-\textbf{APPENDIX S2.}
+\textbf{Table S2.}
+Summary of a linear mixed model for log-transformed total dry mass of leaf discs.
+
+\textbf{Figure S1.}
 Detailed sampling protocol for whole-leaf and leaf disc LMA.
 
-\textbf{APPENDIX S3.}
+\textbf{Figure S2.}
 Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
 
-\textbf{APPENDIX S4.}
+\textbf{Figure S3.}
 Standardized regression coefficients modelig the effects of leaf tissue density, leaf area, leaf thickness, punch size, and their interactios (a) on the mean estimates of whole-leaf LMA, and (b) on the estimated variance of whole-leaf LMA.
 
-\textbf{APPENDIX S5.}
+\textbf{Figure S4.}
 Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
 
-\textbf{APPENDIX S6.}
+\textbf{Figure S5.}
 Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
-
-\textbf{APPENDIX S7.}
-Summary of a linear mixed model for log-transformed total dry mass of leaf discs.
 
@@
 
+\newpage
+
+\hypertarget{figure-legends}{%
+\section{Figure legends}\label{figure-legends}}
+
 \textbf{Fig. 1.}
@@
 Blue solid lines indicate standardized major axis (SMA) regressions.
-The 95\% confidence intervals are resented as the shaded area.
+The 95\% confidence intervals are represented as the shaded area.
 The correlation is significant (\emph{P} \textless{} 0.001).
-
-\includegraphics{../figs/sma.png}
-
-\newpage
 
@@
 Solid lines indicate the posterior means (\(\tilde{\mu}\) in Eq. 1-2), and the shade regions shows \(\pm\) the posterior means of standard deviations (\(\tilde{\sigma}\) in Eq. 3-4).
-
-\includegraphics{../figs/pred_mcmc.png}
-
-\newpage
 
@@
 
-\includegraphics{../figs/petiole.png}
-
-\newpage
-
 \textbf{Fig. 4.}
@@
 
-\includegraphics{../figs/cv_pool.png}
-
 \end{document}

### 2022-06-18 ms/SI.Rmd
update SI
update appendix

@@
 ---
-title: "Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)"
+title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
 geometry: margin=1in
@@
   - \usepackage{xcolor}
-  - \usepackage{lineno}
-  - \linenumbers
+#  - \usepackage{lineno}
+#  - \linenumbers
 output:
@@
 # val <- yaml::yaml.load_file("../values.yml")
-val <- yaml::yaml.load_file("values.yml")
+#val <- yaml::yaml.load_file("values.yml")
 ```
@@
 # Appendix S1:
+
+Supporting Tables and Figures.
+
+# Table S1:
 
@@
 library(jsonlite)
-# for dependency
-targets::tar_load(site_info)
 #site <- fromJSON("../data/site_info.json")
@@
   kable(format = "html") |>
+  # kable_styling() |>
+  kable_styling(latex_options = "scale_down")
+  #kableExtra::landscape()
+```
+
+The site information and climate data in Yunnan, referred to @Fei2018, and @Song2017.
+MAT and MAP of Yakushima were obtained from the Yakushima meteorological station and @Eguchi2006.
+
+\newpage
+
+# Table S2:
+
+Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
+Species was used as a random intercept.
+The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
+
+```{r, eval=TRUE, echo=FALSE}
+targets::tar_load(dm_glmm_tab)
+dm_glmm_tab |>
+  kable(format = "html") |>
   kable_styling()
@@
 
-The site information and climate data in Yunnan, referred to @Fei2018, and @Song2017.
-MAT and MAP at the lower elevation (37 m) on Yakushima were obtained from the Yakushima meteorological stationj.
-MAT at the higher elevation (1800 m) on Yakushima was obtained from @Eguchi2006.
-
 \newpage
 
-# Appendix S2:
+# Figure S1:
 
@@
 
-# Appendix S3:
+# Figure S2:
 
@@
 ```{r, include=FALSE}
-targets::tar_load(lma_ld_png)
+targets::tar_load(lma_ld_plot)
 ```
@@
 
-# Appendix S4:
+# Figure S3:
 
@@
 
-```{r, incude=FALSE}
+```{r, include=FALSE}
 targets::tar_load(coef_sp_punch1_add_plot)
@@
 
-# Appendix S5:
+# Figure S4:
 
@@
 
+```{r, include=FALSE}
+targets::tar_load(sma_sep_plot)
+```
+
 ![](../figs/sma_sep.png){ width="400" style="display: block; margin: 0 auto" }
@@
 
-# Appendix S6:
+# Figure S5:
 
@@
 
+```{r, include=FALSE}
+targets::tar_load(ratio_dm_plot)
+```
+
 ![](../figs/ratio_dm.png){ width="400" style="display: block; margin: 0 auto" }
@@
 
-# Appendix S7:
-
-Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
-Species was used as a random intercept.
-The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
-
-```{r, eval=TRUE, echo=FALSE}
-tar_load(dm_glmm_tab)
-dm_glmm_tab |>
-  kable(format = "html") |>
-  kable_styling()
-```
-
-\newpage
 # LITERATURE CITED

### 2022-06-18 R/sp_analysis.R

@@ -36,19 +36,15 @@ sma_point_sep <- function(data) {
       values = my_col[c(2, 4)],
       name = "Leaf punch diameter"
     ) +
-    xlab(expression(Leaf ~ disc ~ LMA ~ (g ~ m^{
-      -2
-    }))) +
-    ylab(expression(Whole - leaf ~ LMA ~ (g ~ m^{
-      -2
-    }))) +
+    xlab(expression("Leaf disc LMA "(g~m^{-2}))) +
+    ylab(expression("Whole-leaf LMA "(g~m^{-2}))) +
     stat_cor(
       aes(label = paste(..rr.label.., ..n.label.., sep = "~`,`~"), family = "Arial"),
       show.legend = FALSE
     ) +
     theme_bw() +
     theme(text = element_text(family = "Arial"),
-      legend.position = c(0.8, 0.2),
+      legend.position = c(0.7, 0.15),
       legend.key.size = unit(0.5, "cm"),
       legend.spacing.y = unit(0.1, "cm"),
       legend.text.align = 0,

### 2022-06-18 R/stan.R

@@ -300,6 +300,7 @@ coef_pointrange <- function(data, ld = TRUE, add = FALSE) {
   theme_bw() &
   theme(
     legend.position = "none",
+    plot.tag = element_text(face = "bold"),
     text = element_text(family = "Arial"))
 }
 

### 2022-06-18 _targets.R

@@ -527,8 +527,8 @@ list(
         "figs/sma_sep.png",
         p,
         dpi = 300,
-        width = 4,
-        height = 4
+        width = 3.5,
+        height = 3.5
       )
       paste0("figs/sma_sep", c(".png"))
     },
@@ -557,7 +557,7 @@ list(
         "figs/lma_ld.png",
         p,
         dpi = 300,
-        width = 9,
+        width = 6,
         height = 3
       )
       paste0("figs/lma_ld", c(".png"))

### 2022-06-18 ms/response_letter_2.Rmd
add response letter

---
geometry: margin=1in
link-citations: yes
#csl: templates/xxxx.csl
#bibliography: xxxx.bib
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
 # - \linenumbers
output:
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: no
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

Dear Editors,

We hereby resubmit the manuscript (AJB-D-21-00391R1), “Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)” (Phisamai Maenpuen, Masatoshi Katabuchi, Yusuke Onoda, Cong Zhou, Jiao-Lin Zhang, Ya-Jun Chen).
We thank the associate editor and the reviewers for their careful attention to detail in our manuscript and for providing comments that have greatly improved the study.

We found small errors in R codes and the total number of individuals used in our analysis was increased from 1365 to 1469.
Accordingly, several statistical values have changed slightly (highlighted in blue).

Below we provide detailed responses.
The editing history is recorded in a separate pdf file.

Sincerely,

Masatoshi Katabuchi

Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences

(on behalf of coauthors: Phisamai Maenpuen,Yusuke Onoda, Cong Zhou, Jiao-Lin Zhang, and Ya-Jun Chen)

\newpage

# Responses

> Associate Editor Comments:
> AE comments: I agree with the reviewers that the paper looks much improved. Reviewer 1 has several further minor suggestions.

Thank you again for the positive evalutation.

> Reviewer #1: Review of AJB-D-21-00391_R1

> Overall summary: The authors did a really nice job updating this manuscript in response to the previous reviews. I especially appreciate the inclusion of the section "Conversion between whole-leaf and leaf disc LMA". I also appreciate the updated appendices, which very much help to clarify the experimental design. I just have a few lingering comments, the only major one being about the new section (see comment on lines 311-317):

We are pleased that the reviewer was satisfied with the revsied manuscript.
We also thank you for pointing out typos and style errors.

> Line 123: it would be helpful to rephrase this line to clarify what unit is being reported here. For example: "We collected leaves from ___individuals of 334 species from 4 biomes"

Thank you.
We have added the number of individuals (Line 123).

> Line 139-143 Please report the # of individuals and # of species for each of the two datasets here

Thank you for pointing this error out.
We have added the numbers of species and indivdiuals (Line 142-144)

> Line 169 Remove second "using a micrometer".

Thank you.
We have corrected it (Line 170).

> Lines 311-317 I love this inclusion in the revision. However, I'm not clear on the difference between eq. 1 and 2 and between eq. 3 and 4. Please clarify when authors should use each. Also please clarify how generalizable you believe these equations are.

Thank you.
We have added an explnation of the differences, and the text now reads:
"Note that OLS regressions minimize errors of either whole-leaf LMA or leaf disc LMA, and thus those four models are not identical, whereas SMA regressions are not appropriate for predictions (Warton et al., 2006)" (Line 320-322)

> Line 315 Typo

Thank you again for pointing this error out.
We have corrected it (Line 318).

> Reviewer #2: The authors have well responded to my comments. I can recommend accepting it if the associate editor and another reviewer also feel satisfactory with this revised manuscript.

We are very grateful for the positive feedback.

> Editorial Office Comments:

> For the final manuscript, please submit a clean copy without markup, but do retain line numbers and upload an editable file format (not PDF; preferably MS Word DOC).

Confirmed.

> Key words can greatly enhance the discovery of your article. Please review your key words and consider whether they will help the reader find your work, i.e., that will widen the search-window of topics in your manuscript but also emphasize what is most important in the article. If applicable, include the name of the plant family here (instead of in the title of the article).
For more details see “c. Key Words” at https://bsapubs.onlinelibrary.wiley.com/hub/journal/15372197/homepage/forauthors#ps

> In the Materials and Methods section please provide the city, spelled-out state (if in USA), and country for the locations and companies mentioned (such as L175).

Confirmed:
We have spelled-out state (Ohio) (Line 176).

> Would you like to thank the reviewers in the acknowledgements? It is not required, but we recommend it, especially if you found their comments helpful. (They don’t, as a rule, see your final response letter.)

Confirmed:
We have added a new line for the acknowledgements (line 378).

> Data Availability:
> Please provide a doi for your data deposited in the Zenodo database at this time.

> For more information, see “Data Availability” at https://bsapubs.onlinelibrary.wiley.com/hub/journal/15372197/homepage/forauthors#epec and “g. Data Availability Statement” at https://bsapubs.onlinelibrary.wiley.com/hub/journal/15372197/homepage/forauthors#ps

**working**

> For the online supplements:
> a) For appendices with multiple parts, these parts should be labeled Appendix S1, Table (or Fig) S1; Appendix S1, Table S2, etc.

Confirmed.

> b) In the manuscript, after the first mention of the first online appendix, include the following: “Appendix S1 (see the Supplementary Data with this article)”. Please be sure that each appendix is referred to somewhere in the ms text.

Confirmed.

> c) Finalize and upload each appendix file separately, with the formatting and file type you would like to appear online with the article.

Confirmed.

> d) On each file, place a header at the top of the page, using this format: “Smith et al.—American Journal of Botany 2022—Appendix S1”.

Confirmed.

> e) On each file, also include a title/legend, prefaced by, e.g., “Appendix S1”.

Confirmed.

> For the figures:
> a) Please upload each of your figures as a high-resolution file, cropped of white space, and sized as you would like to see them published (1 column = 3.5 inches; 1.5 column = 5-6 inches; 2 columns = 7.25 inches wide).

Confirmed.

> b) If a figure has multiple panels, keep them together in a single file for that figure.

Confirmed.

> c) For photographs we recommend that authors submit files in TIF, PNG, or EPS format, at 300 ppi.

Confirmed.

> d) For graphs/line art, please save figures as PDF or EPS files (not as JPG, TIF, or other pixel-based formats), at 600 ppi.

Confirmed.

> e) Do not include the figure legends with the figures but instead place them in the manuscript document (after the tables). Please also remove any figure images that remain in the manuscript document at this time.

Confirmed.

> f) For more details see “m. Figures/Illustrations” at https://bsapubs.onlinelibrary.wiley.com/hub/journal/15372197/homepage/forauthors#ps

Confirmed.

> g) Note that supplementary figures have different guidelines, and you do not need to make changes to your supplemental figures, except as described above under online supplements.

Confirmed.

### 2022-06-19 ms/LMA_method.Rmd
update target text

@@
 output:
-  html_document:
-    toc: FALSE
+  # html_document:
+  #   toc: FALSE
 #  pdf_document:
@@
 We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
-All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022].
+All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022] using the package targets version 0.12.0 for workflow management [@Landau2021]
 

### 2022-06-19 ms/LMA_method.tex
update target text

@@
 \linenumbers
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
-All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}).
+All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}) using the package targets version 0.12.0 for workflow management (\protect\hyperlink{ref-Landau2021}{Landau, 2021})
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
+Landau, W.
+M.
+2021.
+\href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {Make-like} function-oriented pipeline toolkit for reproducibility and high-performance computing}.
+\emph{Journal of Open Source Software} 6: 2959.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Leps2011}{}}%

### 2022-06-19 ms/response_letter_2.Rmd
fix line numbers

@@
 Accordingly, several statistical values have changed slightly (highlighted in blue).
+Additionally, we have cited one more R package that made a significant contribution to workflow management (Line 233-234).
 
@@
 We have added an explnation of the differences, and the text now reads:
-"Note that OLS regressions minimize errors of either whole-leaf LMA or leaf disc LMA, and thus those four models are not identical, whereas SMA regressions are not appropriate for predictions (Warton et al., 2006)" (Line 320-322)
+"Note that OLS regressions minimize errors of either whole-leaf LMA or leaf disc LMA, and thus those four models are not identical, whereas SMA regressions are not appropriate for predictions (Warton et al., 2006)" (Line 321-323)
 
@@
 Thank you again for pointing this error out.
-We have corrected it (Line 318).
+We have corrected it (Line 319).
 
@@
 Confirmed:
-We have added a new line for the acknowledgements (line 378).
+We have added a new line for the acknowledgements (line 379-380).
 

### 2022-06-19 ms/LMA_method.Rmd
update zenodo

@@
 We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
-All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022] using the package targets version 0.12.0 for workflow management [@Landau2021]
+All statistical analyses were conducted in R version 4.1.3 [@RCoreTeam2022] using the R package *targets* version 0.12.0 for workflow management [@Landau2021]
 
@@
 
-Data and codes for this manuscript are archived on Zenodo (XXX) and also available at https://github.com/mattocci27/leaf-disc.
+Data and codes for this manuscript are archived on Zenodo at https://doi.org/10.5281/zenodo.6665083 and also available on Github at https://github.com/mattocci27/leaf-disc.
 

### 2022-06-19 ms/LMA_method.tex
update zenodo

@@
 We also performed the paired t-test to compare the extent of ITV between whole-leaf LMA and leaf disc LMA.
-All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}) using the package targets version 0.12.0 for workflow management (\protect\hyperlink{ref-Landau2021}{Landau, 2021})
+All statistical analyses were conducted in R version 4.1.3 (\protect\hyperlink{ref-RCoreTeam2022}{R Core Team, 2022}) using the R package \emph{targets} version 0.12.0 for workflow management (\protect\hyperlink{ref-Landau2021}{Landau, 2021})
 
@@
 
-Data and codes for this manuscript are archived on Zenodo (XXX) and also available at \url{https://github.com/mattocci27/leaf-disc}.
+Data and codes for this manuscript are archived on Zenodo at \url{https://doi.org/10.5281/zenodo.6665083} and also available on Github at \url{https://github.com/mattocci27/leaf-disc}.
 

### 2022-06-19 ms/LMA_method.Rmd
update references and ackowledgements

@@
 The relatively low *R^2^* values in the Yunnan dataset (Appendix S1, Figure S4) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA [@John2017] or distinct veins with kite-type appearances [@Grubb1986] but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S1, Figure S5), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S1, Table S2), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S1, Figure S5), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S1, Table S2), tended to show grater variation in whole-leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
@@
 
-The present study was designed to examine the extent to which whole leaf and leaf disc LMA matched.
+The present study was designed to examine the extent to which whole-leaf and leaf disc LMA matched.
 Although our study was not designed to evaluate the effects of diameter sizes of leaf punches, the sizes of leaf punches as well as leaf morphology are the important sources of variance between whole-leaf and leaf disc LMA.
@@
 We also thank Lian-Bin Tao and Peng-Yun Yan for field work.
-This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).
+This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177)
 PM was supported by financial support from CAS-TWAS President’s Fellowship for International Doctoral Students.

### 2022-06-19 ms/LMA_method.tex
update references and ackowledgements

@@
 The relatively low \emph{R\textsuperscript{2}} values in the Yunnan dataset (Appendix S1, Figure S4) compared to the previous study and the Yakushima dataset may suggest not only the effect of distinct veins on variance in LMA (\protect\hyperlink{ref-John2017}{John et al., 2017}) or distinct veins with kite-type appearances (\protect\hyperlink{ref-Grubb1986}{Grubb, 1986}) but also technical difficulty in measuring tiny weight of discs in lower LMA leaves.
-We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S1, Figure S5), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S1, Table S2), tended to show grater variation in whole leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
+We found that estimates of whole-leaf and leaf disc LMA diverged when total dry mass of leaf discs was small (Appendix S1, Figure S5), and thus species with lower leaf tissue density and thin leaves, which have smaller dry mass (Appendix S1, Table S2), tended to show grater variation in whole-leaf to leaf disc LMA ratio especially when we used a smaller leaf punch.
 
@@
 We also thank Lian-Bin Tao and Peng-Yun Yan for field work.
-This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068).
+This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177)
 PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.
@@
 2022.
-Influence of leaf age on the scaling relationships of lamina biomass vs.
-Area in {Photinia}\texttimes{} fraseri'{Red Robin}'.
+\href{https://doi.org/10.3389/fpls.2022.860206}{Influence of leaf age on the scaling relationships of lamina biomass vs.
+area}.
 \emph{Frontiers in Plant Science} 13: 860206.
@@
 2008.
-\href{https://doi.org/10.1126/science.1160662}{Functional {Traits} and {Niche-Based Tree Community Assembly} in an {Amazonian Forest}}.
+\href{https://doi.org/10.1126/science.1160662}{Functional traits and niche-based tree community assembly in an {Amazonian} forest}.
 \emph{Science} 322: 580--582.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Li2013a}{}}%
-Li, S., Y.-J.
+Li, S., Y.
+J.
 Zhang, L.
@@
 Scoffoni, A.
-Ishida, Y.-J.
-Chen, and K.-F.
+Ishida, Y.
+J.
+Chen, and K.
+F.
 Cao.
@@
 2022.
-\href{https://doi.org/10.3389/fpls.2021.822907}{Application of an {Ovate Leaf Shape Model} to {Evaluate Leaf Bilateral Asymmetry} and {Calculate Lamina Centroid Location}}.
+\href{https://doi.org/10.3389/fpls.2021.822907}{Application of an ovate leaf shape model to evaluate leaf bilateral asymmetry and calculate lamina centroid location}.
 \emph{Frontiers in Plant Science} 12: 822907.
@@
 2014.
-\href{https://doi.org/10.1007/s00442-014-2966-y}{Leaf nitrogen distribution in relation to crown architecture in the tall canopy species, {Fagus} crenata}.
+\href{https://doi.org/10.1007/s00442-014-2966-y}{Leaf nitrogen distribution in relation to crown architecture in the tall canopy species, {\emph{Fagus}}{ \emph{Crenata}}}.
 \emph{Oecologia} 175: 1093--1106.
@@
 Deciduous and evergreen oaks show contrasting adaptive responses in leaf mass per area across environments.
-\emph{New Phytologist}.
+\emph{New Phytologist}: 521--534.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
-Song, Q.-H., Y.-P.
-Zhang, L.-Q.
-Sha, X.-B.
+Song, Q.
+H., Y.
+P.
+Zhang, L.
+Q.
+Sha, X.
+B.
 Deng, Y.
-Deng, C.-S.
-Wu, Z.-Y.
+Deng, C.
+S.
+Wu, Z.
+Y.
 Lu, et al.
@@
 2001.
-\href{https://doi.org/10.1007/PL00013972}{Why are {Sun Leaves Thicker} than {Shade Leaves}?
-\textemdash{} {Consideration} based on {Analyses} of {CO2 Diffusion} in the {Leaf}}.
+\href{https://doi.org/10.1007/PL00013972}{Why are sun leaves thicker than shade leaves?
+\textemdash{} {Consideration} based on analyses of {CO}{\textsubscript{2}} diffusion in the leaf}.
 \emph{Journal of Plant Research} 114: 93--105.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Yang2020}{}}%
-Yang, J., J. Lu, Y. Chen, E. Yan, J. Hu, X. Wang, and G. Shen. 2020. Large {Underestimation} of {Intraspecific Trait Variation} and {Its Improvements}. \emph{Frontiers in Plant Science} 11.
+Yang, J., J.
+Lu, Y.
+Chen, E.
+Yan, J.
+Hu, X.
+Wang, and G.
+Shen.
+2020.
+\href{https://doi.org/10.3389/fpls.2020.00053}{Large {Underestimation} of {Intraspecific Trait Variation} and {Its Improvements}}.
+\emph{Frontiers in Plant Science} 11: 53.
 

### 2022-06-20 ms/LMA_method.Rmd
update acknowledgments

@@
 We thank the editors and two anonymous reviewers, whose comments greatly improved the manuscript.
-We also thank Lian-Bin Tao and Peng-Yun Yan for field work.
-This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177)
+We also thank Lian-Bin Tao and Peng-Yun Yan for field work in China.
+The data collection in Yakushima was achieved with help of many colleagues in particular Kenshi Tetsuka and financially supported by the Global COE Program ‘Asian conservation ecology’, MEXT of Japan for Tetsukazu Yahara.
+This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
 PM was supported by financial support from CAS-TWAS President’s Fellowship for International Doctoral Students.

### 2022-06-20 ms/LMA_method.tex
update acknowledgments

@@
 We thank the editors and two anonymous reviewers, whose comments greatly improved the manuscript.
-We also thank Lian-Bin Tao and Peng-Yun Yan for field work.
-This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177)
+We also thank Lian-Bin Tao and Peng-Yun Yan for field work in China.
+The data collection in Yakushima was achieved with help of many colleagues in particular Kenshi Tetsuka and financially supported by the Global COE Program `Asian conservation ecology', MEXT of Japan for Tetsukazu Yahara.
+This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
 PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.

### 2022-06-20 ms/LMA_method.Rmd
clean main text

@@
 
-```{r tb1, echo=FALSE, eval=FALSE}
-tab1 <- read.csv("../data/sma_sp_ld_tab.csv")
-colnames(tab1) <- c("Data", "Slope", "Intercept", "*R^2^*")
-
-tab1 <- tab1 |>
-  mutate(Data = case_when(
-    Data == "Dense~Thick~Large" ~ "Dense-thick-large",
-    Data == "Dense~Thick~Small" ~ "Dense-thick-small",
-    Data == "Dense~Thin~Large" ~ "Dense-thin-large",
-    Data == "Dense~Thin~Small" ~ "Dense-thin-small",
-    Data == "Nondense~Thick~Large" ~ "Nondense-thick-large",
-    Data == "Nondense~Thick~Small" ~ "Nondense-thick-small",
-    Data == "Nondense~Thin~Large" ~ "Nondense-thin-large",
-    Data == "Nondense~Thin~Small" ~ "Nondense-thin-small",
-    TRUE ~ Data
-  ))
-if ("html" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
-  tab1 |>
-    kable(format = "html") |>
-    kable_classic()
-} else if ("docx" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
-  tab1 |>
-    kable(format = "pipe")
-} else if ("latex" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
-  tab1 |>
-    kable(format = "pipe")
-}
-```
-
-\newpage
-
 # Figure legends
@@
 All the correlations are significant (P < 0.001).
-All the samples were obtained with a diameter 1.0-cm leaf punch.
+Note that all the samples were obtained with a diameter 1.0-cm leaf punch.
 

### 2022-06-20 ms/LMA_method.Rmd
update refs

@@
 
-Data and codes for this manuscript are archived on Zenodo at https://doi.org/10.5281/zenodo.6665083 and also available on Github at https://github.com/mattocci27/leaf-disc.
+Data, codes and computing environments to reproduce this manuscript are archived on Zenodo at https://doi.org/10.5281/zenodo.6665083 and also available on Github at https://github.com/mattocci27/leaf-disc.
 

### 2022-06-20 ms/LMA_method.tex
update refs

@@
 
-Data and codes for this manuscript are archived on Zenodo at \url{https://doi.org/10.5281/zenodo.6665083} and also available on Github at \url{https://github.com/mattocci27/leaf-disc}.
+Data, codes and computing environments to reproduce this manuscript are archived on Zenodo at \url{https://doi.org/10.5281/zenodo.6665083} and also available on Github at \url{https://github.com/mattocci27/leaf-disc}.
 
@@
 2020.
-\href{https://doi.org/10.3389/fpls.2020.00053}{Large {Underestimation} of {Intraspecific Trait Variation} and {Its Improvements}}.
+\href{https://doi.org/10.3389/fpls.2020.00053}{Large underestimation of intraspecific trait variation and its improvements}.
 \emph{Frontiers in Plant Science} 11: 53.
@@
 \end{CSLReferences}
-
-\newpage
 
@@
 All the correlations are significant (P \textless{} 0.001).
-All the samples were obtained with a diameter 1.0-cm leaf punch.
+Note that all the samples were obtained with a diameter 1.0-cm leaf punch.
 

### 2022-06-20 ms/LMA_method.Rmd
clean files

@@
 library(methods)
-source("../scripts/rmd_func.R")
 basename <- "LMA_method"

### 2022-06-20 scripts/LA.R

@@ -1,405 +1,0 @@
-library(tidyverse)
-library(tictoc)
-#library(xlsx)
-
-rm(list = ls())
-data_name <- list.files("data")
-data_name <- data_name[str_detect(data_name, "PV")]
-data_name <- data_name[str_detect(data_name, "csv$")]
-data_name <- data_name[!str_detect(data_name, "Yuanjiang")]
-data_name2 <- paste0("data/",data_name)
-
-#d <- #read.csv("data/PV_Bubeng.csv")
-
-#for (k in 1:3) {
-for (k in 1:length(data_name2)) {
-  d <- read.csv(data_name2[k])
-
-  d2 <- d
-  d2[is.na(d2)] <- "hoge"
-
-  tmp <- NULL
-  LA <- NULL
-  for (j in 1:ncol(d2))
-    for (i in 1:nrow(d2)) {
-      if(str_detect(d2[i, j ], "SWC") == TRUE) {
-        tmp <- c(tmp, j)
-        LA <- c(LA, d2[i - 2, j  + 1])
-      }
-  }
-  LA <- as.numeric(LA)
-  #LA <- LA[!is.na(LA)]
-
-# because some data starts from the 2nd row
-  sp_name <- names(d)
-  #sp_name <- c(names(d), d[1,] |> as.character())
-  sp_name2 <- sp_name[!str_detect(sp_name, "水势|重量|塞重|干重|湿重|面积|结束|[a-z]|[0-9]$")]
-  #sp_name2 <- sp_name[!str_detect(sp_name, "X|长|宽|质量|叶重|水势|重量|塞重|干重|湿重|面积|结束|[a-z]|[0-9]$")]
-  sp_name3 <- str_split_fixed(sp_name2, "[0-9]\\.\\.|[0-9]\\.|[0-9]", 3)
-
-  sp_name4 <- NULL
-  for (i in 1:nrow(sp_name3)) {
-    for (j in 1:ncol(sp_name3))
-      if (sp_name3[i,j] != "X" & sp_name3[i,j] != "")
-      sp_name4 <- c(sp_name4, sp_name3[i, j])
-  }
-
-  sp_name5 <- str_split_fixed(sp_name4[sp_name4 != "NA"], " ", 2)
-  sp_name6 <- NULL
-  for (i in 1:nrow(sp_name5)) {
-    for (j in 1:ncol(sp_name5))
[…]

### 2022-06-20 scripts/database.R

@@ -1,13 +1,0 @@
-library(tidyverse)
-library(RSQLite)
-
-if (file.exists("./data/try.sqlite3")) system("rm ./data/try.sqlite3")
-db <- dbConnect(SQLite(), "./data/try.sqlite3", synchronous="off")
-
-d <- read_delim("./data/TRY_DATA.txt", "\t")
-
-db %>% dbWriteTable("try", d)
-
-data_list <- dbListTables(db)
-
-print(paste("Created:", data_list))

### 2022-06-21 ms/response_letter_2.Rmd
update zenodo
update acknowledgments
update contribtuions and acknowledgment

@@
 
-We found small errors in R codes and the total number of individuals used in our analysis was increased from 1365 to 1469.
+First, we found small errors in R codes and the total number of individuals used in our analysis was increased from 1365 to 1469.
 Accordingly, several statistical values have changed slightly (highlighted in blue).
-Additionally, we have cited one more R package that made a significant contribution to workflow management (Line 233-234).
+Second, we have cited one more R package that made a significant contribution to workflow management (Line 233-234).
+Finally, we would like add Masatoshi Katabuchi as co-first author, if the journal does not have the limitation for this arrangement.
 
@@
 
-Thank you again for the positive evalutation.
+Thank you again for the positive evaluation.
 
@@
 
-We are pleased that the reviewer was satisfied with the revsied manuscript.
+We are pleased that the reviewer was satisfied with the revised manuscript.
 We also thank you for pointing out typos and style errors.
@@
 Thank you.
-We have added the number of individuals (Line 123).
+We have added the number of individuals (Line 124).
 
@@
 Thank you for pointing this error out.
-We have added the numbers of species and indivdiuals (Line 142-144)
+We have added the numbers of species and individuals (Line 143-145).
 
@@
 Thank you.
-We have corrected it (Line 170).
+We have corrected it (Line 171).
 
@@
 Thank you again for pointing this error out.
-We have corrected it (Line 319).
+We have corrected it (Line 320).
 
@@
 Confirmed:
-We have spelled-out state (Ohio) (Line 176).
+We have spelled-out state (Ohio) (Line 177).
 
@@
 Confirmed:
-We have added a new line for the acknowledgements (line 379-380).
+We have added a new line for the acknowledgements (line 380-381).
 
@@
 
-**working**
+Confirmed.
+We have added the DOI: https://doi.org/10.5281/zenodo.6665083 (Line 397-398)
 

### 2022-06-21 ms/LMA_method.Rmd
update contribtuions and acknowledgment

@@
 
-Phisamai Maenpuen^1,2,3^,
+Phisamai Maenpuen^1,2,3\*^,
 Masatoshi Katabuchi^1\*^,
@@
 We also thank Lian-Bin Tao and Peng-Yun Yan for field work in China.
+This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
 The data collection in Yakushima was achieved with help of many colleagues in particular Kenshi Tetsuka and financially supported by the Global COE Program ‘Asian conservation ecology’, MEXT of Japan for Tetsukazu Yahara.
-This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS 'Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
 PM was supported by financial support from CAS-TWAS President’s Fellowship for International Doctoral Students.

### 2022-06-21 ms/LMA_method.tex
update contribtuions and acknowledgment

@@
 
-Phisamai Maenpuen\textsuperscript{1,2,3},
+Phisamai Maenpuen\textsuperscript{1,2,3*},
 Masatoshi Katabuchi\textsuperscript{1*},
@@
 Cong Zhou\textsuperscript{1,2},
-Jiao-Lin Zhang\textsuperscript{1,3*},
+Jiao-Lin Zhang\textsuperscript{1,3},
 Ya-Jun Chen\textsuperscript{1,3,5}
@@
 E-mail: \href{mailto:zjl@xtbg.org.cn}{\nolinkurl{zjl@xtbg.org.cn}}
+
+* These authors contributed equally to this work.
 
@@
 We also thank Lian-Bin Tao and Peng-Yun Yan for field work in China.
+This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
 The data collection in Yakushima was achieved with help of many colleagues in particular Kenshi Tetsuka and financially supported by the Global COE Program `Asian conservation ecology', MEXT of Japan for Tetsukazu Yahara.
-This work was funded by the National Natural Science Foundation of China (41861144016, 32071735, 31570406, 32171507), the CAS `Light of West China' Program, Yunnan Provincial Science and Technology Department (2018HB068), and Yunnan Revitalization Talents Support Plan (YNWR-QNBJ-2019-177).
 PM was supported by financial support from CAS-TWAS President's Fellowship for International Doctoral Students.

### 2022-06-25 ms/SI.Rmd
update SI PDF

@@
     keep_tex: yes
-    toc: no
+    toc: yes
     number_sections: no
@@
     #template: null
-    pandoc_args:
-      - "--filter"
-      - "pandoc-crossref"
+    # pandoc_args:
+    #   - "--filter"
+    #   - "pandoc-crossref"
   word_document:
@@
 library(targets)
+library(here)
+library(kableExtra)
 basename <- "LMA_method"
@@
 options(kableExtra.auto_format = FALSE)
-library(kableExtra)
-
 # for dependency
-targets::tar_load(yml)
+#targets::tar_load(yml)
 #  for non-targets
@@
 
+\newpage
+
 # Table S1:
@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, caption = "hopge"}
 library(jsonlite)
 #site <- fromJSON("../data/site_info.json")
-site <- fromJSON("data/site_info.json")
+#site <- fromJSON("data/site_info.json")
+site <- fromJSON(here("data", "site_info.json"))
 site |>
-  kable(format = "html") |>
+  kable(format = "latex",
+    caption = "Site information.
+              MAT: mean annual temperature,
+              MAP: mean annual precipitation,
+              CV: coefficient of variation") |>
   # kable_styling() |>
-  kable_styling(latex_options = "scale_down")
-  #kableExtra::landscape()
+  kable_styling(latex_options = "scale_down") |>
+  # column_spec(13:16, width = "2cm") |>
+  column_spec(1:16, width = "2cm") |>
+  kableExtra::landscape()
 ```
@@
 ```{r, eval=TRUE, echo=FALSE}
-targets::tar_load(dm_glmm_tab)
-dm_glmm_tab |>
-  kable(format = "html") |>
+dm_glmm <- read_csv(here("data", "dm_glmm.csv"))
+dm_glmm |>
+  kable(format = "latex") |>
   kable_styling()
@@
 
-```{r, include=FALSE}
-targets::tar_load(lma_ld_plot)
-```
-
-![](../figs/lma_ld.png){ width="600" style="display: block; margin: 0 auto" }
+![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto" }
 
@@
 
-```{r, include=FALSE}
-targets::tar_load(coef_sp_punch1_add_plot)
-```
-
-![](../figs/coef_sp_punch1_add.png)
+![](../figs/coef_sp_punch1_add.pdf)
 
@@
 
-```{r, include=FALSE}
-targets::tar_load(sma_sep_plot)
-```
-
-![](../figs/sma_sep.png){ width="400" style="display: block; margin: 0 auto" }
+![](../figs/sma_sep.pdf){ width="400" style="display: block; margin: 0 auto" }
 
@@
 
-```{r, include=FALSE}
-targets::tar_load(ratio_dm_plot)
-```
-
-![](../figs/ratio_dm.png){ width="400" style="display: block; margin: 0 auto" }
+![](../figs/ratio_dm.pdf){ width="400" style="display: block; margin: 0 auto" }
 

### 2022-06-25 ms/SI.tex
update SI PDF

@@
 \hypersetup{
-  pdftitle={Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)},
+  pdftitle={Maenpuen et al. --American Journal of Botany-- Appendix S1},
   hidelinks,
@@
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 % add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
@@
 \usepackage{xcolor}
-\usepackage{lineno}
-\linenumbers
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 
-\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
-mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
+\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
+S1}
 \date{}
@@
 \usepackage{titling}
-\title{Maenpuen et al.~Appendix S1-7: Sources and consequences of
-mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
+\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
+S1}
 \author{}
@@
 %
-
-\definecolor{table-row-color}{HTML}{F5F5F5}
-\definecolor{table-rule-color}{HTML}{999999}
-
-%\arrayrulecolor{black!40}
-\arrayrulecolor{table-rule-color}     % color of \toprule, \midrule, \bottomrule
-\setlength\heavyrulewidth{0.3ex}      % thickness of \toprule, \bottomrule
-\renewcommand{\arraystretch}{1.3}     % spacing (padding)
 
@@
   \fancyfoot{}
-  \lhead[]{Maenpuen et al.~Appendix S1-7: Sources and consequences of
-mismatch between leaf disc and whole-leaf leaf mass per area (LMA)}
+  \lhead[]{Maenpuen \emph{et al.} --American Journal of Botany--
+Appendix S1}
   \chead[]{}
-  \rhead[Maenpuen et al.~Appendix S1-7: Sources and consequences of
-mismatch between leaf disc and whole-leaf leaf mass per area (LMA)]{}
+  \rhead[Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
+S1]{}
   %\lfoot[\thepage]{}
@@
 
+{
+\setcounter{tocdepth}{2}
+\tableofcontents
+}
 \hypertarget{appendix-s1}{%
@@
 
-Site information. MAT: mean annual temperature, MAP: mean annual
-precipitation, SPEI: Standardized Precipitation Evapotranspiration
-Index.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0741}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.2469}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0926}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0556}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0617}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1235}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1173}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1049}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Site name
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Vegetation
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Elevation (m)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Locations
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-MAT (℃)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-MAP (mm)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Dry period (month)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Canopy height (m)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Species number
-\end{minipage} \\
-\midrule
-\endhead
-Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35' E & 21 & 1532 &
-6 & 35-45 & 60 \\
-Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 &
-24°32'N,101°01'E & 11.7 & 1931 & - & 25 & 47 \\
-Yuanjiang & Hot-dry savanna (HDS) & 480 & 23°28'N, 102°10'E & 24.7 &
-732.8 & 6 & 4-6 & 34 \\
-Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 19.4
-& 4477 & - & - & 193 \\
-\bottomrule
-\end{longtable}
-
-The site information and climate data referred to Fei et al.
-(\protect\hyperlink{ref-Fei2018}{2018}) and Song et al.
-(\protect\hyperlink{ref-Song2017}{2017}). The 6-month-SPEI data were
-extracted from the Global SPEI database
-(\url{http://spei.csic.es/map/maps.html\#months=1\#month=7\#year=2019}).
+Supporting Tables and Figures.
 
@@
 
-\hypertarget{appendix-s2}{%
-\section{Appendix S2:}\label{appendix-s2}}
+\hypertarget{table-s1}{%
+\section{Table S1:}\label{table-s1}}
+
+Site information. MAT: mean annual temperature, MAP: mean annual
+precipitation, CV: coefficient of variation
+
+\begin{landscape}\begin{table}
+
+\caption{\label{tab:unnamed-chunk-1}Site information.
+              MAT: mean annual temperature,
+              MAP: mean annual precipitation,
+              CV: coefficient of variation}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}}
+\hline
+Data name & Site name & Vegetation & Elevation (m) & Location & MAT (℃) & MAP (mm) & Dry period (month) & Canopy height (m) & Leaf thickness & Leaf disc thickness & Leaf punch diameter (cm) & Number of species for species means & Number of individuals for individuals means & Number of species for CV & Number of individuals for CV\\
+\hline
+Yunnan & Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35'E & 21 & 1532.0 & 6 & 35-45 & Measured & Measured & 0.6 & 60 & 366 & 60 & 366\\
+\hline
+Yunnan & Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 & 24°32'N, 101°01'E & 11.7 & 1931.0 & - & 25 & Measured & Measured & 0.6 & 47 & 282 & 47 & 282\\
+\hline
+Yunnan & Yuanjiang & Hot-dry savanna  (HDS) & 480 & 23°28'N, 102°10'E & 24.7 & 732.8 & 6 & 6-Apr & Measured & Measured & 0.6 & 34 & 204 & 33 & 203\\
+\hline
+Yakushima & Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 8.1 - 19.4 & 4477.0 & - & - & Measured & Not-measured & 1.0 & 193 & 607 & 5 & 26\\
+\hline
+\end{tabular}}
+\end{table}
+\end{landscape}
+
+The site information and climate data in Yunnan, referred to Fei et al.
+(\protect\hyperlink{ref-Fei2018}{2018}), and Song et al.
+(\protect\hyperlink{ref-Song2017}{2017}). MAT and MAP of Yakushima were
+obtained from the Yakushima meteorological station and Eguchi
+(\protect\hyperlink{ref-Eguchi2006}{2006}).
+
+\newpage
+
+\hypertarget{table-s2}{%
+\section{Table S2:}\label{table-s2}}
+
+Summary of a linear mixed model for log-transformed total dry mass of
+leaf discs for each tree individual. Species was used as a random
+intercept. The leaf punch size is described as an effect of `0.6 cm
+diameter' compared with `1.0 cm diameter'.
+
+\begin{table}
+\centering
+\begin{tabular}{r|r|r|r|l}
+\hline
+Estimate & SE & DF & t-value & *P* value\\
+\hline
+-4.410 & 0.013 & 1030 & -333.00 & < 0.001\\
+\hline
+0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
+\hline
+-0.061 & 0.009 & 1030 & -6.94 & < 0.001\\
+\hline
+0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
+\hline
+-0.500 & 0.020 & 332 & -25.60 & < 0.001\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{figure-s1}{%
+\section{Figure S1:}\label{figure-s1}}
+
+Detailed sampling protocol for whole-leaf and leaf disc LMA.
+
+\includegraphics{../figs/S2.jpeg}
+
+\newpage
+
+\hypertarget{figure-s2}{%
+\section{Figure S2:}\label{figure-s2}}
 
@@
 
-\includegraphics[width=6.25in,height=\textheight]{../figs/fig1.png}
+\includegraphics[width=6.25in,height=\textheight]{../figs/lma_ld.pdf}
 
@@
 
-\hypertarget{appendix-s3}{%
-\section{Appendix S3:}\label{appendix-s3}}
+\hypertarget{figure-s3}{%
+\section{Figure S3:}\label{figure-s3}}
 
-Relationships between whole-leaf LMA : disc leaf LMA and (a) total dry
-mass for the leaf disc, (b) leaf thickness, and (c) leaf area. (b) and
-(c) follow the same legend. All the relationships were heteroscedastic
-(unequal variance, \emph{p} \textless{} 0.001; all the samples were
-analyzed together in (a)). Samples with small total dry mass, thin
-leaves, and larger leaves tended to show greater variance.
+Standardized regression coefficients modelig the effects of leaf tissue
+density, leaf area, leaf thickness, punch size, and their interactios
+(a) on the mean estimates of whole-leaf LMA, and (b) on the estimated
+variance of whole-leaf LMA. The leaf disc LMA was used for the baseline
+mean of the whole-leaf LMA. Thick and thin lines indicate 90\% and 95\%
+credible intervals, respectively. Circles show posterior means of
+coefficients. Circles filled with blue indicate significant effects and
+white indicate non-significance effects.
 
-\includegraphics{../figs/LMAratio2.png}
+\includegraphics{../figs/coef_sp_punch1_add.pdf}
 
@@
 
-\hypertarget{appendix-s4}{%
-\section{Appendix S4:}\label{appendix-s4}}
+\hypertarget{figure-s4}{%
+\section{Figure S4:}\label{figure-s4}}
 
-Summary of multiple regression for log-transformed total dry mass of
-leaf discs. The leaf punch size is described as an effect of `1.0 cm
-diameter' compared with `0.6 cm diameter'.
+Relationships between species mean leaf mass per area (LMA) determined
+by using whole-leaves and leaf discs for species obtained with leaf
+punches of different diameters. Dashed lines indicate 1:1 lines. Blue
+solid lines indicate standardized major axis (SMA) regressions. The 95\%
+confidence intervals are resented as the shaded area. The correlation is
+significant (\emph{P} \textless{} 0.001).
 
-\begin{longtable}[]{@{}lllll@{}}
-\toprule
-& Estimate & SE & t-value & \emph{P} value \\
-\midrule
-\endhead
-(Intercept) & -4.86 & 0.012 & -410 & \textless{} 0.001 \\
-log(Leaf thickness) & 0.223 & 0.009 & 23.7 & \textless{} 0.001 \\
-log(Leaf area) & -0.092 & 0.01 & -9.27 & \textless{} 0.001 \\
-Large leaf punch & 0.391 & 0.021 & 18.7 & \textless{} 0.001 \\
-\bottomrule
-\end{longtable}
+\includegraphics[width=4.16667in,height=\textheight]{../figs/sma_sep.pdf}
 
@@
 
-\hypertarget{appendix-s5}{%
-\section{Appendix S5:}\label{appendix-s5}}
+\hypertarget{figure-s5}{%
+\section{Figure S5:}\label{figure-s5}}
 
-Relationships between species mean leaf mass per area (LMA) determined
-by using whole leaves and leaf discs. Species groups are divided into
-four categories on the basis of the medians of the leaf size and leaf
-thickness across all the species. Estimates obtained by different leaf
-punches are plotted separately in different colors. All the correlations
-are significant (\emph{P} \textless{} 0.001).
+Relationships between whole-leaf LMA : disc leaf LMA and total dry mass
+for the leaf disc. The relationships was heteroscedastic (unequal
+variance, \emph{p} \textless{} 0.001; all the samples were analyzed
+together). Samples with small total dry mass tended to show greater
+variance.
 
-\includegraphics[width=6.25in,height=\textheight]{../figs/LMA_sp_gr_both.png}
-
-\hypertarget{appendix-s6}{%
-\section{Appendix S6:}\label{appendix-s6}}
-
-Relationships between petiole to leaf dry mass ratio and (a) leaf area
-and (b) whole-leaf to leaf disc LMA ratio. Blue solid lines indicate
-ordinary least squares (OLS) regressions. The 95\% confidence intervals
-are presented as the shaded area. All the correlations are significant
-(\emph{P} \textless{} 0.001).
-
-\includegraphics[width=6.25in,height=\textheight]{../figs/petiole.png}
-
-\newpage
-
-\hypertarget{appendix-s7}{%
-\section{Appendix S7:}\label{appendix-s7}}
-
-Relationships between coefficient of variation (CV) in LMA determined by
-using whole leaves and leaf discs: (a) 0.6 cm diameter leaf punch, and
-(b) 1.0 cm diameter leaf punch. Dashed lines indicate 1:1 lines. Blue
-solid lines indicate standardized major axis regressions. The 95\%
-confidence intervals are presented as the shaded area. All the
-correlations are significant (\emph{P} \textless{} 0.01). Note that the
-axes are square root scales.
-
-\includegraphics[width=6.25in,height=\textheight]{../figs/fig_cv2.png}
+\includegraphics[width=4.16667in,height=\textheight]{../figs/ratio_dm.pdf}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Eguchi2006}{}}%
+Eguchi, T. 2006. Climate. Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in
+Japanese)}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
-Song, Q.-H., Y.-P. Zhang, L.-Q. Sha, X.-B. Deng, Y. Deng, C.-S. Wu,
-Z.-Y. Lu, et al. 2017.
-\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature
-variability in a tropical rainforest, subtropical evergreen forest, and
-savanna forest in {Southwest China}}. \emph{iForest - Biogeosciences and
-Forestry} 10: 611.
+Song, Q. H., Y. P. Zhang, L. Q. Sha, X. B. Deng, Y. Deng, C. S. Wu, Z.
+Y. Lu, et al. 2017. \href{https://doi.org/10.3832/ifor2223-010}{Canopy
+temperature variability in a tropical rainforest, subtropical evergreen
+forest, and savanna forest in {Southwest China}}. \emph{iForest -
+Biogeosciences and Forestry} 10: 611.
 

### 2022-06-25 R/ind_analysis.R

@@ -25,7 +25,10 @@ dm_glmm <- function(tree) {
   rownames(tb)[3] <- "log(Leaf area)"
   rownames(tb)[4] <- "log(Leaf thickness)"
   rownames(tb)[5] <- "Small leaf punch"
-  tb
+  tb |>
+    as_tibble() |>
+    write_csv("data/dm_glmm.csv")
+  paste("data/dm_glmm.csv")
 }
 
 

### 2022-06-25 _targets.R

@@ -530,7 +530,14 @@ list(
         width = 3.5,
         height = 3.5
       )
-      paste0("figs/sma_sep", c(".png"))
+      ggsave(
+        "figs/sma_sep.pdf",
+        p,
+        device = cairo_pdf,
+        width = 3.5,
+        height = 3.5
+      )
+      paste0("figs/sma_sep", c(".png", ".pdf"))
     },
     format = "file"
   ),
@@ -545,7 +552,14 @@ list(
         width = 3,
         height = 3
       )
-      paste0("figs/ratio_dm", c(".png"))
+      ggsave(
+        "figs/ratio_dm.pdf",
+        p,
+        device = cairo_pdf,
+        width = 3,
+        height = 3
+      )
+      paste0("figs/ratio_dm", c(".png", ".pdf"))
     },
     format = "file"
   ),
@@ -560,7 +574,14 @@ list(
         width = 6,
         height = 3
       )
-      paste0("figs/lma_ld", c(".png"))
+      ggsave(
+        "figs/lma_ld.pdf",
+        p,
+        device = cairo_pdf,
+        width = 6,
+        height = 3
+      )
+      paste0("figs/lma_ld", c(".png", ".pdf"))
     },
     format = "file"
   ),
@@ -631,15 +652,16 @@ list(
 
   tar_target(
     dm_glmm_tab,
-    dm_glmm(tree)
+    dm_glmm(tree),
+    format = "file"
   ),
   tar_render(
     report,
     "report.Rmd"
-   ),
-  tar_render(
-    si,
-    "ms/SI.Rmd",
-    output_format = "html_document"
    )
+  # tar_render(
+  #   si,
+  #   "ms/SI.Rmd",
+  #   output_format = "pdf_document"
+  #  )
 )

### 2022-06-26 ms/SI.Rmd
fix table direction and site information

@@
 ---
-title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
+title: "Appendix S1: Supporting Tables and Figures."
+#title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
 geometry: margin=1in
@@
 #font-famliy: "ebgaramond"
+mainfont: Arial
+sansfont: Arial
 header-includes:
@@
   - \usepackage{tabu}
-  - \usepackage{threeparttable}
-  - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
@@
   - \usepackage{xcolor}
-#  - \usepackage{lineno}
+  - \usepackage{caption}
+  - \usepackage{fancyhdr}
+  - \pagestyle{fancy}  # enable header
+  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
+  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1} # add header on right side
+ # - \captionsetup[figure]{name=Figure S} #  - \usepackage{lineno}
 #  - \linenumbers
@@
       toc: true
-  pdf_document:
-    keep_md: false
-    fig_caption: yes
-    keep_tex: yes
+  bookdown::pdf_document2:
+    citation_package: default
     toc: yes
     number_sections: no
-    template: templates/eisvogel2.tex
-    #template: null
-    # pandoc_args:
-    #   - "--filter"
-    #   - "pandoc-crossref"
-  word_document:
-    fig_width: 6
-    fig_caption: yes
-    toc: FALSE
-    reference_docx: templates/rmd_style.docx
-    pandoc_args:
-    - "--filter"
-    - "pandoc-crossref"
-    - "--mathml"
+    fig_caption: no
+    keep_tex: yes
+    # template: templates/eisvogel2.tex
 ---
@@
 options(kableExtra.auto_format = FALSE)
-# for dependency
-#targets::tar_load(yml)
-#  for non-targets
-# val <- yaml::yaml.load_file("../values.yml")
-#val <- yaml::yaml.load_file("values.yml")
 ```
-
-# Appendix S1:
-
-Supporting Tables and Figures.
 
@@
 MAP: mean annual precipitation,
-CV: coefficient of variation
+CV: coefficient of variation.
 
@@
 library(jsonlite)
-#site <- fromJSON("../data/site_info.json")
-#site <- fromJSON("data/site_info.json")
 site <- fromJSON(here("data", "site_info.json"))
-site |>
-  kable(format = "latex",
-    caption = "Site information.
-              MAT: mean annual temperature,
-              MAP: mean annual precipitation,
-              CV: coefficient of variation") |>
-  # kable_styling() |>
-  kable_styling(latex_options = "scale_down") |>
-  # column_spec(13:16, width = "2cm") |>
-  column_spec(1:16, width = "2cm") |>
-  kableExtra::landscape()
+site2 <- t(site)
+site2[1,] <- t(site)[2,]
+site2[2,] <- t(site)[1,]
+colnames(site2) <- site2[1,]
+site2 <- site2[-1,]
+site2 |>
+  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
+  #kable(format = "simple") |>
+    # caption = "Site information.
+    #           MAT: mean annual temperature,
+    #           MAP: mean annual precipitation,
+    #           CV: coefficient of variation") |>
+  kable_styling(latex_options = c("striped", "HOLD_position")) |>
+  column_spec(1:5, width = "3cm")# |>
+#  kableExtra::landscape()
 ```
@@
 \newpage
-
 # Table S2:
@@
 dm_glmm |>
-  kable(format = "latex") |>
-  kable_styling()
+  rename(`\\textit{P} value` = `*P* value`) |>
+  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
+  kable_styling(latex_options = c("striped", "HOLD_position"))
 ```
@@
 
-![](../figs/S2.jpeg)
+![](../figs/S2.jpeg){ width="470" style="display: block; margin: 0 auto" }
 
@@
 
-Figure: Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
+Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
 Dashed lines indicate 1:1 lines.

### 2022-06-26 ms/SI.tex
fix table direction and site information

@@
-%%
-% Copyright (c) 2017 - 2020, Pascal Wagler;
-% Copyright (c) 2014 - 2020, John MacFarlane
-%
-% All rights reserved.
-%
-% Redistribution and use in source and binary forms, with or without
-% modification, are permitted provided that the following conditions
-% are met:
-%
-% - Redistributions of source code must retain the above copyright
-% notice, this list of conditions and the following disclaimer.
-%
-% - Redistributions in binary form must reproduce the above copyright
-% notice, this list of conditions and the following disclaimer in the
-% documentation and/or other materials provided with the distribution.
-%
-% - Neither the name of John MacFarlane nor the names of other
-% contributors may be used to endorse or promote products derived
-% from this software without specific prior written permission.
-%
-% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
-% "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
-% LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
-% FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE
-% COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
-% INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING,
-% BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
-% LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
-% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
-% LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN
-% ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
-% POSSIBILITY OF SUCH DAMAGE.
-%%
-
-%%
-% This is the Eisvogel pandoc LaTeX template.
-%
-% For usage information and examples visit the official GitHub page:
-% https://github.com/Wandmalfarbe/pandoc-latex-template
-%%
-
-\DeclareUnicodeCharacter{2212}{-}
-
 % Options for packages loaded elsewhere
@@
 \PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*,table}{xcolor}
 %
@@
   12pt,
-  a4paper,
-,tablecaptionabove
-]{scrartcl}
+]{article}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{setspace}
-\setstretch{1.2}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \setmainfont[]{Arial}
+  \setsansfont[]{Arial}
 \fi
@@
 \usepackage{xcolor}
-\definecolor{default-linkcolor}{HTML}{A50000}
-\definecolor{default-filecolor}{HTML}{A50000}
-\definecolor{default-citecolor}{HTML}{4077C0}
-\definecolor{default-urlcolor}{HTML}{4077C0}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \hypersetup{
-  pdftitle={Maenpuen et al. --American Journal of Botany-- Appendix S1},
+  pdftitle={Appendix S1: Supporting Tables and Figures.},
   hidelinks,
-  breaklinks=true,
-  pdfcreator={LaTeX via pandoc with the Eisvogel template}}
+  pdfcreator={LaTeX via pandoc}}
 \urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-% add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
-\usepackage{footnotebackref}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-
-% Make use of float-package and set default placement for figures to H.
-% The option H means 'PUT IT HERE' (as  opposed to the standard h option which means 'You may put it here if you like').
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
 \usepackage{float}
-\floatplacement{figure}{H}
-
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\usepackage{caption}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancypagestyle{plain}{\pagestyle{fancy}}
+\fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
 \usepackage{booktabs}
@@
 \usepackage{xcolor}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
-S1}
-\date{}
-
-%%
-%% added
-%%
-
-%
-% language specification
-%
-% If no language is specified, use English as the default main document language.
-%
-
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-    % Workaround for bug in Polyglossia that breaks `\familydefault` when `\setmainlanguage` is used.
-  % See https://github.com/Wandmalfarbe/pandoc-latex-template/issues/8
-  % See https://github.com/reutenauer/polyglossia/issues/186
-  % See https://github.com/reutenauer/polyglossia/issues/127
-  \renewcommand*\familydefault{\sfdefault}
-    % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
 \fi
 
-%
-% for the background color of the title page
-%
-
-%
-% break urls
-%
-\PassOptionsToPackage{hyphens}{url}
-
-%
-% When using babel or polyglossia with biblatex, loading csquotes is recommended
-% to ensure that quoted texts are typeset according to the rules of your main language.
-%
-\usepackage{csquotes}
-
-%
-% captions
-%
-%\definecolor{caption-color}{HTML}{777777}
-\definecolor{caption-color}{HTML}{37474F}
-%\usepackage[font={stretch=1.2}, textfont={color=caption-color}, position=top, skip=4mm, labelfont=bf, singlelinecheck=false, justification=raggedright]{caption}
-\usepackage[font={stretch=1}, textfont={color=caption-color}, position=top, skip=2mm, labelfont=bf, singlelinecheck=false, justification=raggedright]{caption}
-\setcapindent{0em}
-
-%
-% blockquote
-%
-\definecolor{blockquote-border}{RGB}{221,221,221}
-\definecolor{blockquote-text}{RGB}{119,119,119}
-\usepackage{mdframed}
-\newmdenv[rightline=false,bottomline=false,topline=false,linewidth=3pt,linecolor=blockquote-border,skipabove=\parskip]{customblockquote}
-\renewenvironment{quote}{\begin{customblockquote}\list{}{\rightmargin=0em\leftmargin=0em}%
-\item\relax\color{blockquote-text}\ignorespaces}{\unskip\unskip\endlist\end{customblockquote}}
-
-%
-% Source Sans Pro as the de­fault font fam­ily
-% Source Code Pro for monospace text
-%
-% 'default' option sets the default
-% font family to Source Sans Pro, not \sfdefault.
-%
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-    \usepackage[default]{sourcesanspro}
-  \usepackage{sourcecodepro}
-  %\usepackage{}
-  \else % if not pdftex
-    \usepackage[default]{sourcesanspro}
-  \usepackage{sourcecodepro}
-  %\usepackage{}
-
-  % XeLaTeX specific adjustments for straight quotes: https://tex.stackexchange.com/a/354887
-  % This issue is already fixed (see https://github.com/silkeh/latex-sourcecodepro/pull/5) but the
-  % fix is still unreleased.
-  % TODO: Remove this workaround when the new version of sourcecodepro is released on CTAN.
-  \ifxetex
-    \makeatletter
-    \defaultfontfeatures[\ttfamily]
-      { Numbers   = \sourcecodepro@figurestyle,
-        Scale     = \SourceCodePro@scale,
-        Extension = .otf }
-    \setmonofont
-      [ UprightFont    = *-\sourcecodepro@regstyle,
-        ItalicFont     = *-\sourcecodepro@regstyle It,
-        BoldFont       = *-\sourcecodepro@boldstyle,
-        BoldItalicFont = *-\sourcecodepro@boldstyle It ]
-      {SourceCodePro}
-    \makeatother
-  \fi
-  \fi
-
-%
-% heading color
-%
-\definecolor{heading-color}{RGB}{40,40,40}
-\addtokomafont{section}{\color{heading-color}}
-% When using the classes report, scrreprt, book,
-% scrbook or memoir, uncomment the following line.
-%\addtokomafont{chapter}{\color{heading-color}}
-
-%
-% variables for title and author
-%
-\usepackage{titling}
-\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
-S1}
+\title{Appendix S1: Supporting Tables and Figures.}
 \author{}
-
-%
-% tables
-%
-
-%
-% remove paragraph indention
-%
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-
-%
-%
-% Listings
-%
-%
-
-%
-% header and footer
-%
-\usepackage{fancyhdr}
-
-\fancypagestyle{eisvogel-header-footer}{
-  \fancyhead{}
-  \fancyfoot{}
-  \lhead[]{Maenpuen \emph{et al.} --American Journal of Botany--
-Appendix S1}
-  \chead[]{}
-  \rhead[Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
-S1]{}
-  %\lfoot[\thepage]{}
-  \cfoot[]{}
-  \cfoot[]{\thepage}
-  \renewcommand{\headrulewidth}{0.0pt}
- % \renewcommand{\footrulewidth}{0.0pt}
- % \renewcommand{\headrulewidth}{0.4pt}
- % \renewcommand{\footrulewidth}{0.4pt}
-}
-\pagestyle{eisvogel-header-footer}
-
-%%
-%% end added
-%%
+\date{\vspace{-2.5em}}
 
 \begin{document}
-
-%%
-%% begin titlepage
-%%
-
-%%
-%% end titlepage
-%%
+\maketitle
 
@@
 }
-\hypertarget{appendix-s1}{%
-\section{Appendix S1:}\label{appendix-s1}}
-
-Supporting Tables and Figures.
-
 \newpage
@@
 
-Site information. MAT: mean annual temperature, MAP: mean annual
-precipitation, CV: coefficient of variation
-
-\begin{landscape}\begin{table}
-
-\caption{\label{tab:unnamed-chunk-1}Site information.
+Site information.
 MAT: mean annual temperature,
 MAP: mean annual precipitation,
-              CV: coefficient of variation}
+CV: coefficient of variation.
+
+\begin{table}[H]
 \centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}}
-\hline
-Data name & Site name & Vegetation & Elevation (m) & Location & MAT (℃) & MAP (mm) & Dry period (month) & Canopy height (m) & Leaf thickness & Leaf disc thickness & Leaf punch diameter (cm) & Number of species for species means & Number of individuals for individuals means & Number of species for CV & Number of individuals for CV\\
-\hline
-Yunnan & Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35'E & 21 & 1532.0 & 6 & 35-45 & Measured & Measured & 0.6 & 60 & 366 & 60 & 366\\
-\hline
-Yunnan & Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 & 24°32'N, 101°01'E & 11.7 & 1931.0 & - & 25 & Measured & Measured & 0.6 & 47 & 282 & 47 & 282\\
-\hline
-Yunnan & Yuanjiang & Hot-dry savanna  (HDS) & 480 & 23°28'N, 102°10'E & 24.7 & 732.8 & 6 & 6-Apr & Measured & Measured & 0.6 & 34 & 204 & 33 & 203\\
-\hline
-Yakushima & Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 8.1 - 19.4 & 4477.0 & - & - & Measured & Not-measured & 1.0 & 193 & 607 & 5 & 26\\
-\hline
-\end{tabular}}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}}
+\toprule
+  & Bubeng & Ailao-shan & Yuanjiang & Yakushima\\
+\midrule
+\cellcolor{gray!6}{Site name} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yakushima}\\
+Vegetation & Tropical forest (TRF) & Subtropical evergreen wet forest (STF) & Hot-dry savanna  (HDS) & Warm-temperate forest\\
+\cellcolor{gray!6}{Elevation (m)} & \cellcolor{gray!6}{780} & \cellcolor{gray!6}{2500} & \cellcolor{gray!6}{480} & \cellcolor{gray!6}{14 - 1748}\\
+Location & 21°37'N, 101°35'E & 24°32'N, 101°01'E & 23°28'N, 102°10'E & 30°38'N, 130°62'E\\
+\cellcolor{gray!6}{MAT (℃)} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{11.7} & \cellcolor{gray!6}{24.7} & \cellcolor{gray!6}{8.1 - 19.4}\\
+\addlinespace
+MAP (mm) & 1532.0 & 1931.0 & 732.8 & 4477.0\\
+\cellcolor{gray!6}{Dry period (month)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-}\\
+Canopy height (m) & 35-45 & 25 & 4-6 & -\\
+\cellcolor{gray!6}{Leaf thickness} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured}\\
+Leaf disc thickness & Measured & Measured & Measured & Not-measured\\
+\addlinespace
+\cellcolor{gray!6}{Leaf punch diameter (cm)} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{1.0}\\
+Number of species for species means & 60 & 47 & 34 & 193\\
+\cellcolor{gray!6}{Number of individuals for individuals means} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{204} & \cellcolor{gray!6}{607}\\
+Number of species for CV & 60 & 47 & 33 & 5\\
+\cellcolor{gray!6}{Number of individuals for CV} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{203} & \cellcolor{gray!6}{26}\\
+\bottomrule
+\end{tabular}
 \end{table}
-\end{landscape}
 
-The site information and climate data in Yunnan, referred to Fei et al.
-(\protect\hyperlink{ref-Fei2018}{2018}), and Song et al.
-(\protect\hyperlink{ref-Song2017}{2017}). MAT and MAP of Yakushima were
-obtained from the Yakushima meteorological station and Eguchi
-(\protect\hyperlink{ref-Eguchi2006}{2006}).
+The site information and climate data in Yunnan, referred to Fei et al. (\protect\hyperlink{ref-Fei2018}{2018}), and Song et al. (\protect\hyperlink{ref-Song2017}{2017}).
+MAT and MAP of Yakushima were obtained from the Yakushima meteorological station and Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}).
 
@@
 
-Summary of a linear mixed model for log-transformed total dry mass of
-leaf discs for each tree individual. Species was used as a random
-intercept. The leaf punch size is described as an effect of `0.6 cm
-diameter' compared with `1.0 cm diameter'.
+Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
+Species was used as a random intercept.
+The leaf punch size is described as an effect of `0.6 cm diameter' compared with `1.0 cm diameter'.
 
-\begin{table}
+\begin{table}[H]
 \centering
-\begin{tabular}{r|r|r|r|l}
-\hline
-Estimate & SE & DF & t-value & *P* value\\
-\hline
--4.410 & 0.013 & 1030 & -333.00 & < 0.001\\
-\hline
+\begin{tabular}[t]{rrrrl}
+\toprule
+Estimate & SE & DF & t-value & \textit{P} value\\
+\midrule
+\cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
 0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
-\hline
--0.061 & 0.009 & 1030 & -6.94 & < 0.001\\
-\hline
+\cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
 0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
-\hline
--0.500 & 0.020 & 332 & -25.60 & < 0.001\\
-\hline
+\cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
+\bottomrule
 \end{tabular}
@@
 
-\includegraphics{../figs/S2.jpeg}
+\includegraphics[width=4.89583in,height=\textheight]{../figs/S2.jpeg}
 
@@
 
-Generalization for a relationship between ratios of disc-based and
-whole-leaf estimates of leaf mass per area (LMA), leaf tissue density
-(LD), and leaf thickness (LT). For the \emph{i} tree individual or
-species, the relationship between ratios of disc-based and whole-leaf
-estimates of LMA, LD, and LT is:
+Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
+For the \emph{i} tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:
 
@@
 
-where \emph{d} indicates disc-based estimates, \emph{w} indicates
-whole-leaf based estimates.
+where \emph{d} indicates disc-based estimates, \emph{w} indicates whole-leaf based estimates.
 
-Because thickness is measured on leaf lamina whether one uses a leaf
-disc or a whole-leaf, the expected ratio between thickness for a leaf
-disc and a whole-leaf should be 1. The above relationship, therefore,
-can be rewritten using lognormally distributed multiplicative error
-(\(\epsilon_i\)) on the arithmetic scale:
+Because thickness is measured on leaf lamina whether one uses a leaf disc or a whole-leaf, the expected ratio between thickness for a leaf disc and a whole-leaf should be 1.
+The above relationship, therefore, can be rewritten using lognormally distributed multiplicative error (\(\epsilon_i\)) on the arithmetic scale:
 
@@
 
-LMA requires two times measurements (mass and area) and LD requires
-three time measurements (mass, area and thickness), and thus variance in
-the ratio of whole-leaf LD and leaf disc LD should be greater than that
-of LMA.
+LMA requires two times measurements (mass and area) and LD requires three time measurements (mass, area and thickness), and thus variance in the ratio of whole-leaf LD and leaf disc LD should be greater than that of LMA.
 
-As we expected LD, showed the slightly smaller
-\emph{R\textsuperscript{2}} value than LMA (Figure below) in the Yunnan
-dataset. We have independent measurement for thickness for leaf discs
-and whole-leaves in the Yunnan dataset. If we use the same leaf
-thickness values for leaf discs and whole-leaves (i.e.,
-LTw\textsubscript{i}/LTd\textsubscript{i} =1), the scatter plots will be
-identical for LMA and LD. Consequently, we do not perform further
-analyses for LD, because differences between whole-leaf LD and leaf disc
-LD only depends on the ratio between whole-leaf LMA and leaf disc LMA
-and measurement errors of leaf thickness.
+As we expected LD, showed the slightly smaller \emph{R\textsuperscript{2}} value than LMA (Figure below) in the Yunnan dataset.
+We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
+If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LTw\textsubscript{i}/LTd\textsubscript{i} =1), the scatter plots will be identical for LMA and LD.
+Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.
 
@@
 
-Figure: Relationships between species mean leaf mass per area (LMA) and
-leaf tissue density (LD) determined by using whole leaves and leaf discs
-for the Yunnan dataset that has both leaf thickness for leaf discs and
-whole leaves. Dashed lines indicate 1:1 lines. Blue solid lines indicate
-standardized major axis regressions. The 95\% confidence intervals are
-presented as the shaded area. All the correlations are significant
-(\emph{P} \textless{} 0.001).
+Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
+Dashed lines indicate 1:1 lines.
+Blue solid lines indicate standardized major axis regressions.
+The 95\% confidence intervals are presented as the shaded area.
+All the correlations are significant (\emph{P} \textless{} 0.001).
 
@@
 
-Standardized regression coefficients modelig the effects of leaf tissue
-density, leaf area, leaf thickness, punch size, and their interactios
-(a) on the mean estimates of whole-leaf LMA, and (b) on the estimated
-variance of whole-leaf LMA. The leaf disc LMA was used for the baseline
-mean of the whole-leaf LMA. Thick and thin lines indicate 90\% and 95\%
-credible intervals, respectively. Circles show posterior means of
-coefficients. Circles filled with blue indicate significant effects and
-white indicate non-significance effects.
+Standardized regression coefficients modelig the effects of leaf tissue density,
+leaf area,
+leaf thickness,
+punch size, and
+their interactios
+(a) on the mean estimates of whole-leaf LMA, and
+(b) on the estimated variance of whole-leaf LMA.
+The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
+Thick and thin lines indicate 90\% and 95\% credible intervals, respectively.
+Circles show posterior means of coefficients.
+Circles filled with blue indicate significant effects and white indicate non-significance effects.
 
@@
 
-Relationships between species mean leaf mass per area (LMA) determined
-by using whole-leaves and leaf discs for species obtained with leaf
-punches of different diameters. Dashed lines indicate 1:1 lines. Blue
-solid lines indicate standardized major axis (SMA) regressions. The 95\%
-confidence intervals are resented as the shaded area. The correlation is
-significant (\emph{P} \textless{} 0.001).
+Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
+Dashed lines indicate 1:1 lines.
+Blue solid lines indicate standardized major axis (SMA) regressions.
+The 95\% confidence intervals are resented as the shaded area.
+The correlation is significant (\emph{P} \textless{} 0.001).
 
@@
 
-Relationships between whole-leaf LMA : disc leaf LMA and total dry mass
-for the leaf disc. The relationships was heteroscedastic (unequal
-variance, \emph{p} \textless{} 0.001; all the samples were analyzed
-together). Samples with small total dry mass tended to show greater
-variance.
+Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
+The relationships was heteroscedastic (unequal variance, \emph{p} \textless{} 0.001; all the samples were analyzed together).
+Samples with small total dry mass tended to show greater variance.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Eguchi2006}{}}%
-Eguchi, T. 2006. Climate. Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in
-Japanese)}.
+Eguchi, T. 2006. Climate. Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in Japanese)}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
-Fei, X., Q. Song, Y. Zhang, Y. Liu, L. Sha, G. Yu, L. Zhang, et al.
-2018. \href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon
-exchanges and their responses to temperature and precipitation in forest
-ecosystems in {Yunnan}, {Southwest China}}. \emph{Science of The Total
-Environment} 616--617: 824--840.
+Fei, X., Q.
+Song, Y.
+Zhang, Y.
+Liu, L.
+Sha, G.
+Yu, L.
+Zhang, et al.
+2018.
+\href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon exchanges and their responses to temperature and precipitation in forest ecosystems in {Yunnan}, {Southwest China}}.
+\emph{Science of The Total Environment} 616--617: 824--840.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
-Song, Q. H., Y. P. Zhang, L. Q. Sha, X. B. Deng, Y. Deng, C. S. Wu, Z.
-Y. Lu, et al. 2017. \href{https://doi.org/10.3832/ifor2223-010}{Canopy
-temperature variability in a tropical rainforest, subtropical evergreen
-forest, and savanna forest in {Southwest China}}. \emph{iForest -
-Biogeosciences and Forestry} 10: 611.
+Song, Q.
+H., Y.
+P.
+Zhang, L.
+Q.
+Sha, X.
+B.
+Deng, Y.
+Deng, C.
+S.
+Wu, Z.
+Y.
+Lu, et al.
+2017.
+\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature variability in a tropical rainforest, subtropical evergreen forest, and savanna forest in {Southwest China}}.
+\emph{iForest - Biogeosciences and Forestry} 10: 611.
 

### 2022-06-26 ms/SI.Rmd
fix fig centering

@@
 title: "Appendix S1: Supporting Tables and Figures."
-#title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
 geometry: margin=1in
@@
 fontsize: 12pt
-#font-famliy: "ebgaramond"
-mainfont: Arial
-sansfont: Arial
 header-includes:
+  - \usepackage{float}
   - \usepackage{booktabs}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-  - \usepackage{wrapfig}
-  - \usepackage{float}
   - \usepackage{colortbl}
-  - \usepackage{pdflscape}
-  - \usepackage{tabu}
-  - \usepackage[normalem]{ulem}
-  - \usepackage{makecell}
-  - \usepackage{xcolor}
-  - \usepackage{caption}
   - \usepackage{fancyhdr}
-  - \pagestyle{fancy}  # enable header
-  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
-  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1} # add header on right side
- # - \captionsetup[figure]{name=Figure S} #  - \usepackage{lineno}
-#  - \linenumbers
+  - \pagestyle{fancy}
+  - \usepackage[default]{sourcesanspro}
+  - \usepackage{sourcecodepro}
+  - \fancypagestyle{plain}{\pagestyle{fancy}}
+  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
 output:
@@
   kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
-  #kable(format = "simple") |>
-    # caption = "Site information.
-    #           MAT: mean annual temperature,
-    #           MAP: mean annual precipitation,
-    #           CV: coefficient of variation") |>
   kable_styling(latex_options = c("striped", "HOLD_position")) |>
-  column_spec(1:5, width = "3cm")# |>
-#  kableExtra::landscape()
+  column_spec(1:5, width = "3cm")
 ```
@@
 
-![](../figs/S2.jpeg){ width="470" style="display: block; margin: 0 auto" }
+::: {.center data-latex=""}
+![](../figs/S2.jpeg){ width=470 margin=auto }
+:::
 
@@
 
-![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto" }
+![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto; align: center" }
 

### 2022-07-27 ms/SI.tex
fix fig centering
update for copy edits
- fonts
- eq format in SI
- references in SI

@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-  \setmainfont[]{Arial}
-  \setsansfont[]{Arial}
 \fi
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{float}
+\usepackage{caption}
 \usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
 \usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-\usepackage{caption}
 \usepackage{fancyhdr}
 \pagestyle{fancy}
+\usepackage[default]{sourcesanspro}
+\usepackage{sourcecodepro}
 \fancypagestyle{plain}{\pagestyle{fancy}}
@@
 
+\begin{center}
 \includegraphics[width=4.89583in,height=\textheight]{../figs/S2.jpeg}
+
+\end{center}
 
@@
 
-Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
+Generalization for a relationship between ratios of disc-based and whole-leaf-based estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
 For the \emph{i} tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:
@@
 \[
-\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} \frac{LTw_i}{LTd_i}
+\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} \frac{\mathrm{LT_w}_i}{\mathrm{LT_d}_i}
 \]
@@
 \[
-\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim N(0, \sigma^2).
+\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim \mathcal{N}(0, \sigma^2).
 \]
@@
 
-As we expected LD, showed the slightly smaller \emph{R\textsuperscript{2}} value than LMA (Figure below) in the Yunnan dataset.
+As we expected LD, showed the slightly smaller \emph{R}\textsuperscript{2} value than LMA (Figure below) in the Yunnan dataset.
 We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
-If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LTw\textsubscript{i}/LTd\textsubscript{i} =1), the scatter plots will be identical for LMA and LD.
+If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LT\textsubscript{w\emph{i}}/LT\textsubscript{d\emph{i}} = 1), the scatter plots will be identical for LMA and LD.
 Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.
@@
 
-Standardized regression coefficients modelig the effects of leaf tissue density,
+Standardized regression coefficients modeling the effects of leaf tissue density,
 leaf area,
@@
 punch size, and
-their interactios
-(a) on the mean estimates of whole-leaf LMA, and
-(b) on the estimated variance of whole-leaf LMA.
+their interactions on
+(a) the mean estimates of whole-leaf-based leaf mass per area (LMA) and
+(b) the estimated variance of whole-leaf LMA.
 The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
@@
 
-Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
+Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
 Dashed lines indicate 1:1 lines.
@@
 
-Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
+Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
 The relationships was heteroscedastic (unequal variance, \emph{p} \textless{} 0.001; all the samples were analyzed together).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Eguchi2006}{}}%
-Eguchi, T. 2006. Climate. Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in Japanese)}.
+Eguchi, T. 2006. Climate. \emph{In} M. Ohsawa, H. Tagawa, and J. Yamagiwa {[}eds.{]}, Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in Japanese)}.
 
@@
 \href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon exchanges and their responses to temperature and precipitation in forest ecosystems in {Yunnan}, {Southwest China}}.
-\emph{Science of The Total Environment} 616--617: 824--840.
+\emph{Science of the Total Environment} 616--617: 824--840.
 

### 2022-07-27 R/ind_analysis.R

@@ -47,7 +47,7 @@ ratio_dm <- function(tree) {
       values = my_col[c(2, 4)],
       name = "Leaf punch diameter"
     ) +
-    xlab("Total dry mass of leaf disc (g)") +
+    xlab("Total dry mass of leaf discs (g)") +
     ylab("Whole-leaf LMA / leaf disc LMA") +
     theme_bw() +
     theme(
@@ -56,8 +56,8 @@ ratio_dm <- function(tree) {
       legend.spacing.y = unit(0.1, "cm"),
       legend.text.align = 0,
       legend.key.height = unit(0.3, "cm"),
-      legend.text = element_text(size = 7),
-      legend.title = element_text(size = 7)
+      legend.text = element_text(size = 9),
+      legend.title = element_text(size = 9)
     )
   ratio_mass
 }

### 2022-07-27 R/sp_analysis.R

@@ -22,8 +22,8 @@ sma_point_sep <- function(data) {
     mutate(size_gr = ifelse(location == "Yakushima", "1.0-cm", "0.6-cm")) |>
     ggplot(aes(x = lma_disc, y = lma_leaf, col = size_gr)) +
     geom_point(alpha = 0.8) +
-    scale_x_log10() +
-    scale_y_log10() +
+    scale_x_log10(breaks = c(30, 50, 100, 200)) +
+    scale_y_log10(breaks = c(30, 50, 100, 200, 300)) +
     geom_abline(slope = 1, intercept = 0, lty = 2) +
     geom_sma(se = TRUE, nboot = 2000) +
     scale_color_manual(

### 2022-07-27 _targets.R

@@ -540,14 +540,14 @@ list(
         "figs/ratio_dm.png",
         p,
         dpi = 300,
-        width = 3,
-        height = 3
+        width = 3.5,
+        height = 3.5
       )
       ggsave(
         "figs/ratio_dm.pdf",
         p,
-        width = 3,
-        height = 3
+        width = 3.5,
+        height = 3.5
       )
       paste0("figs/ratio_dm", c(".png", ".pdf"))
     },

### 2022-07-27 ms/SI.Rmd

@@
   - \usepackage{float}
+  - \usepackage{caption}
   - \usepackage{booktabs}
@@
     keep_tex: yes
-    # template: templates/eisvogel2.tex
+  bookdown::word_document2:
+    citation_package: default
+    toc: yes
+    number_sections: no
+    fig_caption: no
 ---
@@
 
-Generalization for a relationship between ratios of disc-based and whole-leaf estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
+Generalization for a relationship between ratios of disc-based and whole-leaf-based estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
 For the *i* tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:
@@
 $$
-\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} \frac{LTw_i}{LTd_i}
+\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} \frac{\mathrm{LT_w}_i}{\mathrm{LT_d}_i}
 $$
@@
 $$
-\frac{LDd_i}{LDw_i} = \frac{LMAd_i}{LMAw_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim N(0, \sigma^2).
+\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim \mathcal{N}(0, \sigma^2).
 $$
@@
 
-As we expected LD, showed the slightly smaller *R^2^* value than LMA (Figure below) in the Yunnan dataset.
+As we expected LD, showed the slightly smaller *R*^2^ value than LMA (Figure below) in the Yunnan dataset.
 We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
-If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LTw~i~/LTd~i~ =1), the scatter plots will be identical for LMA and LD.
+If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LT~w*i*~/LT~d*i*~ = 1), the scatter plots will be identical for LMA and LD.
 Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.
@@
 
-![](../figs/sma_sep.pdf){ width="400" style="display: block; margin: 0 auto" }
+![](../figs/sma_sep.pdf){ width=400 margin=auto }
 
@@
 
-Relationships between whole-leaf LMA : disc leaf LMA and total dry mass for the leaf disc.
+Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
 The relationships was heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together).
@@
 
-![](../figs/ratio_dm.pdf){ width="400" style="display: block; margin: 0 auto" }
+![](../figs/ratio_dm.pdf){ width=400 margin=auto }
 

### 2022-07-29 ms/SI.Rmd
update for copy-edit
- punch -> disc
- errors in table S2
- add csv for S1
- add doi

@@
 Species was used as a random intercept.
-The leaf punch size is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
+The small disc is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
 
@@
 ::: {.center data-latex=""}
-![](../figs/S2.jpeg){ width=470 margin=auto }
+![](../figs/s1.jpeg){ width=470 margin=auto }
 :::

### 2022-07-29 ms/SI.tex
update for copy-edit
- punch -> disc
- errors in table S2
- add csv for S1
- add doi

@@
 Species was used as a random intercept.
-The leaf punch size is described as an effect of `0.6 cm diameter' compared with `1.0 cm diameter'.
+The small disc is described as an effect of `0.6 cm diameter' compared with `1.0 cm diameter'.
 
@@
 \centering
-\begin{tabular}[t]{rrrrl}
+\begin{tabular}[t]{lrrrrl}
 \toprule
-Estimate & SE & DF & t-value & \textit{P} value\\
+Predictors & Estimate & SE & DF & t-value & \textit{P} value\\
 \midrule
-\cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
-0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
-\cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
-0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
-\cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
+\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
+log(Leaf tissue density) & 0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
+\cellcolor{gray!6}{log(Leaf area)} & \cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
+log(Leaf thickness) & 0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
+\cellcolor{gray!6}{Small disc} & \cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
 \bottomrule
@@
 \begin{center}
-\includegraphics[width=4.89583in,height=\textheight]{../figs/S2.jpeg}
+\includegraphics[width=4.89583in,height=\textheight]{../figs/s1.jpeg}
 

### 2022-07-29 R/site_info.R

@@ -32,3 +32,15 @@ update_site_info <- function(site_info_raw, yml) {
   # The return value must be a vector of paths to the files we write:
   paste("data/site_info.json")
 }
+
+#' @title Produce site csv for docx
+write_site_csv <- function(site_info) {
+  site <- fromJSON(site_info)
+  site2 <- t(site)
+  site2[1,] <- t(site)[2,]
+  site2[2,] <- t(site)[1,]
+  colnames(site2) <- site2[1,]
+  site2 <- site2[-1,]
+  write.csv(site2, here("data", "site_info.csv"))
+  paste(here("data", "site_info.csv"))
+}

### 2022-07-29 R/sp_analysis.R

@@ -28,11 +28,11 @@ sma_point_sep <- function(data) {
     geom_sma(se = TRUE, nboot = 2000) +
     scale_color_manual(
       values = my_col[c(2, 4)],
-      name = "Leaf punch diameter"
+      name = "Leaf disc diameter"
     ) +
     scale_fill_manual(
       values = my_col[c(2, 4)],
-      name = "Leaf punch diameter"
+      name = "Leaf disc diameter"
     ) +
     xlab(expression("Leaf disc LMA "(g~m^{-2}))) +
     ylab(expression("Whole-leaf LMA "(g~m^{-2}))) +

### 2022-07-29 R/stan.R

@@ -251,41 +251,41 @@ coef_pointrange <- function(data, ld = TRUE, add = FALSE) {
       "beta_2" = expression(Leaf~tissue~density~(beta[1])),
       "beta_3" = expression(Leaf~area~(beta[2])),
       "beta_4" = expression(Leaf~thickness~(beta[3])),
-      "beta_5" = expression(Small~punch~(beta[4])),
-      "beta_6" = expression(Leaf~tissue~density%*%small~punch~(beta[5])),
-      "beta_7" = expression(Leaf~area%*%small~punch~(beta[6])),
-      "beta_8" = expression(Leaf~thickness%*%small~punch~(beta[7]))
+      "beta_5" = expression(Small~disc~(beta[4])),
+      "beta_6" = expression(Leaf~tissue~density%*%small~disc~(beta[5])),
+      "beta_7" = expression(Leaf~area%*%small~disc~(beta[6])),
+      "beta_8" = expression(Leaf~thickness%*%small~disc~(beta[7]))
       )
 
  gamma_lab <- c(
       "gamma_2" = expression(Leaf~tissue~density~(gamma[1])),
       "gamma_3" = expression(Leaf~area~(gamma[2])),
       "gamma_4" = expression(Leaf~thickness~(gamma[3])),
-      "gamma_5" = expression(Small~punch~(gamma[4])),
-      "gamma_6" = expression(Leaf~tissue~density%*%small~punch~(gamma[5])),
-      "gamma_7" = expression(Leaf~area%*%small~punch~(gamma[6])),
-      "gamma_8" = expression(Leaf~thickness%*%small~punch~(gamma[7]))
+      "gamma_5" = expression(Small~disc~(gamma[4])),
+      "gamma_6" = expression(Leaf~tissue~density%*%small~disc~(gamma[5])),
+      "gamma_7" = expression(Leaf~area%*%small~disc~(gamma[6])),
+      "gamma_8" = expression(Leaf~thickness%*%small~disc~(gamma[7]))
       )
 
 
   if (add) {
     beta_lab[5:7] <- c(
-        "beta_6" = expression(paste("Leaf tissue density (small punch: ", beta[1]+beta[5], ")")),
-        "beta_7" = expression(paste("Leaf area (small punch: ", beta[2]+beta[6], ")")),
-        "beta_8" = expression(paste("Leaf thickness (small punch: ", beta[3]+beta[7], ")"))
[…]

### 2022-07-29 _targets.R

@@ -28,7 +28,8 @@ tar_option_set(packages = c(
   "loo",
   "jsonlite",
   "lmtest",
-  "modelr"
+  "modelr",
+  "here"
 ))
 
 # check if it's inside a container
@@ -64,6 +65,11 @@ list(
   tar_target(
     site_info_raw,
     "data-raw/site_info_raw.json",
+    format = "file"
+  ),
+  tar_target(
+    fig_s1,
+    "data-raw/s1.jpeg",
     format = "file"
   ),
   tar_target(
@@ -125,7 +131,11 @@ list(
     update_site_info(site_info_raw, yml),
     format = "file"
   ),
-
+  tar_target(
+    site_info_csv,
+    write_site_csv(site_info),
+    format = "file"
+  ),
 
   # analyses and figs ---------------------------------------------
   tar_target(

### 2022-08-09 ms/s3.Rmd
add pdf

--- 2022-07-29 ms/SI.Rmd
@@
 ---
-title: "Appendix S1: Supporting Tables and Figures."
+#title: "Appendix S1: Supporting Tables and Figures."
 geometry: margin=1in
@@
   - \fancypagestyle{plain}{\pagestyle{fancy}}
-  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
+  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S3}
 output:
-  html_document:
-    fig_caption: yes
-    theme: spacelab #readable #sandstone #spacelab #flatly
-    highlight: pygments #tango #kate
-    toc: TRUE
-    toc_depth: 2
-    number_sections: FALSE
-    toc_float:
-      collapsed: TRUE
-      smooth_scroll: TRUE
-      toc: true
   bookdown::pdf_document2:
@@
     keep_tex: yes
-  bookdown::word_document2:
-    citation_package: default
-    toc: yes
-    number_sections: no
-    fig_caption: no
 ---
 
-```{r caching, include=FALSE, eval=TRUE}
-library(knitr)
-library(tidyverse)
-library(methods)
-library(targets)
-library(here)
-library(kableExtra)
-basename <- "LMA_method"
-opts_chunk$set(fig.path = paste("figs/", sep = ""))
-opts_chunk$set(tidy = FALSE,
-               warning = FALSE,
-               message = FALSE,
-               comment = NA,
-               verbose = TRUE,
-               cache = FALSE,
-               echo = FALSE)
-# PDF-based figures
-opts_chunk$set(dev='pdf')
-
-# https://github.com/haozhu233/kableExtra/issues/47
-options(kableExtra.auto_format = FALSE)
-```
-
-\newpage
-
-# Table S1:
-
-Site information.
-MAT: mean annual temperature,
-MAP: mean annual precipitation,
-CV: coefficient of variation.
-
-```{r, echo=FALSE, caption = "hopge"}
-library(jsonlite)
-site <- fromJSON(here("data", "site_info.json"))
-site2 <- t(site)
-site2[1,] <- t(site)[2,]
-site2[2,] <- t(site)[1,]
-colnames(site2) <- site2[1,]
-site2 <- site2[-1,]
-site2 |>
-  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
-  kable_styling(latex_options = c("striped", "HOLD_position")) |>
-  column_spec(1:5, width = "3cm")
-```
-
-The site information and climate data in Yunnan, referred to @Fei2018, and @Song2017.
-MAT and MAP of Yakushima were obtained from the Yakushima meteorological station and @Eguchi2006.
-
-\newpage
-# Table S2:
-
-Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
-Species was used as a random intercept.
-The small disc is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
-
-```{r, eval=TRUE, echo=FALSE}
-dm_glmm <- read_csv(here("data", "dm_glmm.csv"))
-dm_glmm |>
-  rename(`\\textit{P} value` = `*P* value`) |>
-  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
-  kable_styling(latex_options = c("striped", "HOLD_position"))
-```
-
-\newpage
-
-# Figure S1:
-
-Detailed sampling protocol for whole-leaf and leaf disc LMA.
-
-::: {.center data-latex=""}
-![](../figs/s1.jpeg){ width=470 margin=auto }
-:::
-
-\newpage
-
-# Figure S2:
+# Appendix S3:
 
@@
 All the correlations are significant (*P* < 0.001).
-
-\newpage
-
-# Figure S3:
-
-Standardized regression coefficients modeling the effects of leaf tissue density,
-leaf area,
-leaf thickness,
-punch size, and
-their interactions on
-(a) the mean estimates of whole-leaf-based leaf mass per area (LMA) and
-(b) the estimated variance of whole-leaf LMA.
-The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
-Thick and thin lines indicate 90% and 95% credible intervals, respectively.
-Circles show posterior means of coefficients.
-Circles filled with blue indicate significant effects and white indicate non-significance effects.
-
-![](../figs/coef_sp_punch1_add.pdf)
-
-\newpage
-
-# Figure S4:
-
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis (SMA) regressions.
-The 95% confidence intervals are resented as the shaded area.
-The correlation is significant (*P* < 0.001).
-
-![](../figs/sma_sep.pdf){ width=400 margin=auto }
-
-\newpage
-
-# Figure S5:
-
-Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
-The relationships was heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together).
-Samples with small total dry mass tended to show greater variance.
-
-![](../figs/ratio_dm.pdf){ width=400 margin=auto }
-
-\newpage
-
-# LITERATURE CITED

### 2022-08-09 ms/s3.tex
add pdf

--- 2022-07-27 ms/SI.tex
@@
 \hypersetup{
-  pdftitle={Appendix S1: Supporting Tables and Figures.},
   hidelinks,
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{float}
@@
 \fancypagestyle{plain}{\pagestyle{fancy}}
-\fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
+\fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S3}
 \ifLuaTeX
@@
 
-\title{Appendix S1: Supporting Tables and Figures.}
 \author{}
@@
 \begin{document}
-\maketitle
 
@@
 }
-\newpage
-
-\hypertarget{table-s1}{%
-\section{Table S1:}\label{table-s1}}
-
-Site information.
-MAT: mean annual temperature,
-MAP: mean annual precipitation,
-CV: coefficient of variation.
-
-\begin{table}[H]
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}}
-\toprule
-  & Bubeng & Ailao-shan & Yuanjiang & Yakushima\\
-\midrule
-\cellcolor{gray!6}{Site name} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yakushima}\\
-Vegetation & Tropical forest (TRF) & Subtropical evergreen wet forest (STF) & Hot-dry savanna  (HDS) & Warm-temperate forest\\
-\cellcolor{gray!6}{Elevation (m)} & \cellcolor{gray!6}{780} & \cellcolor{gray!6}{2500} & \cellcolor{gray!6}{480} & \cellcolor{gray!6}{14 - 1748}\\
-Location & 21°37'N, 101°35'E & 24°32'N, 101°01'E & 23°28'N, 102°10'E & 30°38'N, 130°62'E\\
-\cellcolor{gray!6}{MAT (℃)} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{11.7} & \cellcolor{gray!6}{24.7} & \cellcolor{gray!6}{8.1 - 19.4}\\
-\addlinespace
-MAP (mm) & 1532.0 & 1931.0 & 732.8 & 4477.0\\
-\cellcolor{gray!6}{Dry period (month)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-}\\
-Canopy height (m) & 35-45 & 25 & 4-6 & -\\
-\cellcolor{gray!6}{Leaf thickness} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured}\\
-Leaf disc thickness & Measured & Measured & Measured & Not-measured\\
-\addlinespace
-\cellcolor{gray!6}{Leaf punch diameter (cm)} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{1.0}\\
-Number of species for species means & 60 & 47 & 34 & 193\\
-\cellcolor{gray!6}{Number of individuals for individuals means} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{204} & \cellcolor{gray!6}{607}\\
-Number of species for CV & 60 & 47 & 33 & 5\\
-\cellcolor{gray!6}{Number of individuals for CV} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{203} & \cellcolor{gray!6}{26}\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The site information and climate data in Yunnan, referred to Fei et al. (\protect\hyperlink{ref-Fei2018}{2018}), and Song et al. (\protect\hyperlink{ref-Song2017}{2017}).
-MAT and MAP of Yakushima were obtained from the Yakushima meteorological station and Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}).
-
-\newpage
-
-\hypertarget{table-s2}{%
-\section{Table S2:}\label{table-s2}}
-
-Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
-Species was used as a random intercept.
-The leaf punch size is described as an effect of `0.6 cm diameter' compared with `1.0 cm diameter'.
-
-\begin{table}[H]
-\centering
-\begin{tabular}[t]{rrrrl}
-\toprule
-Estimate & SE & DF & t-value & \textit{P} value\\
-\midrule
-\cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
-0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
-\cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
-0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
-\cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\newpage
-
-\hypertarget{figure-s1}{%
-\section{Figure S1:}\label{figure-s1}}
-
-Detailed sampling protocol for whole-leaf and leaf disc LMA.
-
-\begin{center}
-\includegraphics[width=4.89583in,height=\textheight]{../figs/S2.jpeg}
-
-\end{center}
-
-\newpage
-
-\hypertarget{figure-s2}{%
-\section{Figure S2:}\label{figure-s2}}
+\hypertarget{appendix-s3}{%
+\section{Appendix S3:}\label{appendix-s3}}
 
@@
 
-\newpage
-
-\hypertarget{figure-s3}{%
-\section{Figure S3:}\label{figure-s3}}
-
-Standardized regression coefficients modeling the effects of leaf tissue density,
-leaf area,
-leaf thickness,
-punch size, and
-their interactions on
-(a) the mean estimates of whole-leaf-based leaf mass per area (LMA) and
-(b) the estimated variance of whole-leaf LMA.
-The leaf disc LMA was used for the baseline mean of the whole-leaf LMA.
-Thick and thin lines indicate 90\% and 95\% credible intervals, respectively.
-Circles show posterior means of coefficients.
-Circles filled with blue indicate significant effects and white indicate non-significance effects.
-
-\includegraphics{../figs/coef_sp_punch1_add.pdf}
-
-\newpage
-
-\hypertarget{figure-s4}{%
-\section{Figure S4:}\label{figure-s4}}
-
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis (SMA) regressions.
-The 95\% confidence intervals are resented as the shaded area.
-The correlation is significant (\emph{P} \textless{} 0.001).
-
-\includegraphics[width=4.16667in,height=\textheight]{../figs/sma_sep.pdf}
-
-\newpage
-
-\hypertarget{figure-s5}{%
-\section{Figure S5:}\label{figure-s5}}
-
-Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
-The relationships was heteroscedastic (unequal variance, \emph{p} \textless{} 0.001; all the samples were analyzed together).
-Samples with small total dry mass tended to show greater variance.
-
-\includegraphics[width=4.16667in,height=\textheight]{../figs/ratio_dm.pdf}
-
-\newpage
-
-\hypertarget{literature-cited}{%
-\section*{LITERATURE CITED}\label{literature-cited}}
-\addcontentsline{toc}{section}{LITERATURE CITED}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Eguchi2006}{}}%
-Eguchi, T. 2006. Climate. \emph{In} M. Ohsawa, H. Tagawa, and J. Yamagiwa {[}eds.{]}, Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in Japanese)}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
-Fei, X., Q.
-Song, Y.
-Zhang, Y.
-Liu, L.
-Sha, G.
-Yu, L.
-Zhang, et al.
-2018.
-\href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon exchanges and their responses to temperature and precipitation in forest ecosystems in {Yunnan}, {Southwest China}}.
-\emph{Science of the Total Environment} 616--617: 824--840.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
-Song, Q.
-H., Y.
-P.
-Zhang, L.
-Q.
-Sha, X.
-B.
-Deng, Y.
-Deng, C.
-S.
-Wu, Z.
-Y.
-Lu, et al.
-2017.
-\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature variability in a tropical rainforest, subtropical evergreen forest, and savanna forest in {Southwest China}}.
-\emph{iForest - Biogeosciences and Forestry} 10: 611.
-
-\end{CSLReferences}
-
 \end{document}

### 2022-08-09 ms/s4.Rmd
add pdf

--- 2022-07-29 ms/SI.Rmd
@@
   - \fancypagestyle{plain}{\pagestyle{fancy}}
-  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
+  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S4}
 output:
-  html_document:
-    fig_caption: yes
-    theme: spacelab #readable #sandstone #spacelab #flatly
-    highlight: pygments #tango #kate
-    toc: TRUE
-    toc_depth: 2
-    number_sections: FALSE
-    toc_float:
-      collapsed: TRUE
-      smooth_scroll: TRUE
-      toc: true
   bookdown::pdf_document2:
     citation_package: default
-    toc: yes
+    toc: no
     number_sections: no
@@
     keep_tex: yes
-  bookdown::word_document2:
-    citation_package: default
-    toc: yes
-    number_sections: no
-    fig_caption: no
 ---
 
-```{r caching, include=FALSE, eval=TRUE}
-library(knitr)
-library(tidyverse)
-library(methods)
-library(targets)
-library(here)
-library(kableExtra)
-basename <- "LMA_method"
-opts_chunk$set(fig.path = paste("figs/", sep = ""))
-opts_chunk$set(tidy = FALSE,
-               warning = FALSE,
-               message = FALSE,
-               comment = NA,
-               verbose = TRUE,
-               cache = FALSE,
-               echo = FALSE)
-# PDF-based figures
-opts_chunk$set(dev='pdf')
-
-# https://github.com/haozhu233/kableExtra/issues/47
-options(kableExtra.auto_format = FALSE)
-```
-
-\newpage
-
-# Table S1:
-
-Site information.
-MAT: mean annual temperature,
-MAP: mean annual precipitation,
-CV: coefficient of variation.
-
-```{r, echo=FALSE, caption = "hopge"}
-library(jsonlite)
-site <- fromJSON(here("data", "site_info.json"))
-site2 <- t(site)
-site2[1,] <- t(site)[2,]
-site2[2,] <- t(site)[1,]
-colnames(site2) <- site2[1,]
-site2 <- site2[-1,]
-site2 |>
-  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
-  kable_styling(latex_options = c("striped", "HOLD_position")) |>
-  column_spec(1:5, width = "3cm")
-```
-
-The site information and climate data in Yunnan, referred to @Fei2018, and @Song2017.
-MAT and MAP of Yakushima were obtained from the Yakushima meteorological station and @Eguchi2006.
-
-\newpage
-# Table S2:
-
-Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
-Species was used as a random intercept.
-The small disc is described as an effect of '0.6 cm diameter' compared with '1.0 cm diameter'.
-
-```{r, eval=TRUE, echo=FALSE}
-dm_glmm <- read_csv(here("data", "dm_glmm.csv"))
-dm_glmm |>
-  rename(`\\textit{P} value` = `*P* value`) |>
-  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
-  kable_styling(latex_options = c("striped", "HOLD_position"))
-```
-
-\newpage
-
-# Figure S1:
-
-Detailed sampling protocol for whole-leaf and leaf disc LMA.
-
-::: {.center data-latex=""}
-![](../figs/s1.jpeg){ width=470 margin=auto }
-:::
-
-\newpage
-
-# Figure S2:
-
-Generalization for a relationship between ratios of disc-based and whole-leaf-based estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
-For the *i* tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:
-
-$$
-\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} \frac{\mathrm{LT_w}_i}{\mathrm{LT_d}_i}
-$$
-
-where *d* indicates disc-based estimates, *w* indicates whole-leaf based estimates.
-
-Because thickness is measured on leaf lamina whether one uses a leaf disc or a whole-leaf, the expected ratio between thickness for a leaf disc and a whole-leaf should be 1.
-The above relationship, therefore, can be rewritten using lognormally distributed multiplicative error ($\epsilon_i$) on the arithmetic scale:
-
-$$
-\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim \mathcal{N}(0, \sigma^2).
-$$
-
-LMA requires two times measurements (mass and area) and LD requires three time measurements (mass, area and thickness), and thus variance in the ratio of whole-leaf LD and leaf disc LD should be greater than that of LMA.
-
-As we expected LD, showed the slightly smaller *R*^2^ value than LMA (Figure below) in the Yunnan dataset.
-We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
-If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LT~w*i*~/LT~d*i*~ = 1), the scatter plots will be identical for LMA and LD.
-Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.
-
-![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto; align: center" }
-
-Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis regressions.
-The 95% confidence intervals are presented as the shaded area.
-All the correlations are significant (*P* < 0.001).
-
-\newpage
-
-# Figure S3:
+# Appendix S4:
 
@@
 ![](../figs/coef_sp_punch1_add.pdf)
-
-\newpage
-
-# Figure S4:
-
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis (SMA) regressions.
-The 95% confidence intervals are resented as the shaded area.
-The correlation is significant (*P* < 0.001).
-
-![](../figs/sma_sep.pdf){ width=400 margin=auto }
-
-\newpage
-
-# Figure S5:
-
-Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
-The relationships was heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together).
-Samples with small total dry mass tended to show greater variance.
-
-![](../figs/ratio_dm.pdf){ width=400 margin=auto }
-
-\newpage
-
-# LITERATURE CITED

### 2022-08-09 ms/s4.tex
add pdf

--- 2022-07-27 ms/SI.tex
@@
 \fancypagestyle{plain}{\pagestyle{fancy}}
-\fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
+\fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S4}
 \ifLuaTeX
@@
 \begin{document}
-\maketitle
 
-{
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
-\newpage
-
-\hypertarget{table-s1}{%
-\section{Table S1:}\label{table-s1}}
-
-Site information.
-MAT: mean annual temperature,
-MAP: mean annual precipitation,
-CV: coefficient of variation.
-
-\begin{table}[H]
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}}
-\toprule
-  & Bubeng & Ailao-shan & Yuanjiang & Yakushima\\
-\midrule
-\cellcolor{gray!6}{Site name} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yakushima}\\
-Vegetation & Tropical forest (TRF) & Subtropical evergreen wet forest (STF) & Hot-dry savanna  (HDS) & Warm-temperate forest\\
-\cellcolor{gray!6}{Elevation (m)} & \cellcolor{gray!6}{780} & \cellcolor{gray!6}{2500} & \cellcolor{gray!6}{480} & \cellcolor{gray!6}{14 - 1748}\\
-Location & 21°37'N, 101°35'E & 24°32'N, 101°01'E & 23°28'N, 102°10'E & 30°38'N, 130°62'E\\
-\cellcolor{gray!6}{MAT (℃)} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{11.7} & \cellcolor{gray!6}{24.7} & \cellcolor{gray!6}{8.1 - 19.4}\\
-\addlinespace
-MAP (mm) & 1532.0 & 1931.0 & 732.8 & 4477.0\\
-\cellcolor{gray!6}{Dry period (month)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-}\\
-Canopy height (m) & 35-45 & 25 & 4-6 & -\\
-\cellcolor{gray!6}{Leaf thickness} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured}\\
-Leaf disc thickness & Measured & Measured & Measured & Not-measured\\
-\addlinespace
-\cellcolor{gray!6}{Leaf punch diameter (cm)} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{1.0}\\
-Number of species for species means & 60 & 47 & 34 & 193\\
-\cellcolor{gray!6}{Number of individuals for individuals means} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{204} & \cellcolor{gray!6}{607}\\
-Number of species for CV & 60 & 47 & 33 & 5\\
-\cellcolor{gray!6}{Number of individuals for CV} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{203} & \cellcolor{gray!6}{26}\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-The site information and climate data in Yunnan, referred to Fei et al. (\protect\hyperlink{ref-Fei2018}{2018}), and Song et al. (\protect\hyperlink{ref-Song2017}{2017}).
-MAT and MAP of Yakushima were obtained from the Yakushima meteorological station and Eguchi (\protect\hyperlink{ref-Eguchi2006}{2006}).
-
-\newpage
-
-\hypertarget{table-s2}{%
-\section{Table S2:}\label{table-s2}}
-
-Summary of a linear mixed model for log-transformed total dry mass of leaf discs for each tree individual.
-Species was used as a random intercept.
-The leaf punch size is described as an effect of `0.6 cm diameter' compared with `1.0 cm diameter'.
-
-\begin{table}[H]
-\centering
-\begin{tabular}[t]{rrrrl}
-\toprule
-Estimate & SE & DF & t-value & \textit{P} value\\
-\midrule
-\cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
-0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
-\cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
-0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
-\cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\newpage
-
-\hypertarget{figure-s1}{%
-\section{Figure S1:}\label{figure-s1}}
-
-Detailed sampling protocol for whole-leaf and leaf disc LMA.
-
-\begin{center}
-\includegraphics[width=4.89583in,height=\textheight]{../figs/S2.jpeg}
-
-\end{center}
-
-\newpage
-
-\hypertarget{figure-s2}{%
-\section{Figure S2:}\label{figure-s2}}
-
-Generalization for a relationship between ratios of disc-based and whole-leaf-based estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
-For the \emph{i} tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:
-
-\[
-\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} \frac{\mathrm{LT_w}_i}{\mathrm{LT_d}_i}
-\]
-
-where \emph{d} indicates disc-based estimates, \emph{w} indicates whole-leaf based estimates.
-
-Because thickness is measured on leaf lamina whether one uses a leaf disc or a whole-leaf, the expected ratio between thickness for a leaf disc and a whole-leaf should be 1.
-The above relationship, therefore, can be rewritten using lognormally distributed multiplicative error (\(\epsilon_i\)) on the arithmetic scale:
-
-\[
-\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim \mathcal{N}(0, \sigma^2).
-\]
-
-LMA requires two times measurements (mass and area) and LD requires three time measurements (mass, area and thickness), and thus variance in the ratio of whole-leaf LD and leaf disc LD should be greater than that of LMA.
-
-As we expected LD, showed the slightly smaller \emph{R}\textsuperscript{2} value than LMA (Figure below) in the Yunnan dataset.
-We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
-If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LT\textsubscript{w\emph{i}}/LT\textsubscript{d\emph{i}} = 1), the scatter plots will be identical for LMA and LD.
-Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.
-
-\includegraphics[width=6.25in,height=\textheight]{../figs/lma_ld.pdf}
-
-Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis regressions.
-The 95\% confidence intervals are presented as the shaded area.
-All the correlations are significant (\emph{P} \textless{} 0.001).
-
-\newpage
-
-\hypertarget{figure-s3}{%
-\section{Figure S3:}\label{figure-s3}}
+\hypertarget{appendix-s4}{%
+\section{Appendix S4:}\label{appendix-s4}}
 
@@
 
-\newpage
-
-\hypertarget{figure-s4}{%
-\section{Figure S4:}\label{figure-s4}}
-
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis (SMA) regressions.
-The 95\% confidence intervals are resented as the shaded area.
-The correlation is significant (\emph{P} \textless{} 0.001).
-
-\includegraphics[width=4.16667in,height=\textheight]{../figs/sma_sep.pdf}
-
-\newpage
-
-\hypertarget{figure-s5}{%
-\section{Figure S5:}\label{figure-s5}}
-
-Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
-The relationships was heteroscedastic (unequal variance, \emph{p} \textless{} 0.001; all the samples were analyzed together).
-Samples with small total dry mass tended to show greater variance.
-
-\includegraphics[width=4.16667in,height=\textheight]{../figs/ratio_dm.pdf}
-
-\newpage
-
-\hypertarget{literature-cited}{%
-\section*{LITERATURE CITED}\label{literature-cited}}
-\addcontentsline{toc}{section}{LITERATURE CITED}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Eguchi2006}{}}%
-Eguchi, T. 2006. Climate. \emph{In} M. Ohsawa, H. Tagawa, and J. Yamagiwa {[}eds.{]}, Yakushima, 3--26. {Asakura Shoten}, {Tokyo (in Japanese)}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fei2018}{}}%
-Fei, X., Q.
-Song, Y.
-Zhang, Y.
-Liu, L.
-Sha, G.
-Yu, L.
-Zhang, et al.
-2018.
-\href{https://doi.org/10.1016/j.scitotenv.2017.10.239}{Carbon exchanges and their responses to temperature and precipitation in forest ecosystems in {Yunnan}, {Southwest China}}.
-\emph{Science of the Total Environment} 616--617: 824--840.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Song2017}{}}%
-Song, Q.
-H., Y.
-P.
-Zhang, L.
-Q.
-Sha, X.
-B.
-Deng, Y.
-Deng, C.
-S.
-Wu, Z.
-Y.
-Lu, et al.
-2017.
-\href{https://doi.org/10.3832/ifor2223-010}{Canopy temperature variability in a tropical rainforest, subtropical evergreen forest, and savanna forest in {Southwest China}}.
-\emph{iForest - Biogeosciences and Forestry} 10: 611.
-
-\end{CSLReferences}
-
 \end{document}

### 2022-08-09 ms/s5.Rmd
add pdf

--- 2022-08-09 ms/s3.Rmd
@@
   - \fancypagestyle{plain}{\pagestyle{fancy}}
-  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S3}
+  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S5}
 output:
@@
     citation_package: default
-    toc: yes
+    toc: no
     number_sections: no
@@
 
-# Appendix S3:
+# Appendix S5:
 
-Generalization for a relationship between ratios of disc-based and whole-leaf-based estimates of leaf mass per area (LMA), leaf tissue density (LD), and leaf thickness (LT).
-For the *i* tree individual or species, the relationship between ratios of disc-based and whole-leaf estimates of LMA, LD, and LT is:
+Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
+Dashed lines indicate 1:1 lines.
+Blue solid lines indicate standardized major axis (SMA) regressions.
+The 95% confidence intervals are resented as the shaded area.
+The correlation is significant (*P* < 0.001).
 
-$$
-\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} \frac{\mathrm{LT_w}_i}{\mathrm{LT_d}_i}
-$$
-
-where *d* indicates disc-based estimates, *w* indicates whole-leaf based estimates.
-
-Because thickness is measured on leaf lamina whether one uses a leaf disc or a whole-leaf, the expected ratio between thickness for a leaf disc and a whole-leaf should be 1.
-The above relationship, therefore, can be rewritten using lognormally distributed multiplicative error ($\epsilon_i$) on the arithmetic scale:
-
-$$
-\frac{\mathrm{LD_d}_i}{\mathrm{LD_w}_i} = \frac{\mathrm{LMA_d}_i}{\mathrm{LMA_w}_i} exp(\epsilon_i) \;\;\;\;\epsilon_i \sim \mathcal{N}(0, \sigma^2).
-$$
-
-LMA requires two times measurements (mass and area) and LD requires three time measurements (mass, area and thickness), and thus variance in the ratio of whole-leaf LD and leaf disc LD should be greater than that of LMA.
-
-As we expected LD, showed the slightly smaller *R*^2^ value than LMA (Figure below) in the Yunnan dataset.
-We have independent measurement for thickness for leaf discs and whole-leaves in the Yunnan dataset.
-If we use the same leaf thickness values for leaf discs and whole-leaves (i.e., LT~w*i*~/LT~d*i*~ = 1), the scatter plots will be identical for LMA and LD.
-Consequently, we do not perform further analyses for LD, because differences between whole-leaf LD and leaf disc LD only depends on the ratio between whole-leaf LMA and leaf disc LMA and measurement errors of leaf thickness.
-
-![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto; align: center" }
-
-Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis regressions.
-The 95% confidence intervals are presented as the shaded area.
-All the correlations are significant (*P* < 0.001).
+![](../figs/sma_sep.pdf){ width=400 margin=auto }

### 2022-08-09 ms/s6.Rmd
add pdf

--- 2022-08-09 ms/s5.Rmd
@@
   - \fancypagestyle{plain}{\pagestyle{fancy}}
-  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S5}
+  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S6}
 output:
@@
 
-# Appendix S5:
+# Appendix S6:
 
-Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs obtained with leaf punches of different diameters.
-Dashed lines indicate 1:1 lines.
-Blue solid lines indicate standardized major axis (SMA) regressions.
-The 95% confidence intervals are resented as the shaded area.
-The correlation is significant (*P* < 0.001).
+Relationships between the ratio of whole-leaf leaf mass per area (LMA) to disc leaf LMA and total dry mass for the leaf disc.
+The relationships was heteroscedastic (unequal variance, *p* < 0.001; all the samples were analyzed together).
+Samples with small total dry mass tended to show greater variance.
 
-![](../figs/sma_sep.pdf){ width=400 margin=auto }
+![](../figs/ratio_dm.pdf){ width=400 margin=auto }
